---
##HHHHHHHHHHHHHHHHHH BEGINNING OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##  
# TABLE OF CONTENTS (level 1) ----  
# @@ REFERENCES)                                                            #L247
# @@ DATA) example                                                          #L256
# @@ START) dev                                                             #L276
# @@ SOURCE)                                                                #L311
# @@ START) function                                                        #L353
# @@ MetaData) Read & Check                                                 #L402
# @@ DATA) Read & Check                                                     #L472
# @@ ANALYSIS) (Breif) byVar =                                              #L638
# @@ DATA) mutate()                                                         #L644
# @@ DATA) filter() -> New DS                                               #L675
# @@ DATA) select(matches(VarName.suffix.regex))                            #L708
# @@ ANALYSIS) byVar =                                                      #L722
##HHHHHHHHHHHHHHHHHHHH THE END OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##   
##HHHHHHHHHHHHHHHHHH BEGINNING OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##  
# TABLE OF CONTENTS (level 1) ----  
# @@ REFERENCES)                                                            # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L247
# @@ DATA) example                                                          # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L256
# @@ START) dev                                                             # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L276
# @@ SOURCE)                                                                # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L311
# @@ START) function                                                        # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L353
# @@ MetaData) Read & Check                                                 # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L402
# @@ DATA) Read & Check                                                     # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L472
# @@ ANALYSIS) (Breif) byVar =                                              # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L638
# @@ DATA) mutate()                                                         # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L644
# @@ DATA) filter() -> New DS                                               # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L675
# @@ DATA) select(matches(VarName.suffix.regex))                            # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L708
# @@ ANALYSIS) byVar =                                                      # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L722
##HHHHHHHHHHHHHHHHHHHH THE END OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##   
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  # - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd())  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_filename_ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$LastSourceEditorContext.path_filename_ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(getwd()|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
# env1$path$LastSourceEditorContext.path_filename_ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_filename_ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) Not using a relative path~!
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .filename.source.r = "f_DSN.Search.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.subpath_filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.filename.source.r))
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  
```
  
  
# __________|------  
# @@ REFERENCES) ----  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ DATA) example ----  
## dir(all.files = TRUE)  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

env1$path$path1 %>% dir(all.files = TRUE) %>% dput.deparse.cat0()
# c("-BACKUP", "-info", "-MAGB760M13700KF-3.Rhistory", "-MAGB760M13700KF-4.Rhistory", "-MAGB760M13700KF-5.Rhistory", "-Min-Hyung’s MacBook Pro.Rhistory", "-MKIM-15ZD980-HX70K.Rhistory", "-private-old", "-private - Shortcut.lnk", "-tmp", "-void", "%AppData%Microsoft_Windows_Start Menu_Programs_Startup.lnk", "%OneDriveConsumer%[][Rproject].lnk", "%OneDriveConsumer%[][Rproject]_github_tidystat.lnk", "%OneDriveConsumer%[][Rproject]_github_tidystat_git.lnk", "%OneDriveConsumer%[][Rproject]_github_tidystat_rstudio-prefs.lnk", "%OneDriveConsumer%[][Rproject]_github_tidystat_rstudio-prefs_templates.lnk", "%OneDriveConsumer%[][Rproject]_github_tidystat_rstudio-prefs_VScode-R.lnk", "%OneDriveConsumer%[][Rproject]_Rproject_Rmd.lnk", "%OneDriveConsumer%MHShell.lnk", "%OneDriveConsumer%MHShell_MHdocker.lnk", ".", "..", ".git", ".git.zip", ".gitattributes", ".gitattributes.xz", ".gitattributes@%userProfile% - Shortcut.lnk", ".gitconfig@%userProfile% - Shortcut.lnk", ".gitignore", ".gitignore - Shortcut.lnk", ".gitignore & .git_hooks_pre-commit & .Rprofile -update.r", ".gitignore.xz", ".gitignore@%UserProfile% - Shortcut.lnk", ".gitignore@github_tidystat - Shortcut.lnk", ".gitignore@Rproject_Rmd - Shortcut.lnk", ".lfs.gitattributes", ".non_lfs.gitattributes", ".Rhistory", ".Rprofile", ".Rprofile.debug.log.txt", ".Rprofile.dev.r", ".Rprofile.README.txt", ".Rprofile.xz", ".Rproj.user", ".vscode", "[[Stat]] CRAN R - Shortcut.lnk", "[][Rproject]-private - Shortcut.lnk", "[][Rproject] - Shortcut (2).lnk", "[][Rproject] - Shortcut (3).lnk", "[][Rproject] - Shortcut.lnk", "[][Rproject].code-workspace - Shortcut.lnk", "[Pending Files List] github_tidystat.r", "[Rproj] github_tidystat.Rproj.7z", "[Working Files List] github_tidystat.r", "_--date=local --name-statusgit log --since=.zip", "_.git_hooks_pre-commit - Shortcut.lnk", "_git_hooks_pre-commit - Shortcut.lnk", "01df_dirs_recursive.df_files-github_tidystat.Rmd", "D_Repositories-Shortcut.lnk", "D_Repositories_github_tidystat-BatchRun.ffs_batch.zip", "D_Repositories_github_tidystat-Shortcut.lnk", "D_Repositories_github_tidystat.Rproj", "D_Repositories_github_tidystat.Rproj-Shortcut.lnk", "D_Repositories_tidystat_Rmd_KoGES_AA10030-BatchRun.ffs_batch", "D_Repositories_tidystat_Rmd_KoGES_AA10030-BatchRun.ffs_gui", "D_Repositories_tidystat_Rmd_KoGES_AA10030-BatchRun.ffs_real", "D_Repositories_tidystat_Rmd_KoGES_AA10030-BatchRun.ffs_real@RealTimeSync.exe.lnk", "data", "default.symlink.R", "docker run -d -p --restart=always --name -e -v -private.ps1 - Shortcut (2).lnk", "docker run -d -p --restart=always --name -e -v -private.ps1 - Shortcut.lnk", "env1$env.internal.dev -archive.r.xz", "env1$env.internal.source.r", "f.updateTemplates.dev.Rmd", "f.updateTemplates.exe.r", "f_df.t.tribble_construct.dev.r", "f_df.t.tribble_construct.source.r", "f_df.tribble_construct.source.r.zip", "f_DSN.read.checkEntity.dev.r", "f_DSN.read.checkEntity.dev.Rmd", "f_DSN.Search.read.checkEntity.dev.r", "f_DSN.Search.read.checkEntity.source.r", "f_filename_ext.find_subpath.debugging.r", "f_filename_ext.find_subpath.dev.r", "f_filename_ext.find_subpath.source.r", "f_password.encrypt.dev-private.r - Shortcut.lnk", "f_password.environment.dev-private.r - Shortcut.lnk", "f_path.df_dirs_recursive.df_files.dev -tmp.zip", "f_path.df_dirs_recursive.df_files.dev.r", "f_path.df_dirs_recursive.df_files.source.r", "f_path.list_subpath.dev.r", "f_path.list_subpath.source.r", "git", "github_tidystat - Shortcut.lnk", "github_tidystat (rv433-github_tidystat-58723-restart).code-workspace", "github_tidystat.code-workspace", "github_tidystat.Rproj alias", "github_tidystat_rstudio-prefs_Rocker - Shortcut.lnk", "MH0000 Get-ChildItem -Path $folderPath -File Where-Object $documentExtensions -contains.bat-Shortcut.lnk", "MH0000 Get-ChildItem -Path $folderPath -File Where-Object $Rcode_Extensions -contains.bat-Shortcut.lnk", "MHdocker - Shortcut.lnk", "ProjectDocuments", "Rdev", "README.md", "Removing sensitive data from a repository.url", "Rocker_minimum - Shortcut.lnk", "Rproject_Rmd - Shortcut.lnk", "Rproject_Rmd_00env1-Rproject_Rmd.Rmd - Shortcut (2).lnk", "Rproject_Rmd_00env1-Rproject_Rmd.Rmd - Shortcut.lnk", "Rproject_Rmd_01df_dirs_recursive.df_files-Rproject_Rmd.Rmd - Shortcut (2).lnk", "Rproject_Rmd_01df_dirs_recursive.df_files-Rproject_Rmd.Rmd - Shortcut.lnk", "Rproject_Rmd_20DS.NR.lbl_pending.fct.Rmd - Shortcut (2).lnk", "Rproject_Rmd_20DS.NR.lbl_pending.fct.Rmd - Shortcut.lnk", "Rproject_Rmd_templates-00env1.minimum.Rmd - Shortcut (2).lnk", "Rproject_Rmd_templates-00env1.minimum.Rmd - Shortcut.lnk", "rstudio-prefs", "RStudio.Cloud-setup-void.r", "RStudio.Cloud set up-Min-Hyung’s MacBook Pro.zip", "RStudio.cloud.Rproj", "RStudioServer-setup-old2409.r", "RStudioServer-setup-old241022.r", "RStudioServer-setup.r", "RStudioServer-setup.r - Shortcut (2).lnk", "RStudioServer-setup.r - Shortcut.lnk", "sudo apt-get install openssh-client.sh", "sync.ffs_db", "templates-00env1.minimum.symlink.Rmd", "VScode R settings.txt - Shortcut.lnk", "VScode Replace r files (for pipe).R - Shortcut.lnk", "VScode Replace r files.R - Shortcut.lnk", "VScode Replace Rmd files) codes (for pipes).R - Shortcut.lnk", "VScode Replace Rmd files) codes.R - Shortcut.lnk", "VScode Replace Rmd files) MarkDown.MD - Shortcut.lnk", "VScode Replace Rmd files) opts_chunk.R - Shortcut.lnk", "VScodeSearchRegEx@MHpython - Shortcut (2).lnk", "VScodeSearchRegEx@MHpython - Shortcut (3).lnk", "VScodeSearchRegEx@MHpython - Shortcut.lnk")  
```
  
  
# __________|------  
# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```
  
  
## \% ADS_time2event |>  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ SOURCE) ----  
```{r RUN-ALL-CHUNKS-ABOVE, echo=FALSE, results="hide", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
```


```{r .subpath_filename.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
options(DEVMODE = TRUE);  # isTRUE(getOption("DEVMODE"))
# .subpath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") {.subpath = env1$path$LastSourceEditorContext.path_filename_ext |> dirname(); ".subpath" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
# if(.subpath!="") utils::browseURL(normalizePath(.subpath))
# .filename.source.r = "default.template" |> paste0(".source.r")
if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") {.sourcename_root = env1$path$LastSourceEditorContext.path_filename_ext |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),""); ".sourcename_root" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.subpath = .subpath
if(!exists(".sourcename_root") && exists(".filename.source.r")) .sourcename_root = .filename.source.r |> str_replace("\\.source\\.r$", "")
.filename.source.r = .sourcename_root |> paste0(".source.r")
env1$path$.sourcename_root = .sourcename_root
env1$path$.subpath_filename.dev.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.r")
env1$path$.subpath_filename.dev.Rmd = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.Rmd")
env1$path$.subpath_filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".source.r")
cat("# ",'.sourcename_root = "',.sourcename_root,'"  \n',
    "#### ",env1$path$.subpath_filename.dev.r, "----  \n",
    "#### ",env1$path$.subpath_filename.dev.Rmd, "----  \n",
    "#### ",env1$path$.subpath_filename.source.r, "----  \n",
    '# # source(paste0(env1$path$source_base,"/","',env1$path$.subpath_filename.source.r,'"))', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath_filename.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath_filename.source.r,'")', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.r,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.Rmd,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath_filename.source.r,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext));', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.subpath_filename.source.r) ) ----  
# env1$f$f_sourcePath.execute_if_not_sourced(.subpath_filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.filename.source.r))
```
  
  
# __________|------  
# @@ START) function ----  
## :: function_name = function() -dev -pending  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## ->> Not Yet included in env1$env.internal.source.r ----
## ->> Not Yet included in f_df.t.tribble_construct.source.r ----

##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## :: function_name = function() ====
## Rdev/00_base_program/001_base_file/function_name.dev.Rmd
.tmp$env1_subenv_name = "env.internal"
.tmp$objectname = "function_name" 
env1[[.tmp$env1_subenv_name]][[.tmp$objectname]] = function(input_object) {
    output_object = input_object
    invisible()
}
```
  
  
## https://chatgpt.com/c/6776a797-7698-800e-8a0d-c1c690118ca2
### \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
list_filtered_files <- function(
    dir = ".",
    recursive = TRUE,
    all.files = TRUE,
    full.names = TRUE,
    regex4search,
    regex4inclusion,
    regex4exclusion,
    ignore_case = FALSE
) {
  # 1. Gather all files from the specified directory
  all_files <- list.files(
    path       = dir,
    recursive  = recursive,
    all.files  = all.files,
    full.names = full.names
  )

  # 2. Filter by the primary search pattern (regex4search)
  search_files <- all_files[grepl(regex4search, all_files, ignore.case = ignore_case)]

  # 3. Further filter by the inclusion patterns (regex4inclusion)
  #    Using basename() if the patterns apply only to filenames
  included_files <- search_files[grepl(regex4inclusion, basename(search_files), ignore.case = ignore_case)]

  # 4. Exclude files that match any of the exclusion patterns (regex4exclusion)
  final_files <- included_files[!grepl(regex4exclusion, included_files, ignore.case = ignore_case)]

  # 5. Return the final set of files
  return(final_files)
}

result <- list_filtered_files(
  dir             = env1$path$path1, 
  recursive       = TRUE,
  all.files       = TRUE,
  full.names      = TRUE,
  regex4search    = ".*",
  regex4inclusion = "\\.(R|Rmd|Rprofile)$",
  regex4exclusion = "(-backup|\\.lnk$)",
  ignore_case     = TRUE
)

print(result)


```
  
  
## :: glob_to_regex = function() ----  
## :: styles_to_regex = function() ----  

```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# -----------------------------------------------
# Helper function:
#   Converts a single glob-like pattern (e.g. "**/*.[rR]")
#   into a simplified regex equivalent.
# -----------------------------------------------
glob_to_regex <- function(glob_pattern, anchor = FALSE) {
  # 1) Escape all regex-special characters except '*' (we handle '*' ourselves).
  #    Some minimal set of special chars to escape: . + ? ^ $ ( ) [ ] { } | \
  #    We'll do a gsub for those, ignoring '*' because we handle '*' below.
  safe <- gsub("([.+?^${}()|\\[\\]\\\\])", "\\\\\\1", glob_pattern)
  
  # 2) Handle "**/" (common in shells to mean "any number of directory levels").
  #    We'll convert it into a pattern that allows zero or more directory segments:
  #    "**/" -> "(?:.*/)*"
  # safe <- gsub("\\*\\*/", "(?:.*/)*", safe)
  safe <- gsub("\\*\\*/", "(?:[^/]*/)*", safe)  # only capture subdirectory segments
  
  # 3) Convert remaining "*" to something that doesn't cross directory boundaries
  #    in a strict glob sense. However, many people prefer ".*" for "any characters".
  #    Here, we mimic "any characters except /": "[^/]*"
  safe <- gsub("\\*", "[^/]*", safe)
  
  # 4) If desired, anchor at start and end:
  if (anchor) {
    safe <- paste0("^", safe, "$")
  }
  
  return(safe)
}

# -----------------------------------------------
# Main function:
#   Converts a single string of comma-separated patterns enclosed in braces, e.g.
#     "{**/*.[rR],**/*.[rR][mM][dD],default.R,.Rprofile}"
#   ...into one combined OR-based regex suitable for grepl().
# -----------------------------------------------
styles_to_regex <- function(pattern_string, anchor_each = FALSE) {
  # 1) Remove leading and trailing braces (if present)
  trimmed <- gsub("^\\{", "", pattern_string)
  trimmed <- gsub("\\}$", "", trimmed)
  
  # 2) Split by comma
  parts <- strsplit(trimmed, ",")[[1]]
  
  # 3) Trim whitespace around each pattern (if any)
  parts <- trimws(parts)
  # parts <- gsub("\\*\\*/", "(?:[^/]*/)*", parts)  # only capture subdirectory segments
  # parts <- gsub("\\*\\*/", "", parts)  # only capture subdirectory segments
  
  # 4) Convert each glob-like pattern to a regex
  regex_parts <- vapply(parts, FUN = function(p) {
    glob_to_regex(p, anchor = anchor_each)
  }, FUN.VALUE = character(1))
  
  # 5) Combine them with OR
  final_regex <- paste(regex_parts, collapse = "|")
  
  return(final_regex)
}

# --------------------
# Example usage
# --------------------

# Inclusion example
inclusion_str <- "{**/*.[rR],**/*.[rR][mM][dD],default.R,.Rprofile}"
inclusion_regex <- styles_to_regex(inclusion_str, anchor_each = FALSE)
inclusion_regex
# Possible output (simplified illustration):
# "(?:.*/)*[^/]*\\.[rR]|(?:.*/)*[^/]*\\.[rR][mM][dD]|default\\.R|\\.Rprofile"

# Exclusion example
exclusion_str <- "{.history,-backup,r4ds-master,*symlink*,*.lnk}"
exclusion_regex <- styles_to_regex(exclusion_str, anchor_each = FALSE)
exclusion_regex
# Possible output (simplified):
# "\\.history|-backup|r4ds-master|[^/]*symlink[^/]*|[^/]*\\.lnk"

# Now, for instance, you can use these combined regex strings in grepl():
#   grepl(inclusion_regex, "path/to/file.R")
#   grepl(exclusion_regex, "some-symlink-file")

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
  
```{r MetaData99-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
if(is.null(env1$path$LastSourceEditorContext.path_filename.MetaData.rds)) env1$path$LastSourceEditorContext.path_filename.MetaData.rds = env1$path$LastSourceEditorContext.path_filename_ext |> str_replace("\\.([[:alnum:]]+)$",".MetaData.rds")
if (Sys.getenv("PARENT_RENDERING") != "YES") {    
    if(exists("MetaData") && !is.null(unlist(MetaData))) {
        "MetaData |> str(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        # "MetaData$tblVarName |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        # "MetaData$DSNs |> str(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        "MetaData$VarNames |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        "MetaData$VarNames.select |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        "MetaData$ModelList |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        
        if(!exists(".MetaData0")) .MetaData0 = MetaData
        MetaData$DSNs = MetaData$DSNs %>% map(function(ls) {  if("str" %in% names(attributes(ls))) {  if(!is.environment(attributes(ls)$str)) {  attributes(ls)$str = as.environment(list(DSN.get.str.capture.output = attributes(ls)$str))  }  }; ls  })
        MetaData %>% list_modify(tblVarName = NULL) %>% str(vec.len = 100, list.len = 1000) %>% capture.output(file = env1$path$LastSourceEditorContext.path_filename.MetaData.rds %>% str_replace("\\.rds$", "-str.txt"))
        "all.equal(.MetaData0, MetaData)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        if(!identical(.MetaData0, MetaData)) {
            cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
            .path_file = ifelse(is.null(env1$path$LastSourceEditorContext.path_filename.MetaData.rds), NULL, paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename.MetaData.rds))
            # MetaData |> env1$f$f_object.get_objectname.size.write_rds.git_lfs_track_add_f(.path_file = .path_file, createBACKUP = TRUE, EXECUTE = TRUE)
            env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = "MetaData", .path_file = .path_file, createBACKUP = TRUE, EXECUTE = TRUE)
        }
    } else {warning('> !exists("MetaData") || is.null(unlist(MetaData))  \n')}
}
```


```{r writeRDS-EvalNoEchoNoMsgNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# __________|------  
## @ write_rds( get(.objectname), paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".rds",".xz"), compress = "xz", compression = 9L) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n") ----
if (Sys.getenv("PARENT_RENDERING") != "YES") {    
    .path4write = .path4write %>% str_replace(fixed(env1$path$path1), "") %>% str_replace("^/", "")  # [][Rproject] makes an error in git bash
    if(exists("MetaData") && !is.null(unlist(MetaData))) {
        # MetaData$DSNs |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
        cat("    ________________________________________________________________________    \n")
        for (DSN in names(MetaData$DSNs)) {    
            if(exists(DSN)) {
                assign(DSN, structure(get(DSN, envir = .GlobalEnv), MetaData = as.environment(MetaData)), envir = .GlobalEnv)
                if(is.null(attributes(.GlobalEnv[[DSN]])$DSN)) attributes(.GlobalEnv[[DSN]])$DSN = DSN
                if(attributes(.GlobalEnv[[DSN]])$DSN != DSN) attributes(.GlobalEnv[[DSN]])$DSN = DSN
                if (!is.null(attributes(attributes(.GlobalEnv[[DSN]])$DSN)$.path_file)) {
                    message( "attributes(attributes(",DSN,")$DSN)$.path_file == ",deparse(attributes(attributes(get(DSN))$DSN)$.path_file) )
                    env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = DSN, .path_file = attributes(attributes(.GlobalEnv[[DSN]])$DSN)$.path_file, createBACKUP = FALSE, EXECUTE = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE)
                } else {
                    env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = DSN, .path4write = .path4write, createBACKUP = FALSE, EXECUTE = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE)
                }
            } else {  message("!exists(",deparse(DSN),")")  }
            cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        }
    }
    # #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
    # .path_filename.xlsx = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".xlsx")  ;  openxlsx2::write_xlsx(get(.objectname), file = .path_filename.xlsx, as_table=TRUE, table_style="none", row_names=TRUE, col_widths="auto", first_active_row=2, first_active_col=2) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")  ;  if (Sys.info()["sysname"] == "Linux") browseURL(.path_filename.xlsx) else openxlsx2::xl_open(.path_filename.xlsx)
    # #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
    # .path_filename.UTF8BOM.csv = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".UTF8BOM.csv")
    # if (Sys.info()["sysname"] == "Windows") {
    #     readr::write_excel_csv(get(.objectname), file = .path_filename.UTF8BOM.csv) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
    #     openxlsx2::xl_open(.path_filename.xlsx)
    # } else {
    #     readr::write_excel_csv(get(.objectname), file = .path_filename.UTF8BOM.csv|>paste0(".xz")) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
    # }
    # #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
    # .path_filename.UTF8.csv.xz = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".UTF8.csv.xz")
    # readr::write_csv(get(.objectname), file = .path_filename.UTF8.csv.xz) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    
}
```
  
  
```{r createBACKUP, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_filename_ext.createBACKUP(BACKUP_from_path_filename_ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal.attach$f_filename_ext.createBACKUP(BACKUP_from_path_filename_ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$LastSourceEditorContext.path_filename.pdf = env1$path$LastSourceEditorContext.path_filename_ext |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$LastSourceEditorContext.path_filename.html = env1$path$LastSourceEditorContext.path_filename_ext |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (Sys.info()["sysname"] == "Windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$LastSourceEditorContext.path_filename_ext)),', output_format = "pdf_document")  \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$LastSourceEditorContext.path_filename_ext %>% {paste0(env1$path$path1,"/",.)} %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
        .path_file = env1$path$LastSourceEditorContext.path_filename.pdf %>% {paste0(env1$path$path1,"/",.)}
        env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE)
        env1$env.internal.attach$f_filename_ext.createBACKUP(BACKUP_from_path_filename_ext = .path_file, .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal.attach$f_file_PDF.sumatra(.path_file))
    }
}
# env1$path$LastSourceEditorContext.path_filename_ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_filename.pdf %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_filename_ext.createBACKUP(BACKUP_from_path_filename_ext = ',deparse(.path_file),', .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal.attach$f_file_PDF.sumatra(',deparse(.path_file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path_file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$LastSourceEditorContext.path_filename_ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_filename.html %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_filename_ext.createBACKUP(BACKUP_from_path_filename_ext = ',deparse(.path_file),', .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); cat('  env1$env.internal.attach$f_URL.browse_in_edge_app(',deparse(.path_file),')  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_filename.nb.html = env1$path$LastSourceEditorContext.path_filename_ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/",mustWork=NA),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$LastSourceEditorContext.path_filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_filename_ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
