---
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  # - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = options()$width; cat(options()$width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd())  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_FileNameExt ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# .tmp$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) not a relative path~!  
# env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) Not using a relative path~!
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$path4write = file.path(env1$path$path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$path4write = getwd()
.path4read  = env1$path$path4read
.path4write = env1$path$path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .FileName.source.r = "f_DSname.Search.read.checkEntity" |> paste0(".source.r"); .RelativeSubPath=r"()"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = list(.RelativeSubPath, .FileName.source.r) %>% {.[nzchar(.)]} %>% c(fsep = "/") %>% {do.call(file.path, .)})
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  
```
  
  

# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ START) function 
##@ Base R ----  
## :: f_object.get_objectname <- function(input_object) deparse(substitute(input_object)) ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_object.get_objectname <- function(input_object) {
  input_object.name <- deparse(substitute(input_object))
  return(input_object.name)
}

tmp <- 42
tmp_object <- 42
f_object.get_objectname(tmp_object)
tmp_object |> f_object.get_objectname()
tmp_object %>% f_object.get_objectname()
# > f_object.get_objectname(tmp_object)
# [1] "tmp_object"
# > tmp_object |> f_object.get_objectname()
# [1] "tmp_object"
# > tmp_object %>% f_object.get_objectname()
# [1] "."

```
  
  
## :: f_object.get_objectname <- function(input_object) as.character(match.call()$input_object) ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_object.get_objectname <- function(input_object) {
  input_object.name <- as.character(match.call()$input_object)
  return(input_object.name)
}

tmp_object <- 42
f_object.get_objectname(tmp_object)
tmp_object |> f_object.get_objectname()
tmp_object %>% f_object.get_objectname()
# > tmp_object <- 42
# > f_object.get_objectname(tmp_object)
# [1] "tmp_object"
# > tmp_object |> f_object.get_objectname()
# [1] "tmp_object"
# > tmp_object %>% f_object.get_objectname()
# [1] "."
```
  
  
## :: f_object.get_objectname <- function(input_object) { ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_object.get_objectname <- function(input_object) {
  call <- match.call()
  input_object.name <- deparse(substitute(input_object))
  
  # Handle magrittr pipe (%>%) case where input becomes "."
  if (input_object.name == ".") {
    input_object.name <- as.character(call$input_object)
  }
  
  return(input_object.name)
}

tmp_object <- 42
f_object.get_objectname(tmp_object)
tmp_object |> f_object.get_objectname()
tmp_object %>% f_object.get_objectname()
# > tmp_object <- 42
# > f_object.get_objectname(tmp_object)
# [1] "tmp_object"
# > tmp_object |> f_object.get_objectname()
# [1] "tmp_object"
# > tmp_object %>% f_object.get_objectname()
# [1] "."

```
  
  
## :: f_object.get_objectname <- function(input_object) { ----
```{r eval=FALSE, include=FALSE}
options(width=120)

# f_object.get_objectname <- function(input_object) {
#   expr <- substitute(input_object)
#   obj_name <- deparse(expr)
#   
#   if (obj_name == ".") {
#     # Retrieve the parent call
#     parent_call <- sys.call(-1)
#     
#     # Check if the parent call is a pipe operator
#     if (is.call(parent_call) && (parent_call[[1]] == `%>%` || parent_call[[1]] == `|>`)) {
#       # Extract the left-hand side of the pipe
#       lhs <- parent_call[[2]]
#       obj_name <- deparse(lhs)
#     } else {
#       obj_name <- "."
#     }
#   }
#   
#   return(obj_name)
# }
# tmp_object <- 42
# f_object.get_objectname(tmp_object)
# tmp_object |> f_object.get_objectname()
# tmp_object %>% f_object.get_objectname()
# # > f_object.get_objectname(tmp_object)
# # [1] "tmp_object"
# # > tmp_object |> f_object.get_objectname()
# # [1] "tmp_object"
# # > tmp_object %>% f_object.get_objectname()
# # Error in parent_call[[1]] == `%>%` : 
# #   comparison (==) is possible only for atomic and list types

```
  
  
## :: *** f_object.get_objectname <- function(input_object) { ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_object.get_objectname <- function(input_object) {
  # Capture the expression passed to the function
  obj_expr <- substitute(input_object)
  obj_name <- deparse(obj_expr)
  
  # Check if the function was called using the magrittr pipe (%>%)
  if (identical(obj_expr, quote(.))) {
    # Retrieve the parent call (the call to the pipe)
    parent_call <- sys.call(-1)
    
    # Extract the first argument from the parent call, which is the original object
    if (!is.null(parent_call)) {
      original_obj <- parent_call[[2]]
      obj_name <- deparse(original_obj)
    } else {
      obj_name <- "."
    }
  }
  
  return(obj_name)
}
tmp_object <- 42
f_object.get_objectname(tmp_object)
tmp_object |> f_object.get_objectname()
tmp_object %>% f_object.get_objectname()
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Define an outer function that uses f_object.get_objectname
process_data <- function(data, ...) {
  # Retrieve the name of the data object
  data_name <- f_object.get_objectname(data, ...)
  
  # Example operation: print a message with the data name
  message("Processing data object: ", data_name)
  
  # Return the data unchanged (for demonstration purposes)
  return(data)
}

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Create a test object
my_dataset <- data.frame(x = 1:5, y = letters[1:5])

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Test cases

# 1. Direct Function Call
process_data(my_dataset)
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 2. Using Base R Pipe (|>)
my_dataset |> process_data()
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 3. Using magrittr Pipe (%>%)
my_dataset %>% process_data()
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 4. Passing a Complex Expression Directly
process_data(my_dataset[my_dataset$x > 2, ])
# Expected Output: Warning and "Processing data object: complex_expression"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 5. Using Pipe with a Complex Expression
(my_dataset %>% subset(x > 2)) %>% process_data()
# Expected Output: Warning and "Processing data object: complex_expression"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 6. Using a Custom Pipe Operator
# `%custom%` <- function(lhs, rhs) rhs(lhs)
# my_dataset %custom% process_data(pipe_ops = c("%custom%", "%>%", "|>"))
# Expected Output: "Processing data object: my_dataset"
```
  
  
## :: *** f_object.get_objectname <- function(input_object) { ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_object.get_objectname <- function(input_object) {
  # Capture the expression passed to the function
  obj_expr <- substitute(input_object)
  obj_name <- deparse(obj_expr)
  
  # Check if the function was called using a pipe
  if (identical(obj_expr, quote(.))) {
    # Retrieve the parent call (the call to the pipe)
    parent_call <- sys.call(-1)
    if (!is.null(parent_call)) {
      obj_name <- deparse(parent_call[[2]])  # Left-hand side of the pipe
    }
  } else {
    # Check if we're inside another function
    parent_call <- sys.call(-1)
    if (!is.null(parent_call)) {
      # Retrieve the parent frame
      parent_frame <- parent.frame()
      if (exists(as.character(obj_expr), envir = parent_frame)) {
        obj_name <- as.character(obj_expr)
      }
    }
  }
  
  return(obj_name)
}

tmp_object <- 42
f_object.get_objectname(tmp_object)
tmp_object |> f_object.get_objectname()
tmp_object %>% f_object.get_objectname()
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Define an outer function that uses f_object.get_objectname
process_data <- function(data, ...) {
  # Retrieve the name of the data object
  data_name <- f_object.get_objectname(data, ...)
  
  # Example operation: print a message with the data name
  message("Processing data object: ", data_name)
  
  # Return the data unchanged (for demonstration purposes)
  return(data)
}

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Create a test object
my_dataset <- data.frame(x = 1:5, y = letters[1:5])

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Test cases

# 1. Direct Function Call
process_data(my_dataset)
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 2. Using Base R Pipe (|>)
my_dataset |> process_data()
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 3. Using magrittr Pipe (%>%)
my_dataset %>% process_data()
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 4. Passing a Complex Expression Directly
process_data(my_dataset[my_dataset$x > 2, ])
# Expected Output: Warning and "Processing data object: complex_expression"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 5. Using Pipe with a Complex Expression
(my_dataset %>% subset(x > 2)) %>% process_data()
# Expected Output: Warning and "Processing data object: complex_expression"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 6. Using a Custom Pipe Operator
# `%custom%` <- function(lhs, rhs) rhs(lhs)
# my_dataset %custom% process_data(pipe_ops = c("%custom%", "%>%", "|>"))
# Expected Output: "Processing data object: my_dataset"
```


###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
##@ library(rlang) ====
## :: f_object.get_objectname_rlang <- function(input_object) { ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# f_object.get_objectname_rlang <- function(input_object) {
#   # Capture the expression using rlang
#   expr <- enquo(input_object)
#   obj_name <- as_label(expr)
#   
#   # If the object is the placeholder '.', attempt to retrieve the original name
#   if (obj_name == ".") {
#     # Capture the parent frame's expression
#     expr <- rlang::get_expr(enquo(input_object), parent = 1)
#     obj_name <- as_label(expr)
#   }
#   
#   return(obj_name)
# }
# tmp_object <- 42
# f_object.get_objectname_rlang(tmp_object)
# tmp_object |> f_object.get_objectname_rlang()
# tmp_object %>% f_object.get_objectname_rlang()
# # > f_object.get_objectname_rlang(tmp_object)
# # [1] "tmp_object"
# # > tmp_object |> f_object.get_objectname_rlang()
# # [1] "tmp_object"
# # > tmp_object %>% f_object.get_objectname_rlang()
# # Error in rlang::get_expr(enquo(input_object), parent = 1) : 
# #   unused argument (parent = 1)
```
  
  
## :: f_object.get_objectname_rlang <- function(input_object) { ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_object.get_objectname_rlang <- function(input_object) {
  # Capture the expression using rlang
  expr <- enquo(input_object)
  obj_name <- as_label(expr)
  
  # If the object is the placeholder '.', attempt to retrieve the original name
  if (obj_name == ".") {
    # Retrieve the caller's call (the piping call)
    parent_call <- rlang::caller_call()
    
    if (!is.null(parent_call)) {
      # Extract the first argument from the parent call, which is the original object
      original_obj <- parent_call[[2]]
      obj_name <- as_label(original_obj)
    } else {
      obj_name <- "."
    }
  }
  
  return(obj_name)
}
tmp_object <- 42
f_object.get_objectname_rlang(tmp_object)
tmp_object |> f_object.get_objectname_rlang()
tmp_object %>% f_object.get_objectname_rlang()
# > tmp_object <- 42
# > f_object.get_objectname_rlang(tmp_object)
# [1] "tmp_object"
# > tmp_object |> f_object.get_objectname_rlang()
# [1] "tmp_object"
# > tmp_object %>% f_object.get_objectname_rlang()
# [1] "."

```
  
  
## :: f_object.get_objectname_rlang <- function(input_object) { ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_object.get_objectname_rlang <- function(input_object) {
  # Capture the expression using rlang
  expr <- enquo(input_object)
  obj_name <- as_label(expr)
  
  # If the object is the placeholder '.', attempt to retrieve the original name
  if (obj_name == ".") {
    # Retrieve the caller's call (the piping call)
    parent_call <- rlang::caller_call()
    
    if (!is.null(parent_call)) {
      # Extract the first argument from the parent call, which is the original object
      original_obj <- parent_call[[2]]
      obj_name <- as_label(original_obj)
    } else {
      obj_name <- "."
    }
  }
  
  return(obj_name)
}

tmp_object <- 42
f_object.get_objectname_rlang(tmp_object)
tmp_object |> f_object.get_objectname_rlang()
tmp_object %>% f_object.get_objectname_rlang()
# > f_object.get_objectname_rlang(tmp_object)
# [1] "tmp_object"
# > tmp_object |> f_object.get_objectname_rlang()
# [1] "tmp_object"
# > tmp_object %>% f_object.get_objectname_rlang()
# [1] "."

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
#@@ env1$env.internal.source.r ====
## :: f_objectname.size.write_rds.git_lfs_track_add_f ====  
Rdev/00_base_program/001_base_file/f_objectname.size.write_rds.git_lfs_track_add_f.dev.r
Rdev/00_base_program/001_base_file/f_objectname.size.write_rds.git_lfs_track_add_f.source-exported.r
https://chatgpt.com/c/670e6d4b-ea28-800e-87fe-85897601601a 
https://gemini.google.com/app/6d9de55c5c7085c6 

## :: f_object.get_objectname <- function(input_object, VERBOSE = isTRUE(getOption("verbose"))) { ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_object.get_objectname <- function(input_object, VERBOSE = isTRUE(getOption("verbose"))) {
    input_object.name <- deparse(substitute(input_object))
    if (input_object.name == ".") {
        warning('input_object.name == ',deparse(input_object.name),'   #@ sys.nframe() == ', sys.nframe(), "  \n", immediate. = TRUE)
        # if (VERBOSE) 1:sys.nframe() %>% set_names() %>% map(function(n) { deparse(substitute(input_object, parent.frame(n = n)))}) |> str(max.level = 2, give.attr = TRUE)
        if (VERBOSE) 0:sys.nframe() %>% set_names() %>% map(function(n) { ls(envir = sys.frame(which = n)) }) %>% dput()
        # message('-> Trying: ','deparse(substitute(input_object, parent.frame(n = 2)))')
        # input_object.name <- deparse(substitute(input_object, parent.frame(n = 2)))
        message('-> Trying: ','ls(envir = .GlobalEnv, all.names = TRUE) %>% set_names %>% map(get) %>% keep(function(object) identical(object, input_object)) %>% names')
        input_object.name = ls(envir = .GlobalEnv, all.names = TRUE) %>% set_names %>% map(get) %>% keep(function(object) identical(object, input_object)) %>% names
        if (length(input_object.name) > 1) {
            warning('length(input_object.name) > 1', "  \n", immediate. = TRUE)
            input_object.name %>% dput()
            if (any(!input_object.name %in% c(".", "input_object"))) {
                input_object.name = input_object.name[!input_object.name %in% c(".", "input_object")][1]
            } else {
                input_object.name = input_object.name[1]
            }
        }
        if (input_object.name %in% c(".", "input_object")) {
            warning('input_object.name == ',deparse(input_object.name),'   #@ sys.nframe() == ', sys.nframe())
            "Try using `|>` instead of` `%>%`, or provide a valid object." |> stop(call. = FALSE) |> tryCatch(error = function(e) message("stop: ", e)); return(invisible())
        }
    }
    return(input_object.name)
}
tmp <- 42
tmp_object <- 42
f_object.get_objectname(tmp_object)
tmp_object |> f_object.get_objectname()
tmp_object %>% f_object.get_objectname()
# > tmp <- 42
# > tmp_object <- 42
# > f_object.get_objectname(tmp_object)
# [1] "tmp_object"
# > tmp_object |> f_object.get_objectname()
# [1] "tmp_object"
# > tmp_object %>% f_object.get_objectname()
# Warning in f_object.get_objectname(.) :
#   input_object.name == "."   #@ sys.nframe() == 2  
# 
# -> Trying: ls(envir = .GlobalEnv, all.names = TRUE) %>% set_names %>% map(get) %>% keep(function(object) identical(object, input_object)) %>% names
# Warning in f_object.get_objectname(.) : length(input_object.name) > 1  
# 
# c("tmp", "tmp_object")
# [1] "tmp"
```
  
  
## :: *** f_object.get_objectname <- function(input_object) { ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Define the refined function
f_object.get_objectname <- function(input_object) {
  # Capture the expression passed to the function
  expr <- substitute(input_object)
  obj_name <- deparse(expr)
  
  # Check if the object is the magrittr placeholder '.'
  if (obj_name == ".") {
    # Retrieve the parent call (the call to the pipe)
    parent_call <- sys.call(-1)
    
    # Determine the type of pipe used
    pipe_operator <- as.character(parent_call[[1]])
    is_magrittr_pipe <- pipe_operator == "%>%"
    is_base_pipe <- pipe_operator == "|>"
    
    if (is_magrittr_pipe || is_base_pipe) {
      # Extract the left-hand side (lhs) of the pipe
      lhs <- parent_call[[2]]
      
      # Attempt to retrieve the name of the lhs
      lhs_name <- deparse(lhs)
      
      # Handle cases where lhs is more complex (e.g., expressions)
      # If lhs is a symbol, deparse returns its name; otherwise, it returns the expression as a string
      if (length(lhs_name) > 1) {
        # If the expression is complex, return a placeholder or handle accordingly
        lhs_name <- "complex_expression"
      }
      
      return(lhs_name)
    } else {
      # If not a recognized pipe operator, return the placeholder
      return(obj_name)
    }
  }
  
  return(obj_name)
}

# Create test objects
tmp_object <- 42
f_object.get_objectname(tmp_object)
tmp_object |> f_object.get_objectname()
tmp_object %>% f_object.get_objectname()
# > f_object.get_objectname(tmp_object)
# [1] "tmp_object"
# > tmp_object |> f_object.get_objectname()
# [1] "tmp_object"
# > tmp_object %>% f_object.get_objectname()
# [1] "tmp_object"
```
  
  
## :: *** f_object.get_objectname <- function(input_object) { ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_object.get_objectname <- function(input_object, 
                                    pipe_ops = c("%>%", "|>"), 
                                    placeholder = "complex_expression") {
  # Function to traverse the call stack and find the original object name
  find_original_object <- function(call_stack, pipe_ops, placeholder) {
    for (i in seq_along(call_stack)) {
      current_call <- call_stack[[i]]
      
      if (is.call(current_call)) {
        # Extract the pipe operator
        pipe_operator <- as.character(current_call[[1]])
        
        # Check if it's a recognized pipe
        if (pipe_operator %in% pipe_ops) {
          # Extract the lhs of the pipe
          lhs <- current_call[[2]]
          lhs_name <- deparse(lhs)
          
          # Check if lhs is a complex expression
          if (length(lhs_name) > 1 || grepl("[+*/()-]", lhs_name)) {
            return(placeholder)
          } else {
            return(lhs_name)
          }
        }
      }
    }
    # If no pipe operator is found in the call stack
    return(placeholder)
  }
  
  # Capture the expression passed to the function without evaluating it
  expr <- substitute(input_object)
  obj_name <- deparse(expr)
  
  # Define recognized placeholders indicating a pipe operation
  recognized_placeholders <- c(".", "input_object")
  
  # Check if the object is a recognized placeholder
  if (obj_name %in% recognized_placeholders) {
    # Retrieve the entire call stack
    call_stack <- sys.calls()
    
    # Remove the current function call from the stack
    call_stack <- call_stack[-length(call_stack)]
    
    # Attempt to find the original object name by traversing the call stack
    original_name <- find_original_object(call_stack, pipe_ops, placeholder)
    
    # If the original name is still the placeholder, issue a warning
    if (original_name == placeholder) {
      warning("Encountered a complex expression or could not determine the original object name.")
    }
    
    return(original_name)
  }
  
  # If not a placeholder, return the deparsed object name
  return(obj_name)
}
tmp_object <- 42
f_object.get_objectname(tmp_object)
tmp_object |> f_object.get_objectname()
tmp_object %>% f_object.get_objectname()
# > f_object.get_objectname(tmp_object)
# [1] "tmp_object"
# > tmp_object |> f_object.get_objectname()
# [1] "tmp_object"
# > tmp_object %>% f_object.get_objectname()
# [1] "tmp_object"
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
#@@ Usage Inside Another Function ====
## :: process_data <- function(data) { ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Define the enhanced get_objectname function
f_object.get_objectname <- function(input_object, 
                                    pipe_ops = c("%>%", "|>"), 
                                    placeholder = "complex_expression") {
  # Helper function to traverse the call stack and find the original object name
  find_original_object <- function(call_stack, pipe_ops, placeholder) {
    for (i in seq_along(call_stack)) {
      current_call <- call_stack[[i]]
      
      if (is.call(current_call)) {
        # Extract the pipe operator
        pipe_operator <- as.character(current_call[[1]])
        
        # Check if it's a recognized pipe
        if (pipe_operator %in% pipe_ops) {
          # Extract the left-hand side (lhs) of the pipe
          lhs <- current_call[[2]]
          
          # Attempt to retrieve the name of the lhs
          lhs_name <- deparse(lhs)
          
          # Check if lhs is a complex expression
          if (length(lhs_name) > 1 || grepl("[+*/()-]", lhs_name)) {
            # Assign a placeholder name for complex expressions
            lhs_name <- placeholder
          }
          
          return(lhs_name)
        }
      }
    }
    # If no pipe operator is found in the call stack
    return(placeholder)
  }
  
  # Capture the expression passed to the function without evaluating it
  expr <- substitute(input_object)
  obj_name <- deparse(expr)
  
  # Define recognized placeholders indicating a pipe operation
  recognized_placeholders <- c(".", "input_object")
  
  # Check if the object is a recognized placeholder
  if (obj_name %in% recognized_placeholders) {
    # Retrieve the entire call stack
    call_stack <- sys.calls()
    
    # Remove the current function call from the stack
    call_stack <- call_stack[-length(call_stack)]
    
    # Attempt to find the original object name by traversing the call stack
    original_name <- find_original_object(call_stack, pipe_ops, placeholder)
    
    # If the original name is still the placeholder, issue a warning
    if (original_name == placeholder) {
      warning("Encountered a complex expression or could not determine the original object name.")
    }
    
    return(original_name)
  }
  
  # If not a placeholder, return the deparsed object name
  return(obj_name)
}

##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Define an outer function that uses f_object.get_objectname
process_data <- function(data, ...) {
  # Retrieve the name of the data object
  data_name <- f_object.get_objectname(data, ...)
  
  # Example operation: print a message with the data name
  message("Processing data object: ", data_name)
  
  # Return the data unchanged (for demonstration purposes)
  return(data)
}

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Create a test object
my_dataset <- data.frame(x = 1:5, y = letters[1:5])

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Test cases

# 1. Direct Function Call
process_data(my_dataset)
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 2. Using Base R Pipe (|>)
my_dataset |> process_data()
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 3. Using magrittr Pipe (%>%)
my_dataset %>% process_data()
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 4. Passing a Complex Expression Directly
process_data(my_dataset[my_dataset$x > 2, ])
# Expected Output: Warning and "Processing data object: complex_expression"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 5. Using Pipe with a Complex Expression
(my_dataset %>% subset(x > 2)) %>% process_data()
# Expected Output: Warning and "Processing data object: complex_expression"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# # 6. Using a Custom Pipe Operator
# `%custom%` <- function(lhs, rhs) rhs(lhs)
# my_dataset %custom% process_data(pipe_ops = c("%custom%", "%>%", "|>"))
# Expected Output: "Processing data object: my_dataset"

```
  
  
## :: process_data <- function(data) { ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Define the enhanced get_objectname function
f_object.get_objectname <- function(input_object, 
                                    pipe_ops = c("%>%", "|>"), 
                                    placeholder = "complex_expression") {
  # Helper function to traverse the call stack and find the original object name
  find_original_object <- function(call_stack, pipe_ops, placeholder) {
    for (i in seq_along(call_stack)) {
      current_call <- call_stack[[i]]
      
      if (is.call(current_call)) {
        # Extract the pipe operator
        pipe_operator <- as.character(current_call[[1]])
        
        # Check if it's a recognized pipe
        if (pipe_operator %in% pipe_ops) {
          # Extract the left-hand side (lhs) of the pipe
          lhs <- current_call[[2]]
          
          # Attempt to retrieve the name of the lhs
          lhs_name <- deparse(lhs)
          
          # Check if lhs is a complex expression
          if (length(lhs_name) > 1 || grepl("[+*/()-]", lhs_name)) {
            # Assign a placeholder name for complex expressions
            lhs_name <- placeholder
          }
          
          return(lhs_name)
        }
      }
    }
    # If no pipe operator is found in the call stack
    return(placeholder)
  }
  
  # Capture the expression passed to the function without evaluating it
  expr <- substitute(input_object)
  obj_name <- deparse(expr)
  
  # Define recognized placeholders indicating a pipe operation
  recognized_placeholders <- c(".", "input_object")
  
  # Check if the object is a recognized placeholder
  if (obj_name %in% recognized_placeholders) {
    # Retrieve the entire call stack
    call_stack <- sys.calls()
    
    # Remove the current function call from the stack
    call_stack <- call_stack[-length(call_stack)]
    
    # Attempt to find the original object name by traversing the call stack
    original_name <- find_original_object(call_stack, pipe_ops, placeholder)
    
    # If the original name is still the placeholder, issue a warning
    if (original_name == placeholder) {
      warning("Encountered a complex expression or could not determine the original object name.")
    }
    
    return(original_name)
  }
  
  # If not a placeholder, return the deparsed object name
  return(obj_name)
}

##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Define an outer function that uses f_object.get_objectname
process_data <- function(data, ...) {
  # Retrieve the name of the data object
  data_name <- f_object.get_objectname(data, ...)
  
  # Example operation: print a message with the data name
  message("Processing data object: ", data_name)
  
  # Return the data unchanged (for demonstration purposes)
  return(data)
}

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Create a test object
my_dataset <- data.frame(x = 1:5, y = letters[1:5])

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Test cases

# 1. Direct Function Call
process_data(my_dataset)
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 2. Using Base R Pipe (|>)
my_dataset |> process_data()
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 3. Using magrittr Pipe (%>%)
my_dataset %>% process_data()
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 4. Passing a Complex Expression Directly
process_data(my_dataset[my_dataset$x > 2, ])
# Expected Output: Warning and "Processing data object: complex_expression"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 5. Using Pipe with a Complex Expression
(my_dataset %>% subset(x > 2)) %>% process_data()
# Expected Output: Warning and "Processing data object: complex_expression"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 6. Using a Custom Pipe Operator
# `%custom%` <- function(lhs, rhs) rhs(lhs)
# my_dataset %custom% process_data(pipe_ops = c("%custom%", "%>%", "|>"))
# Expected Output: "Processing data object: my_dataset"

```


## :: process_data <- function(data) { ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_object.get_objectname <- function(input_object, 
                                    pipe_ops = c("%>%", "|>"), 
                                    placeholder = "complex_expression") {
  # Helper function to traverse the call stack and find the original object name
  find_original_object <- function(call_stack, pipe_ops, placeholder) {
    for (i in seq_along(call_stack)) {
      current_call <- call_stack[[i]]
      
      if (is.call(current_call)) {
        # Extract the pipe operator
        pipe_operator <- as.character(current_call[[1]])
        
        # Check if it's a recognized pipe
        if (pipe_operator %in% pipe_ops) {
          # Extract the left-hand side (lhs) of the pipe
          lhs <- current_call[[2]]
          
          # Attempt to retrieve the name of the lhs
          lhs_name <- deparse(lhs)
          
          # Check if lhs is a complex expression
          if (length(lhs_name) > 1 || grepl("[+*/()-]", lhs_name)) {
            # Assign a placeholder name for complex expressions
            lhs_name <- placeholder
          }
          
          return(lhs_name)
        }
      }
    }
    # If no pipe operator is found in the call stack
    return(placeholder)
  }
  
  # Capture the expression passed to the function without evaluating it, from the parent frame
  expr <- substitute(input_object, parent.frame())
  obj_name <- deparse(expr)
  
  # Define recognized placeholders indicating a pipe operation
  recognized_placeholders <- c(".", "input_object")
  
  # Check if the object is a recognized placeholder
  if (obj_name %in% recognized_placeholders) {
    # Retrieve the entire call stack
    call_stack <- sys.calls()
    
    # Remove the current function call from the stack
    call_stack <- call_stack[-length(call_stack)]
    
    # Attempt to find the original object name by traversing the call stack
    original_name <- find_original_object(call_stack, pipe_ops, placeholder)
    
    # If the original name is still the placeholder, issue a warning
    if (original_name == placeholder) {
      warning("Encountered a complex expression or could not determine the original object name.")
    }
    
    return(original_name)
  }
  
  # If not a placeholder, return the deparsed object name
  return(obj_name)
}

##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Define an outer function that uses f_object.get_objectname
process_data <- function(data, ...) {
  # Retrieve the name of the data object
  data_name <- f_object.get_objectname(data, ...)
  
  # Example operation: print a message with the data name
  message("Processing data object: ", data_name)
  
  # Return the data unchanged (for demonstration purposes)
  return(data)
}

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Create a test object
my_dataset <- data.frame(x = 1:5, y = letters[1:5])

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# Test cases

# 1. Direct Function Call
process_data(my_dataset)
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 2. Using Base R Pipe (|>)
my_dataset |> process_data()
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 3. Using magrittr Pipe (%>%)
my_dataset %>% process_data()
# Expected Output: "Processing data object: my_dataset"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 4. Passing a Complex Expression Directly
process_data(my_dataset[my_dataset$x > 2, ])
# Expected Output: Warning and "Processing data object: complex_expression"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 5. Using Pipe with a Complex Expression
(my_dataset %>% subset(x > 2)) %>% process_data()
# Expected Output: Warning and "Processing data object: complex_expression"

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# 6. Using a Custom Pipe Operator
# `%custom%` <- function(lhs, rhs) rhs(lhs)
# my_dataset %custom% process_data(pipe_ops = c("%custom%", "%>%", "|>"))
# Expected Output: "Processing data object: my_dataset"
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_FileName.nb.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") {  try(  paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE),'"') |> shell(wait=FALSE)  )  }  # else { browseURL(env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE)) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileNameExt) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileName.nb.html) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
