---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$LastSourceEditorContext.path_filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .filename.source.r = "f_DataSetName.Search.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.subpath_filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.filename.source.r))
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  
# __________|------  
# @@ START) references ----  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# https://chatgpt.com/c/6738b1e9-6630-800e-b8d6-6f134f2f15ca
# __________|------  
# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```
  
  
## calculate_mutual_information = function() -dev ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)


# Simulated data
set.seed(123)
X <- sample(1:3, 100, replace = TRUE)  # Variable X
Y <- sample(1:3, 100, replace = TRUE)  # Variable Y

# Step 1: Create contingency table (joint frequencies)
joint_table <- table(X, Y)

# Step 2: Calculate joint probabilities P(X, Y)
joint_prob <- prop.table(joint_table)

# Step 3: Calculate marginal probabilities P(X) and P(Y)
px <- rowSums(joint_prob)  # Marginal probability for X
py <- colSums(joint_prob)  # Marginal probability for Y

# Step 4: Compute MI
mi <- 0
for (i in seq_along(px)) {
  for (j in seq_along(py)) {
    if (joint_prob[i, j] > 0) {  # Avoid log(0)
      mi <- mi + joint_prob[i, j] * log(joint_prob[i, j] / (px[i] * py[j]))
    }
  }
}

# Convert to base 2 (optional)
mi <- mi / log(2)

# Print MI
print(mi)

```
  
  
## calculate_mutual_information = function(X, Y, base = exp(1)) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
calculate_mutual_information <- function(X, Y, base = exp(1)) {
  # Ensure X and Y are factors for proper handling
  X <- as.factor(X)
  Y <- as.factor(Y)
  
  # Step 1: Create contingency table (joint frequencies)
  joint_table <- table(X, Y)
  
  # Step 2: Calculate joint probabilities P(X, Y)
  joint_prob <- prop.table(joint_table)
  
  # Step 3: Calculate marginal probabilities P(X) and P(Y)
  px <- rowSums(joint_prob)  # Marginal probability for X
  py <- colSums(joint_prob)  # Marginal probability for Y
  
  # Step 4: Compute Mutual Information
  mi <- 0
  for (i in seq_along(px)) {
    for (j in seq_along(py)) {
      if (joint_prob[i, j] > 0) {  # Avoid log(0)
        mi <- mi + joint_prob[i, j] * log(joint_prob[i, j] / (px[i] * py[j]), base)
      }
    }
  }
  
  # Return MI
  return(mi)
}
# Simulated data
set.seed(123)
X <- sample(1:3, 100, replace = TRUE)  # Variable X
Y <- sample(1:3, 100, replace = TRUE)  # Variable Y

# Calculate Mutual Information
mi_result <- calculate_mutual_information(X, Y, base = 2)  # Base 2 for bits
print(mi_result)

```
  
  
## calculate_mutual_information = function(X, Y, base = exp(1)) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
calculate_mutual_information <- function(X, Y, base = exp(1)) {
  # Ensure X and Y are factors
  X <- as.factor(X)
  Y <- as.factor(Y)
  
  # Create contingency table (joint frequencies)
  joint_table <- table(X, Y)
  
  # Calculate joint probabilities P(X, Y)
  joint_prob <- prop.table(joint_table)
  
  # Calculate marginal probabilities P(X) and P(Y)
  px <- rowSums(joint_prob)
  py <- colSums(joint_prob)
  
  # Compute Expected Joint Probabilities P(X) * P(Y)
  expected_joint_prob <- outer(px, py)
  
  # Flatten matrices to vectors
  joint_prob_vector <- as.vector(joint_prob)
  expected_prob_vector <- as.vector(expected_joint_prob)
  
  # Indices where joint probabilities are greater than zero
  non_zero_indices <- joint_prob_vector > 0
  
  # Compute Mutual Information using vectorized operations
  mi_elements <- joint_prob_vector[non_zero_indices] * 
                 log(joint_prob_vector[non_zero_indices] / expected_prob_vector[non_zero_indices], base)
  
  # Sum up the mutual information contributions
  mi <- sum(mi_elements)
  
  # Return Mutual Information
  return(mi)
}


cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")

# Simulated categorical data
set.seed(123)
X <- sample(LETTERS[1:3], 100, replace = TRUE)
Y <- sample(LETTERS[1:3], 100, replace = TRUE)


# Calculate Mutual Information
mi_result <- calculate_mutual_information(X, Y, base = 2)  # Base 2 for bits
print(paste("Mutual Information (bits):", mi_result))


cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
# Simulated continuous data
set.seed(123)
X_cont <- rnorm(100)
Y_cont <- X_cont^2 + rnorm(100, sd = 0.5)

# Discretize continuous variables into bins
bins <- 5  # Adjust the number of bins as needed
X_disc <- cut(X_cont, breaks = bins, labels = FALSE)
Y_disc <- cut(Y_cont, breaks = bins, labels = FALSE)

# Calculate Mutual Information
mi_continuous <- calculate_mutual_information(X_disc, Y_disc, base = 2)
print(paste("Mutual Information (bits):", mi_continuous))

cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
set.seed(123)
# Independent variables
X_indep <- sample(1:4, 1000, replace = TRUE)
Y_indep <- sample(1:4, 1000, replace = TRUE)

mi_indep <- calculate_mutual_information(X_indep, Y_indep)
print(paste("MI for independent variables:", mi_indep))

cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
# Perfect dependency
set.seed(123)
X_dep <- sample(1:4, 1000, replace = TRUE)
Y_dep <- X_dep  # Y is exactly the same as X

mi_dep <- calculate_mutual_information(X_dep, Y_dep)
print(paste("MI for perfectly dependent variables:", mi_dep))

```
  
  
## calculate_entropy <- function(X, base = exp(1)) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
calculate_entropy <- function(X, base = exp(1)) {
  # Ensure X is a factor for categorical data
  X <- as.factor(X)
  
  # Step 1: Calculate probabilities P(X)
  prob <- prop.table(table(X))
  
  # Step 2: Compute entropy
  entropy <- -sum(prob * log(prob, base), na.rm = TRUE)
  
  # Return the entropy
  return(entropy)
}
# Simulated data
set.seed(123)
X <- sample(LETTERS[1:3], 100, replace = TRUE)

# Calculate Entropy
entropy_result <- calculate_entropy(X, base = 2)  # Base 2 for bits
print(paste("Entropy (bits):", entropy_result))

cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
# Perfect dependency
set.seed(123)
X_dep <- sample(1:4, 1000, replace = TRUE)
Y_dep <- X_dep  # Y is exactly the same as X

# Calculate Entropy
entropy_result <- calculate_entropy(X_dep, base = 2)  # Base 2 for bits
print(paste("Entropy (bits):", entropy_result))
# Calculate Entropy
entropy_result <- calculate_entropy(X_dep, base = exp(1))  
print(paste("Entropy (e):", entropy_result))
mi_dep <- calculate_mutual_information(X_dep, Y_dep)
print(paste("MI for perfectly dependent variables:", mi_dep))

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ START) source ----  
```{r RUN-ALL-CHUNKS-ABOVE, echo=FALSE, results="hide", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
```


```{r .subpath_filename.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
options(DEVMODE = TRUE);  # isTRUE(getOption("DEVMODE"))
# .subpath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(!is.null(env1$path$LastSourceEditorContext.path_filename.ext)) if(env1$path$LastSourceEditorContext.path_filename.ext != "") {.subpath = env1$path$LastSourceEditorContext.path_filename.ext |> dirname(); ".subpath" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
# if(.subpath!="") utils::browseURL(normalizePath(.subpath))
# .filename.source.r = "default.template" |> paste0(".source.r")
if(!is.null(env1$path$LastSourceEditorContext.path_filename.ext)) if(env1$path$LastSourceEditorContext.path_filename.ext != "") {.sourcename_root = env1$path$LastSourceEditorContext.path_filename.ext |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),""); ".sourcename_root" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.subpath = .subpath
if(!exists(".sourcename_root") && exists(".filename.source.r")) .sourcename_root = .filename.source.r |> str_replace("\\.source\\.r$", "")
.filename.source.r = .sourcename_root |> paste0(".source.r")
env1$path$.sourcename_root = .sourcename_root
env1$path$.subpath_filename.dev.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.r")
env1$path$.subpath_filename.dev.Rmd = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.Rmd")
env1$path$.subpath_filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".source.r")
cat("# ",'.sourcename_root = "',.sourcename_root,'"  \n',
    "#### ",env1$path$.subpath_filename.dev.r, "----  \n",
    "#### ",env1$path$.subpath_filename.dev.Rmd, "----  \n",
    "#### ",env1$path$.subpath_filename.source.r, "----  \n",
    '# # source(paste0(env1$path$source_base,"/","',env1$path$.subpath_filename.source.r,'"))', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath_filename.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath_filename.source.r,'")', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.r,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename.ext)) if(env1$path$LastSourceEditorContext.path_filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename.ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.Rmd,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename.ext)) if(env1$path$LastSourceEditorContext.path_filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename.ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath_filename.source.r,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename.ext)) if(env1$path$LastSourceEditorContext.path_filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename.ext));', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.subpath_filename.source.r) ) ----  
# env1$f$f_sourcePath.execute_if_not_sourced(.subpath_filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.filename.source.r))
```
  
  
# __________|------  
# @@ START) function ----  
## \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ MetaData ----  
```{r MetaData0-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
## .GlobalEnv$MetaData = list() ====  
env1$path$LastSourceEditorContext.path_filename.MetaData.rds = env1$path$LastSourceEditorContext.path_filename.ext |> str_replace("\\.([[:alnum:]]+)$",".MetaData.rds")
if(file.exists(env1$path$LastSourceEditorContext.path_filename.MetaData.rds)) { 
    .MetaData0 = env1$path$LastSourceEditorContext.path_filename.MetaData.rds |> read_rds() 
}
if(!exists("MetaData", envir=.GlobalEnv)) { assign("MetaData", list(), envir=.GlobalEnv) }  
.parentname = "MetaData"
# for (.sublistname in c("tblVarName", "DataSetNames", "VarNames", "VarNames.select", "VarNames.filter", "VarNames.recode", "ModelList")) {
for (.sublistname in c("tblVarName", "DataSetNames", "VarNames", "VarNames.select", "ModelList")) {
    if(!.sublistname %in% names(.GlobalEnv[[.parentname]])) { .GlobalEnv[[.parentname]][[.sublistname]] = list() }
}

### @ MetaData\$ModelList  ====   
.parentname = "MetaData"; 
.sublistname = "ModelList"; 
for (.sub2listname in c("time2DM", "time2HTN", "time2DL", "time2MetS")) {
    if(!.sub2listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]])) { .GlobalEnv[[.parentname]][[.sublistname]] = list() }
}

### @ MetaData\$VarNames  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
for (.sub2listname in c("Event", "Mediator", "Exposure", "PMHx", "Tx", "FHx", "Exam", "Social", "Behavioral", "Unclassified", "Calculated")) {
    if(!.sub2listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]])) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]] = list() }
}

#### @ MetaData\$VarNames\$Event  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Event"; 
for (.sub3listname in c("DM", "HTN", "DL", "MetS")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

#### @ MetaData\$VarNames\$Mediator  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Mediator"; 
for (.sub3listname in c("BMI", "Waist")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

#### @ MetaData\$VarNames\$Exposure  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Exposure"; 
for (.sub3listname in c("Exercise", "Diet", "Alcohol", "Smoking")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

#### @ MetaData\$VarNames\$Demographic  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Social"; 
for (.sub3listname in c("Age", "Sex", "Income", "Education", "Residence", "Marriage")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

if(exists(".MetaData0", envir=.GlobalEnv)) { 
    ".MetaData0 |> str(max.level = 2, give.attr = TRUE)" %>% {cat("> ", ., "  \n", sep = "")}
    .MetaData0 |> str(max.level = 2, give.attr = TRUE)
} else { .MetaData0 = MetaData }
"MetaData |> str(max.level = 2, give.attr = TRUE)" %>% {cat("> ", ., "  \n", sep = "")}
MetaData |> str(max.level = 2, give.attr = TRUE)
```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
  
```{r MetaData99-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
if(exists("MetaData")) {
    "MetaData |> str(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    # "MetaData$tblVarName |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    # "MetaData$DataSetNames |> str(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "MetaData$VarNames |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "MetaData$VarNames.select |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "MetaData$ModelList |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    
    "all.equal(.MetaData0, MetaData)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    if(!identical(.MetaData0, MetaData)) {
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        .path_file = ifelse(is.null(env1$path$LastSourceEditorContext.path_filename.MetaData.rds), NULL, env1$path$LastSourceEditorContext.path_filename.MetaData.rds %>% {paste0(env1$path$path1,"/",.)})
        # MetaData |> env1$f$f_object.get_objectname.size.write_rds.git_lfs_track_add_f(.path_file = .path_file, createBackup = TRUE, Execute = TRUE)
        env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = "MetaData", .path_file = .path_file, createBackup = TRUE, Execute = TRUE)
    }
} else {warning("> !exists(MetaData)  \n")}
```


```{r writeRDS-EvalNoEchoNoMsgNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# __________|------  
## @ write_rds( get(.objectname), paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".rds",".xz"), compress = "xz", compression = 9L) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
.path4write = .path4write %>% str_replace(fixed(env1$path$path1), "") %>% str_replace("^/", "")  # [][Rproject] makes an error in git bash
if(exists("MetaData")) {
    # MetaData$DataSetNames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
    cat("    ________________________________________________________________________    \n")
if(exists("MetaData")) {
    # MetaData$DataSetNames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
    cat("    ________________________________________________________________________    \n")
    for (DataSetName in names(MetaData$DataSetNames)) {    
        if(exists(DataSetName)) {
            assign(DataSetName, structure(get(DataSetName, envir = .GlobalEnv), MetaData = as.environment(MetaData)), envir = .GlobalEnv)
            if(is.null(attributes(.GlobalEnv[[DataSetName]])$DataSetName)) attributes(.GlobalEnv[[DataSetName]])$DataSetName = DataSetName
            if(attributes(.GlobalEnv[[DataSetName]])$DataSetName != DataSetName) attributes(.GlobalEnv[[DataSetName]])$DataSetName = DataSetName
            if (!is.null(attributes(attributes(.GlobalEnv[[DataSetName]])$DataSetName)$.path_file)) {
                message( "attributes(attributes(",DataSetName,")$DataSetName)$.path_file == ",deparse(attributes(attributes(get(DataSetName))$DataSetName)$.path_file) )
                env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = DataSetName, .path_file = attributes(attributes(.GlobalEnv[[DataSetName]])$DataSetName)$.path_file, createBackup = FALSE, Execute = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE)
            } else {
                env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = DataSetName, .path4write = .path4write, createBackup = FALSE, Execute = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE)
            }
        } else {  message("!exists(",deparse(DataSetName),")")  }
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    }
}
}
# #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
# .path_filename.xlsx = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".xlsx")
# openxlsx2::write_xlsx(get(.objectname), file = .path_filename.xlsx, as_table = TRUE) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n") 
# if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(.path_filename.xlsx)
# #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
# .path_filename.UTF8BOM.csv = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".UTF8BOM.csv")
# if (Sys.info()["sysname"] == "Windows") {
#     readr::write_excel_csv(get(.objectname), file = .path_filename.UTF8BOM.csv) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
#     openxlsx2::xl_open(.path_filename.xlsx)
# } else {
#     readr::write_excel_csv(get(.objectname), file = .path_filename.UTF8BOM.csv|>paste0(".xz")) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
# }
# #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
# .path_filename.UTF8.csv.xz = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".UTF8.csv.xz")
# readr::write_csv(get(.objectname), file = .path_filename.UTF8.csv.xz) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
```
  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_filename.ext.createBackup(backup_from_path_filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal.attach$f_filename.ext.createBackup(backup_from_path_filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$LastSourceEditorContext.path_filename.pdf = env1$path$LastSourceEditorContext.path_filename.ext |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$LastSourceEditorContext.path_filename.html = env1$path$LastSourceEditorContext.path_filename.ext |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (Sys.info()["sysname"] == "Windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$LastSourceEditorContext.path_filename.ext)),', output_format = "pdf_document")  \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$LastSourceEditorContext.path_filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
        .path_file = env1$path$LastSourceEditorContext.path_filename.pdf %>% {paste0(env1$path$path1,"/",.)}
        env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, Execute = FALSE)
        env1$env.internal.attach$f_filename.ext.createBackup(backup_from_path_filename.ext = .path_file, .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal.attach$f_file_PDF.sumatra(.path_file))
    }
}
# env1$path$LastSourceEditorContext.path_filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_filename.pdf %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, Execute = FALSE); cat('  env1$env.internal.attach$f_filename.ext.createBackup(backup_from_path_filename.ext = ',deparse(.path_file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal.attach$f_file_PDF.sumatra(',deparse(.path_file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path_file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$LastSourceEditorContext.path_filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_filename.html %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, Execute = FALSE); cat('  env1$env.internal.attach$f_filename.ext.createBackup(backup_from_path_filename.ext = ',deparse(.path_file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); cat('  env1$env.internal.attach$f_URL.open_in_edge_app(',deparse(.path_file),')  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_filename.nb.html = env1$path$LastSourceEditorContext.path_filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$LastSourceEditorContext.path_filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_filename.ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename.ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
