---
title: "gitignore_escaped_select.UC.regex from gitignore.Rmd"
output: html_notebook
---

```{r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE}
# ##### Rstudio RMarkDown Shortcuts
# https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE  
# https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html  
# Insert R chunk	Ctrl+Alt+I	Command+Option+I\
# Preview HTML	Ctrl+Shift+K	Command+Shift+K\
# Run all chunks above	Ctrl+Alt+P	Command+Option+P\
# Run current chunk	Ctrl+Alt+C	Command+Option+C\
# Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter\
# Run next chunk	Ctrl+Alt+N	Command+Option+N\
# Run all chunks	Ctrl+Alt+R	Command+Option+R\
# Go to next chunk/title	Ctrl+PgDown	Command+PgDown\
# Go to previous chunk/title	Ctrl+PgUp	Command+PgUp\
# Show/hide document outline	Ctrl+Shift+O	Command+Shift+O\
# F7 spell-check your document.\
# Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).\
# \
# *** Caution: \% \$ \# \* \
```


```{r setup, eval=TRUE, include=FALSE}
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "\n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
```

```{r}
# gitignore_escaped_select.UC.regex from gitignore.Rmd
# f_vec.extract_non_alphanumeric_list.dev.r

library(tidyverse)
f_vec.extract_non_alphanumeric_list <- function(input_vec) {
  f_str.extract_non_alphanumeric_vec <- function(input_string) {
    positions <- gregexpr("[^[:alnum:]]", input_string)  # Match any non-alphanumeric character
    non_alnum_chars <- regmatches(input_string, positions)
    unlist(non_alnum_chars)  # Unlist to get a vector of non-alphanumeric characters
  }
  
  # Use map to apply f_str.extract_non_alphanumeric_vec to each element and maintain list structure
  result_list <- map(input_vec, f_str.extract_non_alphanumeric_vec)
  
  # Set the names of the list elements to match the input vector
  names(result_list) <- input_vec
  
  result_list
}

# # Example usage of the function
# input_vec <- c("Hello, World!", "R4 & Python?", "123% Ready!", "12345")
# result <- f_vec.extract_non_alphanumeric_list(input_vec)
# result |> dput()
# list(`Hello, World!` = c(",", " ", "!"), `R4 & Python?` = c(" ", "&", " ", "?"), `123% Ready!` = c("%", " ", "!"), `12345` = character(0))
```



```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

# @ gitignore = read_lines(".gitignore") =====
# file.edit(".gitignore")
gitignore = read_lines(".gitignore", skip_empty_rows = T)
# gitignore = gitignore %>% c(".*")
gitignore |> dput()
c(".Rproj.user", ".Rhistory", ".RData", ".Ruserdata", "*.zip", 
"*.7z", "*.r.gz", "*.r.xz", "*.rmd.gz", "*.rmd.xz", "*.Rproj", 
".gitignore", ".git", ".github", "MH)*.r", "*.lnk", "*alias", 
"*.ppt", "*.pptx", "*.xls", "*.xlsx", "*.doc", "*.docx", "*- void*.*", 
"*-void*.*", "*- info.*", "*-info.*", "*-dev*.*", "*debug*.*", 
"-tmp", "*- tmp*.*", "*-tmp*.*", "*- old.*", "*-old.*", "*-log*.*", 
"*.rtf")
```



```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
gitignore %>% f_vec.extract_non_alphanumeric_list |> unlist() |> unique() |> dput()
c(".", "*", ")", "-", " ")
```



```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

# @ gitignore_escaped =====
gitignore_escaped = gitignore[gitignore != ""] unique(_replace_all("\\.", "\\\\.") %>% # Caution: dot should be handled before asterisk~!
    str_replace_all("\\*", "\\.\\*") unique(_replace_all("\\)", "\\\\)") unique(_replace_all("\\-", "\\\\-") %>% 
    # str_replace_all("\\ ", "\\\\ ") %>% # spaces  are generally treated as literal spaces in regular expressions 
    unique 
# gitignore_escaped = paste0("(^", gitignore_escaped, "$)")
gitignore_escaped |> dput()
c("\\.Rproj\\.user", "\\.Rhistory", "\\.RData", "\\.Ruserdata", 
".*\\.zip", ".*\\.7z", ".*\\.r\\.gz", ".*\\.r\\.xz", ".*\\.rmd\\.gz", 
".*\\.rmd\\.xz", ".*\\.Rproj", "\\.gitignore", "\\.git", "\\.github", 
"MH\\).*\\.r", ".*\\.lnk", ".*alias", ".*\\.ppt", ".*\\.pptx", 
".*\\.xls", ".*\\.xlsx", ".*\\.doc", ".*\\.docx", ".*\\- void.*\\..*", 
".*\\-void.*\\..*", ".*\\- info\\..*", ".*\\-info\\..*", ".*\\-dev.*\\..*", 
".*debug.*\\..*", "\\-tmp", ".*\\- tmp.*\\..*", ".*\\-tmp.*\\..*", 
".*\\- old\\..*", ".*\\-old\\..*", ".*\\-log.*\\..*", ".*\\.rtf"
)
```



```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

# @ gitignore_escaped_select =====
gitignore_escaped |> str_which("doc|xls|ppt")
gitignore_escaped_select = gitignore_escaped %>% {.[-str_which(., "doc|xls|ppt")]}
gitignore_escaped_select |> dput() #----
c("\\.Rproj\\.user", "\\.Rhistory", "\\.RData", "\\.Ruserdata", 
".*\\.zip", ".*\\.7z", ".*\\.r\\.gz", ".*\\.r\\.xz", ".*\\.rmd\\.gz", 
".*\\.rmd\\.xz", ".*\\.Rproj", "\\.gitignore", "\\.git", "\\.github", 
"MH\\).*\\.r", ".*\\.lnk", ".*alias", ".*\\- void.*\\..*", ".*\\-void.*\\..*", 
".*\\- info\\..*", ".*\\-info\\..*", ".*\\-dev.*\\..*", ".*debug.*\\..*", 
"\\-tmp", ".*\\- tmp.*\\..*", ".*\\-tmp.*\\..*", ".*\\- old\\..*", 
".*\\-old\\..*", ".*\\-log.*\\..*", ".*\\.rtf")
```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# for (i_regex in unique(gitignore_escaped_select)) {
#     df <- df_dir1 |> filter(!str_detect(path.basename, i_regex))
# }
```



```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

# @ gitignore_escaped_select.UC =====
gitignore_escaped_select.UC = gitignore_escaped_select %>% toupper |> unique()
gitignore_escaped_select.UC |> dput() #----
c("\\.RPROJ\\.USER", "\\.RHISTORY", "\\.RDATA", "\\.RUSERDATA", 
".*\\.ZIP", ".*\\.7Z", ".*\\.R\\.GZ", ".*\\.R\\.XZ", ".*\\.RMD\\.GZ", 
".*\\.RMD\\.XZ", ".*\\.RPROJ", "\\.GITIGNORE", "\\.GIT", "\\.GITHUB", 
"MH\\).*\\.R", ".*\\.LNK", ".*ALIAS", ".*\\- VOID.*\\..*", ".*\\-VOID.*\\..*", 
".*\\- INFO\\..*", ".*\\-INFO\\..*", ".*\\-DEV.*\\..*", ".*DEBUG.*\\..*", 
"\\-TMP", ".*\\- TMP.*\\..*", ".*\\-TMP.*\\..*", ".*\\- OLD\\..*", 
".*\\-OLD\\..*", ".*\\-LOG.*\\..*", ".*\\.RTF")
```



```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
gitignore_escaped_select.UC.regex = gitignore_escaped_select.UC %>% 
    {paste0("(", ., ")")} %>% 
    paste(collapse = "|") %>% {paste0("^", ., "$")} |> dput() #----
"^(\\.RPROJ\\.USER)|(\\.RHISTORY)|(\\.RDATA)|(\\.RUSERDATA)|(.*\\.ZIP)|(.*\\.7Z)|(.*\\.R\\.GZ)|(.*\\.R\\.XZ)|(.*\\.RMD\\.GZ)|(.*\\.RMD\\.XZ)|(.*\\.RPROJ)|(\\.GITIGNORE)|(\\.GIT)|(\\.GITHUB)|(MH\\).*\\.R)|(.*\\.LNK)|(.*ALIAS)|(.*\\- VOID.*\\..*)|(.*\\-VOID.*\\..*)|(.*\\- INFO\\..*)|(.*\\-INFO\\..*)|(.*\\-DEV.*\\..*)|(.*DEBUG.*\\..*)|(\\-TMP)|(.*\\- TMP.*\\..*)|(.*\\-TMP.*\\..*)|(.*\\- OLD\\..*)|(.*\\-OLD\\..*)|(.*\\-LOG.*\\..*)|(.*\\.RTF)$"
```



```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

# @ end ----


```



```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

# @ end ----


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
