---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
if(.Platform$OS.type == "windows") Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=TRUE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
env1$info$options.width = options()$width; cat(options()$width, "  \n", sep="")
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
## \$ env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

#@ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
cat("> .tmp |> str(max.level = 1)", "  \n", sep="") 
.tmp |> str(max.level = 1)
cat("> env1 |> as.list() |> str(max.level = 2, give.attr = FALSE)", "  \n", sep="") 
env1 |> as.list() |> str(max.level = 2, give.attr = FALSE)
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
# .sourcename = "f_DataSetName.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  
```{r dfDIRsRecursive-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# *** Results hidden in 00env1 - see 01df_dirs_recursive.df_files ***
# #### env1\$env.internal\$f_path.df_dirs_recursive.df_files() ----  
# .sourcename = "f_path.df_dirs_recursive.df_files" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# env1$path$df_dirs_recursive.df_files = env1$env.internal$f_path.df_dirs_recursive.df_files(input_path=".", print.message=FALSE)
# env1$path$print_tree_path = env1$path$df_dirs_recursive.df_files |> dplyr::filter(path.level <= 2) |> 
#     dplyr::select(print_tree_path) |> unlist() |> paste(collapse="") 
# # env1$path$print_tree_path |> cat("  \n", sep="")
# env1$path$print_tree_path_files.codes = env1$path$df_dirs_recursive.df_files |> dplyr::filter(path.level <= 2) |> 
#     dplyr::select(print_tree_path_files.codes) |> unlist() |> paste(collapse="") 
# # env1$path$print_tree_path_files.codes |> cat("  \n", sep="")
# env1$path$print_tree_path_files.data = env1$path$df_dirs_recursive.df_files |> dplyr::filter(path.level <= 2) |> 
#     dplyr::select(print_tree_path_files.data) |> unlist() |> paste(collapse="") 
# env1$path$print_tree_path_files.data |> cat("  \n", sep="")
```
  
  
```{r sizeFiles-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# *** Results hidden in 00env1 - see 01df_dirs_recursive.df_files ***
# #### env1\$f_path.size_files() ----  
# .sourcename = "f_path.size_files" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# #### env1\$f_DataSetName.read.checkEntity() ----  
# .sourcename = "f_DataSetName.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# env1$f$f_path.size_files(.path4read = .path4read)
```
  
  
```{r open-envCustom-dfDirs-CodeBook, eval=TRUE, include=FALSE}
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
## \$ env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# \$ .GlobalEnv$.tmp = list() ====  
.listname = ".tmp"; if(!exists(.listname, envir=.GlobalEnv)) { assign(.listname, list(), envir=.GlobalEnv) }
for (SourceFileBaseName in rev(c("00env1", "01df_dirs_recursive.df_files", "10CodeBook"))) {
    .tmp$SourceFileName.ext = paste0(SourceFileBaseName,"-",basename(env1$path$path1),".Rmd")
    if(.tmp$SourceFileName.ext != basename(env1$path$CurrentSource.path.filename.ext)) {
        # .tmp$SourceFileName.ext %>% {paste0(env1$path$path1,"/",.)} |> file.edit(); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext))
        .tmp$SourceFileName.ext %>% {paste0(env1$path$path1,"/",.)} %>% {.[file.exists(.)]} |> file.edit(); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext))
    }
}
```
  
  
# @@ CODEBOOK ----  
```{r CODEBOOK-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# \$ .GlobalEnv$CODEBOOK = list() ====  
if(!exists("CODEBOOK", envir=.GlobalEnv)) { assign("CODEBOOK", list(), envir=.GlobalEnv) }  
.sublistname = "MetaData"; if(!.sublistname %in% names(.GlobalEnv$CODEBOOK)) { .GlobalEnv$CODEBOOK[[.sublistname]] <- list() }
.sublistname = "DataSetNames"; if(!.sublistname %in% names(.GlobalEnv$CODEBOOK)) { .GlobalEnv$CODEBOOK[[.sublistname]] <- list() }
.sublistname = "VarNames"; if(!.sublistname %in% names(.GlobalEnv$CODEBOOK)) { .GlobalEnv$CODEBOOK[[.sublistname]] <- list() }
.sublistname = "VarNames.select"; if(!.sublistname %in% names(.GlobalEnv$CODEBOOK)) { .GlobalEnv$CODEBOOK[[.sublistname]] <- list() }
.sublistname = "VarNames.filter"; if(!.sublistname %in% names(.GlobalEnv$CODEBOOK)) { .GlobalEnv$CODEBOOK[[.sublistname]] <- list() }
.sublistname = "VarNames.recode"; if(!.sublistname %in% names(.GlobalEnv$CODEBOOK)) { .GlobalEnv$CODEBOOK[[.sublistname]] <- list() }
.sublistname = "ModelList"; if(!.sublistname %in% names(.GlobalEnv$CODEBOOK)) { .GlobalEnv$CODEBOOK[[.sublistname]] <- list() }
```
  
#@@ START) source ----  
### @ .subpath, .sourcename = "default.template" |> paste0(".source.r") ----  
```{r .subpath.filename.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
# .subpath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") {.subpath = env1$path$CurrentSource.path.filename.ext |> dirname(); ".subpath" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
# if(.subpath!="") utils::browseURL(normalizePath(.subpath))
# .sourcename = "default.template" |> paste0(".source.r")
if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") {.sourcename = env1$path$CurrentSource.path.filename.ext |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),""); ".sourcename" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.subpath = .subpath
.sourcename_root = .sourcename |> str_replace("\\.source\\.r$", "")
env1$path$.sourcename_root = .sourcename_root
env1$path$.subpath.filename.dev.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.r")
env1$path$.subpath.filename.dev.Rmd = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.Rmd")
env1$path$.subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.)
cat("# ",'.sourcename_root = "',.sourcename_root,'"', "  \n",
    "# ",env1$path$.subpath.filename.dev.r, "  \n",
    "# ",env1$path$.subpath.filename.dev.Rmd, "  \n",
    "# ",env1$path$.subpath.filename.source.r, "  \n",
    '# # source("',env1$path$source_base,"/",env1$path$.subpath.filename.source.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'")', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.subpath.filename.source.r) ) ----  
# .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.)
# if(!.sourcename %in% names(.GlobalEnv$env1$source)) {cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); source(.GlobalEnv$env1$source[[.sourcename]])}
```
  
```{r}
source("f_DataSetName.read.checkEntity.source.r")
```

  
# @@ START) Data ----  
  
# \$ DataSetName = "fhs.index100le10" =======  
## \% f_DataSetName.read.checkEntity(print2console = FALSE) =======  
```{r, echo=-1, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#

# \$ DataSetName = "fhs.index100le10" =======  
DataSetName = "fhs.index100le10"
out = env1$f$f_DataSetName.read.checkEntity(DataSetName = DataSetName, print2console = FALSE)
out %>% str
# Warning messages:
# 1: In env1$f$f_DataSetName.read.checkEntity(DataSetName = objectname) :
#   getwd() != .path4read == "."
# 2: In env1$f$f_DataSetName.read.checkEntity(DataSetName = objectname) :
#   varname for ID not identified among: c("ID", "CompositeKey", "PERSON_ID", "RN_INDI", "NIHID")
```
  
  
  
## \% f_DataSetName.read.checkEntity(vec_varname4ID = "randid", print2console = FALSE) =======  
```{r, echo=-1, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
out = env1$f$f_DataSetName.read.checkEntity(DataSetName = DataSetName, vec_varname4ID = "randid", print2console = FALSE)
out %>% str
# > out %>% str
# List of 7
#  $ DataSetName   : chr "fhs.index100le10"
#  $ df_size_files :'data.frame':	1 obs. of  2 variables:
#   ..$ filename: chr "data/fhs.index100le10.rds"
#   ..$ size    : num 35747
#  $ read.proc_time: 'proc_time' Named num [1:5] 0.001 0 0.001 0 0
#   ..- attr(*, "names")= chr [1:5] "user.self" "sys.self" "elapsed" "user.child" ...
#  $ dim           : int [1:2] 450 81
#  $ n_distinct    :List of 2
#   ..$ nrow  : int 450
#   ..$ randid: int 450
#  $ names         : chr [1:81] "randid" "death" "angina" "hospmi" ...
#  $ str           : chr [1:85] "tibble [450 × 81] (S3: tbl_df/tbl/data.frame)" " $ randid   : num [1:450] 24721 54224 83398 84815 95541 ..." " $ death    : num [1:450] 1 1 1 0 1 0 0 0 0 0 ..." " $ angina   : num [1:450] 0 0 0 0 0 0 0 0 0 1 ..." ...


```
  

## \% f_DataSetName.read.checkEntity(print2console = TRUE, return.output = FALSE) =======  
```{r, echo=-1, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
env1$f$f_DataSetName.read.checkEntity(DataSetName = DataSetName, vec_varname4ID = "randid", print2console = TRUE, return.output = FALSE)
```
  
  
## \% f_DataSetName.read.checkEntity(print2console = TRUE, return.output = TRUE) =======  
```{r, echo=-1, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
env1$f$f_DataSetName.read.checkEntity(DataSetName = DataSetName, print2console = TRUE, return.output = TRUE)
```
  
  
```{r, echo=-1, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
```{r, echo=-1, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
```{r, echo=-1, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# @@ END ----  
```
  
  
```{r updateTemplateNotebook-NoEchoNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="hide", collapse=TRUE, paged.print=FALSE}
if (.Platform$OS.type == "windows") {
    .sourcename = "templates-00env1.minimum-Chunks" |> paste0(".source.r"); .subpath=r"(rstudio-prefs/templates)"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); source(.GlobalEnv$env1$source[[.sourcename]])}
    #|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
    ## \$ env1\$path\$CurrentSource.path.filename.ext ====  
    # *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
    # env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
    env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
    #|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
    env1$env.internal$RmdChunk.updateTemplateNotebook(.CurrentSource.path.filename.ext = env1$path$CurrentSource.path.filename.ext)
}
```
  
  
```{r writeRDS-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# # @ write_rds( get(objectname), file.path(.path4write, paste0(objectname,".rds"))) ----  
# objectname = "AnalyticDataset200621"
# system.time(write_rds( get(objectname), paste0(objectname,".rds") ))
# system.time(write_rds( get(paste0(objectname,".NA",".rmAllNA",".fct")), paste0(objectname,".NA",".rmAllNA",".fct",".rds") ))
# # system.time(write_rds( get(objectname), file.path(.path4write, paste0(objectname,".rds"))))
# # system.time(write_rds( get(objectname), file.path(.path4write, paste0(objectname,".rds")), compress = "gz" ))
# # system.time(write_rds( get(objectname), file.path(.path4write, paste0(objectname, ".rds", "")), compress = "xz", compression = 9 ))
# # system.time(openxlsx::write.xlsx(get(objectname), file=paste0(objectname,".xlsx"), asTable=TRUE, withFilter=TRUE))
# # if (.Platform$OS.type == "windows") openxlsx::openXL(paste0(objectname, ".xlsx"))
```
  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (.Platform$OS.type == "windows") {
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$CurrentSource.path.filename.pdf = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all("[ ()]","-")
env1$path$CurrentSource.path.filename.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all("[ ()]","-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (.Platform$OS.type == "windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_format = "pdf_document") \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} |> rmarkdown::render(output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}, .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal$f_file_PDF.sumatra(env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}))
    }
}
# cat(' Sys.setenv(PARENT_RENDERING = "YES"); "',env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)},'" |> rmarkdown::render(output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")',"\n", 
#     ' if (.Platform$OS.type == "windows") { env1$env.internal$f_file_PDF.sumatra("',env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)},'") } else { browseURL("',env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)},'") }',"\n",
#     ' env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = "',env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)},'", .backup_to_path="-backup", timeFormat="%y%m%d", overwrite=TRUE)',"  \n", sep="")
# cat("    ________________________________________________________________________    \n")
env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% cat('  Sys.setenv(PARENT_RENDERING = "YES"); "',.,'" |> rmarkdown::render(output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep=""); env1$path$CurrentSource.path.filename.html %>% {paste0(env1$path$path1,"/",.)} %>% cat('  "',.,'" |> env1$env.internal$f_filename.ext.createBackup(.backup_to_path="-backup", timeFormat="%y%m%d", overwrite=TRUE)  \n', sep=""); env1$path$CurrentSource.path.filename.html %>% {paste0(env1$path$path1,"/",.)} %>% cat('  "',.,'" |> env1$env.internal$f_URL.open_in_edge_app()  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$CurrentSource.path.filename.nb.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (.Platform$OS.type == "windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat(" * To revert to the last commited file, run the following terminal command:\n", 
    '"git checkout -- ',env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)},'" |> system(intern=TRUE)',"\n",
    '"git checkout -- ',env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)},'" |> system(intern=TRUE)',"  \n", sep="")
```
  
  
