---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
mainfont: Arial
monofont: Consolas
header-includes: 
  - \usepackage{kotex}
  - \usepackage{fontspec}
  - \setmainhangulfont{HCR Batang}
  - \setsanshangulfont{HCR Dotum}
  - \setmonohangulfont{HCR Dotum}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Arial', 'Helvetica', sans-serif; }
h1.title { font-size: 28px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>

<!-- font-size: 0.9em; /* 90% of inherited font size */ -->

<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
```{r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE}
# ##### Rstudio RMarkDown Shortcuts
# https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE  
# https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html  
# Insert R chunk	Ctrl+Alt+I	Command+Option+I\
# Preview HTML	Ctrl+Shift+K	Command+Shift+K\
# Run all chunks above	Ctrl+Alt+P	Command+Option+P\
# Run current chunk	Ctrl+Alt+C	Command+Option+C\
# Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter\
# Run next chunk	Ctrl+Alt+N	Command+Option+N\
# Run all chunks	Ctrl+Alt+R	Command+Option+R\
# Go to next chunk/title	Ctrl+PgDown	Command+PgDown\
# Go to previous chunk/title	Ctrl+PgUp	Command+PgUp\
# Show/hide document outline	Ctrl+Shift+O	Command+Shift+O\
# F7 spell-check your document.\
# Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).\
# \
# *** Caution: \% \$ \# \* \
```


```{r setup, eval=TRUE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "\n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=TRUE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=TRUE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)
```


```{r options-width-NoEchoHideResults, echo=FALSE, results="hide"}
if(!exists("env.custom", envir=.GlobalEnv)) 
    assign("env.custom", new.env(), envir=.GlobalEnv)
if(!"info" %in% names(env.custom)) env.custom$info = list()
env.custom$info$options.width = options()$width; cat(options()$width, "\n", sep="")
```


```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
suppressPackageStartupMessages({for(packagename in c("tidyverse","formatR")) {if(!require(packagename,character.only=TRUE))install.packages(packagename) else library(packagename,character.only=TRUE)}});cat(" \n");
if(!exists("env.custom", envir=.GlobalEnv)) 
    assign("env.custom", new.env(), envir=.GlobalEnv)
## env.custom\$path ====
if(!"path" %in% names(env.custom)) env.custom$path = list()
objectname = "source_base_local"; object = ifelse(.Platform$OS.type == "windows", "D:/OneDrive/[][Rproject]/github_tidystat", "~/github_tidystat"); if(!objectname %in% names(env.custom$path)) {env.custom$path[[objectname]] = object};
objectname = "source_base_github"; object = "https://github.com/mkim0710/tidystat/raw/master"; if(!objectname %in% names(env.custom$path)) {env.custom$path[[objectname]] = object};
env.custom$path$source_base = ifelse(dir.exists(env.custom$path$source_base_local), env.custom$path$source_base_local, env.custom$path$source_base_github)  
## env.custom\$env.internal ====
sourcename = "env.custom$env.internal"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
#### env.custom\$f_df.t.tribble_construct() ====
sourcename = "f_df.t.tribble_construct"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
```

<font size="3">\% env.custom</font>\

```{r envCustom-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
if(!exists("env.custom", envir=.GlobalEnv)) 
    assign("env.custom", new.env(), envir=.GlobalEnv)
if(!"info" %in% names(env.custom)) env.custom$info = list()
#### env.custom\$info\$get_system_info() ====
sourcename = "get_system_info"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
env.custom$info$info_system_info = env.custom$info$get_system_info()
# str(env.custom$info$info_system_info)
CodeText = "env.custom$info$info_system_info$machine_nodename"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
CodeText = "env.custom$info$info_system_info$Sys.getlocale$LC_COLLATE"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
# CodeText = "env.custom$info$info_system_info$l10n_info$localization_UTF8"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
env.custom$info$info_software_versions = env.custom$info$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "datapasta","openxlsx"))
# str(env.custom$info$info_software_versions)
```


# @@ CODEBOOK ------------


# @@ START) Data ------------

## \$ DataSetName = "CohortGJ0910.BaselineJKGJ2085NoHx...01" ====
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
suppressPackageStartupMessages(library(tidyverse))
#$ assign( objectname, read_rds(paste0(path4read,"/",objectname,".rds")) ) ====
# path4read = file.path(env.custom$path$path0,"Rproject_KNHIS.CohortGJ0910 NoHx")
# objectname = "CohortGJ0910.BaselineJKGJ2085NoHx.drop_na.MetS_NoMeds"
subpath = "data"
objectname = "CohortGJ0910.BaselineJKGJ2085NoHx...01"
path.filename.ext = ifelse(
    file.exists(paste0(subpath,"/",objectname,".rds"))
    , paste0(subpath,"/",objectname,".rds")
    , paste0(env.custom$path$source_base_github,"/",subpath,"/",objectname,".rds")
)
cat(" path.filename.ext = ", path.filename.ext, "\n", sep = "")
assign( objectname, read_rds(path.filename.ext) )
# > paste0(path4read,"/",objectname,".rds")
# [1] "./data/CohortGJ0910.BaselineJKGJ2085NoHx...01.rds"
# > file.exists(paste0(path4read,"/",objectname,".rds"))
# [1] FALSE
# > assign( objectname, read_rds(normalizePath(paste0(path4read,"/",objectname,".rds"))) )
# Warning: path[1]="./data/CohortGJ0910.BaselineJKGJ2085NoHx...01.rds": No such file or directoryWarning: cannot open file './data/CohortGJ0910.BaselineJKGJ2085NoHx...01.rds': No such file or directoryError in readRDS(con, refhook = refhook) : cannot open the connection

CohortGJ0910.BaselineJKGJ2085NoHx...01 |> names() |> paste0(collapse = ", ") |> cat();cat(" \n") ###### |> cat() ----
```


#@@ START) source -----
### \$ subpath, sourcename = "data.CreateTableOne" ======
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
subpath = r"(Rdev/60_communicate_report_export)" |> str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
# if(subpath!="") utils::browseURL(normalizePath(subpath))
sourcename = "data.CreateTableOne"
# % source( file.path(env.custom$path$source_base,subpath,paste0(sourcename,".source.r")) ) ----
source( file.path(env.custom$path$source_base,subpath,paste0(sourcename,".source.r")) )
```


### %>% function.DataSet.TableOne_byExposure.xlsx(VarNames4Exposure =  c("SEX"))
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

CohortGJ0910.BaselineJKGJ2085NoHx...01 %>% 
    select(
        SEX,
        HEIGHT, WEIGHT, 
        BMI.cut4, 
        WAIST, 
        WAIST_ge9080, WAIST_ge9085, 
        SBP, DBP, BP_ESCESH2018, 
        BP_ge130_85, 
        FPG, 
        FPG_ge100, FPG_ge126, 
        TOT_CHOLE, 
        TRIGLYCERIDE, 
        HDL_CHOLE, LDL_CHOLE, 
        TRIGLYCERIDE_ge150, HDL_CHOLE_lt4050, 
        nMetS_NoMeds_WAIST_ge9080, nMetS_NoMeds_WAIST_ge9080.ge3, 
        nMetS_NoMeds_WAIST_ge9085, nMetS_NoMeds_WAIST_ge9085.ge3
    ) %>% function.DataSet.TableOne_byExposure.xlsx(ObjectName = "CohortGJ0910.BaselineJKGJ2085NoHx...01.select_MetS", VarNames4Exposure =  c("SEX"))

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

system(paste0("git checkout -- ",rstudioapi::getSourceEditorContext()$path))
```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


# @@ END ------------
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# @@ END ------------
```


```{r writeRDS-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# # @ write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds"))) -----
# objectname = "AnalyticDataset200621"
# system.time(write_rds( get(objectname), paste0(objectname,".rds") ))
# system.time(write_rds( get(paste0(objectname,".NA",".rmAllNA",".fct")), paste0(objectname,".NA",".rmAllNA",".fct",".rds") ))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds"))))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds")), compress = "gz" ))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname, ".rds", "")), compress = "xz", compression = 9 ))
# # system.time(openxlsx::write.xlsx(get(objectname), file=paste0(objectname,".xlsx"), asTable=TRUE, withFilter=TRUE))
# # openxlsx::openXL(paste0(objectname, ".xlsx"))
```


```{r createBackup, eval=TRUE, include=FALSE}
env.custom$env.internal$f_filename.ext.createBackup(copying_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), backup_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
# env.custom$env.internal$f_filename.ext.createBackup(copying_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), backup_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
```


```{r Render, eval=TRUE, include=FALSE}
# if (Sys.getenv("PARENT_RENDERING") != "YES") {
#     cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_format = "pdf_document") \n')
#     Sys.setenv(PARENT_RENDERING = "YES"); rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")
#     env.custom$env.internal$f_filename.ext.createBackup(copying_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".pdf"), backup_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
# }
cat(' Sys.setenv(PARENT_RENDERING = "YES"); "',rstudioapi::getSourceEditorContext()$path,'" |> rmarkdown::render(output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")',"\n", sep="")
cat(' env.custom$env.internal$f_filename.ext.createBackup(copying_path.filename.ext = "',rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".pdf"),'", backup_path="-backup", timeFormat="%y%m%d", overwrite=TRUE) ',"\n", sep="")
```


```{r gitCheckout, eval=TRUE, include=FALSE}
cat(" * To revert to the last commited file, run the following terminal command:\n", 
    '"git checkout -- ',rstudioapi::getSourceEditorContext()$path,'" |> system(intern=TRUE) ',"\n",
    '"git checkout -- ',rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"),'" |> system(intern=TRUE) ',"\n", sep="")
```


