---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
env1$info$options.width = options()$width; cat(options()$width, "  \n", sep="")
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
## env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
cat("> .tmp |> str(max.level = 1, give.attr = FALSE)", "  \n", sep="") 
.tmp |> str(max.level = 1, give.attr = FALSE)
cat("> env1 |> as.list() |> str(max.level = 2, give.attr = FALSE)", "  \n", sep="") 
env1 |> as.list() |> str(max.level = 2, give.attr = FALSE)
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
# .sourcename = "f_DataSetName.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  

```{r open-envCustom-dfDirs-df_VarName_ValueOptions, eval=TRUE, include=FALSE}
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
## env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# .GlobalEnv$.tmp = list() ====  
.listname = ".tmp"; if(!exists(.listname, envir=.GlobalEnv)) { assign(.listname, list(), envir=.GlobalEnv) }
for (SourceFileBaseName in rev(c("00env1", "01df_dirs_recursive.df_files", "10CodeBook"))) {
    .tmp$SourceFileName.ext = paste0(SourceFileBaseName,"-",basename(env1$path$path1),".Rmd")
    if(.tmp$SourceFileName.ext != basename(env1$path$CurrentSource.path.filename.ext)) {
        # .tmp$SourceFileName.ext %>% {paste0(env1$path$path1,"/",.)} |> file.edit(); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext))
        .tmp$SourceFileName.ext %>% {paste0(env1$path$path1,"/",.)} %>% {.[file.exists(.)]} |> file.edit(); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext))
    }
}
```
  
  
# @@ START) DataSet example ----  

# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```

## \$ https://chatgpt.com/c/66e1f092-be28-800e-8527-a0815faa0a37 =  ----  
## \$ https://chatgpt.com/c/66e205de-d4d4-800e-a889-5ced38a816ed =  ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# Load necessary libraries
library(dplyr)
library(stringr)

# Example dataset
your_data <- data.frame(
  RID = c(1, 2, 3),
  DATA_CLASS = c(10, 20, 10),
  VISIT = c(0, 1, 1),
  SEX = c(1, 2, 1),
  EDU = c(5, 6, 3)
)

# Example df_VarName_ValueOptions
MetaData <- list(tblVarName = list(tblVarName.suffix = tibble::tibble(
  VarName.suffix = c("DATA_CLASS", "VISIT", "SEX", "EDU"),
  ValueOptions = c(
    "10=안성, 20=안산",
    "0=미참여, 1=참여",
    "1=남자, 2=여자",
    "1=초등학교 이하, 2=중학교, 3=고등학교, 4=전문대, 5=대학교, 6=대학원 이상"
  )
)))
```


## \% f_vec_ValueOptions.factor() 
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
# Load necessary packages
library(stringr)
library(purrr)

# Function to create levels and labels from ValueOptions
f_vec_ValueOptions.factor <- function(vec, ValueOptions, sep4levels = ",\\s*", sep4name_value = "=", print.intermediate = FALSE) {
  # Return the original vector if ValueOptions is missing or empty
  if (is.na(ValueOptions) || ValueOptions == "") {
    return(vec)
  }

  if (print.intermediate) {
    cat("Processing variable with ValueOptions:", ValueOptions, "\n")
  }
  
  # Split ValueOptions by the specified separator for levels
  options_split <- str_split(ValueOptions, sep4levels)[[1]]
  
  if (print.intermediate) {
    cat("Split ValueOptions:", paste(options_split, collapse = ", "), "\n")
  }
  
  # Split each option into level and label using the name-value separator
  levels <- map_dbl(options_split, ~ as.numeric(str_split(.x, sep4name_value)[[1]][1]))
  labels <- map_chr(options_split, ~ str_split(.x, sep4name_value)[[1]][2])
  
  if (print.intermediate) {
    cat("Levels:", paste(levels, collapse = ", "), "\n")
    cat("Labels:", paste(labels, collapse = ", "), "\n")
  }

  # Convert the vector into a factor with specified levels and labels
  vec.factor <- factor(vec, levels = levels, labels = labels)

  return(vec.factor)
}

# Example vector
sex_vector <- c(1, 2, 1, 2, 1)

# ValueOptions string for the variable SEX
sex_ValueOptions <- "1=남자, 2=여자"

# Apply the function
sex_factor <- f_vec_ValueOptions.factor(sex_vector, sex_ValueOptions, print.intermediate = TRUE)

# View the result
print(sex_factor)

```


## \% f_DataSet_CodeBook.map_factor() 
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
# Load necessary packages
library(dplyr)
library(purrr)
library(stringr)

# Function to create levels and labels from ValueOptions (as defined earlier)
f_vec_ValueOptions.factor <- function(vec, ValueOptions, sep4levels = ",\\s*", sep4name_value = "=", print.intermediate = FALSE) {
  if (is.na(ValueOptions) || ValueOptions == "") {
    return(vec)
  }

  if (print.intermediate) {
    cat("Processing variable with ValueOptions:", ValueOptions, "\n")
  }
  
  options_split <- str_split(ValueOptions, sep4levels)[[1]]
  
  if (print.intermediate) {
    cat("Split ValueOptions:", paste(options_split, collapse = ", "), "\n")
  }
  
  levels <- map_dbl(options_split, ~ as.numeric(str_split(.x, sep4name_value)[[1]][1]))
  labels <- map_chr(options_split, ~ str_split(.x, sep4name_value)[[1]][2])
  
  if (print.intermediate) {
    cat("Levels:", paste(levels, collapse = ", "), "\n")
    cat("Labels:", paste(labels, collapse = ", "), "\n")
  }

  vec.factor <- factor(vec, levels = levels, labels = labels)

  return(vec.factor)
}

# Function to apply factor conversion to the entire dataset using the df_VarName_ValueOptions
f_DataSet_CodeBook.map_factor <- function(DataSet, df_VarName_ValueOptions, sep4levels = ",\\s*", sep4name_value = "=", print.intermediate = FALSE) {
  # Loop over each row in the df_VarName_ValueOptions
  for (i in 1:nrow(df_VarName_ValueOptions)) {
    var_name <- df_VarName_ValueOptions$VarName.suffix[i]
    value_options <- df_VarName_ValueOptions$ValueOptions[i]
    
    # Check if the variable exists in the dataset
    if (var_name %in% colnames(DataSet)) {
      # Apply the factor conversion function to the column in the dataset
      DataSet[[var_name]] <- f_vec_ValueOptions.factor(DataSet[[var_name]], 
                                                    value_options, 
                                                    sep4levels, 
                                                    sep4name_value, 
                                                    print.intermediate)
    }
  }
  return(DataSet)
}

# Example usage
# Sample dataset (replace 'your_data' with the actual dataset)
your_data <- data.frame(
  RID = c(1, 2, 3),
  DATA_CLASS = c(10, 20, 10),
  VISIT = c(0, 1, 1),
  SEX = c(1, 2, 1),
  INCOME = c(1, 5, 3),
  stringsAsFactors = FALSE
)

# Sample df_VarName_ValueOptions (replace 'MetaData' with your actual df_VarName_ValueOptions)
MetaData <- list(tblVarName = list(tblVarName.suffix = tibble::tibble(
  VarName.suffix = c("DATA_CLASS", "VISIT", "SEX", "EDU"),
  ValueOptions = c(
    "10=안성, 20=안산",
    "0=미참여, 1=참여",
    "1=남자, 2=여자",
    "1=초등학교 이하, 2=중학교, 3=고등학교, 4=전문대, 5=대학교, 6=대학원 이상"
  )
)))

# Convert the dataset using the df_VarName_ValueOptions
converted_data <- f_DataSet_CodeBook.map_factor(your_data, MetaData$tblVarName$tblVarName.suffix, print.intermediate = TRUE)

# View the converted dataset
print(converted_data)
str(converted_data)

```
  
  
## \% f_DataSet_CodeBook.map2factor() 
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# Load necessary packages
library(stringr)
library(purrr)

# Function to create levels and labels from ValueOptions
f_vec_ValueOptions.factor <- function(vec, ValueOptions, sep4levels = ",\\s*", sep4name_value = "=", print.intermediate = FALSE) {
  if (is.na(ValueOptions) || ValueOptions == "") {
    return(vec)
  }

  if (print.intermediate) {
    cat("Processing variable with ValueOptions:", ValueOptions, "\n")
  }
  
  options_split <- str_split(ValueOptions, sep4levels)[[1]]
  
  if (print.intermediate) {
    cat("Split ValueOptions:", paste(options_split, collapse = ", "), "\n")
  }
  
  levels <- map_dbl(options_split, ~ as.numeric(str_split(.x, sep4name_value)[[1]][1]))
  labels <- map_chr(options_split, ~ str_split(.x, sep4name_value)[[1]][2])
  
  if (print.intermediate) {
    cat("Levels:", paste(levels, collapse = ", "), "\n")
    cat("Labels:", paste(labels, collapse = ", "), "\n")
  }

  vec.factor <- factor(vec, levels = levels, labels = labels)

  return(vec.factor)
}

# Improved function to apply factor conversion to the entire dataset using df_VarName_ValueOptions
f_DataSet_CodeBook.map_factor <- function(DataSet, df_VarName_ValueOptions, sep4levels = ",\\s*", sep4name_value = "=", print.intermediate = FALSE) {
  # Use map2 to iterate over VarName.suffix and ValueOptions in parallel
  DataSet <- map2(df_VarName_ValueOptions$VarName.suffix, df_VarName_ValueOptions$ValueOptions, 
    function(var_name, value_options) {
      if (var_name %in% colnames(DataSet)) {
        DataSet[[var_name]] <- f_vec_ValueOptions.factor(DataSet[[var_name]], 
                                                         value_options, 
                                                         sep4levels, 
                                                         sep4name_value, 
                                                         print.intermediate)
      }
      return(DataSet[[var_name]])
    })
  
  # Return the updated DataSet as a data frame
  return(as.data.frame(DataSet))
}

# Example usage
# Sample dataset
DataSet <- data.frame(
  RID = c(1, 2, 3),
  DATA_CLASS = c(10, 20, 10),
  VISIT = c(0, 1, 1),
  SEX = c(1, 2, 1),
  INCOME = c(1, 5, 3),
  stringsAsFactors = FALSE
)

# Sample df_VarName_ValueOptions
df_VarName_ValueOptions <- tibble::tibble(
  VarName.suffix = c("RID", "DATA_CLASS", "VISIT", "SEX", "INCOME"),
  ValueOptions = c(NA, "10=안성,20=안산", "0=미참여, 1=참여", "1=남자, 2=여자", "1=50만원미만, 5=200-300만원미만, 3=100-150만원미만")
)

# Convert the dataset using the improved function
converted_DataSet <- f_DataSet_CodeBook.map_factor(DataSet, df_VarName_ValueOptions, print.intermediate = TRUE)

# View the converted dataset
print(converted_DataSet)

```
  
  
## \% f_DataSet_CodeBook.walk2_factor() 
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# Load necessary packages
library(stringr)
library(purrr)

# Function to create levels and labels from ValueOptions
f_vec_ValueOptions.factor <- function(vec, ValueOptions, sep4levels = ",\\s*", sep4name_value = "=", print.intermediate = FALSE) {
  if (is.na(ValueOptions) || ValueOptions == "") {
    return(vec)
  }

  if (print.intermediate) {
    cat("Processing variable with ValueOptions:", ValueOptions, "\n")
  }
  
  options_split <- str_split(ValueOptions, sep4levels)[[1]]
  
  if (print.intermediate) {
    cat("Split ValueOptions:", paste(options_split, collapse = ", "), "\n")
  }
  
  levels <- map_dbl(options_split, ~ as.numeric(str_split(.x, sep4name_value)[[1]][1]))
  labels <- map_chr(options_split, ~ str_split(.x, sep4name_value)[[1]][2])
  
  if (print.intermediate) {
    cat("Levels:", paste(levels, collapse = ", "), "\n")
    cat("Labels:", paste(labels, collapse = ", "), "\n")
  }

  vec.factor <- factor(vec, levels = levels, labels = labels)

  return(vec.factor)
}

# Refined function to apply factor conversion to the entire dataset using df_VarName_ValueOptions
f_DataSet_CodeBook.walk2factor <- function(DataSet, df_VarName_ValueOptions, sep4levels = ",\\s*", sep4name_value = "=", print.intermediate = FALSE) {
  # Use walk2 to iterate over VarName.suffix and ValueOptions in parallel and update DataSet in place
  walk2(df_VarName_ValueOptions$VarName.suffix, df_VarName_ValueOptions$ValueOptions, 
    function(var_name, value_options) {
      if (var_name %in% colnames(DataSet)) {
        DataSet[[var_name]] <<- f_vec_ValueOptions.factor(DataSet[[var_name]], 
                                                          value_options, 
                                                          sep4levels, 
                                                          sep4name_value, 
                                                          print.intermediate)
      }
    })
  
  # Return the updated DataSet as a data frame
  return(DataSet)
}

# Example usage
# Sample dataset
DataSet <- data.frame(
  RID = c(1, 2, 3),
  DATA_CLASS = c(10, 20, 10),
  VISIT = c(0, 1, 1),
  SEX = c(1, 2, 1),
  INCOME = c(1, 5, 3),
  stringsAsFactors = FALSE
)

# Sample df_VarName_ValueOptions
df_VarName_ValueOptions <- tibble::tibble(
  VarName.suffix = c("RID", "DATA_CLASS", "VISIT", "SEX", "INCOME"),
  ValueOptions = c(NA, "10=안성,20=안산", "0=미참여, 1=참여", "1=남자, 2=여자", "1=50만원미만, 5=200-300만원미만, 3=100-150만원미만")
)

# Convert the dataset using the renamed function
converted_DataSet <- f_DataSet_CodeBook.walk2factor(DataSet, df_VarName_ValueOptions, print.intermediate = TRUE)

# View the converted dataset
print(converted_DataSet)

```
  
  
#### Rdev/60_communicate_report_export/f_DataSet_CodeBook.walk2factor.source.r  ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
#### Rdev/60_communicate_report_export/f_DataSet_CodeBook.walk2factor.source.r  ----  
.subpath = r"(Rdev/60_communicate_report_export)" |> str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
# if(.subpath!="") utils::browseURL(normalizePath(.subpath))
.sourcename = "f_DataSet_CodeBook.walk2factor.source.r"
### \% source( file.path(env1$path$source_base,.subpath.filename.source.r) ) ----  
.GlobalEnv$env1$source[[.sourcename]]


.subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% .GlobalEnv$env1$source) {cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); source( file.path(env1$path$source_base,.subpath.filename.source.r) ); .GlobalEnv$env1$source[[.sourcename]] = TRUE}


```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# @@ END ----  
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
```{r writeRDS-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
## @ write_rds( get(.objectname), file.path(.path4write, paste0(.objectname,".rds"))) ----  
.path4write = env1$path$.path4write
# MetaData$DataSetNames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
for (.objectname in names(MetaData$DataSetNames)) {
    assign(.objectname, structure(get(.objectname), MetaData = MetaData))
    .path.file = paste0(.path4write,"/",.objectname,".rds")
    cat(.objectname, ' |> write_rds("',.path.file,'", compress = "none") |> system.time()', "  \n", sep="")
    paste0( "git add -f ",shQuote(.path.file) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
}
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# .objectname = MetaData$DataSetNames %>% {names(.)[length(.)]}; .objectname %>% cat(deparse(substitute(.)), ' == "',.,'"  \n', sep="")
assign(.objectname, structure(get(.objectname), MetaData = MetaData))
#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ 
# .path.file = paste0(.path4write,"/",.objectname,".rds")
# system.time(write_rds( get(.objectname), .path.file)))
# # system.time(saveRDS( get(.objectname), .path.file, compress = "gzip" ))
# system.time(write_rds( get(.objectname), .path.file, compress = "gz", compression = 9 ))
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 
.path.file = paste0(.path4write,"/",.objectname,".rds", ".xz")
system.time(write_rds( get(.objectname), .path.file), compress = "xz", compression = 9 ))
env1$f$f_path.size_files(.path4read = .path4write, regex4filename  = .objectname)
#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ 
paste0( "git add -f ",shQuote(.path.file) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
# paste0( "git add -f ",shQuote(.path.file) ) |> system(intern=TRUE)
#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ 
# .path.filename.xlsx = paste0(.path4write,"/",.objectname,".xlsx")
# system.time(openxlsx2::write_xlsx(get(.objectname), file=.path.filename.xlsx, as_table=TRUE))
# if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(.path.filename.xlsx)
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$CurrentSource.path.filename.nb.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
