---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = options()$width; cat(options()$width, "  \n", sep="")
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .sourcename = "f_DataSetName.Search.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(isTRUE(options()$function.reload) || !.sourcename %in% names(.GlobalEnv$env1$source)) {  message('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")'); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  
# __________|------  
# @@ START) data example ----  
## \$ analyticDF_time2event =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# suppressPackageStartupMessages(library(survival))
for(.packagename in c("survminer")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
# ?survival::lung
.objectname = DataSetName = "analyticDF_time2event"
assign(
    DataSetName, 
    survival::lung |> as_tibble() |> mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] |> as.factor(), StudyPopulation = time >= 30) |>
        # dplyr::select(-status, -sex)
        dplyr::select(-status)
)
analyticDF_time2event %>% {cat(" > ",deparse(substitute(.))," |> as_tibble() |> print()","  \n", sep=""); print(as_tibble(.))}
```

  
### :: df_50vars_100obs = sample(c("Group1", "Group2"), num_obs, replace = TRUE) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

# # Set a random seed for reproducibility
# set.seed(42)
# 
# # Create a synthetic dataset with 100 observations and 50 numeric variables
# num_obs <- 100
# num_vars <- 50
# 
# # Generate numeric variables
# numeric_vars <- as.data.frame(matrix(rnorm(num_obs * num_vars), nrow = num_obs))
# colnames(numeric_vars) <- paste0("Var", 1:num_vars)
# 
# # Generate a binary grouping variable
# group_var <- sample(c("Group1", "Group2"), num_obs, replace = TRUE)
# 
# # Combine into a single dataset
# df_50vars_100obs <- data.frame(Group = group_var, numeric_vars)
# df_50vars_100obs %>% env1$f$f_df.tribble_construct()
```
  
    
      tibble::tribble(
          ~Group,               ~Var1,                ~Var2,               ~Var3,                 ~Var4,                ~Var5,                ~Var6,               ~Var7,                ~Var8,                ~Var9,              ~Var10,              ~Var11,              ~Var12,              ~Var13,               ~Var14,              ~Var15,              ~Var16,               ~Var17,               ~Var18,              ~Var19,              ~Var20,              ~Var21,              ~Var22,               ~Var23,               ~Var24,               ~Var25,               ~Var26,              ~Var27,              ~Var28,              ~Var29,               ~Var30,              ~Var31,               ~Var32,              ~Var33,               ~Var34,              ~Var35,              ~Var36,              ~Var37,              ~Var38,               ~Var39,               ~Var40,              ~Var41,              ~Var42,               ~Var43,               ~Var44,              ~Var45,              ~Var46,              ~Var47,              ~Var48,               ~Var49,               ~Var50,
        "Group1",    1.37095844714667,     1.20096537559849,   -2.00092923773151,   -0.0046207678264578,     1.33491258537547,     1.02914071931376,  -0.248482933189933,    0.294692356485688,    0.688807752342063,   0.941924217330924,    2.32505849371513,  -0.650284428487915,  -0.746516451736768,    -1.18554693655878,   0.877294651826757,  -0.601382997836582,   0.0293166527942015,     1.44820167458194,   -1.22133337042893,  0.0978270374471885,    0.25057806717021,  -0.586938576519139,    0.190339844032857,    0.758060825406684,     1.32750455958168,    0.617336709876794,  -0.241815887985519,  -0.544689343472721,  -0.849531062880063,   -0.632586792692066,  -0.685661664496834,     1.37843190060709,   -2.06452596044887,   -0.976293562011762,  -0.106222654973173,   0.290433348159067,  -0.184349380412772,  -0.591796068662362, -0.00723908878469659,   -0.450398744367244,  -0.141808656570536,    -1.1671305153144,    -1.06975411357875,    0.385224800550677,   0.951080448511403,  -0.202515342264725,   0.572396893691075,    1.67587348031072,     1.27337781870638,    0.660817099212903,
        "Group2",  -0.564698171396089,     1.04475108716773,    0.33377719743357,     0.760242167662055,   -0.869271763875442,    0.914774867719613,   0.422320385832393,    0.392741265420726,    0.725083017674864,  -0.248614037279559,   0.524122181151092,   -1.00318322831336,  0.0366061204319243,   -0.658389290697043,   -1.77337143893369,  -0.135816136579885,     1.93431433615124,  -0.0858556605918652,  -0.452985993615507,    1.46502102859676,  -0.277924049161014,   0.926975731943589,  -0.0717387693981193,      1.4796143353762,   -0.600835831817181, -0.00454114147551432,   0.572136317124428,  -0.434532959022116,   0.115138725174226,     1.06719019915197,   -0.79271446858291,    -2.95313731358376,    0.67724922249105,     -1.0083744977457,   -1.28708648621814,   -1.30379423270979,  -0.263044660917602,  -0.885001753474386,   -0.462310513259255,    -1.37722783470441,  -0.813898073869445,  -0.300352441454183,  -0.0159038650102378,    -2.06023179151918,  -0.132976015348185,   -1.21438243722599,  -0.504092170196848,   0.458351194891028,    0.927049266153049,   -0.558583275440896,
        "Group1",   0.363128411337339,    -1.00320864683985,    1.17132512735879,    0.0389909128725626,   0.0554869546651026, -0.00245626667956324,   0.987653293639674,    -1.00084371300082,    0.217380210939088,  0.0964788597064851,   0.970733416408591,  -0.535113912874478,   0.323309624203048,     1.08950794879155, -0.0456873243111543,  -0.987272784920511,    0.837510875177963,    -1.57376980165346,  -0.702319931281128,   0.990435852724289,   -1.72473573426284, -0.0654058453375009, -0.00285171005059469,   -0.619562406414632,   0.0565068582510194,  -0.0912563600897754,   0.705791797687352,  -0.140845191963231,     -1.331337154012,    0.337395921464703,  -0.407004152261873,    0.955836563019408,    0.83638305791437,   -0.256399512370766,  -0.908059860049952,  -0.114100599327674,  -0.525646241251671,  -0.527436558659494,   -0.724387535647471,     1.04859151359238,  -0.325540589312666,   0.769973982367045,    0.538930717398302,   -0.145354412049052,   -1.28558425906626, -0.0195263460837836,   0.298275164165794,  -0.608973926422281,      1.0855162221139,   -0.546194958376543,
        "Group2",    0.63286260496104,     1.84848190167275,     2.0595392422993,     0.735072141614441,   0.0490669131919192,    0.136009552413727,   0.835568172035023,   -0.325727119823434,   -0.201656731618378,  -0.433930941301739,   0.376973397152614,  -0.110414566776788,   0.379676032401592,    0.508785941160661,  -0.394872253984139,   0.831925014618268,   -0.185346331084667,     1.29247615946669,  -0.674380385485126,    1.41438675072227,   -2.00670494385569,  -0.937111758775164,    -1.10821896191248,    0.259687227256229,   -0.531076289581877,    0.399959374815336,   0.204899603994032,    1.75814127006527,    2.37445827173169,   -0.953645663654521,   -1.14867061145898,     1.06003423492052,   0.122243876490421,    0.882816739912026,  -0.283935748679001,  -0.092962085023748,   -0.67522749773812,  0.0310374052801759,   -0.639016919876248,     0.30555621676614,   0.378157397165477,   0.240262799278662,     -1.7847166263677,   0.0979794170841947,    1.66116485621508,  -0.754033536543343,    1.50269854212028,    1.24388746890905,    0.850809408657291,  -0.0501552941200661,
        "Group2",   0.404268323140999,   -0.666773408757817,   -1.37686159824052,     -0.14647262699887,   -0.578355728360897,   -0.720153544943125,  -0.660521859045705,    -1.00834880542884,    -1.36568986058868,    2.17866786745157,  -0.995933396542156,   0.600430169313573,   0.876556495795362,   -0.135906625600424,  -0.128056266421018,  -0.795059516415481,    0.533329177764386,    0.084467755567716,   -2.30302319048591,   -1.33589776931334,   -1.29180833046846,  -0.633859433761416,    0.935191767373595,    -1.08652092497737,  -0.0808987843769502,    0.588901656549108,   0.552103380111652,  -0.830141420577255,   -2.49583641731167,    0.251173574136911,    1.11576046554672,     1.35096056599856,  -0.788249637189588,    0.376027123503681,   0.266592458399183,  -0.122560626447375,  -0.156788604665715,  -0.946515483343574,    0.444142523918265,   -0.918748616451352,     -1.994485362048,   0.754168797301627,   -0.450105347817872,     1.65117286843722,   0.136576555971212,    1.18908758835552,  -0.138564465090582,  -0.417240199159802,    0.866213289418356,     1.39025703407765,
        "Group2",  -0.106124516091484,    0.105513812456069,   -1.15085556562711,   -0.0578873353812826,   -0.998738655996004,   -0.198124330051216,    1.56406949329184,   -0.635431482033766,    -0.30893760867716,   -2.95877961913012,  -0.597482913048045,   0.415845059598682,   0.933387987569637,   -0.108782736956893,    1.09623773188662,   0.340464612015827,     1.78495624201476,    0.967045996480089,  -0.149332904782873,   0.579583638393261,   0.365838228483296,  -0.575224286015068,    -1.48583945173733,    0.086223563193975,    0.160755586671381,  -0.0168780393868136,  -0.568871310357778,   0.514427756122244,    2.20367615406188,   -0.548148703547833,  -0.879456778170003,   -0.401555741178659,   0.633637015638911,    0.104450888453636,    1.22431930895728,  -0.883310771318462,   0.969242741689339,   -2.49897029524684,   -0.584054238178266,   -0.845222587052554,  -0.999356693242897,   -1.76908156428037,    0.478496474306168,   -0.697531585795611,  -0.464363828025639,    1.51016674154176,   0.581056511314598,    1.68909025314131,   -0.984625602881257,    -1.42484238513711,
        "Group2",    1.51152199743894,   -0.422255881868856,  -0.705821394760121,     0.482369466104533, -0.00243278000660164,    -1.02920880604827,   -1.62297593529155,    -1.20984068798734,   -0.452902886537227,  0.0808882391991137,   0.165251423080152,  -0.105750646676992,   -2.42880752268242,    0.754900160454641,    -1.2552178606199,   0.870429820346914,    0.189627819830131,     1.93911299421702,   0.948689589970129,  -0.361821214298648,  -0.152203253908431,   0.188221041759335,     2.22854189842651,   -0.846202449052606,   -0.102140564663634,    0.418704182088633,   0.192717755598882,   0.787131076627757,   0.571396927069173,    0.103236017603065,    1.27932293753161,    0.839986980187328,  -0.203293498180638,     1.57174942774957,   0.821525526825726,   0.600169469401305,    1.86326613150228,   0.145711531004003,    0.186265347755488,    -1.22732567518176,   0.283822423134089,   0.116332320379715,   -0.346428572747648,    0.800353223332998,  -0.306423805718502,   -1.17039262434416,  -0.710107574329743,  0.0300191965400803,    -1.78731703649892,   -0.907690086200588,
        "Group2", -0.0946590384130976,   -0.122350171954971,   -1.05405578207719,     0.992943636775734,    0.655511882812969,   -0.966955895852616,   0.863896373478988,    -1.11646380065269,    0.663229144519792,   0.110137804617221,   -2.92847717857757,  -0.856562538246121,    1.72799402342117,   -0.223811321619966,  -0.265483694629895,   -1.18216100524638,     -0.5690875121866,     1.07987263816564,    1.15636246052357,  -0.046852449651786,  -0.734094090076209,   0.539655974462932,      1.6241352225378,    0.388905864370388,   -0.354749969786071,    0.800727964524838,   0.621347221610975,   0.242015513717525,  -0.583745237218935,     1.86601650513967,   -1.45427725484716,    0.215439257728434,    1.77577501258599,   -0.268640998188145,   -1.24776679226202,   0.717134365632955,    1.01885748883875,   0.858703393437413,   -0.300342713730724,    0.351529308690375,   -1.10119397684316,   0.692022539741815,    -2.04428657828086,  -0.0286260385443061,  -0.435812300530228,   -1.29392827357685,    1.40706683376086,   -1.05539227988081,     2.14701952442045,    -0.22120484884991,
        "Group2",    2.01842371387704,    0.188193034501498,  -0.645743723142491,     -1.24639549803204,     1.47684227897655,    -1.22081308891909,    -0.5116027734362,    0.629881162575935,      1.3086295367487,   0.213448326312653,  -0.847914226578549,    1.12732733432216,   0.456002646277211,   0.0749551709399243,    2.55330249004026,    1.02289397573496,     1.45189294457212,   -0.353593526833153,    2.07435248589762,  -0.599477471411771,  -0.781972056981591,  -0.420884069657012,    0.519764625253335,  -0.0376358153463912,   -0.471227347093368,    0.679893103827864,   -0.10721561163254,   0.559916806561637,   0.274860357622418,    -1.04099380528512,    0.84222876919352,   -0.637977201958245,   0.503354149677886,     1.84852188608278,   0.601275013858363,  -0.390874782474331,  0.0456918216264974,  -0.209938282882933,    0.159700413754183,    0.880826582309925,   0.983346982359529,    1.37798602518764,    -1.48362599388729,    0.929936110491093,   -1.70782279922691,    -0.4850066524442,    1.42853509534363,   0.442194184146143,   -0.608840731481907,    0.172700145711298,
        "Group1",  -0.062714099052421,    0.119160957997006,  -0.185377967676503,   -0.0334875248456097,    -1.90915278827921,    0.836207703944837,    -1.9173650254454,   -0.272521570178626,    0.501040309894498,   -1.55781961263232,   0.798584512223446,   0.916281621448453,  -0.570360345745652,       -1.64595480215,   -1.47830630595052,   -2.10843457624333,     1.86899345256532,   -0.134923124718565,   0.265289970321459,   0.215104493222833,   0.551567034812709,  -0.339466559977085,      -1.352028636762,     1.44560164892583,   0.0340441773616117,     1.30966392253954,  -0.124075919558077,  -0.650418509012264, -0.0482891959610158,    0.219983787127424,  -0.603215007812732,    0.552847982050689,    1.85994569369779,    -1.51059647026223,  -0.908752216129051,   0.427892517086193,   -1.20179167247776,   0.398824020925648,     1.01999508545972,   -0.453966879586077,   -1.01662540554706,   -2.73597021069485,   -0.922956472241783,    0.165499606708942,  -0.171289220774238, -0.0596950692064959,   0.772441783032171,     1.2344811616459,     1.68209881019529,    0.193437013664752,
        "Group2",    1.30486965422349,  -0.0250925508674029,   -1.20122205073999,   -0.0709621812499963,   -0.702439473312409,      1.1149717984954,   -1.86581384861995,   -0.258841168378671,    -1.12828853519737,   0.216211546257758,  -0.298455987965219,  -0.724379592724361,   -1.11462440217797,     1.77400936515502,  -0.626587568230723,   0.229762637699325,   -0.984554893737541,   -0.987132433307501,   -1.05200382914047,   0.093631485479041,   -1.61084098443007,   0.518080388363255,    0.426123827628841,    0.317224482102685,   -0.200721207356766,    -1.89121447886908,  -0.465021846854624,  -0.458392616404943,    2.25246864177724,    -1.42379490646875,   0.131555027342539,    0.370350824990752,  -0.609493045570301,    0.281061228694041,   0.900344887747296,  -0.837105234296302,   0.909354155230945,   0.761127736197585,    0.798351878707584,     1.01804620900246,  -0.863907495138643,  -0.782565190445743,    0.174244530667259,    0.155884163257049,    0.98881575178477,   0.128079710548587,   0.797725022565042,  -0.806793160374736,    -1.61998447843025,     1.96870347281662,
        "Group1",    2.28664539270111,    0.108072727942033,    2.03697216698315,     -0.75892065373095,   -0.311430218011919,   -0.412944852927091,   0.245179063439689,     1.72955817989149,     1.67099730539817,    0.18766381702644,  -0.283611376945371,   0.686779087574742,   0.905064265563895,    0.765967915976575, -0.0410520223413907,    1.51171079155376,    0.718756763904366,   -0.821708146060393,    0.50234223621863,   -2.11983441513135,   0.748176433090443,  -0.869387621013225,    -1.66318758520667,    -0.40398049081909,   -0.544448628769274,    0.344907334668953,   0.573407762486937,  -0.680486321714024,    2.20798222218406,    0.616017410030352,   0.764444556679586,   -0.389023767532155,    1.15305532248777,     0.90429346532004,  -0.953871513946094,  0.0225598675334932,    1.46195822050016,  -0.965406631821685,   -0.044090271581282,   -0.319211879877217,  -0.226986669320353,   0.808043339986812,    -1.81732318496419,   -0.165086221014642,    2.28564205323546,   0.797932250756203,   0.296590308667897,   -1.03761187293862,   -0.155795262456675,    0.225811532500821,
        "Group1",   -1.38886070111234,   -0.485435235846668,   0.107774744885547,     -1.03435936093915,    -1.66315703066738,    -1.12897739800683,    2.22353430190807,  -0.0583921654073717,     1.01035303245212,     1.2586221252136,   0.869519306648764,   0.450085791644612,   0.328096015484134,    0.832287843010755,   0.199953219832439,   0.555437989150677,    0.129347296958262,    0.489530922514731,    1.09984502312187,   0.852443088824704,   0.449296011237588,  -0.160670914154826,   -0.269943621830999,    -1.74023733047524,    0.377362269645537,    0.154762656644616,   0.254936081717929,   -2.19243732797149,   0.766845014645972,    -1.44156317991408,  -0.917135166591924,   -0.460092848631245,   0.969349157258382,     1.13865742762799,   -1.24089171441291,   0.760060847485706,  -0.184626753951705,    1.70425351971367,   -0.992193431605077,    0.258135510658443,  -0.272388059455222,   0.524068585979805,    0.500040679122927,   0.0879751385928528,  -0.535947018691219,   -1.01607550028687,   0.377294511198291,   0.281338992795805,   -0.130185921231863,  -0.0691860441674244,
        "Group2",  -0.278788766817371,   -0.504217130687904, -0.0841081005055806,    -0.630731953970819,    -0.75053344179229,  -0.0879313317770513,   0.273376064144465,   -0.537063784608919,    0.223521215874458,   0.523517780908964,  -0.544355284698977,    1.04522160610504,    1.07808996004782,    -1.90545752247312,  -0.533305600527376,   0.914878801249372,    0.701641308893363,   -0.299277458909478,    1.88650483041417,    0.15437457231326,  -0.870062520443655,  -0.142616786605041,    0.790790959773878,   -0.452821278920118,    0.403728160580446,   -0.766441731925565,    2.67214420120392,   0.625987094854832,  -0.284191743792878,    -1.70176482285391,    0.23739451514297,    -0.26588619338727,   0.637303157074265,    -1.45233814369233,  0.0815500958017237,   0.245713332088109,  -0.190168268382486,   -0.81581184165478,    0.575852522768862,      1.1163642663612,  -0.253790438243238,   0.356117774366909,     1.06354635357899,   0.0858522002455114,  -0.189088750770531,   0.246453295107586,   0.500586036593106,    -1.8380879472145,    0.167954403268229,    0.179468198755704,
        "Group1",  -0.133321336393658,    -1.66109907991481,   0.495619641604594,     0.586807720012995,   -0.777351759181508,     2.24190369331262,    1.13078479452828,     0.74728669616574,    -2.20648459320962,    1.11545427747996,   0.628803235377603,    0.14962903443744,  -0.060315553702501,  -0.0208366761944145,  -0.266032317684011,  -0.553396624279516,    0.526697831887448,    0.658254898574355,   0.811253500689395,  -0.971861640205416, -0.0977479313579405,  -0.765210967844204,    0.840608638772999,   -0.586087506559595,    0.170236937543032,   -0.752915043322023,  -0.134495017662124,  -0.415461682891878,   0.151645292541353,    0.557212957800765, -0.0446890666120593,    0.501441363321569,    1.77216769250851,   -0.626353321542115,  -0.813076911449766,    0.14139134685168,    1.24329480266288,  0.0505031847282846,    0.135781237800526,    -0.77210829956962,   0.415776373443036,   -1.60495501333129,   -0.565202660570903,   -0.171564167050283,   0.657250840978623,  -0.638881930290301,    -0.1701444604447,  -0.327976346867035,   -0.954041390839007,   -0.899070862943706,
        "Group1",   0.635950398070074,   -0.382333726873818,  0.0374151861179653,    -0.416322656183652,   -0.722569699859602,     2.04131317075049,   0.838669374060099,   -0.487257835389733,   -0.954585618553158,   -0.95750224217047,   -1.42233445794539,   -1.14106715320069,  -0.243518761963125,   -0.408933912448218,    1.08414781411867,   0.298376089510017,  -0.0205130989546023,    0.832409549670791,    1.41824380879396,   -1.10142783592314,   0.893100213716266,  -0.659800571317015,   0.0329694848504644,     1.14791904431639,    -1.10107992122072,    0.524270675654365,   0.111574061825906,   -0.17630383376965,  -0.781106086643039,   -0.750511117127875,   -1.11855030356248,  -0.0523528269896142,    1.17831056462201,    -1.93207557597691,    1.06478465880181,     1.3405773256748,    0.18558749818315,    1.81833471172887,    -1.01208196057172,     0.11259430625395,   0.572441869624907,  -0.322682059625519,    0.944092998938886,   -0.147076213012955,  -0.167127618066899,  -0.602284587925851,  -0.551333959150525,  -0.575331411843572,   -0.319356263078315,    0.736943274776188,
        "Group2",  -0.284252921416072,     -0.5126502578778,   -0.13208803695591,    -0.784887809505321,    -2.18883459914707,    -1.71980033672145,  -0.654615277878206,      1.3729077814795,  -0.0685730672102366,  -0.124405579855432,   -1.22751263333428,   0.802499402419657,    2.24142256068828,     -1.3763863065768,  -0.180745479625044,    1.10637953965214,    0.438251047306971,    0.363463261222694,   0.439169901702954,  -0.690244888297098,    1.35091509526625,  -0.307405440413442,   -0.238163753848546,    0.457363259644693,    0.402469699291095,   -0.355425297900245,   -1.01000268728493,   0.665259163558917,  -0.957398363247324,    -1.97093294572214,   0.576705022824006,    -1.35217134346927,    1.10070263616134,   -0.239061590311605,   -1.04901921849595,  -0.749105637416039,    2.27102227928726,   0.233738106743284,     1.00402316383581,    0.531562239371635,   -1.81823624118953,   -2.16145939152144,    0.973098936350998,      0.8500782782269,  -0.536767000075604,   0.549106639701504,  -0.303586949430775,   0.659639611766684,    0.810850422501062,    -0.74525006428211,
        "Group1",   -2.65645542090478,      2.7018910003448,     1.4767874235521,     0.163416319486097,    0.213418550286554,   -0.356906656122387,   0.953960978479396,   -0.377672360646221,     0.76130590156527,   0.191737829049968,   -1.67410551574443,  -0.728716530969446,   -2.03599297085583,    0.727430374393256,   0.251555319378233,   -1.32914958483242,    -1.21052856570154,   -0.398645658616952,    -1.2775016086011,   -1.58363492221125,     1.4889703943085,  -0.881927450206018,    0.263552286150818,   -0.587806362058572,    0.425816177210946,   -0.260266497121109,   0.887879801316048,  0.0498835161725022,   -0.30434111795109,    -1.32446345093933,   -2.30174221004384,    0.308578530105713,    1.37694807585475,   -0.500271500433461,   0.516009325167413,   0.776584537569481, -0.0515549198891902, -0.0287897691741464,    0.876095886998526,   -0.422902650617128,   0.953336849161407,  0.0190967022825058,  -0.0171660701106577,   -0.186019562784106,  -0.333439039169432,   0.124094839861073,   0.529529239210803,    -1.8434448893338,  -0.0575533561695966,    -0.92842858375266,
        "Group1",   -2.44046692857552,    -1.36211623118972,  -0.217030210092104,     -1.23671423510935,   -0.631922936254832,     1.53328049216229,   0.352951465489323,   -0.616152614118394,    -1.17990419995829,   0.272217250603347,  0.0843984822448787,   0.527209285728481,   0.390914465082838,     1.23413078123709,   0.369542235154893,    1.00169412888602,     -1.4044199438289,     -1.4979299895057,  -0.861373205211443,   0.137766066513836,   0.371067212847268, -0.0953451587484263,    -1.59178517406521,    0.227914940694947,   -0.283128718862383,    0.507208110031767,  -0.307217559138982,  -0.111450292883659,     1.5308786534036,     1.07553289349939,    1.54401138418949,   -0.366996403813651,  -0.717265373449893,    0.987471730369109,   0.985746984418363,   0.228181606829711,   -1.61554882919585,   -1.13535799444069,   -0.692968115760895,    0.148623992007772,    1.34424787271312,  -0.992704380579596,   -0.359927350868906,   -0.835441534293473,    0.22290414826286,    0.70955825469573,  -0.385529572230861,   -1.52287546338822,    -0.56827358823646,    0.429195955111476,
        "Group2",    1.32011334573019,    0.137256218558607,   -1.28360220409223,      1.04587377623667,     1.52049119383216,  -0.0382440966102368,   0.206599292649613,    -1.16812505107469,     3.21119895676729,  -0.693814463673255,    -0.2061256639704,    1.67347877221231,   0.384813342899653,   -0.553224405877467,   0.407034259389767,   -1.40930387375741,    0.720749157209312,    0.114628175272466,    1.88698587497109,    1.50234395496283,  -0.214473243512569,   -1.27596937307411,   -0.376235068846935,    0.134147741846246,    0.553632072115556,     1.14320521055163,   0.133164992636376,  -0.529151371898205,  -0.478305936644692,    0.175835094185016,    1.19632123896946,    0.760815256528283,   0.688512737577945,    0.415421227242454,   -0.35165697798206,  -0.736400489379546,    1.05795583994723,   -1.15737781092832,     2.68180948338679,    0.399286308762999,  -0.754470215261657,   -1.43976540953535,   -0.190184285527522,  -0.0945247655139992,    -2.2417021676314,  -0.823690362514076,   -1.92638338710271,  -0.265682623672842,   -0.464012178479885,    0.560469443656528,
        "Group2",  -0.306638594078475,    -1.49362506731629,   0.385667890443402,    -0.484595416218709,    0.795955949415082,     1.59741324232643,    1.00111323431025,    0.328640358591086,    -2.55382485095083,    1.47917192085213,    1.44187164028206,   -1.41882802027083,   0.438695599541397,   -0.229190177928735,   0.492505019245782,  -0.498781024681268,   0.0860355032767252,    -1.03781661733663,   0.704087313182904,   0.192881587148273,   0.455494589939145,   0.375584983964806,     1.81252714991038,    0.329327772114258,     1.26435623247709,      2.0668175182942,   0.945326369680402,    1.61586225377977,   0.275964288525917,    0.207924799285704,  -0.201676879864589,    -1.20877829147781,    1.26810145678412,    -0.29611631915228,   0.451749228471749, -0.0704274811359867,   0.361894756181958,  -0.547340906138225,    -3.13899312896842,     1.18545205531744,   -1.88690223703747,   0.169291552863872,    -1.87755309426937,    -1.26813823932045,  -0.642793087067836,  0.0867371535805039,   0.739343544604603,  -0.891136863522718,     2.49626913723505,    -1.57715910014466,
        "Group2",      -1.78130843398,     -1.4704357414368,  -0.351512873529092,     0.189128811680665,     -1.4535295651328,   -0.333585393309883,   0.747451991640276,     1.46651062744016,   -0.235933949334065,  -0.611767021642771, -0.0417821033853644,    1.56191080116889,    0.55814090204657,     1.71146198892227,  0.0546325790523077,    2.62275685248845,    -0.13161704140846,    0.645978871261567,   -0.66772052533203,   0.527154734523825,  -0.258111110256068,  -0.469230372596356,    -1.73809968261789,   -0.297512213642794,    0.327802463194629,    0.769866343085377,    1.52568672984904,   0.139510593333388,    1.29277985593516,      0.8932027658822,  -0.432271579852631,    -1.90855673202378,   -1.87208877844442,     1.36222173924555,  -0.593572178730932,  -0.376126589747127,  -0.265876705750517,  -0.433572715922771,    0.645956605503056,    0.919095331882198,   -1.63915999611165,     1.8248258610762,    0.560349532587586,     1.71872324145718,   0.129506779309632,  -0.178418195109861,   0.235654540740689,   0.374954755730091,   -0.681539758081261,     1.34443426699639,
        "Group1",  -0.171917355759621,    0.124702386197007,  -0.521796093356269,    0.0510063315749732,   0.0983954210058388,    0.604985923915378,  -0.626574836723139,   -0.356009545088913,   -0.259562643261435,   -1.61430997435935,    1.35375447776378,    1.35316100891808,  -0.276406382977446,    -1.64980790329701,  -0.708674076161911,   0.510665566028528,    -1.67605197893984,    0.772845400058577,  -0.705714342057153,   -1.48320629120238,   -1.00292375210412,    0.79893320361921,     1.62911115074531,     1.18498797306452,    0.765106373309395,     2.00199794550677,  -0.247450568194144,   0.119583697425689,   0.424010706580774,    0.198609916658263,   0.346948643890299,   -0.497749386024871,    1.24808294812689,   -0.144296461718731,   -1.13649526825212,   0.663223068581971,   -1.25578140173536,    1.66248593383382,   -0.480610133856287,   -0.394769701294296,   -1.91281989340237,   -1.58444178208245,     0.33538474743254,      2.4968402752067,   0.500683932489197,    1.02363816801281,   -0.67613702358444,  -0.270247085865336,    0.639024315794198,    -2.02365521848897,
        "Group2",     1.2146746991726,   -0.996639134884037,   -1.06813120068717, -0.000240668886441977,   -0.593770984233154,    0.224241239250251,   0.395223685936714,    0.261467641877431,   -0.663366916619193,   0.402490110590671,    1.94522527592283,  -0.528696776691558,    1.16628807898223,    0.744220785437819, -0.0582707524435477, -0.0908431942191986,   -0.569497990768113,    0.316014158120416,  -0.920718579914376,   -1.53920072330941,   0.844143482797941,   0.426288199258715,    0.528105441488507,     1.30953538662527,     1.28257345881025,     1.27162090872777,   -0.35660370110431,   0.979865755338673,   0.527765253770584,    -3.18128256470893,  -0.485377933779251,   -0.637044510630347,   -1.07730040944452,     1.31572787554448,   -2.33497178127181,   0.410695883940059,    0.87648416717228,  -0.563130851439488,    0.192807393685871,    0.609240909110271,   0.308721061757311,  -0.873830017616974,   -0.153022777564646,  -0.0252063011042785,  -0.980687867797905, -0.0279217867481935,  -0.234396797207434,  -0.571192071610369,     1.28337273160955,     1.01709870131519,
        "Group2",    1.89519346126497,  -0.0018226143047082,   0.428365903266692,      1.80938204244287,    0.888281168634515,     3.22906949548006,  -0.892167954045577,    0.333328855175731,   -0.318990710826149,   0.664555447289484,  -0.490938233708141,  -0.251272775479278,   -2.45427723493739,   -0.314021323980916,  -0.963421822237506,   0.978765679210879,    0.192205150896545,    -1.03811282479823,   0.148473291996029,  -0.896432886914323,   0.694658775896635,  -0.512132013193506,   -0.360444186597554,    -1.17045526511543,     1.65888693382934,    0.333520245850298,   0.207968407569953,   0.379384347932197,  -0.653829982143573,   0.0196831947042364,  -0.195306080234756,    0.676231932030489,   -1.47416956665685,    0.666610766445118,  -0.926597259630885,   -1.83184901351771,   0.592634666890485,   -1.14555224504636,    -1.04925616100414,       1.552754323222,   0.634157592046035,  -0.195780946959777,    -2.71848745728651,   0.0070325800033662,  -0.598420796598819,  -0.796934682282425,   0.404792586245275,    1.45087454017081,    -1.06918610430193,   0.0666759027743099,
        "Group1",    -0.4304691316062,   -0.428258881425815,  -0.174018234426995,    -0.825327957109945,   0.0530704154986665,     0.92045256677252,   0.630818410091773,     1.42219324030954,    0.742395157572315,   0.944127070994937,   0.388439074944612,  -0.685847686292498,  -0.805566259454567,   -0.115310841404454,  0.0933932966058741,  -0.243808656888315,   -0.486322920752822,   -0.755137290088854,  -0.250017361132774,   0.721069979748221,     1.2610037476473,  -0.347515536975732,     2.23761689061182,    0.996118866300114,   -0.480729813134911,    0.254072676090529,    1.20925334744545,  -0.880212619427024,   0.121675552673985,    -1.39417140470677,   0.229797411715838,      -1.869411030258,  -0.102761252843793,    0.661363775992788,   0.395171601492927,    1.64842382136271,   0.271525680875784,    0.70929132488924,    -0.24585186926655,   -0.628994863204225,    1.47396772275126,  -0.706652682485904,    0.292217786590762,   -0.981715100072424,   -1.68698472183606,   0.718795641292891,     1.6452840090843,   -2.07041054435924,   -0.366263709420238,     1.17698600986258,
        "Group2",   -0.25726938276893,   -0.613671606449495,   0.515667728648029,      1.14547045222799,   -0.557023625844656,    -1.20653906921592,  -0.432705183284567,    0.663876600666173,   -0.874292675785773,  -0.946260797708288,   -0.84489325918598,  -0.570367652254122,  -0.119144550620025,    -0.61097434277214,  -0.347901133459108,   0.621808959213633,   0.0812840129938752,   -0.491504309692582,  -0.941768954111299,  -0.884501944686544,    1.66655928933767,   0.609392746386973,  -0.0401996174749625,   -0.746997016690059,   -0.407834514587087,     1.93091427212792,   0.116558887074206,  -0.406452972046551,  -0.986863054729454,   -0.933235885173988, -0.0946537580368488,    -1.06855248625586,   -1.71486614730381,    0.906720372580947,  0.0741714005493914,    -2.1329179344463,    1.55327347117647,   0.160234692884093,   -0.613729291010653,     1.41924953870264,    0.32357209555769,   -1.04368410538297,    0.565322207888516,    0.307234493729012,   0.462985502852242,   0.525314007375558,    1.07107386863872,    2.39516716185455,    0.414995691392273,    0.572207833160936,
        "Group1",   -1.76316308519478,    -2.02467784541911,  -0.234365277305921,    0.0315731875532431,     0.43839703617272,   -0.603881169163268,   0.452138644218517,    -1.07365515569531,    -2.08281376630328,  -0.248288449238896,    0.73799036787109,   0.579631381546157,   0.163216234138794,     1.09669537901904,  -0.118334438145549,  -0.344595219846322,    0.384897246784297,    0.147225745107845,    1.21419901863892,   0.558598525708553,    1.47185793808934,   0.735464318036699,       1.894125331564,    0.221867656465582,   -0.328918791729082,      -1.012929867412,   0.192066193440929,  -0.777125159688669,  -0.755594462248607,    -1.62904088146867,    1.71019954048516,   -0.126005415934356,  -0.774401637213465,   -0.620599459294388,   -1.05649333360304,   0.687006166808365,   -1.06380687634054,   0.113352593811487,    0.497692038896738,    -1.37066534309718,   0.923510125090382,    0.61000173520942,   -0.874218964168323,    0.979590774747593,   0.632984575305104,   0.815408353257702,  -0.606306600372966,   0.230249637780521,     1.21511383357618,     1.47909386450566,
        "Group1",   0.460097354831271,    -1.22474795035999,  -0.658503425821771,     -0.83520580530672,    0.152608158642419,    0.370235284622062,   0.367999045196345,    -0.69690177466674,   0.0937679028102175,   -1.32843646853908,   -1.07976033128386,  -0.898959005252115,   0.406479507762917,    -1.12716761108376,   -1.09909095717492,   -2.35522454584149,   -0.137501971038181,     2.35650304328533,   0.018566433000226,  -0.218737504846289,    0.78931570508443,   0.476708560673323,    0.024804649937664,      1.0009452311825,     1.10107658785062,   0.0644444403932075,   0.786616109492444,   -1.68350202776482,   -1.16098995844004,    0.369097639109454,  -0.335749000921179,   -0.736284418428665,   0.847553967889695,    -1.41157628682664, -0.0775545035183967,  -0.748761646665192,   0.206822497346744,    1.49521350608348,    0.456841757760867,   -0.897031020178635,  -0.556882439326111,   -1.00719181216564,      1.0090338680072,    0.780711033538671, -0.0741200109700842,   0.170546464220667,    2.46543895780787,  -0.726893104262331,     1.13686422127868, -0.00109100951474444,
        "Group1",  -0.639994875960119,    0.179516441117938,    1.25023660407872,   -0.0687636490165125,   -0.164617581749564,    -1.90100064667961,  -0.270387489661909,   -0.746130456934561, -0.00181981200279561,   0.844763742098917,   -1.02647387624363,  -0.190329887912783,   0.639339995644309,    0.962609492438297,  -0.283076412422231,   0.472387633353643,    0.427593109239094,   -0.920668767105904,   0.757831699457548,   0.383623482386597, -0.0364542711833432,   0.328285766781953,    0.553425403100445,    0.494143258559294,    0.581717960782718,    0.192373891357855,   0.739840689710885,  -0.166982560101955,  -0.442801523619572,     2.28565638502981,  -0.875324824335344,   -0.191241809184488,  0.0832352366570336,    0.810244286891991,   -2.41603024212657,    1.06911275932534,  -0.248933255655566,    1.02323662606114,    0.730374039844885,    0.137112823194629,  -0.992930853628641,  -0.161783123191246,    0.577055109325141, -0.00765646730584681,  0.0279615662680733,  -0.837658538121657,    1.29707345786367,   -1.10444665022195,  -0.0667885949517715,    0.854956683201155,
        "Group2",   0.455450123241219,    0.567620594423535,  -0.271763715111397,     0.746771687012467,     2.01989062147597,    -1.80440994496324,   0.465512617712979,    0.141572872132219,   -0.013100652371574,   0.347696732438648,   0.288793361578875,  -0.143903377346461,   -1.50851763737235,     1.40646401623189,   -1.08973467284561,  -0.511480194786914,   -0.243064448539363,    -2.15684778320885,  -0.380062699996006,   -1.03912011024684, -0.0912832766425019,   -1.78126747525362,   -0.574350945442218, -0.00844441753463621,    0.957779202757363,    -2.34002446260473,    1.08669203144834,   0.593948229116086,   0.334947784039575,    0.486544869581778,   -1.13255449171348,     -1.1983002633847,    1.28508496858323,    -1.30099800324336,   0.809519878482719,   0.396829329884725,   0.515388673918764,    1.17446162052015,    0.399518813185011,    -1.70437576028005,   0.267362681279231,   0.980051876335626,    -1.18799741203433,     1.25856749633181,   -2.51209948928412,   -1.48539617991793,   0.488910050373438,   -1.06621061115724,    0.364270046772317,    -1.10461932862212,
        "Group1",   0.704837337228819,   -0.492877353553475,   0.947951995875196,    -0.425518734394604,   -0.529385886317261,    -1.12182260635522,   0.574356225626969, -0.00394722073065307,    0.667968074558104,   0.913762586431107,  0.0908113192871749, -0.0965726512875554, 0.00767060439702689,     -1.6416495088997,  -0.405665544099862,  -0.573602199756116,   -0.318352827853891,   -0.120400049561303,   0.174948713347219,  -0.948992248570827,  -0.412862939041902,   0.119396421345399,   -0.928337006439504,   0.0961369855328748,    0.301421804337359,   -0.351765901032242,   -1.95280729969486,  -0.518159140749171,   -0.10065856814523,     1.93215222070259,   -0.56602063273169,   -0.824254618506077,   0.276044917953572,   -0.903611801788592,  -0.869749853294244,    1.38535325921297,   0.442785820060402,  -0.244503756930785,  -0.0861377871174699,    0.320308058794637,   0.337202940545064,   0.361942258956084,   -0.958594137083384,     1.76683471162832,    1.41348402080082,    1.10055629584881,   0.379561016004508,   0.715481491168421,    0.194713080945651,   -0.108195914327519,
        "Group2",    1.03510352196992, 6.28840653511241e-05,   -1.20158243010894,    -0.772082235193457,   -0.470786972984042,    -0.34792960655914,  -0.230699990157411,    0.367937501091765,  -0.0131677029521626,   0.608274553380681,   0.262623176711222,   0.181446715722357,   0.524168022000385,    -1.12690419254923,   0.526907259597763, 0.00379720372860315,   -0.254106393508011,   -0.839244329563709,    1.03352330902476,  -0.104160953983452,  -0.781061198320081,   -1.41829537201652,    -2.00042544129482,     2.25070523918321,   -0.288461063573085,    0.346590938682391,   -1.18242682652454,    0.44119836360764,  -0.975536842960497,   -0.232129022732062,  -0.974384403128723,   -0.919532671174568,   -1.71114274542409,   -0.218743464648836,  -0.125077441843527,  -0.178080118436893,  -0.117116618623996,  -0.166932131005799,  -0.0963810493728022,    -2.13104361809747,   -2.07330759695566,   -1.60565791906829,   -0.220745542875477,   -0.311547126334333,  -0.303219537073222,   0.935247383136132,  -0.494899479670209,     1.0160232041479,      0.2649364865303,     1.40896855932181,
        "Group1",  -0.608926375407211,     1.12288964337997,  -0.466116096375502,     0.152764106747895,    -1.54593692401752,     1.23890214863198,    1.17224250830245,   -0.657342914697247,    0.776047030476303,  -0.607547987804487,  0.0693349127912537,    1.59657420918631,    1.32633587157079,    0.591545480502423,   0.240419981775496,    1.34255092952781,    0.638887430163066,    -2.17243990871478,   0.675723995432471,  -0.208711102723908,  -0.390092785411881,   0.076034377653877,   -0.622068696299165,      1.4366346913565,    -1.45615158789359,    -2.82894105870644,   -1.18067847791903,   0.755600865049457,  -0.973216625621073,   -0.537445056633885,   0.945082340846264,     -1.7438683437219,   -1.14955002154367,    0.564587997180924,   0.411151618784541,   -2.42988067251115,   -1.49784147274197, -0.0841155041461892,     1.86373382233984,   -0.742451433401934,   0.937936932333045,    1.31105640447589,   -0.990504323908094,    0.426973900055736,  -0.599311133860702,  0.0386837713926043,   0.542065486479523,  -0.699008020065035,   -0.189154595341058,    0.708061848649616,
        "Group2",    0.50495512329797,     1.43985574297619,   -0.26935139515318,     0.988596845178799,  -0.0405267232951771,   -0.274197564852279,    1.39270270673312,   -0.376346670161052,    -2.01073533263526,   0.179658070871844,  -0.528643818856825,  -0.451331739893457,  -0.113567734432564,   -0.956309119505936,   0.898362457249366,   0.295461511559413,    0.821065383166085,   -0.874307976154287,    0.94128124291257,   -1.78873019525217,   0.613837622009258,  -0.660833242210851,    0.727145566485242,   0.0104077495384871,    -1.70465154066219,    0.367872703584524,   0.376981101876066,  -0.112960860177346,   -1.34078652646553,    0.786101903375548,   0.247741105300021,    0.383037424261768,   0.159786319641181,    0.609256391771582,  -0.850435305046767,  -0.232011957059107,  0.0472006059695206,  -0.826498278320729,    0.851283491078538,   -0.951941765720054,  -0.613064599652876,   0.539388173408711,    -1.04605522165573,     1.15457522800862,  0.0196621914579885,   -2.39486002499437,    0.66487153712751,    1.11827526043437,    -1.85752545366634,    -1.48973621490687,
        "Group2",   -1.71700867907334,    -1.09711376840582,  -0.390965408130861,    -0.073458334672174,    0.890356305470676,    0.162380715558193,  -0.661991255709585,    0.741360060425085,     -1.1281804949718,   -1.90840941941738,  -0.130202164518766,  -0.794880224800819,    1.59914947839686,   -0.691529886346393,   0.487968126935476,   0.841786943605435,     2.33547908658196,   -0.373579348902497,   -1.82663007251395,   0.537084421086505,   0.384677020333242,  -0.105506046058469,    -1.10218330324535,   -0.320791891518128,     2.01122119129553,   -0.285484066118437,   -1.35679104068327,   -0.47462538771123,   0.414102402054408,    -1.25237291022481,  -0.104674620432457,   -0.541069423262346,  -0.427212686915226,    -1.83602086878766,     1.4665510712084,   0.105937161925274,     1.4802578676094,   -1.18949684486068,  -0.0592854618366041,      0.9339879197246,  -0.112092904178992,   0.218794224103804,     1.35964791465518,   -0.287162114791727,   0.602632304715408, -0.0962800575605345,  -0.121892708410495,   0.225997274235179,   -0.272458522069372,   -0.600611423948417,
        "Group2",  -0.784459008379496,   -0.117319560250177,    1.34870701199171,     -1.38702655355974,    -2.07138785092921,  -0.0646069097530627,  -0.777369206725014,  -0.0996067564484702,     0.34879957158572,   0.502946257689095,    1.62015874435582,   0.792284349652293,  -0.281528098928179,   -0.445352767351361,   0.111991365197539,    0.62906429822047,   -0.983307557611062,    -1.10219771209642,   0.177204381296563,   -1.94969607009284,   -1.20565664981837,   -1.18008588758692,    -1.15946277085336,     1.84167486726203,  0.00396133245276825,    0.442733260452948,   -0.22860827167565,  -0.702121930359935,   0.274162429825081,    -1.32416495483461,  0.0277616799037131,   -0.555941097834846,   0.907002203909007,    0.244146609668066,   0.306878543209711,    1.21756978398376,   -1.96455496249316,   0.393351860980975,     1.50066953016993,    -1.09948288223523,   -1.01392542362372,  -0.129966893255263,    -1.15592399628206,    0.132768822126551,    1.57368501672031,   0.819046378256676,   0.461896904728203,  -0.625930925461728,    0.288067785289902,    0.127987874061411,
        "Group1",  -0.850907594176518,      1.2014984009197, -0.0227647012984126,     -1.30667590437536,   -0.250065120073019,   -0.705237097025142,    0.51353857890878,   -0.654289878607095,   -0.352898482096924,   0.968899153478499, -0.0178951233234706,   0.380472299761027, -0.0498981389105064,   -0.344484228326568,   0.998313347136219,   0.101598399463067,   -0.707457440006258,    0.715659860663444,  -0.191807861947269,  -0.415234461553216,    1.19785122001404,  -0.164359186462737,    -0.43890563975272,   0.0899247252253415,    0.558221906568822,     0.71767113004586,   0.423256564904682,  -0.279371035837961,   -1.41396295051925,    -2.96823317332063,  -0.907276482340544,     1.10895853127751,   0.150898962830839,     -1.7713618338249,   0.429680832800053,   -1.17176359943771,  -0.538555626716068,  -0.180783643152807,    0.451022941536234,     1.29711010122401,   0.636392746769097,  -0.865052891545505,     0.26084315779637,    -1.10623499986617,   0.388557997669753,  -0.491515207746877,  -0.863652469560376,    1.33093703645417,    0.381455103290408,   -0.868975772211247,
        "Group2",   -2.41420764994663,   -0.469729580566301,    0.24422585110345,    -0.768395325077939,    -1.18165042665332,     1.36219726875099,  -0.913312238041272,    0.971164374061271,    0.944774597917623,  -0.875737125773327,   -1.31848939894929,   0.235787982992453,   0.160214127321124,    0.703698185246122,    1.19171680875342,   0.671120874661013,    0.644149101349918,    0.907640305684175,  -0.650198710009829,  0.0551296705930179,    1.29114126665685,     1.5194407743176,    0.159134206763553,    0.402792818116791,    0.694493685600807,     1.42389508632609,    1.94090825966462,    1.56420974922256,   -1.68193057318907,    -2.22571817714071,     2.3509337520258,    0.667743594836766,   -1.10952726348854,     2.25061026945178,   0.810377064747989,  -0.266475823895061,   0.502786592851959, 0.00218840129337854,  -0.0995630325040558,   -0.811869011460114,  -0.370722808414899,  -0.825638182890832,    -1.55823647505566,   -0.880246859827876,   -1.12489626596291,   0.311656277355361,    1.17209487605869,   0.755160164778093,  -0.0297595351186698,   -0.770532160624135,
        "Group1",  0.0361226068922556,  -0.0524694849389963,  -0.942371707863923,    -0.527108125374458,     1.44193726501691,    -1.09651318808332,  -0.449423805250301,   0.0134963115683865,    -1.00471985252646,   -2.13602453869801,  -0.844560160581277,    0.59098826352041,  -0.502380562405328,   -0.603005764794259,   -1.39938756712371,  -0.138316374561719,     1.63766532994621,   -0.324805133785133,  -0.560696341260001,  -0.701999719088772,    1.48307160252052,    1.82516507817365,    -0.49460068553302,     1.30939370465749,     1.44632123678831,    -1.68539115613733,  -0.241019348067338,   0.091093609568575, -0.0700861139491127,   -0.441654172428568,   0.808769724481045,   -0.693679036361983,  -0.548808731139672,   -0.943008853792748,   0.921172911124199,  -0.454685555577368,   -1.09331277445394,    1.18276728772386,    -1.02102751463047,   -0.338192213747675,   -1.42133301305244,  -0.954139075093771, -0.00714045431300919,    -2.38863342271827, -0.0792878705440688,   -1.03751663263604, -0.0898482493896153,   -1.24044740450407,    0.408812399675477,     1.69363282448629,
        "Group2",   0.205998600200254,  -0.0861072982370896,  -0.729217276509574,   -0.0214270650416246,     1.35789553887886,   -0.228433518546891,   0.802932699103618,   -0.916534667021545,    0.723902732496846,   -1.52282758158501,   -1.10181487249111,   -1.41193020207889,   0.715938048776189,   0.0893504124146815,   0.892147736646772,   -1.24931225315241,     1.22664817466431,    -1.48158593228175,    1.67576579329994,   -1.40383903257398,   -1.22359523581159,   -2.48863985015353,     1.21236784558103,   -0.613254222725411,    0.633468743359524,   0.0417293162320748, -0.0209705719304921,  -0.462187981024542,  -0.460309029288299,    0.124644128489496,   0.784140418846701,    0.879992804711981,    1.01878845500043,      1.6868894561962,   0.544807883194691,    1.50493216814738,   -1.02602611043194,  -0.688825038725034,    0.346607005280016,   -0.829080141784422,   0.289090230395264,    -1.3922237409318,    0.567722227536647,    -0.69004938323951,   0.107542505679699,   0.513595683432519,   -1.82788398254823,   0.841632104460084,   -0.245687552660956,    -1.07374618940762,
        "Group2",  -0.361057298548666,   -0.887679017906432,   0.998068908554848,     0.670498070996282,     0.33450284734065,   -0.347828080610269,  -0.573476850981104,     1.70968856126164,   -0.668832740990364,   -1.11311820788607,  -0.900090143007498,    1.06329579229112,   -1.34578730316321,    0.737494637219904,   0.777958970340806,   0.347635244215357,   -0.467705618330812,    0.594171138863542,   0.430534600439241,  -0.398823930892521,   -0.41317463437103,   -1.65432225038973,    0.292632425911828,   -0.435480084919432,   0.0263703369604992,   -0.632943830350313,   0.235647056296984,  -0.450438751827904,   -1.20714570347743,   -0.349997232679237,   0.170236490795333,    -0.37897335718852,  -0.945412080328207,   -0.338811926433357,    2.36959502355302,   -1.62253834012802,   -1.01203614366599,    1.96360867768691,    0.517299926175581,      1.0766521816494,   -1.64787067570603,   0.532505696903585,     1.11104418692594,   -0.527856748000707,   0.164244787519655,   -1.33149239997633,  -0.455205892352482,    1.33704706202603,    -1.72985213587392,    0.217959234933704,
        "Group2",   0.758163235699517,   -0.444684004884738,    1.25848166459556,    -0.434617038572407,     1.42933808040023,    0.532128619506733,   -1.92812516784833,    -1.16810098994666,     -1.1130401937158,     1.2409838955359,   -1.26108391982248,   0.453917878897591, -0.0056435653021491,    -1.54037944457177,   0.941914516346951,   -2.27781365917161,   -0.678231063737989,   -0.854874687119545,  -0.144606620357246,  -0.110421799564805,  -0.409580866212294,   -1.42085528137192,  -0.0360424610323628,   -0.382106084270801,    0.742875516154548,   0.0300992464318592,  -0.595344815613527,  0.0730966154107931,     1.0404412181286,    -1.90349930252085,   0.159197651530768,   -0.431248632603711,   -1.50031585307676,    0.620713591522164,  -0.603094261358911,    1.05905497807605,  -0.782634176957744,  -0.441910422925586,   -0.639980910158429,     -1.3278948055111,  -0.190245222772756,   -1.36001392024891,    -1.11934473018331,      1.0663108268773,    0.98444414538532,  -0.551782617082327,   0.272339317206077,  -0.212640070558653,   -0.187333955704389,    0.843248468113156,
        "Group1",  -0.726704827076575,  -0.0294448790882381,     1.2488636888101,     -1.11387978331285,   -0.867317850878684,     1.60723456226119,   0.664390833822148,    -1.78103626015252,   -0.342805189366945, 0.00348193506299025,    -2.6258489024829,   0.951312977019787,  -0.540542549739533,   -0.689632292648809,  -0.908802712301102,  -0.986209181193632,     1.69640227133044,   -0.829917536632547,   0.939025712144101,  -0.924078451273399,  -0.451164718262206,   -1.27629656625184,    -1.10261610256618,    0.171328176109932,    0.347303392127326,   -0.129143576065387,   -3.19955843375579,   0.131353009028611, -0.0662050121858745,    -1.15404434196501,   0.678018100413371,    0.166444699682016,   0.565164063059173,   -0.802721086857398,       1.56083962675,    1.15698003542924,   0.359562812057244,   0.781007950063791,   -0.998203710977064,    0.739907498461063,  0.0194040309542796,   0.417999489071495,   -0.745335689322328,    -1.09455421444261, -0.0872647134232467,    1.23567496959979,   0.607610914483794,  -0.591545913982333,   -0.130120091331554,    0.206935689638343,
        "Group2",   -1.36828104441929,   -0.413868849057924,   -1.38063704952533,       0.6071059948785,    0.950651724971886,    0.513814526116594,   -1.60254022379425,    -2.25313244856822,   0.0497793231687396,   -1.23779458599307,   0.669065749190573,  -0.598517713401516,  -0.547073740849682,    0.859793460209431,    2.40893084447621, -0.0595413435522069,     1.54284685008907,    0.149106814964156,  -0.545496749523291,   -1.35724300041576,  -0.564698951728143,    2.07910079937255,   -0.935640286949069,    -2.41656246344689,   -0.628654925909305,    -1.17589928573267,     1.5112784716271,    1.34563639889239, -0.0198577785368134,    -0.78918347437427,   0.434371999584651,    0.140519604666793,   0.182738767924744,    0.116593883188853,   -1.35383614798257,  -0.113958858999298,    1.99862021891536,   -1.13436748209853,    -1.32931604978871,    0.976673150622898,     2.7018310603995,  -0.850258156293663,     0.89568526902501,  -0.0850599489390614,  -0.781784952604271,  -0.222170154196533,   -1.15576960324232,   0.798984409532817,    -2.37751572077173,   -0.177814582420745,
        "Group1",   0.432818025888717,      1.1133860233682,    2.04996069363639,     0.275456968739591,   -0.585011508633235,     1.38237316057303,   -1.35460025745385,      0.6511259695467,    -1.22768196152554,   0.555699118898025,   0.660041509230777,   -1.84194005034614,    1.15144538704443,   -0.376519740675772,   -2.59425017430808,  -0.160759490474124,    0.214527592060943,   -0.976146041384047,   0.138850363215646,   -1.19460448275129,  -0.560010334496702,    1.01553602068229,    0.460837326820304,    -0.41817143658625,    0.958491926298926,    -1.80681938019899,  -0.343587003482767,  -0.423361472072342,   0.615556223378135,    0.899402278193938,   0.780554430230763,   -0.107546272655053,  -0.796728081908326,    0.608067392089781,  -0.508004601076342,   0.855190970106914,    0.55393480042535,   0.273041389468936,   -0.873582293537821,    -0.37681524864787,   0.510971555702922,   0.869526359692787,    0.590244427344547,   -0.415982250479874,    1.39261246235614,    1.42096085799161,  0.0569536657454247,    1.54910827672268,     0.91229420870375,    0.666353495398929,
        "Group2",  -0.811393176186672,   -0.480992841653982,    1.01687282979954,      1.15734706941474,    0.320957522525629,    0.763097048549903,    -3.0179326794179,   -0.532832625602767,   -0.764005910827448,    -2.1831493493599,   -0.25060043539111,  -0.484589533147934,    1.05221968194591,    -2.53508347030523, 0.00686303751409396,  -0.420361520340292,     1.70068829575232,   -0.294684407656388,    1.44686231335255,  -0.528487779287787,  -0.970558066992205,  -0.109612816175039,   -0.332363462610624,    0.707195564900496,    0.164441350143759,     2.12031372450078,  -0.716929115298069,   0.976942283768022,   0.420382969919601,    0.316039999076679,  -0.444567758454349,   -0.251987609311519, -0.0461864850495287,     1.52794183545539,  -0.478311132418979,   0.511139092189725,  -0.808303348930514,  -0.763706558389942,     1.07104687470886,    -1.30089125498605,    -1.2733439430434,    1.03448043626442,   -0.288462279506972,   -0.383489419654003,    2.74527254374431,   0.365370199998336,  -0.100914400619936,  -0.449885967076205,     -1.1051159424841,   -0.484768345562675,
        "Group1",    1.44410126172125,   -0.433169032600729, -0.0267174641382579,     -1.68248085947826,   -0.299396016664908,   -0.624584544634111,   0.831237822230063,   -0.275559356972283,    -1.24618206161788,  -0.247024457097248,  -0.723797316953819,  -0.906846815023397,    1.59802652870266,   -0.857809228617209,   0.118106668928336,   0.988591016328615, -0.00798682964789259,   -0.770974915815347,  -0.332628086150536,   -0.45262688672095,   -0.56282354617343,   0.981518881029313,     1.10616326882244,     0.31180753531698,   -0.034705900963032,    -1.32440568336117,   0.287909147297481,    -0.6309804050454,  -0.327954877427185,   -0.826987275162978,     1.2715164118455,     0.40002038444736,    0.15362674483473,   -0.627075993917891,  -0.898170282231573,  -0.714418985172829,  -0.557018477813349,  -0.737607983989264,    0.468129482172467,    0.725204344924953,   0.376437913312468,  0.0207367874396349,    0.048163466406871,    0.138478429491991,    -0.3003651504219,      1.231845289732,  -0.476390204860624,   0.437068042022732,    0.612495537136808,      1.5796307669078,
        "Group1",  -0.431446202613345,    0.696862576552103,   0.703607778798261,    0.0873190888948744,   -0.278543083293069,   0.0815438004289869,   0.251097088847344,    0.289626972629046,     1.01677397775977,    1.11285692758645,  -0.812181632329413,    2.22276244740438,  -0.263796793108459,    0.816026406926163,   -0.14969732641009,   -1.06961379110863,   -0.817900364802769,    0.392283707078743,  -0.799156272263214,    1.41948519316134,  -0.332036443298219,    2.26134720681062,    -1.63369360485113,    0.350640156782387,   -0.920743815374439,    0.275021593266166,  -0.617472756244325,   0.219751181001007,    -1.1344563021002,    -1.61457054350712,   -1.47339222749877,    0.994170230292134,  -0.766624414368414,    -1.56426674597898,   0.108274523745864,  -0.694971594834713,   -1.08560353078744,   -1.25657614092638,   -0.927321793089823,   -0.970320176942339, -0.0987659900483044,   0.395119304823088,   -0.488926055790903,      1.5025095098193,   0.940070703439003, -0.0665437632093838,  -0.950051574408086,     1.8095190179863,     0.24230360165906,   -0.583880407606718,
        "Group1",   0.655647883402207,    -1.05636841317091,  -0.971385229151864,      1.35336189394267,    0.546115158329532,     1.37607911136477,   0.462293465941329,   -0.466484061790764,    0.723612624058863,  -0.341673237009086,   0.398734336018413,   -0.41346657637618,  0.0324007875469165,   -0.426588909225775,   0.747873287863168,   -2.61364346701511,  -0.0506101702835437,   -0.846305904884495,  -0.548292745132407,   -1.28568114451572,   0.193650109749296,   0.637089923803561,    0.335192800595372,    -1.58686541262596,     1.14805514963721,     -1.1088631832662,   0.920167406912455,  -0.345672485091224,    1.18226830511672,   -0.166432120087956,    1.82601047314349,   -0.393873589955096,   0.364753332338701,    -1.22558199882339,   0.649879562609338,   -2.02251977219747,   -0.71979401765733, -0.0170698956009469,     -1.5818156716694,   -0.887412359318331,   0.220544495588186,   0.276352141875242,    0.712986584937058,    -1.15592439159928,    1.08241285926193,   0.681059674782127,   -1.35925534448218,  -0.242786464324929,   -0.971379214795806,    -1.16208611436047,
        "Group1",   0.321925265203947,  -0.0406984751512149,   -1.09615624155886,     0.724173800683369,    -1.30382115364487,    -1.56126578615704,   0.844792223223237,    -1.60806017494469,    -1.03252713710511,    1.30543834214107,   0.226563573879377,  -0.215673846704644,   -1.55158330768591,    -0.40463684004168,    0.12403480689883,   0.780451897662153,   0.0799210865490335,   -0.843759930930453,   -1.05079620451942,   0.381148939361978,   0.605642856272221,    1.77553654284699,   -0.524657444990143,    0.216521654079693,   -0.389880110029636,     1.50774050493814,  -0.454100665235518,     1.0059050442053,    -1.7107858033122,    -1.77639192189298, -0.0821605442182188,     1.45176227538026,  -0.693518969658329,    0.125967165114114,  -0.820473392742007,    1.58146032169396,  -0.692566843267432,   0.760560550871686,    -2.78399210945974,   -0.686216777211003,   -1.61592686996966,   -1.40690816653097,    0.348591154474638,    0.676586019302704,    0.92009609256069,   0.533263001279274,   0.227434158187342,  -0.361860427127746,     0.24186233076182,     -3.3307353376903,
        "Group1",  -0.783838940880375,    -1.55154482234759,  0.0490504509375971,    -0.832552825764212,    -0.25091446504246,    0.324770660594699, -0.0419715243215621,    -1.94978379604199,    0.557346004122758,    1.79532387144079,   0.421643579753211,    1.06297852007115,  -0.388179430024523,   -0.145769224262472,  -0.778054747212651,  0.0451050735540702,    -1.55957109789405,   -0.961888444288268,   0.252662491033329,  -0.417468601097774,   0.957873599425007,    -1.1475015474698,     1.46337107530221,   -0.114749842879395,  -0.0992632632773881,    -1.76729877966445,   0.855761324504685,    1.39731579966728,     1.3794490444046,   -0.666884015219462,   0.207066157170724,   -0.834997129573646,  -0.343156152059392,    0.259330821064604,   0.359761528557581,    1.29683319578503,     1.4135047045491,  -0.171825915244101,   -0.936595221275909,   -0.934156876357404,    1.68090301749135,   0.804685346315888,  -0.0935614532345968,   -0.693678141249576,  -0.406215218754482,  -0.381406909271378,   -1.10869298062195,  -0.672434404914734,     1.27579067505983,    0.276260473505689,
        "Group2",    1.57572751979198,     1.16716954923568,   -1.19849585655778,     0.732528486768414,     0.17100737371791,   -0.156790316952238,   -1.10557590570003,   -0.340699918230981,   -0.255581423099522,   -1.16783522747345, 0.00483794372409907,   0.620346526580243,    1.76414812218013,     0.71946636806737,    1.41003330549222,  -0.108489158897566,   -0.171497956746292,   0.0110496533565447,   0.327861853995298,   0.092861420787736,  -0.800818438984397,   -1.07932259375455,    0.427178041986581,   0.0203381232290744,  -0.0279660623672148,   -0.888592273848649,  -0.233542837588828,    1.53536108075324,  -0.541005329157528,   -0.307965069586008, -0.0581589957425658,      2.0014571533496,   0.742849337934101,   -0.275286508832528,   0.633324928437982,    1.27035453737285,   0.640962189123194,  -0.265263394261249,    0.477875031833748,     1.65832732814445,   0.558235768607064,   0.775054010807102,   -0.845384979296857,    -1.12948331148021,   0.664502336527224,    1.59602543194098,  -0.792064329484375,    -1.0826704624276,    0.183779755043307,    -1.01052733986274,
        "Group1",   0.642899305717316,   -0.273645701374081,   0.190018998559748,    -0.871926869997213,   -0.403467478747509,    0.877783860734352,   0.563775652330874,     0.17472552733132,    -1.11339175714667,   -1.15228762498202,   0.618983915096519,      0.673066651879,   -0.41652772756372,   -0.491090752219327,  -0.293911808229858,  -0.391224310070966,   -0.418607092832335,     1.21494896542184,   0.855672400490503,  -0.663584535776221,  0.0425486556052422,    1.06794985879243,    -1.02512982017635,    0.892790261937783,  -0.0569888848706201,    -1.21905138661598,  -0.978371478897954,   0.684528247552368,    2.07546679173333,     1.22252541528467,  -0.843052009454205,    0.820293024018973,  -0.285537707961138,   0.0497672155096357,  0.0978159188655356, -0.0160778678538177,    -1.7175207063165,  -0.423995996873209,    -1.19529144352291,    0.614131653946908,  -0.376390838734751,  -0.908145691062996,    0.277606233056156,     0.84732831798785,    1.22705104515592,   0.890507805491638,   0.775830180945342,   -1.35625188887867,   -0.288268153193212,   0.0521830732815136,
        "Group2",  0.0897606465996057,   -0.467845324672254,    1.29770589960467,    -0.453397511229793,    0.104659440835727,    0.750166575180638,    1.30336475581967,    -2.27777756077723,    0.421197439614804,  -0.914455469345649,   0.431133944485928,    2.63370956294833,   -1.16633868878939,    0.475958438418499,   0.610678645005375,    -1.6869995043286,    0.491286818033161,   -0.888878515738284,    1.80176227162749,   0.802827389507556,    2.33570086201341,    0.89175319136426,    -1.30805832132281,     1.44808414754465,    0.555659016748442,   0.0502813662769896,   0.737215963533884,  -0.505352566351758,   -0.20476050301274,    0.895862262639488,  -0.466487279539017,   -0.361525358178745,   -1.66988367567976,   -0.310697724950738,  -0.801183755949992,  -0.581762953398202,    0.82618859480234,   0.689272118280285,    0.305301660949113,    0.338641287474492,   -2.02756608489503,  -0.996020115936964,    -0.28890129987681,    -1.28432033562367,    2.98890253663116,   -0.82457010254821,  -0.515016505863068,   0.593281971433118,   0.0398795727165739,    -1.56106906490804,
        "Group2",   0.276550747291463,    -1.23825232798621,   -1.03387372296475,      1.18753427862908,   -0.318880786734009,     0.30105340384283,   -1.50022093779466,    0.290524480947084,   -0.322950311846374,   0.528728032533629,   0.558312370187223,    0.16611439867297,  0.0418945661851059,    0.573153668052675,  -0.666510079863262,  -0.952704455151679,    -0.53122843123103,    0.218101261446603,    1.40524081174873,   -1.70308264539455,  -0.461867455821985,   0.870096509939708,    0.229601886628634,   -0.252030872055032,    0.901923838993518,   -0.490812951536646,    2.44160362468046,  -0.124233092127789,  -0.551416985520336,    0.203905063037902,    1.51644902909499,    -2.12565181990003,  -0.264390041455333,   -0.421435447880268,   -1.10229315336733,   -1.65357546614648,    1.28077530846579,    1.05045042906015,     1.73266163127779,   -0.576008960512498,   0.397905309906828,   0.362546645148159,     -1.8513267476268,   -0.951203283276817,   0.399669065766003,    1.18924798131828,   0.310196948333655,   -0.29203559590948,   -0.316339818018865,     0.97173397004454,
        "Group2",   0.679288816055271, -0.00776203377732663,  -0.738440754213064,    -0.290145311790079,     1.61834393588343,     1.49281111722931,  -0.606989235119036,    0.422306357473614,    0.880179901191522,   0.835078927048582,   0.495961280672009,    1.90517553753426,    1.24648913025954,    -1.01885957771565,    -1.0598828782705,   0.507414112103395,    0.482220117734896,   -0.656116999607038,   -1.25079179413567,   0.153907072564843,   0.740429906040657,    0.48576246486856,   -0.307021277811913,   -0.597471279167578,    0.536623088234037,     2.38505995846631,  -0.992492651489919,   0.301334745178827,  0.0411968667731968,   -0.215998412229601,    2.07396139462956,    -0.39804944688126,   -1.69995439627627,     2.24620779511287,  -0.851657012572341,  -0.574408772223323,  -0.231344204570623,   -2.19402499653358,    -2.16316306849597,     1.05067558510226,   -1.39689726524874,   -1.08608236477082,   -0.955468599993092,     1.01151549368614,  0.0715461512758006,  -0.479534867181896,    1.02688876308036,   -1.41393186361165,    -1.58517187616385,   -0.226291783572956,
        "Group1",  0.0898328865790817,    -0.80028217795166,  0.0465639394508634,     0.828546144965436,    0.714188601488617,     -1.5254938001697,  -0.292245065656577,     1.29473736320671,   -0.194863606775901,    1.20913697409153,    1.66188574094578,   0.253718401313083,   -1.57797130420835,  -0.0618722344363663,  -0.605838699162315,  0.0188160990067223,    0.536291040049325,    -1.08851584728066,    1.99910885447275,  0.0260754999213632,  -0.698344660682268,  -0.471093692846051,  -0.0838330995421848,   -0.247740839749518,    -1.47118613826484, -0.00438812697078212,  -0.440736144505333,   -2.08736714684124,     1.3170476310258,   -0.488006321935387,   -1.05674676492714,   -0.347597923190669,  -0.526832813660561,   0.0866573729924924,   0.519418173048002,  -0.907622087912097,    1.35882748116687,  -0.502965563297584,   -0.119819499989917,    -1.01644723113006,   -1.18227052196702,   0.175262128847649,    -1.68713584936332,   -0.106991612669397,  -0.948678112117658,   -2.61804602409254,   0.207645142587312,    0.51275917033726,    0.160829909495481,     1.11342070453125,
        "Group2",   -2.99309008315293,   -0.533492329950436,   -1.01759611982611,    -0.291227708779169,     2.96586536983324,    0.910717558486022,    -1.2896833433236,    0.164714018573954,     1.18805498210378,    1.29947254536082,    -1.0550346122045,    -1.4590219672543,  -0.253820471789102,   -0.538305101604451,   -1.05684142085412,   -1.41891037358562,   -0.279324207858902,      1.0911308981077,   0.139278487592147,    1.05586337908511,    1.06536890145562,   0.949629993820546,   -0.165731840611065,    0.774365940151647,    -2.40935940826857,     1.33169035546128,   -1.16938753229774,     1.4203970626931,   -1.80965020341038,    0.602052313710202,   0.355248794893353,     1.44495230883333,  -0.637015796844457,     1.22351387547554,    1.78231561329573,   -1.36553956640524,   0.341239054522143,   0.880319117538282,   -0.975527419817999,   -0.210170203015396,   0.542324933740678,   0.634523421021894,    0.933252713848061,     1.58067688954012,  0.0133995953743361,  -0.221847073936981,   0.077839334291833,  -0.604524842917402,   -0.924235424001103,    0.514568050211903,
        "Group2",   0.284882953530659,     1.28767524558459,  -0.383283959886278,     -1.57636240474791,   -0.795077604559211,    -1.57953202785754,   0.694105848774699,    0.204953840800235,   -0.509764511767954,    1.07573230420989,       1.50832468678,   -2.22724824128035,   0.467830542050614,    0.416954726110764,    0.53310647267496,   0.598171931352236,  -0.0435072647005839,   -0.569227321657799,  -0.386669103439724,  -0.224467114350504,   0.545516821338762,    1.84772759129207,    0.655012558663501,   -0.118587206170082,   -0.365017377779538,    0.820808669126654,    1.59198798945038,   -1.06897934731921,  -0.307988794620669,    -1.39410021352359,  -0.537626676315252,    0.376236073898798,    3.17451978428008,     2.61823281991171,  -0.600027010216181,   0.308299926829597,   0.642236181244163,    1.54835282944109,    0.957784463175755,     1.10298560260448,   0.734721150305722,  -0.268304978918258,      1.5139508755078,     2.70884536477196,   0.706013814600333,  -0.926637575506017,  -0.601473088580168,   -1.71338042520059,    -1.57689362202097,    0.937697576181779,
        "Group1",  -0.367234642740975,   -0.175525870242127,   0.872755411671398,    -0.848815696948922,    0.814365914679913,    0.587716257118581,  -0.599181902897119,    0.604603626725806,    0.219548010873294,   0.939801023514297,  -0.334208656655074,   0.649683551167725,    1.97752999445585,    -1.50827665613024,   -1.55209261464742,   0.786379621743228,     2.38151529195951,      1.6208101305906,    1.85563569044348,   0.496596389373037,  -0.918209320243205,    1.24040742887073,    -1.07483472817753,   -0.417581271100897,   -0.181268484634166,    0.685679030525222,   0.127274716720975,  -0.459351897002142,   0.294561194585387,   -0.354163671111447,  0.0903163658583597,    -1.82111553207448,   0.491205589873476,    -1.32538097725393,    1.47202881872208,  -0.472627502422465,  -0.321210717862453,   0.578006183928215,  0.00494753450098241,   -0.933756564769499,  -0.378504196411471,  -0.143418596403623,     2.35428526164579,       0.198800479198,   0.665694316377917,  -0.407807008274702,  -0.764501945443505,  -0.666540633304246,    -1.94415033053522,    0.557936192540109,
        "Group1",   0.185230564865609,    -1.07178238415068,   0.969545013970117,      -1.0885198619572,     2.09803081013037,   0.0896422960007244,    1.25690664397164,  -0.0191407691689314,    0.370294421364558,   0.163374693406766, -0.0649807438184409,  -0.999249864768557,  -0.615605794843624,     1.53916992776747,  -0.978489465308578,  -0.134633045902237,     1.54803111335561,   -0.686988445583741,    0.42885538447628,   0.399633954636834,    1.02519134367607,   -1.38081421835124,      3.4709096034659,   -0.052426353257736,   -0.149062942660811,    0.515880947876038,   -2.32709865557149,    1.33166610954918,   0.147770817116647,     1.23104957794247,   0.348538284602587,    0.272687271115478,    0.44201615873174,   -0.137758822174659,   -1.03754711208436,   0.446222235667692,    1.44019566135034,   -0.13083383528347,    0.354204596046414,   0.0373396617812627,   -1.64280557175606,   -0.68532621612298,     2.13661687737965,    0.760569649919817,  -0.906183125009281,  -0.602296259309144,  -0.865204839546204,   -1.06934950358275,   -0.378703723581663,    0.211012783762694,
        "Group1",   0.581823727365507,    0.163206882467382,   0.383846665027094,    -0.484290571117173,     0.30098005515257,     0.96726165694984,   0.053508013627363,  -0.0797143473788086,    0.279108393730607,  -0.888138558640392,  0.0810815387134028,  0.0419723836763139,    1.51942160121109,       1.346018088596,  0.0272183551599775,  -0.016386517615323,     1.55476199852898,    0.656996703568632,    1.73079013958977,  -0.646912750685488,    1.12573840290613,   0.474676877291482,    0.294080892384017,     1.35395020283372,    -1.39271469385941,    0.273801847190434,   -2.19677491732732,   0.409776277697745,   0.115951531975112,   -0.813405828015018,  -0.517518995099845,   -0.942807734498255,     0.2001981832427, -0.00266898450538929,  -0.571449343788699,  -0.775157770851509,  0.0537341212031113,   0.607857026905798,    0.176206004043117,    -0.76907614575847,   -2.35363430203608,  -0.310462136836296,   -0.752573791675776,    0.113335188334946, 0.00476971504793765,   -2.44385774047663,   0.354686155682594, -0.0800493864182336,    0.634368333986067,     1.51658512458091,
        "Group1",    1.39973682729268,    -0.36273841562795,   -1.85155566306746,    -0.336311209009573,    -1.08307514183923,   0.0788123529148234,   0.728092517671852,    0.115984464402805,    0.201942437313324,  -0.726160982756351,  -0.448214795538841,    1.77704370004004,   -0.43289519356181,   -0.842855777501525,   -1.71557231699709,    1.40914040823509,    0.058111230113913,      1.1106922152347, -0.0435236741393199, -0.0837627647875345,   0.882800384998406,  0.0123463579876949,   -0.536373846346391,   -0.920651427306943,   -0.679359244378277,   -0.713335909234141,   0.939165264428458,   0.472336504221015,   -0.32333184856328,      -1.526672181655,   0.287301302415267,    -1.70089310223139,  -0.529195211918201,     1.20590945018439, -0.0767891104349022,    2.06068761751814,  -0.269713563078948,   0.217520387392552,    0.230682050535359,   -0.387566229908299,   -1.40018450981963,  -0.570169549397608,    -1.25293572924985,   -0.562871825842673,   -1.08293551279599,  -0.502961774931847,   -1.86214819737199,   0.748247344948633,    -1.52081560880892,   -0.433232872525924,
        "Group2",  -0.727292059474465,    0.590013547987339, -0.0539967368261657,    -0.153357890661644,    -1.00632250180328,    -1.56869983648609,    1.56109806821061,    0.744173364048388,  -0.0129965424313442,   0.407597005613739,   -2.55380695026597,   0.347182677337207,   -1.03101770806171,   -0.669874227807658,  -0.504888026492709,   0.394838698802266,   -0.839778915527164,     2.14072073006633,   -0.73108580813751,  -0.133621200009519,   -2.76807861085069,  0.0870999372857267,   -0.144773495445704,   -0.310771373996955,    -1.81911796861397,   -0.343044145090591,   0.299162155572667,  -0.749698629326992,   -1.14036672389761, 0.000913154019056691,    1.66807499684583,      0.9190367632293,   -2.67716885487045,   -0.328449075698023,  -0.429972380474222,    2.58539637352218,   0.466756268777527,   0.526191223166367,    0.329397305970626,  -0.0538397421329862,  -0.696793174595107,    2.53434623037214,   -0.624828084817834,   -0.717980765062782,   0.406418715411654,   0.962870362552424,   0.419568829487478,   0.992287348258555,   -0.736445210255799,    -1.29784149705717,
        "Group1",    1.30254263204414,     1.43242192773099,    1.06477321433828,    -0.243247228574846,   -0.035414564917612,    -2.00782318401609,    0.26562475359719,   -0.431290603527693,  -0.0908650060774901,    1.68353633925179,  -0.312932535119014,  -0.287097446149789,   -1.13433449832271,   -0.908487448146122,  -0.304922680917571,    1.21987512807247,    0.571123448655483,   -0.830971809132396,   -1.96596407622063,    1.11960385547419,   0.143826578856264,  -0.182368193763325,    0.542130527840553,    -1.05580296818196,     2.63898221848215,    0.468979532578923,   -1.98992669349438,   -1.60169156402432,    2.86131949086317,     0.29515790450453,   -1.08093672458647,    0.601705715750341,     1.8127119312971,    0.314285567309573,   0.178345151589542,    1.49980640309029,   -0.11071137212952,   0.461979537951275,    -0.97239308578563,   -0.188542475976531,  -0.973673476625389,   0.601535968134076,     1.27206446910862,     1.07634568722594,  0.0908270190452244,   -1.68492017327728,   -1.17693365754157,   0.487005333676022,    0.447918828187212,     2.02252934988147,
        "Group1",   0.335848119752074,   -0.992692511109493,   0.813195037411605,      1.89220204160011,     1.30912436085341,    0.540973524238763,    1.07672625920727,   -0.499528951911234,     1.36503136531884,    1.70597982356461,  0.0413831520402976,   -1.92457665210911,  -0.221098125377531,   -0.136540641797694,    1.34607823542665, -0.0450772128729762,   0.0660477825630555,   0.0764058561981353,    1.12686531518852,   0.239220972582604,     1.5198831251518,   -1.26567026582532,    0.634175193192409,      2.2387442557997,    0.546608278218245,    -2.47583251603368,   -1.20413480040692,  -0.791447325580303,   -1.45138694483397,     1.70653756587127,  -0.397851104622374,   -0.400022724222342,  -0.516250386678411,    0.181465253704035,   0.834921341167059,  -0.100192607788636,   -0.25606542122908,    1.50399120650089,     1.28169363205409,    0.965698413257635,   0.321376423697846,    1.12756120883178,   -0.993816376439543,    0.729188701930514,    1.21517392458224,    1.45060876612427,   0.171173448858464,  -0.773574527345658,    -1.28788170924236,   -0.280771388384867,
        "Group1",    1.03850609869762,    0.454650297580283,  -0.190816474104282,     -1.38599833728542,    0.750400486646719,  -0.0733765981084255,   0.210697931679245,   -0.865162076755711,    0.908130568883166,   -1.92616670082608,   -1.73772806133762,  -0.800649109339913, -0.0224146989039466,   -0.501037963291251,  -0.257536690796696,    1.47948784483878,     3.58465949292999,    0.935824446199053,  -0.888084388434115,   0.290602215857855,  -0.171316078021067,   0.331283912940739,    -1.77485606890494,   -0.473062140033249, -0.00615393892940771,    -1.85544128847299,   0.398345738001552,   0.502010547640313,   0.983744020219985,   -0.907496040184693,   0.297208816443405,     1.43747168052874,  -0.862041813735341,     0.37478409203679,     1.0466507568352,   0.647185814663537,   0.726092190740559,   0.353009602570219,     1.52914308593026,    0.625906596890689,  -0.819010373585505,  -0.470251565380531,   -0.708438488507119,    0.472008520170886,    0.15063891156249,    1.52951689120498,    1.26606917740873,   0.484279380891144,     1.50446367636167,    0.953238504171681,
        "Group1",   0.920728568290646,   0.0848980586784873,    -2.6999298085637,     -0.41482430070778,    -2.13836832761242,   -0.571018393558081,   -1.51167352582237,   -0.957757283271874,   -0.609888171401906,  -0.833998015228465,    0.54993965969838,  -0.575617970726623,   -0.32290182802397,      0.1126384468164,  -0.523287300658334, -0.0756837866923921,    -1.93189555365127,    -0.50166670286481,   0.871359260391992,    2.34360141841864,  -0.658144999317951,    1.35172863098665,    -2.06613588468656,    0.906054085480868,     -1.8901394678583,   -0.420507917893379,  0.0447565860236231,   0.717195270520938,   -1.10784132708532,   -0.526613810298107,    0.37342905926644,   -0.312205370263461,  -0.629968970094094,   -0.642525197682587,   0.762496037757118,   -1.40458976481618,  -0.200982022267937,  -0.398902404734734,   -0.150879530345409,    0.817892823041214,   0.472704589780157,  -0.207428502167303,    -0.74678043290112,    0.888964554031627,    1.00672183123613,  -0.947020586730197,   0.515227938879634,   -1.07965145555786,   -0.813281920003751,   -0.306332909990624,
        "Group1",   0.720878162866862,    0.895565582264545,  0.0609666388011166,     0.349081528106831,   -0.700354108866634,   -0.311068459853641,   0.022402259913625,    0.326799971338638,     1.39643722121945,    1.41913251633319,  -0.597273692593322,   0.684205732670356,    1.05222315972554,    -1.87521756309427,  -0.663217798972631,   0.917748457199555,   -0.202832504245977,     0.59485346385118,   0.119893566616341,     0.4162981123864,  -0.154294602086388,    1.63656573626269,  -0.0899069094632118,    0.037916931594142,   -0.266783371165174,    -1.86603756721418,    -1.8661608131691,  0.0433551906169097,   -1.99889265684803,     1.24000855550231,  0.0675844815430184,    -1.68538439471542,     1.0749624618669,     2.57545331864491,   -1.50551867529972,   -1.33411764776861,  -0.422671961211497,    1.02355959954025,   -0.181568669642687,    0.846438126417034,     1.1954171235144,     2.7456733627009,   -0.277310210041919,    -1.13356486953053,   0.590408986990219,    2.29465825850715,  -0.272150175335622,   0.709756653395665,   -0.468393203956805,    0.258262001823186,
        "Group2",   -1.04311893856785,   -0.229778138946266,   0.573751697483578,      1.62844226581541, -0.00905647529298544,   -0.671415067101365,   0.718136206042103,     1.54737222568518,    0.144798373308446,   -1.06410971501924,    1.44774180603655,   0.483457347617138,   0.189541165695199,    0.158546714458315,   0.447221039692659,  -0.344778713742413,     1.48371520427311,   -0.430651169136371,   0.472434944803404,   0.362481077869282,    -2.3830393163367,   0.479932228852687,    0.836802178058687,   -0.175362283023761,    0.820431010197318,    0.113504700739202,   0.752522837991073,  -0.394144346444174,    0.15072249695782,   -0.267901819188712,   0.346634030494695,    0.910952091072493,   0.745689854002288,    -1.14069051222224,  -0.590709411561947,  -0.446729345052682,  -0.542169755678539,  -0.800870910576536,    -1.84093919530514,     1.33169732315778,  -0.445658345235482,  -0.830290714875519,    0.659896700957193,    -1.09760333280958,  -0.849094928959333,   -1.09941501918092,   0.314766217809498,   -0.16400365294094,     1.20696426606273,    0.526532410487888,
        "Group2", -0.0901863866107067,    0.836619068460613,  0.0458035797250989,    0.0885218957136163,    -1.45813348724477,   -0.157340452080979,    0.48945701784227,   -0.968859568864431,   -0.640606771595302,   -1.61357747248045,   0.264868114264259,  0.0139634087073798,  -0.105827608865873,   0.0155626712640043,  -0.319450981926009,   -1.07700265605392,    -2.09851640016451,    -1.13333905267279,    1.26663990982006,   0.531682625476121,    -1.1382970912816,  -0.736315911257857,    0.166240833093532,   -0.361609025278738,    0.778193540049604,    0.470018677123532,  -0.425684374542395,   0.380004825407965,    2.10896809219341,    0.304236349386971,  -0.164571372800586,   -0.675000828576545,    1.32158580355189,   -0.309747123005815,  -0.353384418087923,    1.69061986061771,   -1.39017790544112,  -0.297780153902299,     0.16519261489522,    0.226968255002825,   -1.35312998679368,  -0.642700128605558,     -1.5121388803747,    0.155016187191699,   -1.49130279627827,   0.143670976702823,   -1.65668417491622,  -0.406454687062378,    0.541972911959017,    -1.88416256460521,
        "Group1",   0.623518161999544,    -1.74505586133669,   0.157412540175875,      1.23915070840056,    0.694529646494869,   -0.931305070999869,   -0.17388834587827,   -0.188440426259463,    0.169802259558534,   0.599811088697427,  -0.788782807782472,   0.180243734625121,  -0.602554472532716,    -1.60060346126013,  -0.543778849936917,    1.00160472735829,    -0.25964866605676,    -2.23717155976963,  -0.485316378946902,    1.54804223833981, -0.0872555328125386,  -0.583016619413601,     1.02552557344612,   -0.803621542084907,    0.454092023522563,    0.884594160133231,    1.24417031633511,  -0.622427952571525,   0.629190672836399,    0.470303455680992,   0.189982806585771,    0.137311566647961,   0.279469141307329,    0.416243047192508,    0.69327791161614,  -0.223365145696298,    1.60713541056557,   -2.40109468243829,    -2.25342167258279,     0.65350981979275,   -1.18503067452279,   -0.14161198106721,  -0.0216116895578993,     0.54070797485713, -0.0406862486068376,  -0.394432348238862,  -0.552661954985865,   0.612738368586642,    0.855523295262332,     0.33094699895771,
        "Group1",  -0.953523357772344,     1.68945892131337,   0.431565372868771,     -1.64455553575371,    -2.46133547518649,    -1.98300947947013,    -1.2176994886684,    -1.03000116145592,   -0.157187487420844,    1.73296470538705,   0.167732220671529,    -0.2881232483085,   -1.29601593126204,    0.275973089169957,  -0.279673442488512,    2.29600404077134,    0.334067935887184,    0.514639572443142,  -0.461533586184343,   0.961488300605771,   0.835326720644202,  -0.611431981951386,    0.403188458132936,     1.34157635107538,     1.41005217305168,     1.11360999293018,   0.450349279282091,   0.511387206007391,   -1.63764554215991,      1.2861921743485, -0.0686986351389328,   -0.923241797486208,  -0.115006245548185,     0.43153057070049,   -1.56587278497252,   0.923438510803911,  -0.652838190922449,   0.193998228900719,   -0.203377537798555,   -0.340644344731065,   0.760606964346921,    1.10436615092869,    -1.75457004400806,     1.15080723331547,    2.19531483288217,    1.25948661179934,  -0.268666472042434,    0.35493597329444,    -1.14980244755602,   -0.943592183318653,
        "Group2",  -0.542828814573857,    0.864777978518578,  -0.396549736050212,      1.44635652537848,    0.143289764040456,   -0.219599804249378,   0.646398368709462,    0.908086441860496,    0.100939594546104,    1.93450456245773,    0.25758310820126,  0.0302272228902285,   -1.95932663870655,   0.0549526398709077,    1.06523260036693,  -0.325878115450014,    -0.21963759163322,   -0.341907115162922,  -0.231758337278765,   0.338436178606463,   0.212110868191506,   0.603350043610892,      0.4115921198628,    0.625930654378281,    -1.81106410509648,    0.566850429321619,    1.18280748259793,   -1.10137305663194,  -0.658475714017313,    0.916977260029937,   0.916450207694266,    -1.30445974873968,  -0.250234587572854,     -1.1691369060341,  -0.677897326851043, -0.0495256938434538,  -0.380368509294336,    0.63054874598584,    -1.48901267982703,   -0.115979062343394,   -1.55734809274195,   -3.00102477350675,     1.03546625106255,     1.47704988933306,   0.763238192115647,   -1.25349459868026,   -2.68089203175411,   -1.92351871398073,     1.06335662830357,     1.90365454427142,
        "Group2",   0.580996497681682,   -0.150775988885748,    1.30997822575155,    -0.690560171665183,   -0.391222119127056,     1.04527586946239,   -0.91645602834789,   -0.317381864708129,    -0.97339415414828,   0.532820575670794,   0.912047367450309,   0.271674108529485,    0.21341173052117,   -0.230573354697258,    1.56782874914562,    1.46885612852932,   -0.931771803289107,     1.71787742881929,    1.06035377243819,  -0.610953004269112,   0.641346301404555,  -0.235763339357311,     1.68018682802245,   0.0311307079941854,    -1.10245174108699,    0.546022842611285,   -1.96397811110401,    1.86141559956748,  -0.750308265911284,  -0.0409726646299108,   0.710549614762121,    0.441432625274536,   -1.55717429972123,   -0.150172391372914,   0.665215998411031,  -0.346890884284201,  0.0867430365496318,   -1.72234774234449,   -0.805923131593089,    0.535850478938863,    1.60220703903869,    2.05359382706753,    0.862397608654754,    0.182187910542094,   0.523443744399958,  -0.461954577916793,    1.76506855185261,   -1.98629922477166, -0.00764969714568288,    0.681237475593895,
        "Group2",   0.768178737834591,    -1.44900713013917,   0.470393399873943,    -0.276431085453852,   -0.491164085614075,     1.87732956629967,   -1.25182344242557,    0.179003966540422,   -0.819825275253199,   0.719665756019785,  -0.156872382554867,   0.449158427413426,  0.0253358701112366,  -0.0132162906038914,  -0.643112078958536,  -0.236908933173859,   -0.122240218296576,    -1.11637790865796,  -0.474785704501272,   0.357052050410198,    -1.0321009677859,    2.90421609162339,    -1.06210757323509,    -1.09491334946943,  -0.0191678713168816,     0.23984260522916,   0.746612868701424,   -2.70498912238434,   -1.14513189552459,    -1.28916280671522, -0.0190896861258043,   -0.898687030626516,    0.25959546534259,    -1.39912211804635,    0.95524504180699,   0.199251919612581,  -0.649057964312564,    2.53904641213465,   -0.163240061919337,   -0.337686762629956,   0.279216025367745,   -1.09379605229137,    0.265544767018382,    -1.10108235737537,   0.639752697916849,   -1.48844389104682,   0.328554648876665,    2.06490401472519,    0.482883485113326,     1.22175223046536,
        "Group1",   0.463767588540167,    0.643008700041982,    -1.2426702705746,     -1.10941875989944,   -0.283647452452051,  0.00260619595716637,   0.594927718405501,    0.348028187729177,     1.36291896902543,   0.560093385755184,   -2.03337570844709,    1.82762765843039,    1.36502318785994,    0.384949196022327,  0.0205217485106878,   0.923493117890428,     1.33852842346176,   -0.488479619162847,  -0.175510280957714,   0.141508679877188,     1.4857706537531,  -0.268291279315417,   -0.791235649678155,   -0.486414065558645,    0.149303719680044,   0.0341353438230838,    1.05132374710196,    1.41793781636752,     1.0276132769215,  -0.0792973699461192,    1.31312687307811,   -0.541572099750972,  -0.337374377540247,    0.917339213683056,   0.291004470673687,  -0.132327785051881,   -2.01649070787307,   -0.93202765273661,    0.525835784591219,   -0.374418781703754,   0.958156714510435,   -1.22656351514338,   -0.231326977263818,    -1.20252726325904,    1.28960951841132,   0.838214566189021,    1.04800709689384,   0.186260849628837,    0.025645949450268,   -0.277563567566576,
        "Group1",  -0.885776297409679,    0.483193863814768,    1.38157545638553,     0.133869316429452,    0.314794804707843,  -0.0806699347091655,   -1.23281066518983,    -1.05427902127444,    0.961370930531278,  -0.018086931659967,   -1.29966582307858,   -1.11202371088381,   0.291093808244857,    0.346723717001246,  -0.324184458375485,  -0.989191806701409,    -1.34833119004437,    0.807332293407758,   0.796324499089145,   -1.83629134377865,    1.19047624727791,   0.148092848403041,    0.388512274160985,    0.953093683264103,   -0.532431870264935,   -0.808091219300186,   0.524171085063729,  -0.655309498116006,    2.47804042183143,    0.739894802319146,   0.170386155804506,     0.72408190306176,  -0.382965170050938,   -0.919625545674867,    1.68452398458178,    1.45423172269893,   0.448577388746643,    -1.2920278081392,     1.40240703340828,    0.272783555184757,  -0.737894964320054,  -0.342277227142286,      1.0243577681252,   -0.966708676495849,    1.68831239184355,    0.57237513194415, -0.0207645518372601,    1.35214558584758,   -0.177861789976426,   0.0836000568027311,
        "Group2",   -1.09978089864786, -0.00635562642138871,    1.20445893700982,      1.78533905173155,    0.396326577938989,     0.96298228123987,   0.244364414906138,   -0.104744288110701,   -0.883724474401114,   -3.37173908255051,  -0.857250659929035,    1.47480743158371,    0.79721770112609,   -0.431612760578627,    1.85739602217537,   0.275646278286709,     1.41483572450998,   -0.261008741670786,    0.77874531585307,   -1.54103104639384,   0.617226731476436,  -0.206794982835284,    0.253998499450374,   -0.994513348092816,     1.19784612620355,     2.22763232322792,   -1.11558427972451,    1.25228304742217,    -1.4533163643196,     1.27676023028368,   0.578816605533788,    -2.56237882677918,    1.05269226069953,    -1.12619356163764,   -2.41416486207894,   -1.32063917335026,   0.523388159192163,  -0.329125469198937,   -0.426245303013057,     1.53591780168055,  -0.641051896129936,   0.658532578195758,    0.617370042573925,     1.39449126043296,   0.964284046069921,  -0.129107508148844,   0.483833682725908,    1.42387183533754,     2.11528094082124,     0.33226335311816,
        "Group1",    1.51270700980493,    0.151455892862424,   0.824073963681881,      2.42216335525159,    -0.22560371103596,   0.0535710165465174, 0.00277218534359506,   -0.228342617094529,   -0.900092115436322,   0.760703244759755,   0.426265294536191,   0.671512460144392,  0.0409863743756614,      1.1501780393287,   0.590763995069064,  -0.763661093561037,    0.914048945514682,    0.488059917826579,   0.796802566246094,   -1.79438286441787,  -0.172938324465871,  -0.642560138451547,    -2.18716829258598,   -0.571870322518042,     -2.0425957688947,   -0.792524128713455,   -0.04776622165316,   -1.46028743217333,   0.822264445361829,    0.665132817105951,   0.227904874997665,    -0.93721767452518,    1.21121347353879, -0.00583503886139956,   0.229897633620541,   0.109207163477544,  -0.246122239665679,   0.299302194344734,   -0.212596795069938,    -1.39188968640531,   0.446461847481247,  -0.851445102760097,    -1.17103081674999,    0.404360270712859,    1.29184696326074,  -0.803988673422418,     1.9079589147774,  -0.068415304889387,    -1.34227866146778,    0.379695239303798,
        "Group1",   0.257921437532031,   -0.584108970349804,   -1.66262940218559,     -1.07682890211841,    -1.92495043034056,   -0.434898408910037,   -1.32820968602556,    0.675355562427539,     1.72333313279683,   -0.39122685224321,  -0.284836263084754,   -1.54532854371443,  -0.818324049625889,  -0.0365321928878792,    -1.7806267173964,   -1.35211198419997,    -1.23668791849331,     1.35278382096951,  0.0490515728363375,    1.41451490845874,   0.861580440756975,   0.847571823884568,    0.537800433283471,    0.783173181570287,    -1.01431086481328,     1.69728053235192,   -1.91702894207942,  -0.330734876793339,   -1.06644799364953,    -1.52269035459494,  -0.612459865597317,     1.52956064823639,    2.45369487222183,    -1.25613298158102, -0.0680445791345913, -0.0254722179209988,  -0.544545707183516,  -0.440187586812284,   -0.230817019099012,   -0.471635008527422,  -0.189212251041565,   -1.87598302993031,     2.51918956720831,     1.49031586219406,     1.0349947432296,  -0.973259056167225,  0.0270725035924755,   -1.30213553388525,     1.42916563474189,   -0.958207670654434,
        "Group1",  0.0884402291595864,    0.368806732630242,  -0.569306343605481,     0.485941110403099,    -1.43922929832198,    -1.73729725534231,    1.17969641183277,    -1.23324469350631,     1.90904216212893,    1.00990122381185,  -0.614368541969862,  -0.277047227991105,   0.289640643164427,   -0.135801421736564,  -0.434108699575314,   0.655024410228004,    -1.50076035467463,     2.17681559130925,   0.762612934834823,   0.618337891760976,  -0.620085924544441,  -0.527572126400654,    -1.28988641170683,    0.381366421089077,     1.60391822138318,    0.938924807290475,  -0.571730237839681,   0.210817790526989,    1.09430673251488,    0.126223111685365,   0.734030133030624, -0.00538613808929788,   0.464927336754254,     0.21279147402541,   -1.00173505397238,  -0.135157590930348,  -0.803683014742773,   0.496934162455209,   -0.492154208159477,    0.381585018084879,   0.588090755966724,   -0.48985664144872,   -0.633089812097794,   -0.680715286073036,    1.40410315391404,  0.0916671567997696,   0.311601071206303,   -1.42605702269244,   -0.336904933568333,   -0.227389012209278,
        "Group2",  -0.120896537539089,    0.294654339719516,   0.635513817289526,      1.38852173874429,     -1.4696577739724,    -1.26369559978243,  -0.592804999148929,    -1.19996154442278,   -0.777141195855263,  -0.626973147073749,  -0.844890832157483,   -0.62934299197198,   0.339787111301115,    0.944618045644523,   -2.29274971170602,    1.60964676035496,   0.0345386838965327,    0.051387111206838,   0.285993069636396,   -2.35045538719928,  -0.878213047268405, 0.00237075710813171,    -1.22554397015877,    -0.60005817395716,    0.892350034157026,     2.03529495828804,  -0.748196633636421,   -1.00949926422224,   0.220596182329357,    -1.13138211800086,   -1.85050186253115,    -1.68318369036016, -0.0948498082529971,   -0.555619629469677,  -0.560015463091365,  -0.640525314131231,    1.95447105047381,   -0.89057085460159,   -0.307399420096093,    0.319341086263141,  -0.188046258983758,   0.328243402709361,    -1.02353018715821,  -0.0522803800696862,      1.157207222839,   -1.39855532835217,    0.54486313129866,   -2.40884160605589,   -0.738067428888895,    -1.22494595874735,
        "Group1",   -1.19432889516053,   -0.279259373342575,  0.0437220075778579,    -0.195656817284544,    0.761863446891932,    0.406308512069273,    1.19997831633667,    0.765866576616108,    -1.30230526261311,   -1.63457736950186,   0.153694957218872,  -0.933000451619752,  -0.817392730763433,    0.992041361670064, -0.0929652384515409,   -0.78850696587791,    0.286299645402692,   -0.838095445235414,  -0.632815038152827,   0.467031586094115,   -2.22859514687621,  -0.281880233551283,     1.72711355277575,     1.65261512009413,    -1.51770556163796,    0.731626386528303,   0.345178956409604,  -0.534776646171061,  -0.283239590537479,   -0.477425235416266,  -0.968544839770566,  -0.0494187800249314,  -0.908331474152175,   -0.628310089043471,   0.240568027183605,    0.71748255574154,  -0.296887442895346,   0.731639832631132,    0.713397005310362,    -1.41476618244951,  -0.183047444540422,   0.865162051806121,    0.435693940706874,    0.636823632832134,   -1.59933315934367,    2.05728369985151,   0.380849055646667,    1.57327897753296,    0.692330073051101,     1.46817217233113,
        "Group2",   0.611996898040387,    -1.33623665489315,   0.348012303661307,    -0.218174797706211,    -0.24361498187128,    -1.45965396777976,  -0.475033679612135,   -0.588097861282977,     2.62349516681868,    1.24524265203048,  -0.851432275778188,   -1.53788648422826, -0.0287493152280801,   -0.700669754968901,    0.70396445332971,  -0.883876112525995,     1.18620809384561,    -1.08461500930842,     1.8043844808011,  0.0638319381435125,   0.193263225267502,    -2.8284746523873,      1.1603578032903,    -1.19076693514159,    0.823528276152144,   -0.419847340595375,    2.16395110444013,   0.495058274885941,   0.710050753433561,    -1.09847279446978,    0.62762646905029,   0.0454931089477718, -0.0333366032934899,    -1.59500145340402,    1.21394151451887,   -1.47690981302073,  -0.035404687210021,   0.126996462004796,     1.75659582364803,   -0.739714251249943,    1.76037108613501,    1.13971671684903,    0.267296542526631,     0.35688325862053,  -0.751627165888285,   -1.10198624116492,   0.641074999539806, -0.0735462886504976,   -0.412510700934761,   -0.226548468245322,
        "Group2",  -0.217139845746521,    0.700748818440034,    2.45959354887041,    -0.304777954546445,    0.269676607418008,      1.0484573701547,  -0.575057096150816,   -0.660295829975576,    0.229628914346807,   0.181377446555404,  -0.397921072942885,  -0.494102049599945,    2.00078165111199,   -0.991058671834594,  -0.894489621256767,   -1.07251461179358,   -0.037549371842548,   -0.546532769073342,   -1.86301097301425,  -0.256260441820274,   -2.31265671694031,   0.650930316327698,    -0.74816158375162,     1.41567745190252,    0.365562248008499,   -0.309743506851099,   0.336646342204412,   0.548494049782142,    2.21047686646211,     1.70744236642163,    1.24027762938144,   -0.775870282801966,    1.72059724640604,    -2.47645049452256,   0.252358485164026,    0.75410479816319,   0.107189714468554,    1.88904233606744,     1.56873629399177,    -1.12173115267717,   0.491819019266072,  -0.433955263226009,     0.15153477759341,    -1.17561605038368,  -0.239148031041161, -0.0741207330096798,  -0.235946428663467,   0.872665824048119,    0.912620184483832,    0.704418095095258,
        "Group2",  -0.182756706331922,    0.554196622274033,  -0.818380324399669,     0.597832724111443,    -1.55892752095582,     -1.3464305394502,  -0.031226024608499,    0.113013522197344,    0.186749892141885,     3.4953042639856,  -0.939977226280953,  -0.435360015270196,   -1.12926606328462,   -0.705618052658819,   -1.28250679207462,  -0.458140981447841,    0.420371593973559,   -0.426509704704706,   0.845528381213056,   -0.74452203825337, -0.0243337921357311,   0.157759171113334,     1.66667232493041,    0.814172817192482,    -1.33092166830989,    -1.36067647446631,   -0.41786398353582,   -1.22774261421895,    1.41206657562142,   -0.184102959599903,    -1.5069030571303,   -0.685338106241904,  -0.236251623660883,     1.11029541174685,   0.652414104692385,   -2.18980917487403,  -0.230620531545034,   0.379767693804555,   -0.114376060875312,  -0.0455645969922295,   -2.32690137102039,    1.46297579684964,    -1.42910809944283,    -1.48605282360582, -0.0204756200877358,  -0.599930705397576,  -0.311749390401156,  -0.204903909956811,   -0.958172741669908,   -0.146193821684404,
        "Group2",    0.93334632857116,   -0.836306592801415,   -2.11320011492914,      1.39742941081576,   -0.535588006696314,   -0.193570558113494,  -0.358056995978456,   -0.320398799686039,   0.0761366349502805,   0.915591913326913,   -1.38825374141942,  -0.323544676280226,    1.47217859206972,    -1.17577589332822,    1.25578417415048,   0.665647015578227,     1.28924648234277,    -1.21099755539979,   0.341667682894606,   -1.26902527654423,   0.441340589239052,  -0.853437022665369,   -0.529697424571316,    -2.09757104835645,      0.3595761544677,     1.03771431038458,   0.923691020706285,   -1.00661264436047,  -0.196598080152223,      1.8614262207002,    1.18259689371289,  -0.0390248343539803,    1.70869864132557,     1.76051759457602,  -0.928892644960027,    1.55309984771205,    2.39007004059566, -0.0448161139871802,    0.585612246214135,     1.31356314065774,   0.717234053379376,    1.19780771096557,    0.092244038071599,    -2.44537238317247,    1.96337329857487,  -0.259277542615363,   -1.15662266773139,    1.26119194435528,    -1.07196489744233,    0.769280974950692,
        "Group1",   0.821773110508249,    -1.59458816200624,   0.273695272430415,     0.687619761239963,    0.562451973173495, -0.00233595711367605,  -0.356601077647731,     1.86638149693879,     1.40486018632133,    1.04850651742624,   0.955184588863398,   -2.06111361891619,  -0.227068916484902,    -1.78119695174032,  -0.964629979588376,   0.712228212418725,     1.17068918509962,    0.597792997779025,  0.0227776061434687,   0.862628007930791,   0.789576753769568,    1.36310008597407,     1.02864835063927,    0.320165082487674,    0.892994609988693,   0.0462178272837366,   0.766766592335207,   0.207167201609838,    0.75538456981956,    -1.74204706626444,   -1.33418855936283,    0.839742870342485,  -0.222756799545589,     1.25649974649894,  -0.444693950906624,   0.702061998975102, -0.0116323437326994,   0.136043976842453,   -0.583870739389275, -0.00158204230492996,   -0.68233877507983,   -0.46228665944604,    0.387349852747071,     0.65019931683817,   0.389845579003813, -0.0800452087853731,  -0.334276425827971,   0.298291440645197,     1.27302546189127,    0.365235938065276,
        "Group1",    1.39211637593427,    0.204958580587634,  -0.687596841243412,     0.320188014296969,   -0.178326123419918,  -0.0128297338671881,  -0.877664383433726,    0.259531455767799,   -0.191722235336317,   0.763824936934856,   -1.31749547003238,   0.441502555095545,    1.48231059624201,    0.310607521838391,   0.907783881064091,   0.442954227499162,    0.826093654084712,     1.42389578908393,  -0.611399988446644,  -0.576934671897015,    1.02181962668272,   -1.26289617117116,      1.3767179910649,    0.801025120424051,   -0.995098995899314,  -0.0577733552767567,   0.248748147903931,    1.41740118033914,   -1.09410087019746,   -0.783457421295062,  -0.596320294015713,   -0.841408017043754,    0.21033018312288,  -0.0815338980196429, -0.0393421854237676,  0.0515238125352395,   -1.08905940665858,   0.550276535752571,    -1.50778289137984,   -0.212091233815896,   0.038614423126172,   0.912847756741927,     2.24373592299426,    0.597458845595852,    1.06658275219461,   0.541063018196555,  -0.416751365438524,   0.309227566485526,    0.740891261191436,     1.04633575204747,
        "Group1",  -0.476173923054674,    -0.34508797797289,   0.446041052961866,    -0.301869925777261,   -0.115135986202651,    0.151947321984398,   -1.21289712517796,     0.16156007091807,     1.45939216415609,  -0.603387376859399,  0.0730291461596218,   0.746351246566367,  -0.843053174487288,   -0.145110360949431,   0.214073613669174,   0.759587312059179,    0.323917065090484,   -0.443298625558346,  -0.260526772474753,   -0.13226734829003,   0.615261159537096,   -1.77794654572074,     1.33100295826265,   -0.791680654042778,     0.51967192258579,   0.0767390706997009,  -0.657218034949707,   0.747089396555255,   0.430180024146149,    0.795270542310834,   -1.32949216503638,    0.716228276161418,    2.48092038385889,    0.147271584663551,   0.143080057160209,   -2.42797370995882,   0.313769183171077,  -0.808080397534084,    0.518631721220592,     2.25347500925588,    1.35344327237485,    1.05656727466585,   -0.781466209509284, -0.00591553466537692,  -0.271213134547158,  -0.827200700837816,  -0.576274860540099,  -0.272791029401605,   -0.167711206765435,    0.909742838918374,
        "Group2",   0.650348560726305,    0.252611703364455,  -0.812384723790597,     0.498348685557949,  -0.0720614721063666,    0.598511131401079,   0.613286618687034,    0.931074909335354,   -0.220655451134541,  -0.370429662702776,   -0.56818584856837,   0.789642873824685, -0.0661953274558979,    0.642549753692457,   0.881023122748974,  -0.468877666019124,    0.380950411454549,    -1.04033346567429,    1.80567031464304,   0.586828100587993,  -0.859577856168591,  -0.686919645075559,     1.25465594943585,  -0.0106662632339682,    -1.23573344828329,   -0.633641164106258,   0.583124169133963,   -1.51943307234853,   0.960549711583255,   -0.532270009991016,  -0.182113418617215,    -1.86746565295771,  0.0271648423874321,    0.354597559542375,   0.529199978876831, -0.0860707324535189,    1.09572140336201,   -1.00699603251889,    0.367644068718127,    -0.60624713210924,    1.69138981336243,   -1.38155427610757,    0.739967670482954,     2.03488045755017,   0.187356631287273,  -0.971392457482621,   0.507011462510784,  -0.087984183416195,    0.503768894999758,    0.484817302440194,
        "Group1",       1.39111045639,    -1.29400246548455,    2.21205548033514,    -0.549536917916756,      1.2109098069263,   -0.126212437298279,  -0.806203341462477,  -0.0599467492596211,     0.50514588627314,    1.05982593833365,   -1.05845066878383,   0.770740507039544,   0.311233498357864, -0.00165936230130426,    1.00254499828277,  -0.172709977883837,     1.20261958279329,    -1.27389707840725, -0.0969992670036506,   0.535000276997602,   0.890748976368977,   -1.18433552229326,   -0.287334553809268,    -1.62351793994448,    0.529726874322073,   -0.423413462128983,   0.690682867666824,  -0.720070739324317,   0.459059522904321,      1.9858043427389,  0.0491385446373278,     1.99085671970778,   -1.45270517345354,   -0.337141103361032,  -0.185558488318001,  -0.738357445758921,   -1.01889460165192,   0.858202267276623,     1.59744004592723,    0.113822755103304,   -1.97724922370716,    1.52242167132902,   -0.858421801859811,    0.276288979880555,     -0.179024547426,   0.787895160523123,   0.294197761772827,   0.925880812678206,   0.0545179125713212,   -0.399249387586168,
        "Group1",    -1.1107888794479,   -0.959170444380363,   -0.12370597157743,    -0.279256503637243,   -0.614896900799703,   -0.248535565846776,    -1.3764569299089,   0.0487397000774502,    -1.03349700607288,    1.05511052983939,   0.259313538417069,   0.200506317830367,  -0.112590228303414,    0.409162962077351,    1.13991050456775,   0.682049899385807,     1.10220575073214,    0.770151612011797,  -0.384486699785057,  -0.393409936967253,  0.0632747474874033,   0.789677301727648,   -0.546735518159085,   -0.907567051887799,   -0.983041720955936,    0.776691007043517,   0.291864679995948,   -1.83821203439613,  -0.596455394517824,   -0.651800415504399,   0.412076431613412,    0.771086495860009,  -0.673642807416947,    0.492653951656481,   0.766675058621243,    1.16772402635259,    1.67087514103806,  0.0844163440587337,   -0.173505779423678,   -0.334740454208365,   -1.52539749092167, -0.0780192840566323,    0.302018596365049,   -0.496466209356325,  -0.156586475829431,    2.01158578967806,    -1.0834104076964,   -2.70047279265272,   0.0768784904987114,   -0.445050778224049,
        "Group2",  -0.860792586877842,      1.0857748536799,  -0.477335506030052,      1.09651344311173,    0.676126458314701,    0.160327394904622,  -0.507847899163547,    -1.07287540073396,     0.17047347145922,   0.582972161120319,   0.373134504519161,    1.46835003167775,   0.658738838942645,   -0.496058147310148,    1.23603585230776,  -0.281577328241543,  -0.0615149399791465,    0.031522621976529,  -0.878362142505014,  -0.540609417209361,   -1.86466105555997,  0.0859637709502686,       1.253927471065,    0.136766722422639,   -0.375745484254249,     1.31090723646561,    1.92307416746338,   0.784395864352993, -0.0450862072387442,    -2.15696206847162,  -0.422353546385099,   -0.622598108012433,   -1.05691633473035,    0.829866793583872,   0.264323015982099,   -1.63264961625291,   0.275183470718412,   -1.48179176140082,    -1.71396796503711,   -0.907281697378612,   0.437746900882553,   0.502346304431283,   -0.961095221822742,     1.17021622041948,    1.78944297458623,   0.719118194619255,  -0.424363568579712,  -0.855505101047477,   -0.487458837260032,    0.561711690105433,
        "Group1",   -1.13173868085377,    0.403774904715714,  -0.166261491486608,     0.442013088178811,    0.898599605537552,   -0.433641941597269,  -0.800935486737338,    -2.29297143048067,     1.20066816089193,  -0.986567435539539,    1.26466676928415,  -0.876455483940752,   -0.16686150010949,   -0.960107958901165,   0.295401510142675,  -0.961622573931821,    0.364589913995779,    -1.90485475143827,  -0.495578521936918,   0.259450915234582,    -0.1131368509232,  -0.370061442579403,  -0.0717229189590111,    0.271187956531974,    -1.04173538449989,   0.0583013062676336,    2.30612974849875,  -0.871052149527092,  -0.581518594777576,  -0.0920274969247368, -0.0196536597344667,   -0.103594550359097,  0.0898368491080017,    0.947611539603209,    -1.3558222763288,   -1.61312915574097,  -0.181866399727406,    -0.9651266161995,    0.284856517472213,    0.605857718423736,  -0.643125319354182, -0.0872131289547691,    -1.99760903604053,     1.00415049965311,   0.308503977294177,   0.444444322327806,   0.255939264181965,   -1.10403579300387,    0.269912880371111,   -0.797507564198517,
        "Group1",    -1.4592139995024,    0.586487536719298,   0.862563383626431,     0.241016294026112,    -1.18931790352102,     1.53741241910027,   -2.19278568567007,    -1.20720685006434,   -0.163405914765736,    1.68462181174398,   0.325224996068265,   -1.22660469372111,    1.20887346516015,    0.778132224570433,   0.171761023605458,   -1.37765014473256,     1.69255229998577,   -0.123755177145571, -0.0842924535744518,   -1.17827876100886,   -1.78338637587516, 0.00933636704307702,   -0.682436621264268,    -0.07366121520502,    0.697667357430169,    0.245398357259442,   -0.98919526784311, -0.0108663130165317,   0.442863237126202,   -0.397400116998658,   0.303016425333838,     -1.2325383205798,  -0.572289502826511,     1.16542883446602,   0.359071548321692,  -0.224659351788146,   0.867355430722069,   0.103600145420958,    -1.51545966092347,   -0.522815844166493,    -0.4760779533788,  -0.690953385894807,    -2.30690186737447,   -0.706639694712762,   0.365197009298427,   0.188869109052605,   0.348409277694668,  -0.393212709744721,   -0.119801806947925,     1.15940351252905,
        "Group1",  0.0799825532411612,     1.81522844615395,  0.0973404852028189,    -0.255607655355518,    0.121258849819009,    -2.17024657661608,  -0.290937149267675,    0.114109429797191,     1.28247586312264,   -1.36684104568263,  -0.138467319508306,   0.337837919974576,   0.170419433884223,    0.761120616327841,  -0.955389282695438,    2.69758663663836,     1.47136701247198, 0.000328377213438334,   -1.35772206705499,   0.306138478548671,   -1.05349044072366,  -0.951059591672823,    -1.02499645828567,    -0.77443032842804,   -0.144448803419361,    0.232324718377114,   0.401427408509758,   0.609141558215759,  -0.310230689543812,   -0.138327302570867,  -0.972422343455087,   -0.932907862773239,   0.378039438656651,   -0.421166366290429,   -1.70825283944633, -0.0551681503459401,   -1.40279690623594,     1.1773236654154,    -1.11722842504756,    0.850439392709796,    1.22940126860004,    1.52642292910877,     0.86723155891422,   0.0685642509355788, -0.0419215729776343,  0.0771917022259067,   0.114131821276163,   -1.00528864307356,     1.27674983971827,    0.629350954722465,
        "Group2",    0.65320433964919,    0.128821428602383,   -1.62561673921129,     0.931032901484882,  -0.0112216861304115,     1.02700461929143,   0.167174121160518,    -1.03329707910538,     2.72719638791127,  -0.433214348611114,     2.6024688972798,   0.440824087254149,   0.692419636244747,    -1.73371218388323,   -1.21040912105673,   -1.69971505556293,   -0.977247661344119,   -0.843778344728857,    1.14269781676707,   0.173481229120353,  -0.619354677304664,   0.181717711397805,     1.30157781471653,    0.593816135526189,    0.498543397139294,    0.188775899725465,   -1.23238817325492,  -0.133051648058773,  -0.222829768082489,   -0.825764999237853,  -0.701155053616588,     0.29751851452647,    1.62382151287374,    0.334602756436989,  -0.635928277355224,  -0.627365956924184,    1.48230141230567,   0.192566454895148,   -0.462236253258946,   -0.408036071471018,  -0.461557933995871,     1.3140666822661,    0.076113269906901,    0.887426250052947,  -0.598982530139343,   -1.92878912192965,  -0.606208464561042,   0.682137975116011,    -1.68373922526588,    0.493970156030412
        )  
  
  
  
### :: df_5vars_10obs ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Manually create a dataset
df_5vars_10obs <- data.frame(
  Group = rep(c("Group1", "Group2"), each = 5),
  Var1 = c(2.5, 3.0, 2.8, 2.9, 3.1, 3.6, 3.7, 3.5, 3.8, 3.9),
  Var2 = c(7.1, 7.3, 7.2, 7.4, 7.5, 6.8, 6.9, 7.0, 6.7, 6.6),
  Var3 = c(15, 16, 15, 14, 15, 18, 17, 19, 18, 17),
  Var4 = c(0.5, 0.6, 0.55, 0.58, 0.57, 0.65, 0.66, 0.64, 0.67, 0.68),
  Var5 = c(100, 105, 102, 101, 103, 110, 112, 111, 113, 114)
)

# Display the dataset
print(df_5vars_10obs)
```
  
  
### :: mtcars_5vars =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Load the mtcars dataset
data("mtcars")

mtcars_5vars = mtcars
# Create a binary grouping variable based on the number of cylinders
mtcars_5vars$Group <- ifelse(mtcars$cyl == 4, "Group1", "Group2")

# Select relevant variables
mtcars_5vars <- mtcars_5vars %>%
  select(Group, mpg, disp, hp, wt, qsec)

# Display the dataset
print(mtcars_5vars)

```
  
  
# __________|------  
# @@ START) dev ----  
# https://chatgpt.com/c/6714b3de-a9a4-800e-8ffd-f901081dcae1
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```
  
  
### df_5vars_10obs |> group_by(Group) |> summarise_all() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}

library(glmnet)
library(flextable)
library(dplyr)
library(tidyr)


input_data = df_5vars_10obs

# Prepare the predictor matrix X and response vector y
X <- input_data %>%
  select(-Group) %>%
  select_if(is.numeric) %>%
  drop_na()

# Extract y
y <- input_data$Group[complete.cases(input_data[, c("Group", names(X))])]

# Convert y to a factor and then to numeric
y_numeric <- as.numeric(factor(y)) - 1  # Now y_numeric contains 0s and 1s

# Standardize predictors
X_scaled <- scale(X)

# Perform Elastic Net regression with cross-validation
cv_model <- cv.glmnet(
  x = as.matrix(X_scaled),
  y = y_numeric,
  family = "binomial",
  alpha = 0.5,
  standardize = FALSE
)

# Extract coefficients at the lambda that gives minimum cross-validated error
coef_min <- coef(cv_model, s = "lambda.min")
coef_min_matrix <- as.matrix(coef_min)

# Print the coefficient matrix
print(coef_min_matrix)

# Extract coefficients at lambda.1se
coef_1se <- coef(cv_model, s = "lambda.1se")
coef_1se_matrix <- as.matrix(coef_1se)

# Print the coefficient matrix
print(coef_1se_matrix)


# # Identify selected variables (non-zero coefficients excluding intercept)
# selected_vars <- rownames(coef_min_matrix)[coef_min_matrix[, 1] != 0]
# selected_vars <- selected_vars[selected_vars != "(Intercept)"]

# Define a threshold for considering coefficients as zero
threshold <- 1e-6

# # Identify selected variables (non-zero coefficients excluding intercept)
# selected_vars <- rownames(coef_min_matrix)[abs(coef_min_matrix[, 1]) > threshold]
# selected_vars <- selected_vars[selected_vars != "(Intercept)"]

selected_vars <- rownames(coef_1se_matrix)[abs(coef_1se_matrix[, 1]) > threshold]
selected_vars <- selected_vars[selected_vars != "(Intercept)"]

# Print selected variables
print(selected_vars)

if (length(selected_vars) == 0) {
  stop("No variables were selected by the model.")
}

# Prepare the summary statistics table
summary_table <- input_data %>%
  select(Group, all_of(selected_vars)) %>%
  group_by(Group) %>%
  summarise_all(
    list(
      Mean = ~ mean(., na.rm = TRUE),
      SD = ~ sd(., na.rm = TRUE),
      Median = ~ median(., na.rm = TRUE),
      Min = ~ min(., na.rm = TRUE),
      Max = ~ max(., na.rm = TRUE)
    )
  ) %>%
  pivot_longer(
    -Group,
    names_to = c("Variable", "Statistic"),
    names_sep = "_"
  ) %>%
  pivot_wider(
    names_from = "Statistic",
    values_from = "value"
  )

# Display the summary table
print(summary_table)

```


### df_5vars_10obs |> group_by(Group) |> summarise_all() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}

library(glmnet)
library(flextable)
library(dplyr)
library(tidyr)


input_data = mtcars_5vars

# Prepare the predictor matrix X and response vector y
X <- input_data %>%
  select(-Group) %>%
  select_if(is.numeric) %>%
  drop_na()

# Extract y
y <- input_data$Group[complete.cases(input_data[, c("Group", names(X))])]

# Convert y to a factor and then to numeric
y_numeric <- as.numeric(factor(y)) - 1  # Now y_numeric contains 0s and 1s

# Standardize predictors
X_scaled <- scale(X)

# Perform Elastic Net regression with cross-validation
cv_model <- cv.glmnet(
  x = as.matrix(X_scaled),
  y = y_numeric,
  family = "binomial",
  alpha = 0.5,
  standardize = FALSE
)

# Extract coefficients at the lambda that gives minimum cross-validated error
coef_min <- coef(cv_model, s = "lambda.min")
coef_min_matrix <- as.matrix(coef_min)

# Print the coefficient matrix
print(coef_min_matrix)

# Extract coefficients at lambda.1se
coef_1se <- coef(cv_model, s = "lambda.1se")
coef_1se_matrix <- as.matrix(coef_1se)

# Print the coefficient matrix
print(coef_1se_matrix)


# # Identify selected variables (non-zero coefficients excluding intercept)
# selected_vars <- rownames(coef_min_matrix)[coef_min_matrix[, 1] != 0]
# selected_vars <- selected_vars[selected_vars != "(Intercept)"]

# Define a threshold for considering coefficients as zero
threshold <- 1e-6

# # Identify selected variables (non-zero coefficients excluding intercept)
# selected_vars <- rownames(coef_min_matrix)[abs(coef_min_matrix[, 1]) > threshold]
# selected_vars <- selected_vars[selected_vars != "(Intercept)"]

selected_vars <- rownames(coef_1se_matrix)[abs(coef_1se_matrix[, 1]) > threshold]
selected_vars <- selected_vars[selected_vars != "(Intercept)"]

# Print selected variables
print(selected_vars)

if (length(selected_vars) == 0) {
  stop("No variables were selected by the model.")
}

# Prepare the summary statistics table
summary_table <- input_data %>%
  select(Group, all_of(selected_vars)) %>%
  group_by(Group) %>%
  summarise_all(
    list(
      Mean = ~ mean(., na.rm = TRUE),
      SD = ~ sd(., na.rm = TRUE),
      Median = ~ median(., na.rm = TRUE),
      Min = ~ min(., na.rm = TRUE),
      Max = ~ max(., na.rm = TRUE)
    )
  ) %>%
  pivot_longer(
    -Group,
    names_to = c("Variable", "Statistic"),
    names_sep = "_"
  ) %>%
  pivot_wider(
    names_from = "Statistic",
    values_from = "value"
  )

# Display the summary table
print(summary_table)

```
  
  
#### lambda_seq <- 10^seq(2, -2, by = -0.1) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Set a custom lambda sequence
lambda_seq <- 10^seq(2, -2, by = -0.1)

# Perform Elastic Net regression with custom lambda
cv_model <- cv.glmnet(
  x = as.matrix(X_scaled),
  y = y_numeric,
  family = "binomial",
  alpha = 0.5,
  lambda = lambda_seq,
  standardize = FALSE
)

# Use the largest lambda that results in a model with desired sparsity
best_lambda <- cv_model$lambda[which.min(cv_model$cvm)]
best_lambda
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ START) source ----  
```{r .subpath.filename.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
options(function.reload = TRUE);  # getOption("function.reload")
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
# .subpath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") {.subpath = env1$path$CurrentSource.path.filename.ext |> dirname(); ".subpath" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
# if(.subpath!="") utils::browseURL(normalizePath(.subpath))
# .sourcename = "default.template" |> paste0(".source.r")
if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") {.sourcename_root = env1$path$CurrentSource.path.filename.ext |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),""); ".sourcename_root" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.subpath = .subpath
if(!exists(".sourcename_root") && exists(".sourcename")) .sourcename_root = .sourcename |> str_replace("\\.source\\.r$", "")
.sourcename = .sourcename_root |> paste0(".source.r")
env1$path$.sourcename_root = .sourcename_root
env1$path$.subpath.filename.dev.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.r")
env1$path$.subpath.filename.dev.Rmd = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.Rmd")
env1$path$.subpath.filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".source.r")
cat("# ",'.sourcename_root = "',.sourcename_root,'"  \n',
    "#### ",env1$path$.subpath.filename.dev.r, "----  \n",
    "#### ",env1$path$.subpath.filename.dev.Rmd, "----  \n",
    "#### ",env1$path$.subpath.filename.source.r, "----  \n",
    '# # source(paste0(env1$path$source_base,"/","',env1$path$.subpath.filename.source.r,'"))', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'")', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.subpath.filename.source.r) ) ----  
# .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.)
# if(isTRUE(options()$function.reload) || !.sourcename %in% names(.GlobalEnv$env1$source)) {message('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")'); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); source(.GlobalEnv$env1$source[[.sourcename]])}
```
  
  
# __________|------  
# @@ START) function ----  
## ECHO :: create_table1() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
library(glmnet)
library(flextable)
library(dplyr)
library(tidyr)

create_table1 <- function(dataset, byVar, alpha = 1, output_as_flextable = FALSE) {
  # Convert byVar to factor
  dataset[[byVar]] <- as.factor(dataset[[byVar]])
  
  # Prepare predictor matrix X and response y
  X <- dataset %>%
    select(-all_of(byVar)) %>%
    select_if(is.numeric) %>%
    drop_na()
  
  y <- dataset[[byVar]][complete.cases(dataset[, c(byVar, names(X))])]
  y_numeric <- as.numeric(factor(y)) - 1
  
  # Standardize predictors
  X_scaled <- scale(X)
  
  # Perform Elastic Net regression
  cv_model <- cv.glmnet(
    x = as.matrix(X_scaled),
    y = y_numeric,
    family = "binomial",
    alpha = alpha,
    standardize = FALSE
  )
  
  # Extract coefficients at lambda.1se
  coef_1se <- coef(cv_model, s = "lambda.1se")
  coef_1se_matrix <- as.matrix(coef_1se)
  
  # Define threshold
  threshold <- 1e-6
  
  # Identify selected variables
  selected_vars <- rownames(coef_1se_matrix)[abs(coef_1se_matrix[, 1]) > threshold]
  selected_vars <- selected_vars[selected_vars != "(Intercept)"]
  
  # Check if any variables were selected
  if (length(selected_vars) == 0) {
    stop("No variables were selected by the model.")
  }
  
  # Prepare summary table
  summary_table <- dataset %>%
    select(all_of(byVar), all_of(selected_vars)) %>%
    group_by_at(byVar) %>%
    summarise_all(
      list(
        Mean = ~ mean(., na.rm = TRUE),
        SD = ~ sd(., na.rm = TRUE),
        Median = ~ median(., na.rm = TRUE),
        Min = ~ min(., na.rm = TRUE),
        Max = ~ max(., na.rm = TRUE)
      )
    ) %>%
    pivot_longer(
      -all_of(byVar),
      names_to = c("Variable", "Statistic"),
      names_sep = "_"
    ) %>%
    pivot_wider(
      names_from = "Statistic",
      values_from = "value"
    )
  
  if (output_as_flextable) {
    # Create flextable
    ft <- flextable(summary_table)
    ft <- autofit(ft)
    return(ft)
  } else {
    return(summary_table)
  }
}


```
  
  
### df_5vars_10obs |> create_table1() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Run the function with alpha = 0.5 for Elastic Net regression
df_5vars_10obs.table1 <- create_table1(dataset = df_5vars_10obs, byVar = "Group", alpha = 0.5)

df_5vars_10obs.table1
# Since we might not be able to display flextable here, let's extract and display the summary table
# Rewriting the part of the function to extract summary_table
```



  
  
###  mtcars_5vars |> create_table1() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Run the function
mtcars_5vars.table1 <- mtcars_5vars %>% create_table1(byVar = "Group", alpha = 0.5)

# Display the flextable
print(mtcars_5vars.table1)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
  
```{r MetaData99-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
if(exists("MetaData")) {
    "MetaData |> str(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    # "MetaData$tblVarName |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    # "MetaData$DataSetNames |> str(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "MetaData$VarNames |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "MetaData$VarNames.select |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "MetaData$ModelList |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    
    "all.equal(.MetaData0, MetaData)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    if(!identical(.MetaData0, MetaData)) {
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        .path.file = ifelse(is.null(env1$path$CurrentSource.path.filename.MetaData.rds), NULL, env1$path$CurrentSource.path.filename.MetaData.rds %>% {paste0(env1$path$path1,"/",.)})
        MetaData |> env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.path.file = .path.file, createBackup = TRUE, Execute = TRUE)
    }
} else {warning("> !exists(MetaData)  \n")}
```


```{r writeRDS-EvalNoEchoNoMsgNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# __________|------  
## @ write_rds( get(.objectname), paste0(.path4write,"/",.objectname,".rds",".xz"), compress = "xz", compression = 9L) ----  
if(exists("MetaData")) {
    # MetaData$DataSetNames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
    cat("    ________________________________________________________________________    \n")
    for (.objectname in names(MetaData$DataSetNames)) {
        assign(.objectname, structure(get(.objectname), MetaData = MetaData))
        env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = .objectname, .path4write = env1$path$.path4write, createBackup = FALSE, Execute = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE, CompressionMethod = "xz")
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    }
}
# #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
# .path.filename.xlsx = paste0(.path4write,"/",.objectname,".xlsx")
# system.time(openxlsx2::write_xlsx(get(.objectname), file=.path.filename.xlsx, as_table=TRUE))
# if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(.path.filename.xlsx)
```
  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$CurrentSource.path.filename.pdf = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$CurrentSource.path.filename.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (Sys.info()["sysname"] == "Windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$CurrentSource.path.filename.ext)),', output_format = "pdf_document")  \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
        .path.file = env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}
        env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, Execute = FALSE)
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = .path.file, .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal$f_file_PDF.sumatra(.path.file))
    }
}
# env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path.file = env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, Execute = FALSE); cat('  env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = ',deparse(.path.file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal$f_file_PDF.sumatra(',deparse(.path.file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path.file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path.file = env1$path$CurrentSource.path.filename.html %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, Execute = FALSE); cat('  env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = ',deparse(.path.file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); cat('  env1$env.internal$f_URL.open_in_edge_app(',deparse(.path.file),')  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$CurrentSource.path.filename.nb.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
