---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  # - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$f$MH_shortcuts()
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd())  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_FileNameExt ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# .tmp$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) not a relative path~!  
# env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) Not using a relative path~!
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$path4write = file.path(env1$path$path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$path4write = getwd()
.path4read  = env1$path$path4read
.path4write = env1$path$path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .FileName.source.r = "f_DSname.Search.read.checkEntity" |> paste0("-source.R"); .RelativeSubPath=r"(R)"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = list(.RelativeSubPath, .FileName.source.r) %>% {.[nzchar(.)]} %>% c(fsep = "/") %>% {do.call(file.path, .)})
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  
```
  
  
# __________|------  
# @@ DATA) example ----  
## \$ ADS_time2event =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# suppressPackageStartupMessages(library(survival))
for(.packagename in c("survminer")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
# ?survival::lung
.objectname = DSN = "ADS_time2event"
assign(
    DSN, 
    survival::lung |> as_tibble() |> mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] |> as.factor(), StudyPopulation = time >= 30) |>
        # dplyr::select(-status, -sex)
        dplyr::select(-status)
)
ADS_time2event %>% {cat(" > ",deparse(substitute(.))," |> as_tibble() |> print()","  \n", sep=""); print(as_tibble(.))}
```
  
  
## \$ gtsummary::trial ----  

We’ll be using the [`trial`](https://www.danieldsjoberg.com/gtsummary/reference/trial.html) data set throughout this example.

*   This set contains data from 200 patients who received one of two types of chemotherapy (Drug A or Drug B). The outcomes are tumor response and death.
    
*   Each variable in the data frame has been assigned an **attribute label** (i.e. `attr(trial$trt, "label") == "Chemotherapy Treatment")` with the **[labelled](http://larmarange.github.io/labelled/)** package. These labels are displayed in the {gtsummary} output table by default. Using {gtsummary} on a data frame without labels will simply print variable names in place of variable labels; there is also an option to add labels later.
    
    
Includes mix of continuous, dichotomous, and categorical variables

```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# suppressPackageStartupMessages(library(survival))
for(.packagename in c("gtsummary")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
trial = gtsummary::trial
trial %>% {cat(" > ",deparse(substitute(.))," |> as_tibble() |> print()","  \n", sep=""); print(as_tibble(.))}
trial %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); (str(.))}
```



# __________|------  
# @@ REFERENCES) ----  


# __________|------  
## @ EPI library(gtsummary) CheatSheet.Rmd
## @ EPI library(gtsummary) danieldsjoberg.com FAQ+gallery.Rmd
## https://www.danieldsjoberg.com/gtsummary/articles/gallery.html

### # Summary by trt. 

### ECHO \% |> tbl_summary(by = trt, statistic = all_continuous() ~ "{median} ({p25}, {p75})") ----  
##### **ECHO** \% |> modify_header(all_stat_cols() ~ "**{level}**  \nN = {n} ({style_percent(p)}%)") ----  
##### **ECHO** \% |> add_n() ----  
##### **ECHO** \% |> bold_labels() ----  
###### ECHO \% |> modify_spanning_header(all_stat_cols() ~ "**Chemotherapy Treatment**") ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
trial |> 
    tbl_summary(
        by = trt,
        include = c(age, grade),
        missing = "no",
        statistic = all_continuous() ~ "{median} ({p25}, {p75})"
    ) |> 
    modify_header(all_stat_cols() ~ "**{level}**  \nN = {n} ({style_percent(p)}%)") |>
    add_n() |> 
    bold_labels() |>
    modify_spanning_header(all_stat_cols() ~ "**Chemotherapy Treatment**") |>
    print() |> invisible()
```


### ECHO \% |> tbl_summary(by) ----  
##### **ECHO** \% |> add_n() ----  
##### **ECHO** \% |> add_overall() ----  
##### ECHO \% |> add_p() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
trial %>%
    select(trt, age,
           response) %>%
    tbl_summary(
        by = trt,
        missing= "no"
    ) %>%
    add_n() %>%
    add_overall() %>%
    add_p() |>
    print() |> invisible()
```
  
  
  
### # Show continuous summary statistics on multiple lines.

### ECHO \% |> tbl_summary(by = trt, type = all_continuous() ~ "continuous2", statistic = all_continuous() ~ "{median} ({p25}, {p75})") ----  
##### **ECHO** \% |> italicize_levels() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
    trial |> 
      tbl_summary(
        by = trt,
        include = c(age, marker),
        type = all_continuous() ~ "continuous2",
        statistic =
          all_continuous() ~ c("{N_nonmiss}",
                               "{mean} ({sd})",
                               "{median} ({p25}, {p75})",
                               "{min}, {max}"),
        missing = "no"
      ) |> 
      italicize_levels()

```


### # Report treatment differences between two groups. 

### **ECHO** \% |> tbl_summary(by, statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{p}%")) ----  
##### ECHO \% |> add_difference() ----  
##### **ECHO** \% |> add_n() ----  
##### ECHO \% |> modify_header(all_stat_cols() ~ "**{level}**") ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
    trial |> 
      tbl_summary(
        by = trt,
        include = c(response, marker),
        statistic = list(
          all_continuous() ~ "{mean} ({sd})",
          all_categorical() ~ "{p}%"
        ),
        missing = "no"
      ) |> 
      add_difference() |> 
      add_n() |> 
      modify_header(all_stat_cols() ~ "**{level}**") |>
    print() |> invisible()
```


### # Include p-values comparing all groups to a single reference group.

### ECHO \% |> tbl_summary(by = grade) ----  
##### ECHO \% |> add_p() ----  
##### ECHO \% |> modify_header() ----  
##### ECHO \% |> modify_column_hide(all_stat_cols()) ----  
### **ECHO** \% tbl_merge(list(t0, t1, t2)) ----  
###### **ECHO** \% |> modify_spanning_header(all_stat_cols() ~ paste0("**",labelled::var_label(byVar),"**")) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
    # table summarizing data with no p-values
    small_trial <- trial |> select(grade, age, response)
    t0 <- small_trial |> 
      tbl_summary(by = grade, missing = "no") |> 
      modify_header(all_stat_cols() ~ "**{level}**")
    
    # table comparing grade I and II
    t1 <- small_trial |> 
      dplyr::filter(grade %in% c("I", "II")) |> 
      tbl_summary(by = grade, missing = "no") |> 
      add_p() |> 
      modify_header(p.value ~ "**I vs. II**") |> 
      # hide summary stat columns
      modify_column_hide(all_stat_cols())
    
    # table comparing grade I and II
    t2 <- small_trial |> 
      dplyr::filter(grade %in% c("I", "III")) |> 
      tbl_summary(by = grade, missing = "no") |> 
      add_p() |> 
      modify_header(p.value = "**I vs. III**") |> 
      # hide summary stat columns
      modify_column_hide(all_stat_cols())
    
    # merging the 3 tables together, and adding additional gt formatting
    tbl_merge(list(t0, t1, t2)) |> 
      modify_spanning_header(
        all_stat_cols() ~ "**Tumor Grade**",
        starts_with("p.value") ~ "**p-values**"
      ) |>
    print() |> invisible()
```


### # summarize a continuous variable by one, two, or more categorical variables. 

It’s often needed to summarize a continuous variable by one, two, or more categorical variables. The example below shows a table summarizing a continuous variable by two categorical variables. To summarize by more than two categorical variables, use `tbl_continuous` in conjunction with `tbl_strata` (see an example of `tbl_strata` [here](#tbl_strata)).

### ? ECHO \% |> tbl_continuous(variable = marker, by = trt, include = grade) ----  
###### ECHO \% |> modify_spanning_header() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
    trial |> 
      tbl_continuous(variable = marker, by = trt, include = grade) |> 
      modify_spanning_header(all_stat_cols() ~ "**Treatment Assignment**") |>
    print() |> invisible()
```



### # Build a summary table stratified by more than one variable.

### **ECHO** \% |> tbl_strata(strata = grade, ~ .x |> tbl_summary(by = trt)) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
    trial |> 
      select(trt, grade, age, stage) |> 
      mutate(grade = paste("Grade", grade)) |> 
      tbl_strata(
        strata = grade,
        ~ .x |> 
          tbl_summary(by = trt, missing = "no") |> 
          modify_header(all_stat_cols() ~ "**{level}**")
      ) |>
    print() |> invisible()
```


# __________|------  
## @ EPI library(gtsummary) library(Z.gtsummary.addons) add_SMD().Rmd

## https://github.com/zheer-kejlberg/Z.gtsummary.addons  
## library(gtsummary) ----  
## ECHO \% devtools::install_github("zheer-kejlberg/Z.gtsummary.addons") ----  
## library(Z.gtsummary.addons) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

.packagename = "gtsummary"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}

for(.packagename in c("devtools")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  

devtools::install_github("zheer-kejlberg/Z.gtsummary.addons")
library(Z.gtsummary.addons)
```
  
  
### ECHO \% |> tbl_summary() ----  
#### **ECHO** \% |> add_SMD(location = "both") ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
trial %>%
  tbl_summary(by = grade, include = c(age, stage)) %>%
  add_SMD(location = "both") |>
    print() |> invisible()
```
  
  
### ECHO \% |> tbl_summary() ----  
#### **ECHO** \% |> add_SMD(location = "level", ci = TRUE, ci_bracket="[]", ci_sep=";") ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
trial %>% 
  tbl_summary(by = grade, include = c(age, stage)) %>%
  add_SMD(location = "level", ci = TRUE, ci_bracket="[]", ci_sep=";") |>
    print() |> invisible()
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ DATA) mutate() ----  
```{r DATA-MUTATE-SYNC, eval=FALSE, include=FALSE}
paste0('### ->> Now synced to: "',dir(env1$path$path1, ".*\\.Rmd$", ignore.case = TRUE),'"  \n') |> cat(sep="")
```
## ->> Now synced to: ""  
## ()()()()()()()()()()------  
## ()()()()()()()()()()------  
## ->> PENDING synced to: ""  
## \$ CohortGJ0910.BaselineJKGJ2085NoHx...01  
#### \$ DS.DNR =  
#### \% |> env1\$f\$f_df.Table1byExposure.xlsx(VarNames4Exposure =  c("SEX"))  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# # \$ assign( DSN, read_rds(paste0(.path4read,"/",DSN,".rds")) ) ====  
# # .path4read = file.path(env1$path$path0,"Rproject_KNHIS.CohortGJ0910 NoHx")
# # DSN = "CohortGJ0910.BaselineJKGJ2085NoHx.drop_na.MetS_NoMeds"
# .path4read = paste0(env1$path$path1,"/data")
# DSN = "CohortGJ0910.BaselineJKGJ2085NoHx...01" |> str_replace("\\.rds$", "")
# assign( DSN, read_rds(paste0(.path4read,"/",DSN,".rds")) )
# 
# CohortGJ0910.BaselineJKGJ2085NoHx...01 |> names() |> paste0(collapse = ", ") |> cat("  \n", sep="") ###### |> cat("  \n", sep="") ----
# # > CohortGJ0910.BaselineJKGJ2085NoHx...01 |> names() |> paste0(collapse = ", ") |> cat("  \n", sep="") ###### |> cat("  \n", sep="") ----  
# # PERSON_ID, EnrollYear, SEX, AGE_GROUP, DTH_YM, DTH_CODE1, DTH_CODE2, SIDO, SGG, IPSN_TYPE_CD, CTRB_PT_TYPE_CD, DFAB_GRD_CD, DFAB_PTN_CD, DFAB_REG_YM, YKIHO_GUBUN_CD, 
# # HEIGHT, WEIGHT, 
# # BP_HIGH, BP_LWST, BLDS, 
# # TOT_CHOLE, 
# # HMG, OLIG_PROTE_CD, SGOT_AST, SGPT_ALT, GAMMA_GTP, FMLY_HPRTS_PATIEN_YN, FMLY_APOP_PATIEN_YN, FMLY_HDISE_PATIEN_YN, FMLY_DIABML_PATIEN_YN, FMLY_CANCER_PATIEN_YN, SMK_STAT_TYPE_RSPS_CD, DRNK_HABIT_RSPS_CD, TM1_DRKQTY_RSPS_CD, 
# # WAIST, TRIGLYCERIDE, HDL_CHOLE, LDL_CHOLE, 
# # CREATININE, HCHK_APOP_PMH_YN, HCHK_HDISE_PMH_YN, HCHK_HPRTS_PMH_YN, HCHK_DIABML_PMH_YN, HCHK_HPLPDM_PMH_YN, HCHK_ETCDSE_PMH_YN, PAST_SMK_TERM_RSPS_CD, PAST_DSQTY_RSPS_CD, CUR_SMK_TERM_RSPS_CD, CUR_DSQTY_RSPS_CD, MOV20_WEK_FREQ_ID, MOV30_WEK_FREQ_ID, WLK30_WEK_FREQ_ID, HCHK_PHSS_PMH_YN, n.ICD_E0814, minDate.ICD_E0814, maxDate.ICD_E0814, diffDate.ICD_E0814, n.ICD_I1016, minDate.ICD_I1016, maxDate.ICD_I1016, diffDate.ICD_I1016, n.ICD_I2025, minDate.ICD_I2025, maxDate.ICD_I2025, diffDate.ICD_I2025, n.ICD_I3052, minDate.ICD_I3052, maxDate.ICD_I3052, diffDate.ICD_I3052, n.ICD_I6069, minDate.ICD_I6069, maxDate.ICD_I6069, diffDate.ICD_I6069, n.ICD_I7079, minDate.ICD_I7079, maxDate.ICD_I7079, diffDate.ICD_I7079, Female, BMI, BMI_lt185, BMI_ge185lt230, BMI_ge230lt250, BMI_ge185lt250, BMI_ge250lt300, BMI_ge300, BMI_ge350, BMI_ge400, 
# # BMI.4bins, FPG, 
# # FPG_ge100, FPG_ge126, 
# # SBP, DBP, BP_ESCESH2018, 
# # FPG_ge100lt126, 
# # TRIGLYCERIDE_ge150, HDL_CHOLE_lt4050, WAIST_ge9080, WAIST_ge9085, BP_ge130_85, 
# # nMetS_NoMeds_WAIST_ge9080, nMetS_NoMeds_WAIST_ge9080.ge3, 
# # nMetS_NoMeds_WAIST_ge9085, nMetS_NoMeds_WAIST_ge9085.ge3


##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# # :: DS.DNR = DataSet.Date.NA.rmAllNA = =====
# DS.DNR = CohortGJ0910.BaselineJKGJ2085NoHx...01 %>% 
#     rownames_to_column() 

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# DS.DNR %>% 
#     select(
#         SEX,
#         HEIGHT, WEIGHT, 
#         BMI.4bins, 
#         WAIST, 
#         WAIST_ge9080, WAIST_ge9085, 
#         SBP, DBP, BP_ESCESH2018, 
#         BP_ge130_85, 
#         FPG, 
#         FPG_ge100, FPG_ge126, 
#         TOT_CHOLE, 
#         TRIGLYCERIDE, 
#         HDL_CHOLE, LDL_CHOLE, 
#         TRIGLYCERIDE_ge150, HDL_CHOLE_lt4050, 
#         nMetS_NoMeds_WAIST_ge9080, nMetS_NoMeds_WAIST_ge9080.ge3, 
#         nMetS_NoMeds_WAIST_ge9085, nMetS_NoMeds_WAIST_ge9085.ge3
#     ) |> env1$f$f_df.Table1byExposure.xlsx(DSN4output = "CohortGJ0910.BaselineJKGJ2085NoHx...01.select_MetS", VarNames4Exposure =  c("SEX"))
```
  
  
# __________|------  
# @@ DATA) select(matches(VarName.suffix.regex)) ----  
## @ VarNames.select.vec = VarNames.select.txt %>% strsplit("\n") %>% unlist
## :: VarName.suffix.regex = VarNames.select.vec %>% paste0(collapse="|")
## :: DS.DNR = get(DSN) |> select(matches(VarName.suffix.regex))
### \% |> select(matches("A0[0-3]")) ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
VarNames.select.txt = "SEX
AGE
DRINK
SMOKE
PACKYR
PHYACTL
PHYACTM
PHYACTH
MET
EXERCUR
EXER
EXERFQ
EXERDU
IB1_2
IB1_3
IB1_4
BODYFAT
OBDIG1
OBDIG2
OBDEG
HBA1C
GLU0_TR
GLU60_TR
GLU120_TR
R_GTP_TR
TCHL_TR
HDL_TR
TRIGLY_TR
INS0
INS60
INS120
SBP_L
DBP_L
SBP_R
DBP_R
WAIST
HIP
MEALRG
OVEREAT
MEALSPD
MEATFAT
CKOIL
CKOILETC
SPCOIL
SPCOILETC
RMEALFQA
BMEALFQA
SKPMEAL
ALNMEALFQ
FRFOILY
B01
B02
B03
B04
B24"

VarNames.select.vec = VarNames.select.txt %>% strsplit("\n") %>% unlist
VarNames.select.vec %>% dput
# > VarNames.select.vec %>% dput
c("SEX", "AGE", "DRINK", "SMOKE", "PACKYR",
  "PHYACTL", "PHYACTM", "PHYACTH", "MET", "EXERCUR", "EXER", "EXERFQ", "EXERDU",
  "BODYFAT", "OBDIG1", "OBDIG2", "OBDEG", # "IB1_2", "IB1_3", "IB1_4",
  "HBA1C", "GLU0_TR", "GLU60_TR", "GLU120_TR",
  "R_GTP_TR",
  "TCHL_TR", "HDL_TR", "TRIGLY_TR",
  "INS0", "INS60", "INS120",
  "SBP_L", "DBP_L", "SBP_R", "DBP_R",
  "WAIST", "HIP",
  "BRF", "MEALRG", "AFTDNN", "OVEREAT", "MEALSPD",
  "MEATFAT", # "CKOIL", "CKOILETC", "SPCOIL", "SPCOILETC", "RMEALFQA", "BMEALFQA", "SKPMEAL", "ALNMEALFQ", "FRFOILY",
  "B01", "B02", "B03", "B04", "B24")
VarName.suffix.regex = VarNames.select.vec %>% paste0(collapse="|")
VarName.suffix.regex %>% dput
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# :: DS.DNR = DataSet.Date.NA.rmAllNA = ===== 
# if(!exists("DSN")) {  warning('!exists("DSN"); '); DSsampleName = "df_NewDMv3.CensorEND.n88.select293.NR.recode.lbl.fct"; cat("DSsampleName == ", deparse(DSsampleName), "\n", sep = ""); assign(DSsampleName, read_csv(paste0(env1$path$path0,"/Rproject_KoGES_AA10030/",DSsampleName,".UTF8.csv")))  }  
if(!exists("DSN")) {  warning('!exists("DSN"); '); DSsampleName = "as1_7.na.Date.fct.select.sample.03"; cat("DSsampleName == ", deparse(DSsampleName), "\n", sep = ""); assign(DSsampleName, read_rds(paste0(env1$path$path0,"/Rproject_KoGES_AA10030/",DSsampleName,"/",DSsampleName,".rds.xz")))  }  
DS.DNR = get(DSN) %>% 
    select(matches(VarName.suffix.regex)) %>% # select(matches(VarName.suffix.regex), matches("A0[0-2]")) %>%
    # select(matches("A00|A01|A04|A07"))
    # select(matches("A00|A01|A07"))
    select(matches("A0[0-3]"))
# DS.DNR = DS.DNR[sort(names(DS.DNR))]
DS.DNR = DS.DNR %>% mutate_if(function(vec) {is.numeric(vec) && n_distinct(vec) <= 10}, as.factor)
DS.DNR |> str(max.level = 2, give.attr = TRUE)
```
  

## \$ df_NewDMv3.CensorEND.n88.select293.NR.recode  
## \$ df_NewDMv3.CensorEND.n88.select293.NR.recode.lbl.fct  
### :: VarName.suffix.regex = "A0[0-2]"
### :: DS.DNR = get(DSN) |> select(matches(VarName.suffix.regex))
#### \% |> select(matches("A0[0-3]")) ----  
#### \% |> env1\$f\$f_df.Table1byExposure.xlsx(VarNames4Exposure =  c("A01_BMI.5bins"))  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.path4read = paste0(env1$path$path0,"/Rproject_KoGES_AA10030")
# DSN = "df_NewDMv3.CensorEND.n88.select293.NR.recode"
DSN = "df_NewDMv3.CensorEND.n88.select293.NR.recode.lbl.fct"

# env1$f$f_DSname.Search.read.checkEntity(DSN = DSN, ext = "rds", .path4read = .path4read, vec_candidate4ID = c("rowname", "rownum", "Num", "ID", "CompositeKey", "PERSON_ID", "RN_INDI", "NIHID"), BreathFirstSearch = TRUE, max_depth = 3, .width.cutoff=120-15, print2console = TRUE, return.output = TRUE, print.name.dput = FALSE, print.names.tidyeval = FALSE, VERBOSE = isTRUE(getOption("verbose")))
assign(  DSN, read_csv(file.path(.path4read, paste0(DSN,".UTF8.csv")))  )   
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
VarName.suffix.regex =
    c(
        paste0("A0[1-5]_",
               c("WEIGHT", "HEIGHT",
                 "BMI.5bins")),
        # outer(c("delta", "pdelta"), 1:4, paste0),
        paste0("A02_", ".*",
               c("delta", "pdelta"),
               "1"),
        paste0("A03_", ".*",
               c("delta", "pdelta"),
               "1"),
        paste0("A03_", ".*",
               c("delta", "pdelta"),
               "2"),
        paste0("A05_", ".*",
               c("delta", "pdelta"),
               "4"),
        paste0("A00_",
               c("SEX")),
        "Female",
        paste0("A01_",
               c("AGE", "INCOME",
                 "WAIST", "HIP",
                 "BODYFAT", "OBDIG1", "OBDIG2", "OBDEG",
                 # "BP", "PULSE", "HTN_C", "HTNCU", "TREATD1", "DRUGHTCU", "FMHTN",
                 "PULSE", "HTN_C", "HTNCU", "DRUGHTCU", "FMHTN",
                 "HBA1C", "GLU0_TR", "GLU60_TR", "GLU120_TR", "DM_C", "DMCU", "TREATD2", "DRUGDMCU", "DRUGINSCU", "FMDM",
                 "INS0", "INS60", "INS120", 
                 # "PHYSTB", "PHYSIT", 
                 # "PHYACTL", "PHYACTM", "PHYACTH",
                 "MET", "EXERCUR", "EXER", "EXERDU", # "EXERFQ", 
                 "BRF", "MEALRG", "AFTDNN", "OVEREAT", "MEALSPD",
                 "MEATFAT", # "CKOIL", "CKOILETC", "SPCOIL", "SPCOILETC", "RMEALFQA", "BMEALFQA", "SKPMEAL", "ALNMEALFQ", "FRFOILY",
                 "B01", "B02", "B03", "B04", "B24", 
                 "DRINK", # "DRDU",
                 "SMOKE", "PACKYR", # "SMAG", "SMDU", "SMAM", "PSM", "PSMDU",
                 "TCHL_TR", "HDL_TR", "TRIGLY_TR", "LIPCU", 
                 # "MICU", "CHFCU", "CADCU", "PVDCU", "TREATD8", "FMHEA",
                 # "R_GTP_TR", 
                 # "CEVACU",
                 # "KIDCU", "TREATD14",
                 "EDATE"))
    ) %>% paste0(collapse="|")
VarName.suffix.regex %>% dput
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# :: DS.DNR = DataSet.Date.NA.rmAllNA = ===== 
# if(!exists("DSN")) {  warning('!exists("DSN"); '); DSsampleName = "df_NewDMv3.CensorEND.n88.select293.NR.recode.lbl.fct"; cat("DSsampleName == ", deparse(DSsampleName), "\n", sep = ""); assign(DSsampleName, read_csv(paste0(env1$path$path0,"/Rproject_KoGES_AA10030/",DSsampleName,".UTF8.csv")))  }  
if(!exists("DSN")) {  warning('!exists("DSN"); '); DSsampleName = "as1_7.na.Date.fct.select.sample.03"; cat("DSsampleName == ", deparse(DSsampleName), "\n", sep = ""); assign(DSsampleName, read_rds(paste0(env1$path$path0,"/Rproject_KoGES_AA10030/",DSsampleName,"/",DSsampleName,".rds.xz")))  }  
DS.DNR = get(DSN) %>% 
    select(matches(VarName.suffix.regex)) %>% # select(matches(VarName.suffix.regex), matches("A0[0-2]")) %>%
    # select(matches("A00|A01|A04|A07"))
    # select(matches("A00|A01|A07"))
    select(matches("A0[0-3]"))
# DS.DNR = DS.DNR[sort(names(DS.DNR))]
DS.DNR = DS.DNR %>% mutate_if(function(vec) {is.numeric(vec) && n_distinct(vec) <= 10}, as.factor)
DS.DNR |> str(max.level = 2, give.attr = TRUE)

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
.VarNames4Exposure =  c("A01_BMI.5bins")  
.DSN4output = DSN
# DS.DNR |> env1$f$f_df.Table1byExposure.xlsx(DSN4output = .DSN4output, VarNames4Exposure = .VarNames4Exposure, output.xlsx = Sys.getenv("PARENT_RENDERING") != "YES") |> env1$f$f_expression.eval.withCallingHandlers.attr_warnings.summary()
```



# __________|------  
# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```


## library(gtsummary) ----  
## ECHO \% devtools::install_github("zheer-kejlberg/Z.gtsummary.addons") ----  
## library(Z.gtsummary.addons) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

.packagename = "gtsummary"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}

for(.packagename in c("devtools")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  

devtools::install_github("zheer-kejlberg/Z.gtsummary.addons")
library(Z.gtsummary.addons)
```


    
    
### **ECHO** \% |> tbl_summary(by, statistic = list(all_continuous() ~ "{median} ({p25};{p75})", all_categorical() ~ "{n} ({p}%)")) ---- 
#### \% |> add_n() ----  
#### \% |> add_overall() ----  
#### **ECHO** \% |> add_SMD(location = "both", ci = TRUE, ci_bracket = "()", ci_sep = ";", ref_group = TRUE) ----  
#### **ECHO** \% |> add_p() ----  
##### **ECHO** \% |> modify_header(all_stat_cols() ~ "**{level}**  \nN = {n} ({style_percent(p)}%)", p.value ~ "***p***") ----  
###### **ECHO** \% |> modify_spanning_header(all_stat_cols() ~ paste0("**",labelled::var_label(byVar),"**")) ----  
##### **ECHO** \% |> bold_p(t = 0.10) ----  
##### **ECHO** \% |> bold_labels() ----  
##### **ECHO** \% |> italicize_levels() ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
GT1 = trial %>% 
    # select(grade, age, stage) %>% 
    # tbl_summary(by = grade, include = c(age, stage)) %>%
    # tbl_summary(by = grade) %>%
    tbl_summary(
        by = grade,
        statistic = list(all_continuous() ~ "{median} ({p25};{p75})", all_categorical() ~ "{n} ({p}%)"),
        # statistic = list(all_continuous() ~ "**{median}** ({p25};{p75})", all_categorical() ~ "{n} (**{p}%**)"),
        missing = "ifany"
    ) |> 
    # add_n() %>%
    # add_overall() |>
    add_SMD(location = "both", ci = TRUE, ci_bracket = "()", ci_sep = ";", ref_group = TRUE) %>%
    add_p() |>
    modify_header(all_stat_cols() ~ "**{level}**  \nN = {n} ({style_percent(p)}%)", p.value ~ "***p***") |>
    # modify_spanning_header(all_stat_cols() ~ paste0("**",labelled::var_label(trial$grade),"**"), starts_with("SMD") ~ "**{colname |> str_replace("^SMD: ","")}**", starts_with("p.value") ~ "***p***") |>
    modify_spanning_header(all_stat_cols() ~ paste0("**",labelled::var_label(trial$grade),"**")) |>
    bold_p(t = 0.10) |>
    bold_labels() |>
    italicize_levels()
GT1 %>% show_header_names
GT1$table_body %>% select(starts_with("variable"), label, starts_with("stat"), starts_with("SMD"), starts_with("test_result") , starts_with("statistic"), starts_with("parameter") , p.value) |> print(n=99)
GT1 |>
    print() |> invisible()
```
  
  
## \$ df_NewDMv3.CensorEND.n88.select293.NR.recode.lbl.fct  
### :: VarName.suffix.regex = "A0[0-2]"
### :: DS.DNR = get(DSN) |> select(matches(VarName.suffix.regex))

### **ECHO** \% |> tbl_summary(by, statistic = list(all_continuous() ~ "{median} ({p25};{p75})", all_categorical() ~ "{n} ({p}%)")) ---- 
#### \% |> add_n() ----  
#### \% |> add_overall() ----  
#### **ECHO** \% |> add_SMD(location = "both", ci = TRUE, ci_bracket = "()", ci_sep = ";", ref_group = TRUE) ----  
#### **ECHO** \% |> add_p() ----  
##### **ECHO** \% |> modify_header(all_stat_cols() ~ "**{level}**  \nN = {n} ({style_percent(p)}%)", p.value ~ "***p***") ----  
##### **ECHO** \% |> modify_table_body(  ~ .x %>% mutate( label = if_else(row_type == "level", label, if_else(label == variable, label, paste0(variable, " (", label, ")"))) )  ) ----  
###### **ECHO** \% |> modify_spanning_header(all_stat_cols() ~ paste0("**",labelled::var_label(byVar),"**")) ----  
##### **ECHO** \% |> bold_p(t = 0.10) ----  
##### **ECHO** \% |> bold_labels() ----  
##### **ECHO** \% |> italicize_levels() ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
.byVar = "A01_BMI.5bins"
DS = DS.DNR %>% 
    mutate_if(is.factor, droplevels) %>% 
    select_if(function(x) !all(is.na(x))) %>% 
    select_if(function(vec) !is.Date(vec))
env1$env.internal.attach$Sys.time.set_t0()
GT1 = DS %>% 
    mutate_if(is.factor, droplevels) %>% 
    select_if(function(x) !all(is.na(x))) %>% 
    select_if(function(vec) !is.Date(vec)) %>% 
    tbl_summary(
        by = !!rlang::sym(.byVar),
        statistic = list(all_continuous() ~ "{median} ({p25};{p75})", all_categorical() ~ "{n} ({p}%)"),
        # statistic = list(all_continuous() ~ "**{median}** ({p25};{p75})", all_categorical() ~ "{n} (**{p}%**)"),
        missing = "ifany"
    ) |> 
    # add_n() %>%
    # add_overall() |>
    # add_SMD(location = "both", ci = TRUE, ci_bracket = "()", ci_sep = ";", ref_group = TRUE) %>%
    add_p() |>
    modify_header(label = "**Variable (label)**", all_stat_cols() ~ "**{level}**  \nN = {n} ({style_percent(p)}%)", p.value ~ "***p***") |> 
    # modify_table_styling(columns = "label", fmt_fun = function(i.label) {paste0(names(DS), " (", i.label, ")")}) |>
    modify_table_body(  ~ .x %>% mutate( label = if_else(row_type == "level", label, if_else(label == variable, label, paste0(variable, " (", label, ")"))) )  ) |>
    # modify_spanning_header(all_stat_cols() ~ paste0("**",labelled::var_label(trial$grade),"**"), starts_with("SMD") ~ "**{colname |> str_replace("^SMD: ","")}**", starts_with("p.value") ~ "***p***") |>
    # modify_spanning_header(all_stat_cols() ~ paste0("**",.$meta_data %>% filter(variable == .byvar) %>% pull(var_label),"**")) |>
    modify_spanning_header(all_stat_cols() ~ paste0("**",ifelse(is.null(labelled::var_label(DS[[.byVar]])), .byVar, labelled::var_label(DS[[.byVar]])),"**")) |>
    bold_p(t = 0.10) |>
    bold_labels() |>
    italicize_levels()
env1$env.internal.attach$Sys.time.from_t0()
GT1 %>% show_header_names
GT1$table_body %>% select(starts_with("variable"), label, starts_with("stat"), starts_with("SMD"), starts_with("test_result") , starts_with("statistic"), starts_with("parameter") , p.value) |> print(n=99)
GT1 |>
    print() |> invisible()
```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ SOURCE) ----  
```{r RUN-ALL-CHUNKS-ABOVE, echo=FALSE, results="hide", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
```


```{r .RelativeSubPath_FileName.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
options(DEVMODE = TRUE);  # isTRUE(getOption("DEVMODE"))
# .RelativeSubPath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(env1$f$f_object.is_not_null.nor_na.nor_blank(env1$path$LastSourceEditorContext.path_FileNameExt)) {    .RelativeSubPath = env1$path$LastSourceEditorContext.path_FileNameExt |> dirname() |> env1$f$f_path.relative()  ;    ".RelativeSubPath" |> env1$f$f_ObjectName.get.dput.ECHO()    }
# if(.RelativeSubPath!="") .RelativeSubPath |> normalizePath(winslash="/",mustWork=TRUE) |> utils::browseURL() |> try()
# .FileName.source.r = "default.template" |> paste0(".source.r")
if(env1$f$f_object.is_not_null.nor_na.nor_blank(env1$path$LastSourceEditorContext.path_FileNameExt)) {    .SourceName_root = env1$path$LastSourceEditorContext.path_FileNameExt |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),"")  ;    ".SourceName_root" |> env1$f$f_ObjectName.get.dput.ECHO()    }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$f$showCodeText2open.FileName.source.r(.RelativeSubPath, .FileName.source.r)
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.RelativeSubPath_FileName.source.r) )  ----  
# env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = list(.RelativeSubPath, .FileName.source.r) %>% {.[nzchar(.)]} %>% c(fsep = "/") %>% {do.call(file.path, .)})
```
  
  
# __________|------  
# @@ START) function ----  
## \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  

###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
  
```{r writeRDS-EvalNoEchoNoMsgNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# __________|------  
## @ write_rds( get(.objectname), paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".rds",".xz"), compress = "xz", compression = 9L) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n") ----
if (Sys.getenv("PARENT_RENDERING") != "YES") {    
    .path4write = .path4write %>% str_replace(fixed(env1$path$path1), "") %>% str_replace("^/", "")  # [][Rproject] makes an error in git bash
    if(exists("MetaData") && !is.null(unlist(MetaData))) {
        # MetaData$DSnames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
        cat("    ________________________________________________________________________    \n")
        for (DSname in names(MetaData$DSnames)) {    
            if(exists(DSname)) {
                assign(DSname, structure(get(DSname, envir = .GlobalEnv), MetaData = as.environment(MetaData)), envir = .GlobalEnv)
                if(is.null(attributes(.GlobalEnv[[DSname]])$DSname)) attributes(.GlobalEnv[[DSname]])$DSname = DSname
                if(attributes(.GlobalEnv[[DSname]])$DSname != DSname) attributes(.GlobalEnv[[DSname]])$DSname = DSname
                if (!is.null(attributes(attributes(.GlobalEnv[[DSname]])$DSname)$.path_file)) {
                    message( "attributes(attributes(",DSname,")$DSname)$.path_file == ",deparse(attributes(attributes(get(DSname))$DSname)$.path_file) )
                    env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = DSname, .path_file = attributes(attributes(.GlobalEnv[[DSname]])$DSname)$.path_file, createBACKUP = FALSE, EXECUTE = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE)
                } else {
                    env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = DSname, .path4write = .path4write, createBACKUP = FALSE, EXECUTE = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE)
                }
            } else {  message("!exists(",deparse(DSname),")")  }
            cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        }
    }
    # #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
    # .path_FileName.xlsx = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".xlsx") |> str_replace("^D:/D_Repositories", "D:/OneDrive/[][Rproject]")  ;  openxlsx2::write_xlsx(get(.objectname), file = .path_FileName.xlsx, as_table=TRUE, table_style="none", row_names=TRUE, col_widths="auto", first_active_row=2, first_active_col=2) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")  ;  if (Sys.info()["sysname"] == "Linux") browseURL(.path_FileName.xlsx) else openxlsx2::xl_open(.path_FileName.xlsx)
    # #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
    # .path_FileName.UTF8BOM.csv = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".UTF8BOM.csv") |> str_replace("^D:/D_Repositories", "D:/OneDrive/[][Rproject]")
    # if (Sys.info()["sysname"] == "Windows") {
    #     readr::write_excel_csv(get(.objectname), file = .path_FileName.UTF8BOM.csv) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
    #     openxlsx2::xl_open(.path_FileName.UTF8BOM.csv)
    # } else {
    #     readr::write_excel_csv(get(.objectname), file = .path_FileName.UTF8BOM.csv|>paste0(".xz")) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
    # }
    # #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
    # .path_FileName.UTF8.csv.xz = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".UTF8.csv.xz")
    # readr::write_csv(get(.objectname), file = .path_FileName.UTF8.csv.xz) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    
}


.path4write = env1$path$path1
.objectname = "GT1"
write_rds( get(.objectname), paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".rds",".xz"), compress = "xz", compression = 9L) |> system.time()

library(flextable)
.flextable = get(.objectname) %>% as_flex_table() 
.flextable %>% save_as_docx(path = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".docx"))

for(.packagename in c("remotes", "flexlsx")) {if(!require(.packagename,character.only=TRUE)) remotes::install_github("pteridin/flexlsx")  ;  library(.packagename,character.only=TRUE)}
.wb <- openxlsx2::wb_workbook()
.wb$add_worksheet(.objectname)
.wb <- .wb %>% flexlsx::wb_add_flextable(.objectname, .flextable, start_col = 2, start_row = 3)    # offset the table to cell 'C2'
.wb$save("GT1.flextable.xlsx")
```
  
  
```{r createBACKUP, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%dT%H", overwrite=TRUE)
        # env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%dT%H", overwrite=TRUE)
    # }
}
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_FileName.nb.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") {  try(  paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE),'"') |> shell(wait=FALSE)  )  }  # else { browseURL(env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE)) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileNameExt) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileName.nb.html) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
