---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = options()$width; cat(options()$width, "  \n", sep="")
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)
```
  
  
```{r MetaData0-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}

```
  
  
# @@ START) source ----  
### @ .subpath, .sourcename = "f_df.Table1byExposure.xlsx" |> paste0(".source.r") ----  
```{r .subpath.filename.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
.subpath = r"(Rdev/60_communicate_report_export)" |> str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
# if(.subpath!="") utils::browseURL(normalizePath(.subpath))
.sourcename = "f_df.Table1byExposure.xlsx" |> paste0(".source.r")
### \% source( file.path(env1$path$source_base,.subpath.filename.source.r) ) ----  
.subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% .GlobalEnv$env1$source) {cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); source( file.path(env1$path$source_base,.subpath.filename.source.r) ); .GlobalEnv$env1$source[[.sourcename]] = TRUE}
```
  
  
# @@ START) Data ----  
## \$ CohortGJ0910.BaselineJKGJ2085NoHx...01  
### \$ DataSet.Date.NA.rmAllNA =  
#### \% |> env1\$f\$f_df.Table1byExposure.xlsx(VarNames4Exposure =  c("SEX"))  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# # \$ assign( DataSetName, read_rds(paste0(.path4read,"/",DataSetName,".rds")) ) ====  
# # .path4read = file.path(env1$path$path0,"Rproject_KNHIS.CohortGJ0910 NoHx")
# # DataSetName = "CohortGJ0910.BaselineJKGJ2085NoHx.drop_na.MetS_NoMeds"
# .path4read = paste0(env1$path$path1,"/data")
# DataSetName = "CohortGJ0910.BaselineJKGJ2085NoHx...01" |> str_replace("\\.rds$", "")
# assign( DataSetName, read_rds(paste0(.path4read,"/",DataSetName,".rds")) )
# 
# CohortGJ0910.BaselineJKGJ2085NoHx...01 |> names() |> paste0(collapse = ", ") |> cat("  \n", sep="") ###### |> cat("  \n", sep="") ----
# # > CohortGJ0910.BaselineJKGJ2085NoHx...01 |> names() |> paste0(collapse = ", ") |> cat("  \n", sep="") ###### |> cat("  \n", sep="") ----  
# # PERSON_ID, EnrollYear, SEX, AGE_GROUP, DTH_YM, DTH_CODE1, DTH_CODE2, SIDO, SGG, IPSN_TYPE_CD, CTRB_PT_TYPE_CD, DFAB_GRD_CD, DFAB_PTN_CD, DFAB_REG_YM, YKIHO_GUBUN_CD, 
# # HEIGHT, WEIGHT, 
# # BP_HIGH, BP_LWST, BLDS, 
# # TOT_CHOLE, 
# # HMG, OLIG_PROTE_CD, SGOT_AST, SGPT_ALT, GAMMA_GTP, FMLY_HPRTS_PATIEN_YN, FMLY_APOP_PATIEN_YN, FMLY_HDISE_PATIEN_YN, FMLY_DIABML_PATIEN_YN, FMLY_CANCER_PATIEN_YN, SMK_STAT_TYPE_RSPS_CD, DRNK_HABIT_RSPS_CD, TM1_DRKQTY_RSPS_CD, 
# # WAIST, TRIGLYCERIDE, HDL_CHOLE, LDL_CHOLE, 
# # CREATININE, HCHK_APOP_PMH_YN, HCHK_HDISE_PMH_YN, HCHK_HPRTS_PMH_YN, HCHK_DIABML_PMH_YN, HCHK_HPLPDM_PMH_YN, HCHK_ETCDSE_PMH_YN, PAST_SMK_TERM_RSPS_CD, PAST_DSQTY_RSPS_CD, CUR_SMK_TERM_RSPS_CD, CUR_DSQTY_RSPS_CD, MOV20_WEK_FREQ_ID, MOV30_WEK_FREQ_ID, WLK30_WEK_FREQ_ID, HCHK_PHSS_PMH_YN, n.ICD_E0814, minDate.ICD_E0814, maxDate.ICD_E0814, diffDate.ICD_E0814, n.ICD_I1016, minDate.ICD_I1016, maxDate.ICD_I1016, diffDate.ICD_I1016, n.ICD_I2025, minDate.ICD_I2025, maxDate.ICD_I2025, diffDate.ICD_I2025, n.ICD_I3052, minDate.ICD_I3052, maxDate.ICD_I3052, diffDate.ICD_I3052, n.ICD_I6069, minDate.ICD_I6069, maxDate.ICD_I6069, diffDate.ICD_I6069, n.ICD_I7079, minDate.ICD_I7079, maxDate.ICD_I7079, diffDate.ICD_I7079, Female, BMI, BMI_lt185, BMI_ge185lt230, BMI_ge230lt250, BMI_ge185lt250, BMI_ge250lt300, BMI_ge300, BMI_ge350, BMI_ge400, 
# # BMI.cut4, FPG, 
# # FPG_ge100, FPG_ge126, 
# # SBP, DBP, BP_ESCESH2018, 
# # FPG_ge100lt126, 
# # TRIGLYCERIDE_ge150, HDL_CHOLE_lt4050, WAIST_ge9080, WAIST_ge9085, BP_ge130_85, 
# # nMetS_NoMeds_WAIST_ge9080, nMetS_NoMeds_WAIST_ge9080.ge3, 
# # nMetS_NoMeds_WAIST_ge9085, nMetS_NoMeds_WAIST_ge9085.ge3


#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# DataSet.Date.NA.rmAllNA = CohortGJ0910.BaselineJKGJ2085NoHx...01 %>% 
#     rownames_to_column() 

#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# DataSet.Date.NA.rmAllNA %>% 
#     select(
#         SEX,
#         HEIGHT, WEIGHT, 
#         BMI.cut4, 
#         WAIST, 
#         WAIST_ge9080, WAIST_ge9085, 
#         SBP, DBP, BP_ESCESH2018, 
#         BP_ge130_85, 
#         FPG, 
#         FPG_ge100, FPG_ge126, 
#         TOT_CHOLE, 
#         TRIGLYCERIDE, 
#         HDL_CHOLE, LDL_CHOLE, 
#         TRIGLYCERIDE_ge150, HDL_CHOLE_lt4050, 
#         nMetS_NoMeds_WAIST_ge9080, nMetS_NoMeds_WAIST_ge9080.ge3, 
#         nMetS_NoMeds_WAIST_ge9085, nMetS_NoMeds_WAIST_ge9085.ge3
#     ) |> env1$f$f_df.Table1byExposure.xlsx(DataSetName4output = "CohortGJ0910.BaselineJKGJ2085NoHx...01.select_MetS", VarNames4Exposure =  c("SEX"))
```
  

## \$ df_NewDMv3.CensorEND.n88.select293.NA.rmAllNA.recode  
### @ VarName.suffix.regex = "A0[0-2]"
### :: DataSet.Date.NA.rmAllNA = get(DataSetName) |> select(matches(VarName.suffix.regex))
#### \% |> select(matches("A0[0-3]")) ----  
#### \% |> env1\$f\$f_df.Table1byExposure.xlsx(VarNames4Exposure =  c("A01_BMI.cut5"))  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
.path4read = paste0(env1$path$path0,"/Rproject_KoGES_AA10030/df_NewDMv3.CensorEND.n88.select971.NA.rmAllNA.recode")
DataSetName = "df_NewDMv3.CensorEND.n88.select293.NA.rmAllNA.recode"
paste0(.path4read,"/",DataSetName,".rds") |> env1$f$f_DataSet_path_filename_ext.read.checkEntity()

#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
VarName.suffix.regex =
    c(
        paste0("A0[1-5]_",
               c("WEIGHT", "HEIGHT",
                 "BMI.cut5")),
        # outer(c("delta", "pd"), 1:4, paste0),
        paste0("A02_", ".*",
               c("delta", "pd"),
               "1"),
        paste0("A02_", ".*",
               c("delta", "pd"),
               "1"),
        paste0("A03_", ".*",
               c("delta", "pd"),
               "2"),
        paste0("A05_", ".*",
               c("delta", "pd"),
               "4"),
        paste0("A00_",
               c("SEX")),
        "Female",
        paste0("A01_",
               c("EDATE", "AGE", "INCOME",
                 "WAIST", "HIP",
                 "BODYFAT", "OBDIG1", "OBDIG2", "OBDEG",
                 # "BP", "PULSE", "HTN_C", "HTNCU", "TREATD1", "DRUGHTCU", "FMHTN",
                 "PULSE", "HTN_C", "HTNCU", "DRUGHTCU", "FMHTN",
                 "HBA1C", "GLU0_TR", "DM_C", "DMCU", "TREATD2", "DRUGDMCU", "DRUGINSCU", "FMDM",
                 "PHYSTB", "PHYSIT", "MET", "EXERCUR", "EXER", "EXERFQ", "EXERDU",
                 "BRF", "MEALRG", "AFTDNN",
                 "DRINK", "DRDU",
                 "SMOKE", "SMAG", "SMDU", "SMAM", "PSM", "PSMDU",
                 "LIPCU",
                 "MICU", "CHFCU", "CADCU", "PVDCU", "TREATD8", "FMHEA",
                 "CEVACU",
                 "KIDCU", "TREATD14"))
    ) %>% paste0(collapse="|")
VarName.suffix.regex %>% dput
DataSet.Date.NA.rmAllNA = get(DataSetName) %>% select(matches(VarName.suffix.regex), matches("A0[0-2]")) %>%
    # select(matches("A00|A01|A04|A07"))
    # select(matches("A00|A01|A07"))
    select(matches("A0[0-3]"))
DataSet.Date.NA.rmAllNA = DataSet.Date.NA.rmAllNA[sort(names(DataSet.Date.NA.rmAllNA))]
DataSet.Date.NA.rmAllNA = DataSet.Date.NA.rmAllNA %>% mutate_if(function(vec) {is.numeric(vec) && n_distinct(vec) <= 10}, as.factor)
DataSet.Date.NA.rmAllNA %>% str(max.level = 2)

#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
.VarNames4Exposure =  c("A01_BMI.cut5")  
.DataSetName4output = DataSetName
# DataSet.Date.NA.rmAllNA |> env1$f$f_df.Table1byExposure.xlsx(DataSetName4output = .DataSetName4output, VarNames4Exposure = .VarNames4Exposure, output.xlsx = Sys.getenv("PARENT_RENDERING") != "YES")
```


# \% library(tableone) -----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
library(tableone)

```

##@ DataSet.Table1 -----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
# #@ DataSet.Table1 -----  
# # DataSet.Table1 = DataSet.Date.NA.rmAllNA %>% select(-rowname, -PERSON_ID) |> as.data.frame() %>% 
# #     CreateTableOne(data = ., test = T, includeNA = T, addOverall = T)
# DataSet.Table1 = DataSet.Date.NA.rmAllNA %>% 
#     {.[map_lgl(., function(vec) if_else(is.numeric(vec), T, n_distinct(vec) <= 19) )]} |> as.data.frame() %>%  # debug181115 not to remove numeric 
#     CreateTableOne(data = ., test = T, includeNA = T, addOverall = T)
# DataSet.is.na.Table1 = DataSet.Date.NA.rmAllNA %>% 
#     map_df(is.na) %>% setNames(paste0(names(.), ".is.na")) %>% 
#     as.data.frame %>%  # debug181115 not to remove numeric 
#     CreateTableOne(data = ., test = T, includeNA = T, addOverall = T)

# Vars4IQR = names(DataSet.Date.NA.rmAllNA)[DataSet.Date.NA.rmAllNA %>% map_lgl(is.numeric)]

# sink(paste0(.path4write,"/","DataSet.Table1.txt"), append = FALSE)
# DataSet.Table1 |> print(showAllLevels = F, smd = T) ###### |> print(showAllLevels = F, smd = T) ----  
# sink()
# sink(paste0(.path4write,"/","DataSet.Table1.IQR.txt"), append = FALSE)
# DataSet.Table1 |> print(showAllLevels = F, smd = T, nonnormal = Vars4IQR) ###### |> print(showAllLevels = F, smd = T, nonnormal = Vars4IQR) ----  
# sink()


# # =NUMBERVALUE(MID(B2,1,SEARCH("(",B2,1)-1)) ----  
# DataSet.Table1 |> print(showAllLevels = F, nonnormal = NULL, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) %>% 
#     write.csv("DataSet.Table1 -clean.csv")
# DataSet.is.na.Table1 |> print(showAllLevels = F, nonnormal = NULL, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) %>% 
#     write.csv("DataSet.is.na.Table1 -clean.csv")
# # if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open("DataSet.Table1 -clean.csv")

# list(
#     Table1 = DataSet.Table1 |> print(showAllLevels = F, nonnormal = NULL, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) %>% as.data.frame(stringsAsFactors = F) |> rownames_to_column()
#     , Table1.IQR = DataSet.Table1 |> print(showAllLevels = F, nonnormal = Vars4IQR, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) %>% as.data.frame(stringsAsFactors = F) |> rownames_to_column()
#     , is.na.Table1 = DataSet.is.na.Table1 |> print(showAllLevels = F, nonnormal = NULL, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) %>% as.data.frame(stringsAsFactors = F) |> rownames_to_column()
# ) %>% openxlsx2::write_xlsx("DataSet.Table1.xlsx")
# # if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open("DataSet.Table1.xlsx")
```


##@ DataSet.Table1.byExposure -----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
## @ DataSet.Table1.byExposure -----  
DataSet.Date.NA.rmAllNA %>% summarise_all(function(x) sum(is.na(x))) %>% t #-----
DataSet.Date.NA.rmAllNA.select = DataSet.Date.NA.rmAllNA |> as.data.frame() %>% select(-rowname, -PERSON_ID) %>% 
    mutate(Intervention.ge1 = !BMI_ge300) %>% 
    # mutate(Intervention = ifelse(Intervention.ge1 == T, "Intervention", "Control") %>% as.factor)
    # mutate(Intervention = ifelse(Intervention.ge1 == T, "Intervention >= 1", "Intervention == 0") %>% as.factor)
    mutate(InterventionGroup = ifelse(Intervention.ge1 == T, "Group 1", "Group 0") %>% as.factor)
DataSet.Date.NA.rmAllNA.select %>% summarise_all(function(x) sum(is.na(x))) %>% t #-----
# DataSet.Date.NA.rmAllNA.select %>% mutate_if(is.numeric, replace_na, 0)
                          
VarNames4Exposure =  c("InterventionGroup")
DataSetName = "DataSet.Date.NA.rmAllNA"
DataSetName.select = paste0(DataSetName,".select")
DataSetName.Table1byExposure = paste0(DataSetName,".Table1by", VarNames4Exposure)
DataSetName.is.na.Table1byExposure = paste0(DataSetName,".is.na.Table1by", VarNames4Exposure)
DataSetName.select |> cat("  \n", sep="") ###### |> cat("  \n", sep="") ----
DataSetName.Table1byExposure |> cat("  \n", sep="") ###### |> cat("  \n", sep="") ----
DataSetName.is.na.Table1byExposure |> cat("  \n", sep="") ###### |> cat("  \n", sep="") ----
                              
assign(DataSetName.Table1byExposure, 
       get(DataSetName.select) %>% 
           {.[map_lgl(., function(vec) if_else(is.numeric(vec), T, n_distinct(vec) <= 10) )]} |> as.data.frame() %>%  # debug181115 not to remove numeric 
           CreateTableOne(strata = VarNames4Exposure, data = ., test = T, includeNA = T, addOverall = T)
)
assign(DataSetName.is.na.Table1byExposure, 
       get(DataSetName.select) %>% 
           {.[map_lgl(., function(vec) if_else(is.numeric(vec), T, n_distinct(vec) <= 10) )]} %>%
           map_df(is.na) %>% setNames(paste0(names(.), ".is.na") |> str_replace_all("\\`", "")) %>%  # debug) Error in parse(text = x, keep.source = FALSE)
           # mutate( !!rlang::sym(VarNames4Exposure) :=get(DataSetName.select)[[VarNames4Exposure]]) %>%
           cbind(get(DataSetName.select)[VarNames4Exposure]) |>
           as.data.frame() %>%
           CreateTableOne(strata = VarNames4Exposure, data = ., test = T, includeNA = T, addOverall = T)
)

Vars4IQR = names(get(DataSetName.select))[get(DataSetName.select) %>% map_lgl(is.numeric)]
# get(DataSetName.Table1byExposure) |> print(showAllLevels = F, smd = T) ###### |> print(showAllLevels = F, smd = T) ----  
# get(DataSetName.Table1byExposure) |> print(showAllLevels = F, smd = T, nonnormal = Vars4IQR) ###### |> print(showAllLevels = F, smd = T, nonnormal = Vars4IQR) ----  
# get(DataSetName.is.na.Table1byExposure) |> print(showAllLevels = F, smd = T) ###### |> print(showAllLevels = F, smd = T) ----  
# sink(paste0(env1$path$CurrentSource.path,"/",DataSetName.Table1byExposure, " -AllLevels.txt"), append = FALSE)
get(DataSetName.Table1byExposure) |> print(showAllLevels = F, smd = T) ###### |> print(showAllLevels = F, smd = T) ----
# sink()
# sink(paste0(env1$path$CurrentSource.path,"/",DataSetName.Table1byExposure, " -AllLevels -IQR.txt"), append = FALSE)
get(DataSetName.Table1byExposure) |> print(showAllLevels = F, smd = T, nonnormal = Vars4IQR) ###### |> print(showAllLevels = F, smd = T, nonnormal = Vars4IQR) ----
# sink()
# sink(paste0(env1$path$CurrentSource.path,"/",DataSetName.is.na.Table1byExposure, " -AllLevels(is.na).txt"), append = FALSE)
get(DataSetName.is.na.Table1byExposure) |> print(showAllLevels = F, smd = T) ###### |> print(showAllLevels = F, smd = T) ----
# sink()


# =NUMBERVALUE(MID(B2,1,SEARCH("(",B2,1)-1)) ----            
DataSet.is.na.Table1byExposure.print = get(DataSetName.is.na.Table1byExposure) |> print(showAllLevels = F, smd = F, nonnormal = NULL, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) |> as_tibble(rownames = "Variable")
DataSet.is.na.Table1byExposure.print |> print(n=5) ###### |> print(n=5) ----

DataSet.Table1byExposure.print = get(DataSetName.Table1byExposure) |> print(showAllLevels = F, smd = T, nonnormal = NULL, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) |> as_tibble(rownames = "Variable")
DataSet.Table1byExposure.print_showAllLevels = get(DataSetName.Table1byExposure) |> print(showAllLevels = T, smd = T, nonnormal = NULL, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) |> as_tibble(rownames = "Variable")
DataSet.Table1byExposure.print_showAllLevels.IQR = get(DataSetName.Table1byExposure) |> print(showAllLevels = T, smd = T, nonnormal = Vars4IQR, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) |> as_tibble(rownames = "Variable")
DataSet.Table1byExposure.print |> print(n=5) ###### |> print(n=5) ----
DataSet.Table1byExposure.print_showAllLevels |> print(n=5) ###### |> print(n=5) ----
DataSet.Table1byExposure.print_showAllLevels.IQR |> print(n=5) ###### |> print(n=5) ----
              
# DataSet.Table1byExposure.print %>% writexl::write_xlsx(paste0(DataSetName.Table1byExposure, " -clean.xlsx"))
# # if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(paste0(DataSetName.Table1byExposure, " -clean.xlsx"))
# DataSet.Table1byExposure.print_showAllLevels %>% writexl::write_xlsx(paste0(DataSetName.Table1byExposure, " -AllLevels -clean.xlsx"))
# # if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(paste0(DataSetName.Table1byExposure, " -AllLevels -clean.xlsx"))
# DataSet.Table1byExposure.print_showAllLevels.IQR %>% writexl::write_xlsx(paste0(DataSetName.Table1byExposure, " -AllLevels -IQR -clean.xlsx"))
# # if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(paste0(DataSetName.Table1byExposure, " -IQR -clean.xlsx"))
```
  
  
## \% function.DataSet.Table1byExposure.print.addCols() ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
## \% function.DataSet.Table1byExposure.print.addCols() ----
function.DataSet.Table1byExposure.print.addCols = function(DataSet.Table1byExposure.print) {
    DataSet.Table1byExposure.print %>% add_column(level = as.character(NA), .after = "Variable") %>% add_row(.before = 1) |> 
        as.data.frame() %>% {.[1,]=paste0(names(.), " (N = ", .[2,], ")");.[1,1]=VarNames4Exposure;.[1,c("p","test","SMD")]=c("p-value", "test", "SMD");.} %>% 
        select(-p, -test, p, test) %>%
        {names(.)[!names(.) %in% c("Variable", "level", "Overall", "SMD", "p", "test")] = paste0("Group ", 1:(ncol(.)-6));.} %>% 
        add_column(VarType = as.character(NA), .before = "Variable") %>%
        mutate(VarType = if_else(Variable |> str_detect("%"), "factor", VarType), Variable = Variable |> str_replace_all(" \\(%\\)", "")) %>% 
        mutate(VarType = if_else(Variable |> str_detect("^   "), "level", VarType), Variable = Variable |> str_replace_all(" \\(%\\)", "")) %>% 
        mutate(VarType = if_else(Variable |> str_detect("mean"), "numeric", VarType), Variable = Variable |> str_replace_all(" \\(mean \\(SD\\)\\)", "")) %>% 
        mutate(greatest = as.character(NA), G1geG2 = as.logical(NA), G1leG2 = as.logical(NA)) %>% 
        mutate(G1numeric = if_else(VarType == "numeric", `Group 1`, as.character(NA)), G2numeric = if_else(VarType == "numeric", `Group 2`, as.character(NA))) %>% separate(G1numeric, into = paste0("G1", c("mean", "sd")), sep = "[\\(\\)]") %>% separate(G2numeric, into = paste0("G2", c("mean", "sd")), sep = "[\\(\\)]") %>% 
        mutate(G1categorical = if_else(VarType %in% c("factor", "level"), `Group 1`, as.character(NA)), G2categorical = if_else(VarType %in% c("factor", "level"), `Group 2`, as.character(NA))) %>% separate(G1categorical, into = paste0("G1", c("n", "prop")), sep = "[\\(\\)]") %>% separate(G2categorical, into = paste0("G2", c("n", "prop")), sep = "[\\(\\)]") %>% 
        mutate_at(vars(matches("mean$"), matches("sd$"), matches("G[0-9]n$"), matches("prop$")), as.numeric) %>%
        mutate(G1geG2 = if_else(VarType == "numeric", G1mean >= G2mean, G1geG2), G1leG2 = if_else(VarType == "numeric", G1mean <= G2mean, G1leG2)) %>% 
        mutate(G1geG2 = if_else(VarType %in% c("factor", "level"), G1prop >= G2prop, G1geG2), G1leG2 = if_else(VarType %in% c("factor", "level"), G1prop <= G2prop, G1leG2)) %>% 
        mutate(greatest = paste0(if_else(G1geG2, "G1", ""), if_else(G1leG2, "G2", ""))) %>% 
        {add_column(., `#` = 1:nrow(.), `#2` = "", Class = "", .before = 1)} %>%    
        add_column(`p-value` = "", star = "   ", .before = "p") %>% mutate(`p-value` = p, p = as.numeric(if_else(p == "<0.001", "0", p))) %>% 
        mutate(star = case_when(p<0.001~"***", p<0.01~"** ", p<0.05~"*  ", p<0.1~".  ", is.na(p)~"   ", TRUE~"   ")) %>% 
        add_column(smd = as.numeric(NA), .before = "p") %>% mutate(smd = as.numeric(SMD)) %>% 
        add_column(Label = "", Level = "", .before = "Overall") %>% 
        as_tibble
}
```
  
  
## \% function.df.edit_Label_Level()  ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
function.df.edit_Label_Level = function(DataSet.Date.NA.rmAllNA) {
    DataSet.Date.NA.rmAllNA = DataSet.Date.NA.rmAllNA %>% 
        mutate(Level = if_else(VarType  == "level", Variable |> str_replace_all("^   ", ""), Level)) %>% 
        mutate(Level = if_else(Variable |> str_detect(" = "), Variable |> str_extract(" = .*$") |> str_replace_all("^ = ", ""), Level)) %>% 
        mutate(Level = if_else(Level == "TRUE", "", Level)) %>% 
        mutate(Level = if_else(Level == "NA", "N/A", Level)) %>% 
        mutate(Label = if_else(VarType  %in% c("factor", "numeric"), Variable, Label)) %>% 
        mutate(Label = if_else(Variable |> str_detect(" = "), Label |> str_extract("^.* = ") |> str_replace_all(" = $", ""), Label)) %>% 
        mutate(Label = Label |> str_replace_all("[_\\.]", " ")) %>%
        mutate(Label = Label |> str_replace_all("ge([0-9]+)lt([0-9]+)", "[\\1~,\\2)")) %>%
        mutate(Label = Label |> str_replace_all("gt([0-9]+)le([0-9]+)", "(\\1~,\\2]")) %>%
        mutate(Label = Label |> str_replace_all("gt([0-9]+)", ">\\1")) %>%
        mutate(Label = Label |> str_replace_all("ge([0-9]+)", ">=\\1")) %>%
        mutate(Label = Label |> str_replace_all("lt([0-9]+)", "<\\1")) %>%
        mutate(Label = Label |> str_replace_all("le([0-9]+)", "<=\\1")) %>%
        mutate(Label = Label |> str_replace_all("([a-z]+)([A-Z])", "\\1 \\2")) %>%
        as_tibble
    DataSet.Date.NA.rmAllNA
}
```
  
  
## \% function.DataSet.Table1byExposure.print_showAllLevels.addCols()  ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
function.DataSet.Table1byExposure.print_showAllLevels.addCols = function(DataSet.Table1byExposure.print_showAllLevels) {
    DataSet.Table1byExposure.print_showAllLevels %>% add_row(.before = 1) |> 
        as.data.frame() %>% {.[1,]=paste0(names(.), " (N = ", .[2,], ")");.[1,1]=VarNames4Exposure;.[1,c("p","test","SMD")]=c("p-value", "test", "SMD");.} %>% 
        select(-p, -test, p, test) %>%
        {names(.)[!names(.) %in% c("Variable", "level", "Overall", "SMD", "p", "test")] = paste0("Group ", 1:(ncol(.)-6));.} %>% 
        add_column(VarType = as.character(NA), .before = "Variable") %>%
        mutate(VarType = if_else(Variable |> str_detect("%"), "factor", VarType), Variable = Variable |> str_replace_all(" \\(%\\)", "")) %>% 
        mutate(VarType = if_else(Variable |> str_detect("^   "), "level", VarType), Variable = Variable |> str_replace_all(" \\(%\\)", "")) %>% 
        mutate(VarType = if_else(Variable |> str_detect("mean"), "numeric", VarType), Variable = Variable |> str_replace_all(" \\(mean \\(SD\\)\\)", "")) %>% 
        mutate(greatest = as.character(NA), G1geG2 = as.logical(NA), G1leG2 = as.logical(NA)) %>% 
        mutate(G1numeric = if_else(VarType == "numeric", `Group 1`, as.character(NA)), G2numeric = if_else(VarType == "numeric", `Group 2`, as.character(NA))) %>% separate(G1numeric, into = paste0("G1", c("mean", "sd")), sep = "[\\(\\)]") %>% separate(G2numeric, into = paste0("G2", c("mean", "sd")), sep = "[\\(\\)]") %>% 
        mutate(G1categorical = if_else(VarType %in% c("factor", "level"), `Group 1`, as.character(NA)), G2categorical = if_else(VarType %in% c("factor", "level"), `Group 2`, as.character(NA))) %>% separate(G1categorical, into = paste0("G1", c("n", "prop")), sep = "[\\(\\)]") %>% separate(G2categorical, into = paste0("G2", c("n", "prop")), sep = "[\\(\\)]") %>% 
        mutate_at(vars(matches("mean$"), matches("sd$"), matches("G[0-9]n$"), matches("prop$")), as.numeric) %>%
        mutate(G1geG2 = if_else(VarType == "numeric", G1mean >= G2mean, G1geG2), G1leG2 = if_else(VarType == "numeric", G1mean <= G2mean, G1leG2)) %>% 
        mutate(G1geG2 = if_else(VarType %in% c("factor", "level"), G1prop >= G2prop, G1geG2), G1leG2 = if_else(VarType %in% c("factor", "level"), G1prop <= G2prop, G1leG2)) %>% 
        mutate(greatest = paste0(if_else(G1geG2, "G1", ""), if_else(G1leG2, "G2", ""))) %>% 
        {add_column(., `#` = 1:nrow(.), `#2` = "", Class = "", .before = 1)} %>%    
        add_column(`p-value` = "", star = "   ", .before = "p") %>% mutate(`p-value` = p, p = as.numeric(if_else(p == "<0.001", "0", p))) %>% 
        mutate(star = case_when(p<0.001~"***", p<0.01~"** ", p<0.05~"*  ", p<0.1~".  ", is.na(p)~"   ", TRUE~"   ")) %>% 
        add_column(smd = as.numeric(NA), .before = "p") %>% mutate(smd = as.numeric(SMD)) %>% 
        add_column(Label = "", Level = "", .before = "Overall") %>% 
        as_tibble
}

```
  
  
## @ writexl::write_xlsx(paste0(DataSetName.Table1byExposure, "(list).xlsx")) -----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
list(
    byExposure = DataSet.Table1byExposure.print %>% function.DataSet.Table1byExposure.print.addCols %>% function.df.edit_Label_Level
    , byExposure.AllLevels = DataSet.Table1byExposure.print_showAllLevels %>% function.DataSet.Table1byExposure.print_showAllLevels.addCols %>% function.df.edit_Label_Level %>% mutate(Level = level)
    , byExposure.IQR = DataSet.Table1byExposure.print_showAllLevels.IQR
    # , is.na.byExposure = DataSet.is.na.Table1byExposure.print
) %>% writexl::write_xlsx(paste0(DataSetName.Table1byExposure, "(list).xlsx"))
if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(paste0(DataSetName.Table1byExposure, "(list).xlsx"))

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
```{r writeRDS-EvalNoEchoNoMsgNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## @ write_rds( get(.objectname), file.path(.path4write, paste0(.objectname,".rds"))) ----  
.path4write = env1$path$.path4write
# MetaData$DataSetNames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
cat("    ========================================================================    \n")
for (.objectname in names(MetaData$DataSetNames)) {
    assign(.objectname, structure(get(.objectname), MetaData = MetaData))
    .path.file = paste0(.path4write,"/",.objectname,".rds",".xz")
    cat(.objectname, ' |> write_rds(',shQuote(.path.file),', compress = "xz", compression = 9) |> system.time()', "  \n", sep="")
    cat('env1$f$f_path.size_files(.path4read = ',shQuote(.path4write),', regex4filename = ',shQuote(.objectname),")  \n", sep="")
    env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, execute_code = FALSE)
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
}
# #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
# .path.filename.xlsx = paste0(.path4write,"/",.objectname,".xlsx")
# system.time(openxlsx2::write_xlsx(get(.objectname), file=.path.filename.xlsx, as_table=TRUE))
# if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(.path.filename.xlsx)
```
  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  

```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$CurrentSource.path.filename.nb.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
