---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = options()$width; cat(options()$width, "  \n", sep="")
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .sourcename = "f_DataSetName.Search.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  
# @@ START) data example ----  
## \$ analyticDF_time2event =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
suppressPackageStartupMessages(library(tidyverse))
# suppressPackageStartupMessages(library(survival))
for(.packagename in c("survminer")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
# ?survival::lung
.objectname = DataSetName = "analyticDF_time2event"
assign(
    DataSetName, 
    survival::lung |> as_tibble() |> mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] |> as.factor(), StudyPopulation = time >= 30) |>
        # dplyr::select(-status, -sex)
        dplyr::select(-status)
)
analyticDF_time2event %>% {cat(" > ",deparse(substitute(.))," |> as_tibble() |> print()","  \n", sep=""); print(as_tibble(.))}
```
  
  
## \$ gtsummary::trial ----  

We’ll be using the [`trial`](https://www.danieldsjoberg.com/gtsummary/reference/trial.html) data set throughout this example.

*   This set contains data from 200 patients who received one of two types of chemotherapy (Drug A or Drug B). The outcomes are tumor response and death.
    
*   Each variable in the data frame has been assigned an **attribute label** (i.e. `attr(trial$trt, "label") == "Chemotherapy Treatment")` with the **[labelled](http://larmarange.github.io/labelled/)** package. These labels are displayed in the {gtsummary} output table by default. Using {gtsummary} on a data frame without labels will simply print variable names in place of variable labels; there is also an option to add labels later.
    
    
Includes mix of continuous, dichotomous, and categorical variables

```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
suppressPackageStartupMessages(library(tidyverse))
# suppressPackageStartupMessages(library(survival))
for(.packagename in c("gtsummary")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
trial = gtsummary::trial
trial %>% {cat(" > ",deparse(substitute(.))," |> as_tibble() |> print()","  \n", sep=""); print(as_tibble(.))}
trial %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); (str(.))}
```


# @@ START) Data ----  
## \$ CohortGJ0910.BaselineJKGJ2085NoHx...01  
### \$ DataSet.Date.NA.rmAllNA =  
#### \% |> env1\$f\$f_df.Table1byExposure.xlsx(VarNames4Exposure =  c("SEX"))  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# # \$ assign( DataSetName, read_rds(paste0(.path4read,"/",DataSetName,".rds")) ) ====  
# # .path4read = file.path(env1$path$path0,"Rproject_KNHIS.CohortGJ0910 NoHx")
# # DataSetName = "CohortGJ0910.BaselineJKGJ2085NoHx.drop_na.MetS_NoMeds"
# .path4read = paste0(env1$path$path1,"/data")
# DataSetName = "CohortGJ0910.BaselineJKGJ2085NoHx...01" |> str_replace("\\.rds$", "")
# assign( DataSetName, read_rds(paste0(.path4read,"/",DataSetName,".rds")) )
# 
# CohortGJ0910.BaselineJKGJ2085NoHx...01 |> names() |> paste0(collapse = ", ") |> cat("  \n", sep="") ###### |> cat("  \n", sep="") ----
# # > CohortGJ0910.BaselineJKGJ2085NoHx...01 |> names() |> paste0(collapse = ", ") |> cat("  \n", sep="") ###### |> cat("  \n", sep="") ----  
# # PERSON_ID, EnrollYear, SEX, AGE_GROUP, DTH_YM, DTH_CODE1, DTH_CODE2, SIDO, SGG, IPSN_TYPE_CD, CTRB_PT_TYPE_CD, DFAB_GRD_CD, DFAB_PTN_CD, DFAB_REG_YM, YKIHO_GUBUN_CD, 
# # HEIGHT, WEIGHT, 
# # BP_HIGH, BP_LWST, BLDS, 
# # TOT_CHOLE, 
# # HMG, OLIG_PROTE_CD, SGOT_AST, SGPT_ALT, GAMMA_GTP, FMLY_HPRTS_PATIEN_YN, FMLY_APOP_PATIEN_YN, FMLY_HDISE_PATIEN_YN, FMLY_DIABML_PATIEN_YN, FMLY_CANCER_PATIEN_YN, SMK_STAT_TYPE_RSPS_CD, DRNK_HABIT_RSPS_CD, TM1_DRKQTY_RSPS_CD, 
# # WAIST, TRIGLYCERIDE, HDL_CHOLE, LDL_CHOLE, 
# # CREATININE, HCHK_APOP_PMH_YN, HCHK_HDISE_PMH_YN, HCHK_HPRTS_PMH_YN, HCHK_DIABML_PMH_YN, HCHK_HPLPDM_PMH_YN, HCHK_ETCDSE_PMH_YN, PAST_SMK_TERM_RSPS_CD, PAST_DSQTY_RSPS_CD, CUR_SMK_TERM_RSPS_CD, CUR_DSQTY_RSPS_CD, MOV20_WEK_FREQ_ID, MOV30_WEK_FREQ_ID, WLK30_WEK_FREQ_ID, HCHK_PHSS_PMH_YN, n.ICD_E0814, minDate.ICD_E0814, maxDate.ICD_E0814, diffDate.ICD_E0814, n.ICD_I1016, minDate.ICD_I1016, maxDate.ICD_I1016, diffDate.ICD_I1016, n.ICD_I2025, minDate.ICD_I2025, maxDate.ICD_I2025, diffDate.ICD_I2025, n.ICD_I3052, minDate.ICD_I3052, maxDate.ICD_I3052, diffDate.ICD_I3052, n.ICD_I6069, minDate.ICD_I6069, maxDate.ICD_I6069, diffDate.ICD_I6069, n.ICD_I7079, minDate.ICD_I7079, maxDate.ICD_I7079, diffDate.ICD_I7079, Female, BMI, BMI_lt185, BMI_ge185lt230, BMI_ge230lt250, BMI_ge185lt250, BMI_ge250lt300, BMI_ge300, BMI_ge350, BMI_ge400, 
# # BMI.cut4, FPG, 
# # FPG_ge100, FPG_ge126, 
# # SBP, DBP, BP_ESCESH2018, 
# # FPG_ge100lt126, 
# # TRIGLYCERIDE_ge150, HDL_CHOLE_lt4050, WAIST_ge9080, WAIST_ge9085, BP_ge130_85, 
# # nMetS_NoMeds_WAIST_ge9080, nMetS_NoMeds_WAIST_ge9080.ge3, 
# # nMetS_NoMeds_WAIST_ge9085, nMetS_NoMeds_WAIST_ge9085.ge3


##________________________________________________________________________________
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# DataSet.Date.NA.rmAllNA = CohortGJ0910.BaselineJKGJ2085NoHx...01 %>% 
#     rownames_to_column() 

##________________________________________________________________________________
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# DataSet.Date.NA.rmAllNA %>% 
#     select(
#         SEX,
#         HEIGHT, WEIGHT, 
#         BMI.cut4, 
#         WAIST, 
#         WAIST_ge9080, WAIST_ge9085, 
#         SBP, DBP, BP_ESCESH2018, 
#         BP_ge130_85, 
#         FPG, 
#         FPG_ge100, FPG_ge126, 
#         TOT_CHOLE, 
#         TRIGLYCERIDE, 
#         HDL_CHOLE, LDL_CHOLE, 
#         TRIGLYCERIDE_ge150, HDL_CHOLE_lt4050, 
#         nMetS_NoMeds_WAIST_ge9080, nMetS_NoMeds_WAIST_ge9080.ge3, 
#         nMetS_NoMeds_WAIST_ge9085, nMetS_NoMeds_WAIST_ge9085.ge3
#     ) |> env1$f$f_df.Table1byExposure.xlsx(DataSetName4output = "CohortGJ0910.BaselineJKGJ2085NoHx...01.select_MetS", VarNames4Exposure =  c("SEX"))
```
  

## \$ df_NewDMv3.CensorEND.n88.select293.NA.rmAllNA.recode  
### @ VarName.suffix.regex = "A0[0-2]"
### :: DataSet.Date.NA.rmAllNA = get(DataSetName) |> select(matches(VarName.suffix.regex))
#### \% |> select(matches("A0[0-3]")) ----  
#### \% |> env1\$f\$f_df.Table1byExposure.xlsx(VarNames4Exposure =  c("A01_BMI.cut5"))  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
.path4read = paste0(env1$path$path0,"/Rproject_KoGES_AA10030/df_NewDMv3.CensorEND.n88.select971.NA.rmAllNA.recode")
DataSetName = "df_NewDMv3.CensorEND.n88.select293.NA.rmAllNA.recode"
paste0(.path4read,"/",DataSetName,".rds") |> env1$f$f_DataSet_path_filename_ext.read.checkEntity()

##________________________________________________________________________________
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
VarName.suffix.regex =
    c(
        paste0("A0[1-5]_",
               c("WEIGHT", "HEIGHT",
                 "BMI.cut5")),
        # outer(c("delta", "pd"), 1:4, paste0),
        paste0("A02_", ".*",
               c("delta", "pd"),
               "1"),
        paste0("A02_", ".*",
               c("delta", "pd"),
               "1"),
        paste0("A03_", ".*",
               c("delta", "pd"),
               "2"),
        paste0("A05_", ".*",
               c("delta", "pd"),
               "4"),
        paste0("A00_",
               c("SEX")),
        "Female",
        paste0("A01_",
               c("EDATE", "AGE", "INCOME",
                 "WAIST", "HIP",
                 "BODYFAT", "OBDIG1", "OBDIG2", "OBDEG",
                 # "BP", "PULSE", "HTN_C", "HTNCU", "TREATD1", "DRUGHTCU", "FMHTN",
                 "PULSE", "HTN_C", "HTNCU", "DRUGHTCU", "FMHTN",
                 "HBA1C", "GLU0_TR", "DM_C", "DMCU", "TREATD2", "DRUGDMCU", "DRUGINSCU", "FMDM",
                 "PHYSTB", "PHYSIT", "MET", "EXERCUR", "EXER", "EXERFQ", "EXERDU",
                 "BRF", "MEALRG", "AFTDNN",
                 "DRINK", "DRDU",
                 "SMOKE", "SMAG", "SMDU", "SMAM", "PSM", "PSMDU",
                 "LIPCU",
                 "MICU", "CHFCU", "CADCU", "PVDCU", "TREATD8", "FMHEA",
                 "CEVACU",
                 "KIDCU", "TREATD14"))
    ) %>% paste0(collapse="|")
VarName.suffix.regex %>% dput
DataSet.Date.NA.rmAllNA = get(DataSetName) %>% select(matches(VarName.suffix.regex), matches("A0[0-2]")) %>%
    # select(matches("A00|A01|A04|A07"))
    # select(matches("A00|A01|A07"))
    select(matches("A0[0-3]"))
DataSet.Date.NA.rmAllNA = DataSet.Date.NA.rmAllNA[sort(names(DataSet.Date.NA.rmAllNA))]
DataSet.Date.NA.rmAllNA = DataSet.Date.NA.rmAllNA %>% mutate_if(function(vec) {is.numeric(vec) && n_distinct(vec) <= 10}, as.factor)
DataSet.Date.NA.rmAllNA %>% str(max.level = 2)

##________________________________________________________________________________
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
.VarNames4Exposure =  c("A01_BMI.cut5")  
.DataSetName4output = DataSetName
# DataSet.Date.NA.rmAllNA |> env1$f$f_df.Table1byExposure.xlsx(DataSetName4output = .DataSetName4output, VarNames4Exposure = .VarNames4Exposure, output.xlsx = Sys.getenv("PARENT_RENDERING") != "YES")
```


# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```

# https://www.danieldsjoberg.com/gtsummary/articles/gallery.html


### # Summary by trt. 

### ECHO \% |> tbl_summary(by = trt, statistic = all_continuous() ~ "{median} ({p25}, {p75})") ----  
##### ECHO \% |> modify_header(all_stat_cols() ~ "**{level}**  \nN = {n} ({style_percent(p)}%)") ----  
##### ECHO \% |> add_n() ----  
##### ECHO \% |> bold_labels() ----  
##### ECHO \% |> modify_spanning_header(all_stat_cols() ~ "**Chemotherapy Treatment**") ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
trial |> 
  tbl_summary(
    by = trt,
    include = c(age, grade),
    missing = "no",
    statistic = all_continuous() ~ "{median} ({p25}, {p75})"
  ) |> 
  modify_header(all_stat_cols() ~ "**{level}**  \nN = {n} ({style_percent(p)}%)") |> 
  add_n() |> 
  bold_labels() |> 
  modify_spanning_header(all_stat_cols() ~ "**Chemotherapy Treatment**")
```


### # Show continuous summary statistics on multiple lines.

### ECHO \% |> tbl_summary(by = trt, type = all_continuous() ~ "continuous2", statistic = all_continuous() ~ "{median} ({p25}, {p75})") ----  
##### ECHO \% |> italicize_levels() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
    trial |> 
      tbl_summary(
        by = trt,
        include = c(age, marker),
        type = all_continuous() ~ "continuous2",
        statistic =
          all_continuous() ~ c("{N_nonmiss}",
                               "{mean} ({sd})",
                               "{median} ({p25}, {p75})",
                               "{min}, {max}"),
        missing = "no"
      ) |> 
      italicize_levels()

```


### # Report treatment differences between two groups. 

### ECHO \% |> tbl_summary(by = trt, statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{p}%")) ----  
##### ECHO \% |> add_difference() ----  
##### ECHO \% |> add_n() ----  
##### ECHO \% |> modify_header(all_stat_cols() ~ "**{level}**") ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
    trial |> 
      tbl_summary(
        by = trt,
        include = c(response, marker),
        statistic = list(
          all_continuous() ~ "{mean} ({sd})",
          all_categorical() ~ "{p}%"
        ),
        missing = "no"
      ) |> 
      add_difference() |> 
      add_n() |> 
      modify_header(all_stat_cols() ~ "**{level}**")
```


### # Include p-values comparing all groups to a single reference group.

### ECHO \% |> tbl_summary(by = grade) ----  
##### ECHO \% |> add_p() ----  
##### ECHO \% |> modify_header() ----  
##### ECHO \% |> modify_column_hide(all_stat_cols()) ----  
### ECHO \% tbl_merge(list(t0, t1, t2)) ----  
##### ECHO \% |> modify_spanning_header() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
    # table summarizing data with no p-values
    small_trial <- trial |> select(grade, age, response)
    t0 <- small_trial |> 
      tbl_summary(by = grade, missing = "no") |> 
      modify_header(all_stat_cols() ~ "**{level}**")
    
    # table comparing grade I and II
    t1 <- small_trial |> 
      dplyr::filter(grade %in% c("I", "II")) |> 
      tbl_summary(by = grade, missing = "no") |> 
      add_p() |> 
      modify_header(p.value ~ "**I vs. II**") |> 
      # hide summary stat columns
      modify_column_hide(all_stat_cols())
    
    # table comparing grade I and II
    t2 <- small_trial |> 
      dplyr::filter(grade %in% c("I", "III")) |> 
      tbl_summary(by = grade, missing = "no") |> 
      add_p() |> 
      modify_header(p.value = "**I vs. III**") |> 
      # hide summary stat columns
      modify_column_hide(all_stat_cols())
    
    # merging the 3 tables together, and adding additional gt formatting
    tbl_merge(list(t0, t1, t2)) |> 
      modify_spanning_header(
        all_stat_cols() ~ "**Tumor Grade**",
        starts_with("p.value") ~ "**p-values**"
      )
```


### # summarize a continuous variable by one, two, or more categorical variables. 

It’s often needed to summarize a continuous variable by one, two, or more categorical variables. The example below shows a table summarizing a continuous variable by two categorical variables. To summarize by more than two categorical variables, use `tbl_continuous` in conjunction with `tbl_strata` (see an example of `tbl_strata` [here](#tbl_strata)).

### ECHO \% |> tbl_continuous(variable = marker, by = trt, include = grade) ----  
##### ECHO \% |> modify_spanning_header() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
    trial |> 
      tbl_continuous(variable = marker, by = trt, include = grade) |> 
      modify_spanning_header(all_stat_cols() ~ "**Treatment Assignment**")
```



### # Build a summary table stratified by more than one variable.

### ECHO \% |> tbl_strata(strata = grade, ~ .x |> tbl_summary(by = trt)) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
    trial |> 
      select(trt, grade, age, stage) |> 
      mutate(grade = paste("Grade", grade)) |> 
      tbl_strata(
        strata = grade,
        ~ .x |> 
          tbl_summary(by = trt, missing = "no") |> 
          modify_header(all_stat_cols() ~ "**{level}**")
      )
```



## \% analyticDF_time2event |>  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ START) function ----  
## \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ START) source ----  
```{r .subpath.filename.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
# .subpath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") {.subpath = env1$path$CurrentSource.path.filename.ext |> dirname(); ".subpath" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
# if(.subpath!="") utils::browseURL(normalizePath(.subpath))
# .sourcename = "default.template" |> paste0(".source.r")
if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") {.sourcename_root = env1$path$CurrentSource.path.filename.ext |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),""); ".sourcename_root" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.subpath = .subpath
if(!exists(".sourcename_root") && exists(".sourcename")) .sourcename_root = .sourcename |> str_replace("\\.source\\.r$", "")
.sourcename = .sourcename_root |> paste0(".source.r")
env1$path$.sourcename_root = .sourcename_root
env1$path$.subpath.filename.dev.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.r")
env1$path$.subpath.filename.dev.Rmd = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.Rmd")
env1$path$.subpath.filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".source.r")
cat("# ",'.sourcename_root = "',.sourcename_root,'"  \n',
    "#### ",env1$path$.subpath.filename.dev.r, "----  \n",
    "#### ",env1$path$.subpath.filename.dev.Rmd, "----  \n",
    "#### ",env1$path$.subpath.filename.source.r, "----  \n",
    '# # source(paste0(env1$path$source_base,"/","',env1$path$.subpath.filename.source.r,'"))', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'")', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.subpath.filename.source.r) ) ----  
# .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.)
# if(!.sourcename %in% names(.GlobalEnv$env1$source)) {cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); source(.GlobalEnv$env1$source[[.sourcename]])}
```
  
  

  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```

  
  
```{r MetaData99-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
if(exists("MetaData")) {
    "MetaData |> str(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    # "MetaData$tblVarName |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    # "MetaData$DataSetNames |> str(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "MetaData$VarNames |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "MetaData$VarNames.select |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "MetaData$ModelList |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    
    "all.equal(.MetaData0, MetaData)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
    if(!identical(.MetaData0, MetaData)) {
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        .path.file = ifelse(is.null(env1$path$CurrentSource.path.filename.MetaData.rds), NULL, env1$path$CurrentSource.path.filename.MetaData.rds %>% {paste0(env1$path$path1,"/",.)})
        MetaData |> env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.path.file = .path.file, createBackup = TRUE, Execute = TRUE)
    }
} else {warning("> !exists(MetaData)  \n")}
```


```{r writeRDS-EvalNoEchoNoMsgNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
##________________________________________________________________________________
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## @ write_rds( get(.objectname), file.path(.path4write, paste0(.objectname,".rds"))) ----  
if(exists("MetaData")) {
    # MetaData$DataSetNames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
    cat("    ========================================================================    \n")
    for (.objectname in names(MetaData$DataSetNames)) {
        assign(.objectname, structure(get(.objectname), MetaData = MetaData))
        env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = .objectname, .path4write = env1$path$.path4write, Execute = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE, CompressionMethod = "xz")
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    }
}
# #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
# .path.filename.xlsx = paste0(.path4write,"/",.objectname,".xlsx")
# system.time(openxlsx2::write_xlsx(get(.objectname), file=.path.filename.xlsx, as_table=TRUE))
# if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(.path.filename.xlsx)
```
  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$CurrentSource.path.filename.pdf = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$CurrentSource.path.filename.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (Sys.info()["sysname"] == "Windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$CurrentSource.path.filename.ext)),', output_format = "pdf_document")  \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
        .path.file = env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}
        env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, Execute = FALSE)
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = .path.file, .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal$f_file_PDF.sumatra(.path.file))
    }
}
# env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path.file = env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, Execute = FALSE); cat('  env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = ',deparse(.path.file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal$f_file_PDF.sumatra(',deparse(.path.file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path.file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path.file = env1$path$CurrentSource.path.filename.html %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, Execute = FALSE); cat('  env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = ',deparse(.path.file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); cat('  env1$env.internal$f_URL.open_in_edge_app(',deparse(.path.file),')  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$CurrentSource.path.filename.nb.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
