---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=TRUE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
env1$info$options.width = options()$width; cat(options()$width, "  \n", sep="")
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
## env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

# @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
cat("> .tmp |> str(max.level = 1, give.attr = FALSE)", "  \n", sep="") 
.tmp |> str(max.level = 1, give.attr = FALSE)
cat("> env1 |> as.list() |> str(max.level = 2, give.attr = FALSE)", "  \n", sep="") 
env1 |> as.list() |> str(max.level = 2, give.attr = FALSE)
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
# .sourcename = "f_DataSetName.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  
```{r dfDIRsRecursive-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# *** Results hidden in 00env1 - see 01df_dirs_recursive.df_files ***
# #### env1\$env.internal\$f_path.df_dirs_recursive.df_files() ----  
# .sourcename = "f_path.df_dirs_recursive.df_files" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# env1$path$df_dirs_recursive.df_files = env1$env.internal$f_path.df_dirs_recursive.df_files(input_path=".", print.message=FALSE)
# env1$path$print_tree_path = env1$path$df_dirs_recursive.df_files |> dplyr::filter(path.level <= 5) |> 
#     dplyr::select(print_tree_path) |> unlist() |> paste(collapse="") 
# # env1$path$print_tree_path |> cat("  \n", sep="")
# env1$path$print_tree_path_files.codes = env1$path$df_dirs_recursive.df_files |> dplyr::filter(path.level <= 5) |> 
#     dplyr::select(print_tree_path_files.codes) |> unlist() |> paste(collapse="") 
# # env1$path$print_tree_path_files.codes |> cat("  \n", sep="")
# env1$path$print_tree_path_files.data = env1$path$df_dirs_recursive.df_files |> dplyr::filter(path.level <= 5) |> 
#     dplyr::select(print_tree_path_files.data) |> unlist() |> paste(collapse="") 
# env1$path$print_tree_path_files.data |> cat("  \n", sep="")
```
  
  
```{r sizeFiles-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# *** Results hidden in 00env1 - see 01df_dirs_recursive.df_files ***
# #### env1\$f_path.size_files() ----  
# .sourcename = "f_path.size_files" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# #### env1\$f_DataSetName.read.checkEntity() ----  
# .sourcename = "f_DataSetName.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# env1$f$f_path.size_files(.path4read = .path4read)
```
  
  
```{r open-envCustom-dfDirs-CodeBook, eval=TRUE, include=FALSE}
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
## env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# .GlobalEnv$.tmp = list() ====  
.listname = ".tmp"; if(!exists(.listname, envir=.GlobalEnv)) { assign(.listname, list(), envir=.GlobalEnv) }
for (SourceFileBaseName in rev(c("00env1", "01df_dirs_recursive.df_files", "10CodeBook"))) {
    .tmp$SourceFileName.ext = paste0(SourceFileBaseName,"-",basename(env1$path$path1),".Rmd")
    if(.tmp$SourceFileName.ext != basename(env1$path$CurrentSource.path.filename.ext)) {
        # .tmp$SourceFileName.ext %>% {paste0(env1$path$path1,"/",.)} |> file.edit(); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext))
        .tmp$SourceFileName.ext %>% {paste0(env1$path$path1,"/",.)} %>% {.[file.exists(.)]} |> file.edit(); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext))
    }
}
```
  
  
https://www.r-bloggers.com/2021/11/publication-ready-tables-with-flextable-and-own-theme-in-r/#:~:text=function%20can%20be%20used%20to%20export%20Table%201.&text=package%20is%20a%20great%20package%20for%2C%20you%20guessed%20it%2C%20generating,the%20output%20that%20you%20need.  
https://chatgpt.com/c/66ef713d-52ac-800e-aca5-ac9bb72d680b  
# @@ START) data example ----  
## \$ GermanBreastCancerStudyGroup =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
suppressPackageStartupMessages(library(tidyverse))
# Load Required Libraries
library(survival)

# Load Dataset and Rename
GermanBreastCancerStudyGroup <- survival::gbsg

# Prepare the Data
GermanBreastCancerStudyGroup <- GermanBreastCancerStudyGroup %>%
    select(-pid, -rfstime, -status) %>% 
    mutate(meno = as_factor(meno),
           grade = as_factor(grade),
           hormon = as_factor(hormon)) %>%
    rename(`Age, years (mean (SD))` = age,
           Postmenopausal = meno,
           `Tumor size, mm (mean (SD))` = size,
           `Tumor grade` = grade,
           `Positive lymph nodes, (n)` = nodes,
           `Progesterone receptors, fmol/L (median [IQR])` = pgr,
           `Estrogen receptors, fmol/L (median [IQR])` = er,
           `Hormone treatment` = hormon)

# Recode Factor Levels
GermanBreastCancerStudyGroup$`Hormone treatment` <- fct_recode(GermanBreastCancerStudyGroup$`Hormone treatment`,
                                                               Treated = "1",
                                                               Placebo = "0")
GermanBreastCancerStudyGroup %>% str
GermanBreastCancerStudyGroup %>% as_tibble
```
  
  
# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```

  
# @@ START) function ----  
https://chatgpt.com/c/66f444ad-c638-800e-a884-e76216e05329?model=gpt-4o
## 1. Replace common alternative column names
### \% |> replace_column_names() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# Load required libraries
library(dplyr)
library(flextable)
library(rlang)

# Helper Functions

# 1. Replace common alternative column names
replace_column_names <- function(colnames) {
  sapply(colnames, function(name) {
    case_when(
      name %in% c("p.value", "pvalue") ~ "p",
      name == "chisq" ~ "chi2",
      name %in% c("conf.low", "CI_low") ~ "CI_lower",
      name %in% c("conf.high", "CI_high") ~ "CI_upper",
      name == "df_error" ~ "df",
      name == "Cohens_d" ~ "d",
      name == "Coefficient" ~ "b",
      name == "t.ratio" ~ "t",
      name == "Std_Coefficient" ~ "B",
      name == "r_rank_biserial" ~ "rrb",
      name %in% c("Eta2", "Eta2_partial") ~ sub("Eta2", "n2", name),
      name == "mu" ~ "Mu",
      name == "term" ~ "Term",
      name == "method" ~ "Method",
      name == "alternative" ~ "Alternative",
      TRUE ~ name
    )
  }, USE.NAMES = FALSE)
}
```


## 2. Prepare data from broom package
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
## 2. Prepare data from broom package
prepare_broom <- function(dataframe, broom_type) {
  if (!is.null(broom_type)) {
    dataframe <- dataframe %>%
      rename_with(~ case_when(
        . == "statistic" ~ "t",
        . == "std.error" ~ "SE",
        . == "parameter" ~ "df",
        TRUE ~ .
      ))
    
    if (broom_type == "t.test") {
      dataframe <- dataframe %>%
        rename_with(~ case_when(
          . == "estimate" ~ "M_diff",
          . == "estimate1" ~ "Mean1",
          . == "estimate2" ~ "Mean2",
          TRUE ~ .
        )) %>%
        relocate(df, .before = p) %>%
        relocate(Method:Alternative)
    } else if (broom_type == "lm") {
      dataframe <- dataframe %>%
        rename_with(~ case_when(
          . == "estimate" ~ "b",
          TRUE ~ .
        ))
    } else if (broom_type == "cor.test") {
      dataframe <- dataframe %>%
        rename_with(~ case_when(
          . == "estimate" ~ "r",
          TRUE ~ .
        )) %>%
        relocate(df, .before = p) %>%
        relocate(Method:Alternative, .before = r)
    } else if (broom_type == "wilcox.test") {
      dataframe <- dataframe %>%
        rename_with(~ case_when(
          . == "statistic" ~ "W",
          TRUE ~ .
        )) %>%
        relocate(Method:Alternative, .before = W)
    }
  }
  return(dataframe)
}
```


## 3. Prepare data from report package
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
## 3. Prepare data from report package
prepare_report <- function(dataframe, report_type, short) {
  if (!is.null(report_type) || any(class(dataframe) == "report_table")) {
    if ("Method" %in% names(dataframe)) {
      if (all(grepl("t-test", dataframe$Method))) {
        report_type <- "t.test"
      } else if (all(grepl("Wilcox", dataframe$Method))) {
        report_type <- "wilcox"
      }
    } else if ("Sum_Squares" %in% names(dataframe)) {
      report_type <- "aov"
    } else if (!is.null(attr(dataframe, "model_class"))) {
      if ("lm" %in% attr(dataframe, "model_class")) {
        report_type <- "lm"
      } else if (grepl("correlation", attr(dataframe, "title"))) {
        report_type <- "cor.test"
      }
    }
    
    # Remove unnecessary columns and format CI
    if (report_type == "t.test") {
      dataframe <- dataframe %>%
        mutate(`95% CI` = paste0("(", round(CI_lower, 2), ", ", round(CI_upper, 2), ")")) %>%
        relocate(`95% CI`, .after = t)
      if (short) {
        dataframe <- dataframe %>% select(-c(Method, Alternative, Mean1, Mean2, M_diff))
      }
    } else if (report_type == "lm") {
      dataframe <- dataframe %>%
        mutate(`95% CI (b)` = paste0("(", round(CI_lower, 2), ", ", round(CI_upper, 2), ")")) %>%
        relocate(`95% CI (b)`, .after = b)
      if (short) {
        dataframe <- dataframe %>% select(-c(Method, Alternative, Fit, `95% CI (b)`))
      }
    } else if (report_type == "cor.test") {
      dataframe <- dataframe %>%
        mutate(`95% CI (r)` = paste0("(", round(CI_lower, 2), ", ", round(CI_upper, 2), ")")) %>%
        relocate(`95% CI (r)`, .after = r)
    } else if (report_type == "wilcox") {
      dataframe <- dataframe %>%
        mutate(`95% CI (rrb)` = paste0("(", round(CI_lower, 2), ", ", round(CI_upper, 2), ")")) %>%
        relocate(`95% CI (rrb)`, .after = W)
    }
  }
  return(dataframe)
}
```


## 4. Format Confidence Intervals
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
## 4. Format Confidence Intervals
format_CI <- function(dataframe, CI_low_high = c("CI_lower", "CI_upper"), col.name = "95% CI") {
  dataframe %>%
    mutate(across(all_of(CI_low_high), ~ round(as.numeric(.), 2))) %>%
    mutate(!!col.name := paste0("(", .[[CI_low_high[1]]], ", ", .[[CI_low_high[2]]], ")")) %>%
    select(-all_of(CI_low_high))
}
```


## 5. Create the JAMA flextable
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
## 5. Create the JAMA flextable
create_jama_flextable <- function(data, highlight, width, spacing, note, separate.header) {
  table <- flextable(data)
  
  # Standard JAMA formatting
  table <- table %>%
    hline_top(part = "head") %>%
    hline_bottom(part = "head") %>%
    hline_top(part = "body") %>%
    hline_bottom(part = "body") %>%
    align(j = 1, align = "left", part = "body") %>%
    align(j = names(data)[sapply(data, is.numeric)], align = "right", part = "body") %>%
    valign(valign = "center", part = "all") %>%
    line_spacing(space = spacing, part = "all") %>%
    fix_border_issues()
  
  # Set table properties
  table <- table %>%
    set_table_properties(layout = "autofit")
  if (!is.null(width)) {
    table <- table %>% set_table_properties(layout = "autofit", width = width)
  }
  
  # Add footnotes if any
  if (!is.null(note)) {
    table <- table %>%
      add_footer_lines("") %>%
      compose(i = 1, j = 1, value = as_paragraph(as_i("Note. "), note[[1]]), part = "footer") %>%
      align(part = "footer", align = "left")
    if (length(note) > 1) {
      table <- table %>% add_footer_lines(note[-1])
    }
  }
  
  # Separate headers if needed
  if (!is.null(separate.header)) {
    table <- table %>% separate_header("span-top", split = "[.]")
  }
  
  # Font settings
  table <- table %>%
    fontsize(part = "all", size = 10) %>%
    font(part = "all", fontname = "Arial") %>%
    bold(part = "header")
  
  # Merge Dependent Variable if present and duplicated
  if ("Dependent Variable" %in% names(data) && any(duplicated(data$`Dependent Variable`))) {
    model.rows <- which(!duplicated(data$`Dependent Variable`, fromLast = TRUE))
    table <- table %>%
      merge_v(j = "Dependent Variable") %>%
      hline(i = model.rows, border = fp_border(width = 1))
  }
  
  return(table)
}
```


## 6. Format columns for JAMA style
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
## 6. Format columns for JAMA style
format_jama_columns <- function(data, table, separate.header, col.format.p, col.format.r, col.format.custom, format.custom, sh.pattern) {
  # Format p-values
  if ("p" %in% names(data)) {
    table <- table %>%
      colformat_double(j = "p", big.mark = ",", digits = 3) %>%
      mutate(p = ifelse(p < 0.001, "<0.001", sprintf("%.3f", p))) %>%
      colformat_char(j = "p", na_str = "")
  }
  
  # Format r-values
  if ("r" %in% names(data)) {
    table <- table %>%
      colformat_double(j = "r", digits = 2)
  }
  
  # Format custom columns if any
  if (!is.null(col.format.custom) && !is.null(format.custom)) {
    for (col in col.format.custom) {
      if (col %in% names(data)) {
        # Assuming format.custom is a function
        table <- table %>%
          compose(j = col, value = as_paragraph(format.custom(data[[col]])))
      }
    }
  }
  
  # Right-align numeric columns (already handled in create_jama_flextable)
  # Left-align text columns (already handled in create_jama_flextable)
  
  # Remove any background shading (already handled)
  
  return(table)
}
```


## 7. Finalize the JAMA table with title and borders
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
## 7. Finalize the JAMA table with title and borders
finalize_jama_table <- function(table, title) {
  if (!is.null(title)) {
    table <- table %>%
      add_header_lines(values = title) %>%
      align(part = "header", i = seq_along(title), align = "left") %>%
      hline(part = "header", i = seq_len(length(title) - 1), border = fp_border(width = 0)) %>%
      hline(part = "header", i = length(title), border = fp_border(width = 1)) %>%
      bold(part = "header", bold = TRUE)
  }
  return(table)
}

# 8. Generate header patterns based on delimiters (if needed)
generate_header_patterns <- function(data) {
  filtered.names <- grep("[.]", names(data), value = TRUE)
  unique(gsub("[^\\.]*$", "", filtered.names))
}

# Main JAMA table function
jama_table <- function(data,
                       highlight = FALSE,
                       col.format.p = NULL,
                       col.format.r = NULL,
                       col.format.ci = NULL,
                       format.custom = NULL,
                       col.format.custom = NULL,
                       width = NULL,
                       spacing = 1.5,
                       broom = NULL,
                       report = NULL,
                       short = FALSE,
                       title = NULL,
                       note = NULL,
                       separate.header = NULL) {
  
  # Check required packages
  if (!requireNamespace("flextable", quietly = TRUE) || !requireNamespace("dplyr", quietly = TRUE)) {
    stop("Packages 'flextable' and 'dplyr' are required for this function. Please install them.", call. = FALSE)
  }
  
  # Ensure data is a data frame
  if (!inherits(data, "data.frame")) {
    message("Non-dataframe detected. Attempting to coerce to dataframe")
    data <- as.data.frame(data)
  }
  
  # Replace common alternative column names
  data <- data %>%
    rename_with(~ replace_column_names(.))
  
  # Integrate broom package output if specified
  data <- prepare_broom(data, broom)
  
  # Integrate report package output if specified
  data <- prepare_report(data, report, short)
  
  # Separate headers if required
  if (!is.null(separate.header)) {
    sh.pattern <- generate_header_patterns(data)
  }
  
  # Format confidence intervals
  if (!is.null(col.format.ci)) {
    # Assuming col.format.ci is a list of columns with lower and upper bounds
    for (ci_cols in col.format.ci) {
      if (all(c("CI_lower", "CI_upper") %in% names(data))) {
        data <- format_CI(data, c("CI_lower", "CI_upper"), "95% CI")
      }
    }
  }
  
  # Highlight significant p-values if requested
  if ("p" %in% names(data) && !is.null(highlight)) {
    highlight_threshold <- if (isTRUE(highlight)) 0.05 else highlight
    data <- data %>%
      mutate(signif = p < highlight_threshold)
  }
  
  # Create the flextable with JAMA formatting
  table <- create_jama_flextable(data, highlight, width, spacing, note, separate.header)
  
  # Apply column-specific formatting
  table <- format_jama_columns(data, table, separate.header, col.format.p, col.format.r, col.format.custom, format.custom, sh.pattern)
  
  # Finalize table with title and borders
  table <- finalize_jama_table(table, title)
  
  # Remove 'signif' column if exists to avoid displaying it
  if ("signif" %in% names(data)) {
    table <- table %>% delete_part("body", i = "signif")
  }
  
  return(table)
}
```


# @@ START) Sample Data ----  
## :: sample_data = 
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
# Sample Data
sample_data <- data.frame(
  `Dependent Variable` = c("Group A", "Group A", "Group B", "Group B"),
  t = c(2.35, 3.12, 1.98, 2.45),
  df = c(30, 30, 30, 30),
  p = c(0.025, 0.003, 0.075, 0.015),
  b = c(0.5, 0.7, 0.4, 0.6),
  CI_lower = c(0.2, 0.3, 0.1, 0.4),
  CI_upper = c(0.8, 1.1, 0.7, 0.9)
)
```


### \% |> jama_table() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
# Create JAMA Table
jama_tbl <- jama_table(
  data = sample_data,
  title = "Table 1. Comparison of Groups",
  note = "Note. p-values < 0.05 are considered statistically significant."
)

# Display the table
print(jama_tbl)

```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# @@ END ----  
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  

```{r writeRDS-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# @ write_rds( get(.objectname), file.path(.path4write, paste0(.objectname,".rds"))) ----  
.path4write = env1$path$.path4write
# MetaData$DataSetNames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
for (.objectname in names(MetaData$DataSetNames)) {
    cat(.objectname, ' |> write_rds("',paste0(.path4write,"/",.objectname,".rds"),'", compress = "none") |> system.time()', "  \n", sep="")
    paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
}
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# .objectname = MetaData$DataSetNames %>% {names(.)[length(.)]}; .objectname %>% cat(deparse(substitute(.)), ' == "',.,'"  \n', sep="")
cat(.objectname, ' |> write_rds("',paste0(.path4write,"/",.objectname,".rds"),'", compress = "none") |> system.time()', "  \n", sep="")
paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
# paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> system(intern=TRUE)
.objectname = paste0(.objectname,".NA",".rmAllNA",".fct")
cat(.objectname, ' |> write_rds("',paste0(.path4write,"/",.objectname,".rds"),'", compress = "none") |> system.time()', "  \n", sep="")
paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
# paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> system(intern=TRUE)
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# .objectname = MetaData$DataSetNames %>% {names(.)[length(.)]}; .objectname %>% cat(deparse(substitute(.)), ' == "',.,'"  \n', sep="")
system.time(write_rds( get(.objectname), paste0(.objectname,".rds") ))
# system.time(write_rds( get(.objectname), file.path(.path4write, paste0(.objectname,".rds"))))
# # system.time(saveRDS( get(.objectname), file.path(.path4write, paste0(.objectname,".rds")), compress = "gzip" ))
# system.time(write_rds( get(.objectname), file.path(.path4write, paste0(.objectname,".rds")), compress = "gz", compression = 9 ))
# system.time(write_rds( get(.objectname), file.path(.path4write, paste0(.objectname, ".rds", ".xz")), compress = "xz", compression = 9 ))
# system.time(openxlsx2::write_xlsx(get(.objectname), file=paste0(.objectname,".xlsx"), as_table=TRUE))
# if (.Platform$OS.type == "windows") openxlsx2::xl_open(paste0(.objectname, ".xlsx"))
env1$f$f_path.size_files(.path4read = .path4write, regex4filename  = .objectname)
paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
# paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> system(intern=TRUE)
```
  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (.Platform$OS.type == "windows") {
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$CurrentSource.path.filename.nb.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (.Platform$OS.type == "windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
