---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = options()$width; cat(options()$width, "  \n", sep="")
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .sourcename = "f_DataSetName.Search.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(isTRUE(options()$function.reload) || !.sourcename %in% names(.GlobalEnv$env1$source)) {  message('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")'); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  


https://www.r-bloggers.com/2021/11/publication-ready-tables-with-flextable-and-own-theme-in-r/#:~:text=function%20can%20be%20used%20to%20export%20Table%201.&text=package%20is%20a%20great%20package%20for%2C%20you%20guessed%20it%2C%20generating,the%20output%20that%20you%20need.  
https://chatgpt.com/c/66ef713d-52ac-800e-aca5-ac9bb72d680b  
# @@ START) data example ----  
## \$ GermanBreastCancerStudyGroup =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# Load Required Libraries
.packagename = "survival"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}

# Load Dataset and Rename
GermanBreastCancerStudyGroup <- survival::gbsg

# Prepare the Data
GermanBreastCancerStudyGroup <- GermanBreastCancerStudyGroup %>%
    select(-pid, -rfstime, -status) %>% 
    mutate(meno = as_factor(meno),
           grade = as_factor(grade),
           hormon = as_factor(hormon)) %>%
    rename(`Age, years (mean (SD))` = age,
           Postmenopausal = meno,
           `Tumor size, mm (mean (SD))` = size,
           `Tumor grade` = grade,
           `Positive lymph nodes, (n)` = nodes,
           `Progesterone receptors, fmol/L (median [IQR])` = pgr,
           `Estrogen receptors, fmol/L (median [IQR])` = er,
           `Hormone treatment` = hormon)

# Recode Factor Levels
GermanBreastCancerStudyGroup$`Hormone treatment` <- fct_recode(GermanBreastCancerStudyGroup$`Hormone treatment`,
                                                               Treated = "1",
                                                               Placebo = "0")
GermanBreastCancerStudyGroup %>% str
GermanBreastCancerStudyGroup %>% as_tibble
```
  
  
# __________|------  
# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```

  
# __________|------  
# @@ START) function ----  
## @ f_df.Table1byExposure.xlsx.dev.r  
```{r EchoNoEval, eval=FALSE, echo=TRUE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
DataSet.Date.NA.rmAllNA.select = DataSet.Date.NA.rmAllNA |> as.data.frame() %>% select(-rowname, -PERSON_ID) %>%
    mutate(Intervention.ge1 = !BMI_ge300) %>%
    # mutate(Intervention = ifelse(Intervention.ge1 == T, "Intervention", "Control") %>% as.factor)
    # mutate(Intervention = ifelse(Intervention.ge1 == T, "Intervention >= 1", "Intervention == 0") %>% as.factor)
    mutate(InterventionGroup = ifelse(Intervention.ge1 == T, "Group 1", "Group 0") %>% as.factor)
DataSet.Date.NA.rmAllNA.select %>% summarise_all(function(x) sum(is.na(x))) %>% t #---
# DataSet.Date.NA.rmAllNA.select %>% mutate_if(is.numeric, replace_na, 0)

VarNames4Exposure =  c("InterventionGroup")
DataSetName = "DataSet.Date.NA.rmAllNA"
DataSetName.select = paste0(DataSetName,".select")
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
assign(DataSetName.Table1byExposure,
       get(DataSetName.select) %>%
           {.[map_lgl(., function(vec) if_else(is.numeric(vec), T, n_distinct(vec) <= 10) )]} |> as.data.frame() %>%  # debug181115 not to remove numeric
           CreateTableOne(strata = VarNames4Exposure, data = ., test = T, includeNA = T, addOverall = T)
)

Vars4IQR = names(get(DataSetName.select))[get(DataSetName.select) %>% map_lgl(is.numeric)]
# get(DataSetName.Table1byExposure) |> print(showAllLevels = F, smd = T) ###### |> print(showAllLevels = F, smd = T) ---


##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
DataSet.Table1byExposure.print = get(DataSetName.Table1byExposure) |> print(showAllLevels = F, smd = T, nonnormal = NULL, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) |> as_tibble(rownames = "Variable")

DataSet.Table1byExposure.print_showAllLevels = get(DataSetName.Table1byExposure) |> print(showAllLevels = T, smd = T, nonnormal = NULL, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) |> as_tibble(rownames = "Variable")

DataSet.Table1byExposure.print_showAllLevels.IQR = get(DataSetName.Table1byExposure) |> print(showAllLevels = T, smd = T, nonnormal = Vars4IQR, exact = NULL, quote = FALSE, noSpaces = TRUE, printToggle = FALSE) |> as_tibble(rownames = "Variable")


##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# function.DataSet.Table1byExposure.print.addCols = function(DataSet.Table1byExposure.print) {

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# function.df.edit_Label_Level = function(df) {

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# function.DataSet.Table1byExposure.print_showAllLevels.addCols = function(DataSet.Table1byExposure.print_showAllLevels) {

##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
list(
    byExposure = DataSet.Table1byExposure.print %>% function.DataSet.Table1byExposure.print.addCols %>% function.df.edit_Label_Level
    , byExposure.AllLevels = DataSet.Table1byExposure.print_showAllLevels %>% function.DataSet.Table1byExposure.print_showAllLevels.addCols %>% function.df.edit_Label_Level %>% mutate(Level = level)
    , byExposure.IQR = DataSet.Table1byExposure.print_showAllLevels.IQR
    # , is.na.byExposure = DataSet.is.na.Table1byExposure.print
) %>% writexl::write_xlsx(paste0(DataSetName.Table1byExposure, "(list).xlsx"))
if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(paste0(DataSetName.Table1byExposure, "(list).xlsx"))
```



## \% f_DataSet.Table1.print.df()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)



# Function to Generate Table 1
f_DataSet.Table1.print.df <- function(DataSet, VarNames4Exposure = c("InterventionGroup"), Varnames_factor.exclude = NULL, addOverall = TRUE, includeNA = TRUE, print.Varnames_nonnormal = NULL, print.showAllLevels = TRUE) {
    .packagename = "tableone"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}

    Varnames.except_Exposure <- setdiff(names(DataSet), VarNames4Exposure)
    Varnames_factor <- names(DataSet %>% select(where(is.factor)))
    
    if (!is.null(Varnames_factor.exclude)) {
        Varnames_factor <- setdiff(Varnames_factor, Varnames_factor.exclude)
    }

    Table1.print.df <- CreateTableOne(vars = Varnames.except_Exposure, data = DataSet, 
                                factorVars = Varnames_factor, strata = VarNames4Exposure, 
                                addOverall = addOverall, includeNA = includeNA, test = TRUE) %>%
        print(nonnormal = print.Varnames_nonnormal,
              showAllLevels = print.showAllLevels, 
              quote = FALSE, noSpaces = TRUE,
              exact = NULL, 
              smd = TRUE, 
              test = FALSE, contDigits = 1,
              printToggle = FALSE, dropEqual = TRUE, 
              explain = FALSE) |> 
        as_tibble(rownames = "Variable") %>% 
        rename(Level = level)
        
    # Update First Row's Variable Name
    Table1.print.df$Variable[1] <- "No."
    
    return(Table1.print.df)
}

```
  
  
## \% set_flextable_defaults() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# # Custom Table Defaults
# set_flextable_defaults(font.family = "Calibri", font.size = 10, border.color = "black")
# -> now within f_Table1_print_df.flextable() function
```


## \% f_Table1_print_df.flextable() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
# Function to Create Custom Table
# Function to Create Custom Table
f_Table1_print_df.flextable <- function(Table1_print_df, header_text, footer_text, 
                       font.family = "Times New Roman", font.size = 10, border.color = "black",
                       header.border.color = "red", background.color = "#f5f5f5") {
    .packagename = "flextable"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
    .packagename = "officer"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
    
    # Set default flextable formatting
    set_flextable_defaults(
        font.family = font.family,
        font.size = font.size,
        border.color = border.color
    )
    
    # Clean up header and footer text
    header_text <- str_squish(str_remove(header_text, "\\n"))    # Remove newline characters and squish spaces in header_text
    footer_text <- str_squish(str_remove(footer_text, "\\n"))    # Remove newline characters and squish spaces in footer_text
    
    flextable(Table1_print_df) %>%    # Initialize a flextable .object with the provided data frame (df)
        add_header_lines(header_text) %>%    # Add a custom header line using the header_text
        add_footer_lines(footer_text) %>%    # Add a custom footer line using the footer_text
        bold(i = 1, part = "header") %>%    # Make the text in the first row of the header bold
        hline_top(part = "header", border = fp_border(color = header.border.color, width = 3)) %>%    # Add a thick line at the top of the header
        hline(i = 1, part = "header", border = fp_border(color = border.color, width = 0.25)) %>%    # Add a thin black line below the header row
        hline_top(part = "body", border = fp_border(color = border.color, width = 0.25)) %>%    # Add a thin black line at the top of the body section
        hline_bottom(part = "body", border = fp_border(color = border.color, width = 0.25)) %>%    # Add a thin black line at the bottom of the body section
        hline_bottom(part = "footer", border = fp_border(color = border.color, width = 0.25)) %>%    # Add a thin black line at the bottom of the footer section
        border_inner_h(part = "body", border = fp_border(color = border.color, width = 0.25, style = "dotted")) %>%    # Add dotted horizontal lines between rows in the body section
        autofit(part = "body") %>%    # Automatically adjust column widths to fit the content in the body
        bg(part = "body", bg = background.color) %>%    # Set a background color for the body of the table
        align(part = "all", align = "center") %>%    # Center align the text in all parts of the table
        align(j = 1, part = "all", align = "left")    # Align the text in the first column to the left
}
```


### :: Table1_print_df = GermanBreastCancerStudyGroup |> generate_table_one() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
# Generate Table 1 Data Frame
Table1_print_df <- f_DataSet.Table1.print.df(
    GermanBreastCancerStudyGroup, 
    VarNames4Exposure = "Hormone treatment", 
    print.Varnames_nonnormal = c("Progesterone receptors, fmol/L (median [IQR])",
                       "Estrogen receptors, fmol/L (median [IQR])"),
    Varnames_factor.exclude = "Hormone treatment"
)
Table1_print_df
```

### :: flextable1 = Table1_print_df |> f_Table1_print_df.flextable() ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
# Generate and Save Flextable
header_text <- "Table 1. Baseline characteristics of 686 patients enrolled in the German Breast Cancer Study Group between 1984 and 1989"
footer_text <- "Numbers are No. (%) unless otherwise noted. SD = standard deviation, fmol/L = femtomole per liter, IQR = interquartile range"

flextable1 <- f_Table1_print_df.flextable(Table1_print_df, header_text = header_text, footer_text = footer_text)
flextable1
```


###### \% |> save_as_docx() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
# # Save the Table as a Word Document with A4 Paper Size and Small Margins
# save_as_docx(flextable1, path = "library(flextable) flextable1.docx",
#              pr_section = prop_section(
#                  page_size = page_size(orient = "portrait", width = 8.27, height = 11.69),  # A4 size in inches
#                  type = "continuous",
#                  page_margins = page_mar(top = 0.5, bottom = 0.5, right = 0.5, left = 0.5, gutter = 0)  # Small margins in inches
#              ))


# # Convert millimeters to inches for A4 paper size and margins
# a4_width_in_inches <- 210 / 25.4  # 210 mm converted to inches
# a4_height_in_inches <- 297 / 25.4  # 297 mm converted to inches
# small_margin_in_inches <- 12.7 / 25.4  # 12.7 mm converted to inches
# 
# # Save the Table as a Word Document with A4 Paper Size, Small Margins, and No Gutter
# save_as_docx(flextable1, path = "library(flextable) flextable1.docx",
#              pr_section = prop_section(
#                  page_size = page_size(orient = "portrait", width = a4_width_in_inches, height = a4_height_in_inches),  # A4 size in inches
#                  type = "continuous", 
#                  page_margins = page_mar(top = small_margin_in_inches, bottom = small_margin_in_inches, 
#                                          left = small_margin_in_inches, right = small_margin_in_inches,
#                                          gutter = 0)  # Small margins in inches and no gutter
#              ))

# Save the Table as a Word Document with A4 Paper Size and Small Margins
save_as_docx(flextable1, path = "library(flextable) flextable1.docx",
             pr_section = prop_section(
                 page_size = page_size(orient = "landscape", width = 210 / 25.4, height = 297 / 25.4),  # A4 size in inches
                 type = "continuous",
                 page_margins = page_mar(top = 12.7 / 25.4, bottom = 12.7 / 25.4, 
                                         left = 12.7 / 25.4, right = 12.7 / 25.4,
                                         gutter = 0)  # Small margins in inches and no gutter
             ))

f_file.switch_open <- function(file) {
    stopifnot(file.exists(file))
    
    file <- normalizePath(file, mustWork = TRUE)
    
    switch(Sys.info()["sysname"], 
        Linux = {
            app <- Sys.getenv("BROWSER", "xdg-open")
            system2(app, file)
        }, 
        Windows = {
            shell.exec(file)
        }, 
        Darwin = {
            system2("open", shQuote(file))
        }, 
        stop("Operating system not handled: ", toString(userSystem))
    )
}
env1$f$f_file.switch_open("library(flextable) flextable1.docx")
```
  
 
  
## library(openxlsx2) ----  
## library(flextable) ----  
## library(remotes) ----  
## library(flexlsx) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
for(.packagename in c("openxlsx2", "flextable")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}

# Warning in install.packages :
#   package ‘flexlsx’ is not available for this version of R
# 
# A version of this package for your version of R might be available elsewhere,
# see the ideas at
# https://cran.r-project.org/doc/manuals/r-patched/R-admin.html#Installing-packages

for(.packagename in c("remotes")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}

for(.packagename in c("flexlsx")) {if(!require(.packagename,character.only=TRUE)) remotes::install_github("pteridin/flexlsx")  ;  library(.packagename,character.only=TRUE)}
```
  
  
### \% |> wb_workbook()$add_worksheet() ----  
### \% |> wb_add_flextable() ----  
### \% |> wb$save() ----  
```{r wb-save-NoEcho, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    .wb <- openxlsx2::wb_workbook()

    .names4data.frame = if(exists("MetaData")) {
        MetaData$DataSetNames |> names()
    } else mget(ls()) |> keep(is.data.frame) |> names()
    cat(".names4data.frame == ", deparse(.names4data.frame), "  \n", sep="")
    # for (.objectname in .names4data.frame) {    # name of the data.frame .object
    #     .wb$add_worksheet(.objectname)  # make sheet name same as .objectname
    #     .wb$add_data(.objectname, get(.objectname), start_col = 2, start_row = 3, row_names = TRUE)    # offset the table to cell 'C2'
    # }

    .names4flextable = mget(ls()) |> purrr::keep(~"flextable" %in% class(.x)) |> names()
    cat(".names4flextable == ", deparse(.names4flextable), "  \n", sep="")
    for (.objectname in .names4flextable) {    # name of the flextable .object
        .wb$add_worksheet(.objectname)  # make sheet name same as .objectname
        .wb <- .wb %>% flexlsx::wb_add_flextable(.objectname, get(.objectname), start_col = 2, start_row = 3)    # offset the table to cell 'C2'
    }

    # .path.file <- tempfile(fileext = ".xlsx")
    .path4write = env1$path$path1
    .CurrentSource.path.filename = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$","")
    .path.file = paste0(.path4write,"/",.CurrentSource.path.filename,".xlsx")
    .wb$save(.path.file)
    cat(".path.file == ", deparse(.path.file), "  \n", sep="")
    if(Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(.path.file)
    env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, Execute = FALSE)
}
```


###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  

```{r writeRDS-EvalNoEchoNoMsgNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# __________|------  
## @ write_rds( get(.objectname), paste0(.path4write,"/",.objectname,".rds",".xz"), compress = "xz", compression = 9L) |> system.time() ----  
if(exists("MetaData")) {
    # MetaData$DataSetNames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
    cat("    ________________________________________________________________________    \n")
    for (.objectname in names(MetaData$DataSetNames)) {
        assign(.objectname, structure(get(.objectname), MetaData = MetaData))
        env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = .objectname, .path4write = env1$path$.path4write, createBackup = FALSE, Execute = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE, CompressionMethod = "xz")
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    }
}
# #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
# .path.filename.xlsx = paste0(.path4write,"/",.objectname,".xlsx")
# system.time(openxlsx2::write_xlsx(get(.objectname), file=.path.filename.xlsx, as_table=TRUE))
# if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(.path.filename.xlsx)
```
  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$CurrentSource.path.filename.nb.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
