---
title: "MHKim's R Notebook"
output: html_notebook
    df_print: tibble
---

# Rstudio RMarkDown Shortcuts
https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE
https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html
Insert R chunk	Ctrl+Alt+I	Command+Option+I
Preview HTML	Ctrl+Shift+K	Command+Shift+K
Run all chunks above	Ctrl+Alt+P	Command+Option+P
Run current chunk	Ctrl+Alt+C	Command+Option+C
Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter
Run next chunk	Ctrl+Alt+N	Command+Option+N
Run all chunks	Ctrl+Alt+R	Command+Option+R
Go to next chunk/title	Ctrl+PgDown	Command+PgDown
Go to previous chunk/title	Ctrl+PgUp	Command+PgUp
Show/hide document outline	Ctrl+Shift+O	Command+Shift+O
F7 spell-check your document. 
Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS). 


#% env.custom
##% env.custom$info
###% env.custom$info$DocumentTitle1 ====
```{r, paged.print=FALSE}
# if(!exists("env.custom")) env.custom = new.env()
if(!exists("env.custom")) env.custom = list()
if(!exists("env.custom$info")) env.custom$info = list()
env.custom$info$DocumentTitle0 = "Blank) env.custom.fun.t.tribble_construct"
env.custom$info$DocumentTitle1 = paste0(env.custom$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env.custom$info$DocumentTitle1); cat("\r\n");
cat(env.custom$info$DocumentTitle1, ".R", sep = ""); cat("\r\n");
cat(env.custom$info$DocumentTitle1, " -dev.R", sep = ""); cat("\r\n");
cat(env.custom$info$DocumentTitle1, " -clean.R", sep = ""); cat("\r\n");
cat(env.custom$info$DocumentTitle1, ".RMD", sep = ""); cat("\r\n");
cat(env.custom$info$DocumentTitle1, " -dev.RMD", sep = ""); cat("\r\n");
cat(env.custom$info$DocumentTitle1, " -clean.RMD", sep = ""); cat("\r\n");
```

###% env.custom$info$info_system_info ====
```{r, paged.print=FALSE}
env.custom$info$get_system_info = function() {
    summary_list = list(
        GUI = .Platform$GUI,
        OS.type = .Platform$OS.type,
        OS.sysname = as.character(Sys.info()["sysname"]),
        OS.version = as.character(Sys.info()["version"]),
        machine.type = as.character(Sys.info()["machine"]),
        machine.nodename = as.character(Sys.info()["nodename"]),
        machine.CPU = if (.Platform$OS.type == "unix" & Sys.info()["sysname"] == "Darwin") 
            trimws(system("sysctl -n machdep.cpu.brand_string", intern=TRUE))
        else if (.Platform$OS.type == "unix" & Sys.info()["sysname"] == "Linux") 
            trimws(system("awk '/model name/' /proc/cpuinfo | uniq | awk -F': ' '{print $2}'", intern=TRUE))
        else if (.Platform$OS.type == "windows") 
            trimws(system("wmic cpu get name", intern=TRUE)[2])
        else NA,
        Sys.getlocale = list(
            LC_COLLATE = Sys.getlocale(category = "LC_COLLATE"), 
            LC_CTYPE = Sys.getlocale(category = "LC_CTYPE"), 
            LC_locale_NUMERIC = Sys.getlocale(category = "LC_NUMERIC"), 
            LC_locale_TIME = Sys.getlocale(category = "LC_TIME")
        ), 
        l10n_info = list(
            localization_UTF8 = l10n_info()$`UTF-8`,
            localization_Latin1 = l10n_info()$`Latin-1`,  
            localization_codeset = l10n_info()$codeset,
            localization_codepage = l10n_info()$codepage,
            localization_system.codepage = l10n_info()$system.codepage
        )
    )
}
env.custom$info$info_system_info = env.custom$info$get_system_info()
str(env.custom$info$info_system_info)
```



@ASROCKX300RYZEN
List of 9
 $ GUI             : chr "RStudio"
 $ os_type         : chr "windows"
 $ os_sysname      : chr "Windows"
 $ os_version      : chr "build 22621"
 $ machine_type    : chr "x86-64"
 $ machine_nodename: chr "ASROCKX300RYZEN"
 $ machine_cpu     : chr "AMD Ryzen 5 5600G with Radeon Graphics"
 $ Sys.getlocale   :List of 4
  ..$ LC_COLLATE       : chr "Korean_Korea.utf8"
  ..$ LC_CTYPE         : chr "Korean_Korea.utf8"
  ..$ LC_locale_NUMERIC: chr "C"
  ..$ LC_locale_TIME   : chr "Korean_Korea.utf8"
 $ l10n_info       :List of 5
  ..$ localization_UTF8           : logi TRUE
  ..$ localization_Latin1         : logi FALSE
  ..$ localization_codeset        : NULL
  ..$ localization_codepage       : int 65001
  ..$ localization_system.codepage: int 65001
  
  
@LIVAI7-8700
List of 9
 $ GUI             : chr "RStudio"
 $ os_type         : chr "windows"
 $ os_sysname      : chr "Windows"
 $ os_version      : chr "build 19045"
 $ machine_type    : chr "x86-64"
 $ machine_nodename: chr "LIVAI7-8700"
 $ machine_cpu     : chr "Intel(R) Core(TM) i7-8700 CPU @ 3.20GHz"
 $ Sys.getlocale   :List of 4
  ..$ LC_COLLATE       : chr "Korean_Korea.utf8"
  ..$ LC_CTYPE         : chr "Korean_Korea.utf8"
  ..$ LC_locale_NUMERIC: chr "C"
  ..$ LC_locale_TIME   : chr "Korean_Korea.utf8"
 $ l10n_info       :List of 5
  ..$ localization_UTF8           : logi TRUE
  ..$ localization_Latin1         : logi FALSE
  ..$ localization_codeset        : NULL
  ..$ localization_codepage       : int 65001
  ..$ localization_system.codepage: int 65001


@Posit Cloud
List of 9
 $ GUI             : chr "RStudio"
 $ os_type         : chr "unix"
 $ os_sysname      : chr "Linux"
 $ os_version      : chr "#96~18.04.1-Ubuntu SMP Mon Oct 17 02:57:48 UTC 2022"
 $ machine_type    : chr "x86_64"
 $ machine_nodename: chr "application-9677950-deployment-19172365-82455"
 $ machine_cpu     : chr "AMD EPYC 7R13 Processor"
 $ Sys.getlocale   :List of 4
  ..$ LC_COLLATE       : chr "C.UTF-8"
  ..$ LC_CTYPE         : chr "C.UTF-8"
  ..$ LC_locale_NUMERIC: chr "C"
  ..$ LC_locale_TIME   : chr "C.UTF-8"
 $ l10n_info       :List of 5
  ..$ localization_UTF8           : logi TRUE
  ..$ localization_Latin1         : logi FALSE
  ..$ localization_codeset        : chr "UTF-8"
  ..$ localization_codepage       : NULL
  ..$ localization_system.codepage: NULL
  

% env.custom$info$info_software_versions ====
```{r, paged.print=FALSE}
library(purrr)

env.custom$info$get_software_versions <- function(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr")) {
  version_list <- list(OS.type = .Platform$OS.type, R.version = R.version$version.string)
  version_list$RStudio_version <- ifelse(!is.null(.Platform$GUI) && .Platform$GUI == "RStudio" && exists("RStudio.Version"), RStudio.Version()$version, NA)
  version_list$library_versions <- setNames(map(library_names, function(lib) {
    if (!requireNamespace(lib, quietly = TRUE)) return(paste(lib, "not installed"))
    (packageVersion(lib))
  }), library_names)
  return(version_list)
}
env.custom$info$info_software_versions = env.custom$info$get_software_versions(
    library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr",
                      "datapasta")
)
str(env.custom$info$info_software_versions)
# dput(env.custom$info$info_software_versions)

```


################################################
##% env.custom$path
% env.custom$path$data_suffix ====
% env.custom$path$project_suffix ====
```{r, paged.print=FALSE}
library(tidyverse); cat("\r\n"); 
cat("\r\n"); cat("getwd() == "); dput(getwd()) #----
env.custom$path$getwd = getwd()
# env.custom$path$path0 = file.path("D:", "OneDrive - SNU", "[][Rproject]")
# env.custom$path$project_base = "Rproject_HEALS0215"
# env.custom$path$data_suffix = "_01"
# # env.custom$path$data_suffix = ""
# env.custom$path$project_suffix = "GJ3"
# 
# 
# env.custom$path$path1 = file.path(env.custom$path$path0, paste0(env.custom$path$project_base, env.custom$path$data_suffix))
# env.custom$path$path2 = file.path(env.custom$path$path1, paste0(env.custom$path$project_base, env.custom$path$data_suffix, env.custom$path$project_suffix))
# 
# path4read = env.custom$path$path1
# # path4write = env.custom$path$path1
# # path4write = env.custom$path$path2
path4read = getwd()
path4write = getwd()
if (getwd() != path4read) warning("getwd() != path4read == ") else cat("getwd() == path4read == "); dput(path4read)  #----
if (getwd() != path4write) warning("getwd() != path4write  == ") else cat("getwd() == path4write == "); dput(path4write)  #----
```


##% env.custom$fun.path_files_size() ====
```{r, paged.print=FALSE}
# tribble_paste = datapasta::tribble_paste
# https://github.com/mkim0710/tidystat/blob/master/Rdev/env.custom.fun.t.tribble_construct.source.r
load(url("https://github.com/mkim0710/tidystat/raw/master/Rdev/env.custom.fun.t.tribble_construct.RData"))
# attach(env.custom)

# regex4filename = "\\.rds(\\.xz)?$"
regex4filename = "\\.rds\\.xz$"
list.files(path4write) %>% grep(regex4filename, ., value = T) %>% {cat('----\n', deparse(., width.cutoff=120), '\n\n', sep='')} # dput() cat(deparse(., width.cutoff=120)), width.cutoff=500 is the max ----
env.custom$fun.path_files_size(path4read = path4write, regex4filename = regex4filename)

cat("----\n"); #----
regex4filename = "\\.rds$"
list.files(path4write) %>% grep(regex4filename, ., value = T) %>% {cat('----\n', deparse(., width.cutoff=120), '\n\n', sep='')} # dput() cat(deparse(., width.cutoff=120)), width.cutoff=500 is the max ----
env.custom$fun.path_files_size(path4read = path4write, regex4filename = regex4filename)
```



#@@ START ------
#$ objectname = "tblID_gj3_jk" ====
##@ assign(objectname, readRDS(file.path(path4read, filename2read))) 
```{r, paged.print=FALSE}
# if (getwd() != path4read) warning("getwd() != path4read == ") else cat("getwd() == path4read == "); dput(path4read)  #----
# objectname = "tblID_gj3_jk"; cat("----\n> ", 'objectname = "', objectname, '"\n', sep = ""); 
# filename2read = if(file.exists(file.path(path4read, paste0(objectname, ".rds")))) paste0(objectname, ".rds") else paste0(objectname, ".rds.xz")
# env.custom$fun.path_files_size(path4read = path4read, regex4filename = filename2read)
# system.time(assign(objectname, readRDS(file.path(path4read, filename2read)), envir = .GlobalEnv))
# get(objectname) %>% dim
# get(objectname) %>% {.$PERSON_ID} %>% n_distinct
# get(objectname) %>% {.$RN_INDI} %>% n_distinct
# get(objectname) %>% names %>% {cat('----\n', deparse(., width.cutoff=120), '\n\n', sep='')} # dput() cat(deparse(., width.cutoff=120)), width.cutoff=500 is the max ----
# get(objectname) %>% names %>% paste(collapse = ", ") %>% {cat('----\n', ., '\n\n', sep='')}; # tidyselect: paste(collapse = ", ") %>% cat ----
# cat("----\n> ", "str(get(objectname), max.level = 2, give.attr = F)", "\n", sep = ""); str(get(objectname), max.level = 2, give.attr = F); 
# # get(objectname) %>% select_if(is.numeric) %>% summary #-----
# # get(objectname) %>% select_if(is.logical) %>% summary #-----
```


#$ lung <- as.tibble(survival::lung) ======
## Step 1: Load the Required Libraries and Data
## Step 2: Exploratory Data Analysis
```{r, paged.print=FALSE}
library(tidyverse)
library(survival)
library(survminer)

# # Load the lung dataset
# # data("lung")
# lung <- as.tibble(survival::lung)
# lung
as.tibble(survival::lung)
summary(survival::lung)
```



## Step 3: Kaplan-Meier Survival Curve
```{r, paged.print=FALSE, fig.width=8, fig.height=6}
library(tidyverse)
# library(survival)
# library(survminer)
survminer::ggsurvplot(survival::survfit(survival::Surv(time = time, event = status) ~ 1, data = survival::lung)
           , break.time.by = 365
           , conf.int = TRUE, risk.table = TRUE, pval = TRUE
           , title = "Kaplan-Meier Survival Curve"
           , xlab = "Time in days", ylab = "Survival Probability")

```

## Step 4: Stratified Kaplan-Meier Survival Curve
```{r, paged.print=FALSE, fig.width=8, fig.height=6}
library(tidyverse)
# library(survival)
# library(survminer)
survminer::ggsurvplot(survival::survfit(survival::Surv(time = time, event = status) ~ sex, data = survival::lung), palette = c("#00AFBB", "#FC4E07")
           , break.time.by = 365
           , conf.int = TRUE, risk.table = TRUE, pval = TRUE
           , title = "Survival Curves Stratified by Sex"
           , xlab = "Time in days", ylab = "Survival Probability")

```

## Step 5: Cox Proportional Hazards Model
```{r, paged.print=FALSE}
# Fit a Cox proportional hazards model
cox_model <- coxph(surv_obj ~ sex + age + ph.ecog, data = survival::lung)

# Summary of the Cox model
summary(cox_model)

```

## Step 6: Check Proportional Hazards Assumption
```{r, paged.print=FALSE}
# Test for proportional hazards
cox.zph(cox_model)
```

# https://github.com/mkim0710/tidystat/blob/master/Rdev/50_model_formula_evaluation/57_model_time2event/AnalyticDataset.censor1yr.survfit.ggsurvplot_CIRiskTableP.source.r
##$ AnalyticDataset ====
```{r, paged.print=FALSE}
AnalyticDataset = lung %>% rename(event = status, Group = sex)
AnalyticDataset.survfit <- survfit(Surv(time = time, event = event) ~ Group, data = AnalyticDataset)

?survminer::ggsurvplot  # "event" plots cumulative events (f(y) = 1-y), "cumhaz" plots the cumulative hazard function (f(y) = -log(y)), and "pct" for survival probability in percentage.

# AnalyticDataset.survfit %>% ggsurvplot(fun = "pct")  # default fun = "pct"?
# AnalyticDataset.survfit %>% ggsurvplot(fun = "event")
# AnalyticDataset.survfit %>% ggsurvplot(fun = "cumhaz")  # Cumulative Hazard = -log S(t)

AnalyticDataset.survfit %>% ggsurvplot  # default fun = "pct"?
```


```{r, paged.print=FALSE}
AnalyticDataset.survfit %>% ggsurvplot(conf.int = T, risk.table = T, pval = T)
```



```{r, paged.print=FALSE}
AnalyticDataset.coxph <- coxph(Surv(time = time, event = event) ~ Group, data = AnalyticDataset)
AnalyticDataset.coxph %>% summary #----
AnalyticDataset.coxph %>% cox.zph # * Caution) significant = bad news, large p = good news~! Having very small p values indicates that there are time dependent coefficients which you need to take care of ----
AnalyticDataset.coxph %>% cox.zph %>% ggcoxzph #----
```


##$ AnalyticDataset.censor1yr ====
```{r, paged.print=FALSE}

value_for_censor_at_1yr = 365 * 1
value_for_break.time.by = 30
AnalyticDataset.censor1yr = AnalyticDataset %>% mutate(
    time.censor1yr = pmin(time, value_for_censor_at_1yr)
    , event.censor1yr = ifelse(time < value_for_censor_at_1yr, event, 0)
)
AnalyticDataset.censor1yr.survfit = survfit(Surv(time = time.censor1yr, event = event.censor1yr) ~ Group, data = AnalyticDataset.censor1yr)

# AnalyticDataset.censor1yr.survfit %>% ggsurvplot(fun = "pct")  # default fun = "pct"?
# AnalyticDataset.censor1yr.survfit %>% ggsurvplot(fun = "event")
# AnalyticDataset.censor1yr.survfit %>% ggsurvplot(fun = "cumhaz")  # Cumulative Hazard = -log S(t)

AnalyticDataset.censor1yr.survfit %>% ggsurvplot  # default fun = "pct"?

```


```{r, paged.print=FALSE}
AnalyticDataset.censor1yr.survfit %>% ggsurvplot(conf.int = T, risk.table = T, pval = T, break.time.by = value_for_break.time.by)

```


```{r, paged.print=FALSE}
AnalyticDataset.censor1yr.survfit %>% ggsurvplot(conf.int = T, risk.table = T, pval = T, break.time.by = value_for_break.time.by)

```


```{r, paged.print=FALSE}

```


```{r, paged.print=FALSE}

```


```{r, paged.print=FALSE}

```



# [Plot] Stratified Kaplan-Meier Survival Curve
```{r, paged.print=FALSE, fig.width=8, fig.height=6}
library(tidyverse)
# library(survival)
# library(survminer)
?survival::lung 
AnalyticDataset = survival::lung %>% mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] %>% as.factor)
# AnalyticDataset %>% select(sex, Group) %>% str
# AnalyticDataset %>% select(sex, Group) %>% table
# # > AnalyticDataset %>% select(sex, Group) %>% str
# # 'data.frame':	228 obs. of  2 variables:
# #  $ sex  : num  1 1 1 1 1 1 2 2 1 1 ...
# #  $ Group: Factor w/ 2 levels "Female","Male": 2 2 2 2 2 2 1 1 2 2 ...
# # > AnalyticDataset %>% select(sex, Group) %>% table
# #    Group
# # sex Female Male
# #   1      0  138
# #   2     90    0
AnalyticDataset %>% select(time, event, Group) %>% summary

?survminer::ggsurvplot  # "event" plots cumulative events (f(y) = 1-y), "cumhaz" plots the cumulative hazard function (f(y) = -log(y)), and "pct" for survival probability in percentage.
# AnalyticDataset.survfit %>% ggsurvplot(fun = "pct")  # default fun = "pct"?
# AnalyticDataset.survfit %>% ggsurvplot(fun = "event")
# AnalyticDataset.survfit %>% ggsurvplot(fun = "cumhaz")  # Cumulative Hazard = -log S(t)
value_for_censor_at_1yr = 365 * 1
value_for_break.time.by = 30
time_scale = "days"
varname4Group = "Group"
AnalyticDataset.censor1yr = AnalyticDataset %>% mutate(
    # time.censor1yr = pmin(time, value_for_censor_at_1yr)
    # , event.censor1yr = ifelse(time < value_for_censor_at_1yr, event, 0)
    time = pmin(time, value_for_censor_at_1yr)
    , event = ifelse(time < value_for_censor_at_1yr, event, F)
)
survminer::ggsurvplot(survival::survfit(survival::Surv(time = time, event = event) ~ Group, data = AnalyticDataset.censor1yr), palette = c("#00AFBB", "#FC4E07")
           , break.time.by = value_for_break.time.by
           , conf.int = TRUE, risk.table = TRUE, pval = TRUE
           , title = paste0("Survival Curves Stratified by ", varname4Group)
           , xlab = paste0("Time in ", time_scale), ylab = "Survival Probability")

```

#@@ END -----
```{r, paged.print=FALSE}
#@@ END -----
```

#$ objectname = "AnalyticDataset200621" ====
##@ write_rds( get(objectname), file.path(path4write, paste0(objectname, ".rds"))) -----
```{r, paged.print=FALSE}
# #@ write_rds( get(objectname), file.path(path4write, paste0(objectname, ".rds"))) -----
# objectname = "AnalyticDataset200621"
# system.time(write_rds( get(objectname),paste0(objectname, ".rds")))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname, ".rds"))))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname, ".rds")), compress = "gz" ))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname, ".rds", "")), compress = "xz", compression = 9 ))
# # openxlsx::write.xlsx(get(objectname), file = paste0(objectname, ".xlsx"), asTable = T, withFilter = T)
# # openxlsx::openXL(paste0(objectname, ".xlsx"))
```


