---
title: "MHKim's R Notebook"
output: html_notebook
    df_print: tibble
---
  
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
  eval=TRUE, echo=TRUE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
  comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
  warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
  tidy.opts=list(width.cutoff=120), tidy=FALSE, 
  R.options = list(width=120), paged.print=FALSE
) 
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
# env1$info$DocumentTitle0 = paste0("00env1","-",basename(getwd()))
# env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
# cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
#     env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
#     env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
#     env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
#     sep="")
```  
  


  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_filename_ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$LastSourceEditorContext.path_filename_ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(getwd()|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_filename_ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .filename.source.r = "f_DataSetName.Search.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.subpath_filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.filename.source.r))
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  
# __________|------  
# @@ START ----  
  
## \$ tblID_gj3_jk =  ----  
@ assign(.objectname, read_rds(file.path(.path4read, paste0(.objectname,".rds")))) 
```{r DataSetName-read.checkEntity-NoEcho, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# .filename.source.r = "f_DataSetName.Search.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.subpath_filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.filename.source.r))
# .objectname = "tblID_gj3_jk"; cat(" ----\n> ", '.objectname = "', .objectname, '"  \n', sep="")
# filename2read = if(file.exists(file.path(.path4read, paste0(.objectname,".rds")))) paste0(.objectname,".rds") else paste0(.objectname, ".rds.xz")
# env1$f$f_path.size_files(.path4read = .path4read, regex4filename = filename2read)
# system.time(assign(.objectname, readRDS(file.path(.path4read, filename2read)), envir=.GlobalEnv))
# cat(" dim(",.objectname,") == ",deparse(dim(get(.objectname))),"  \n", sep="")
  
# get(.objectname) %>% {.$PERSON_ID} |> n_distinct()
# get(.objectname) %>% {.$RN_INDI} |> n_distinct()
# get(.objectname) |> names() |> deparse(width.cutoff=120-15) |> paste0(collapse="  \n  ") %>% {cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n", ., "  \n", sep="")}  # dput(); |> deparse(width.cutoff=120-15) |> paste0(collapse="  \n") |> cat("  \n", sep=""); # width.cutoff=500 is the max ---    
# get(.objectname) |> names() |> paste(collapse=", ") %>% {cat(" ----\n", ., "\n\n", sep="")}  ;   # tidyeval) paste(collapse=", ") |> cat("  \n", sep="") ---    
# cat(" ----\n> ", "str(get(.objectname), max.level = 2, give.attr = F)", "  \n", sep=""); str(get(.objectname), max.level = 2, give.attr = F)
# # get(.objectname) |> select_if(is.numeric) |> summary() #----  
# # get(.objectname) |> select_if(is.logical) |> summary() #----  
```
  
  
# \$ lung <- as_tibble(survival::lung) ----  
## Step 1: Load the Required Libraries and Data  
## Step 2: Exploratory Data Analysis  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
.packagename = "survival"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
library(survminer)
  
# # Load the lung dataset
# # data("lung")
# lung <- as_tibble(survival::lung)
# lung
as_tibble(survival::lung)
summary(survival::lung)
```
  
  
## Step 3: Kaplan-Meier Survival Curve  
```{r, paged.print=FALSE, fig.width=8, fig.height=6}
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# .packagename = "survival"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# library(survminer)
survminer::ggsurvplot(survival::survfit(survival::Surv(time = time, event = status) ~ 1, data = survival::lung)
           , break.time.by = 365
           , conf.int = TRUE, risk.table = TRUE, pval = TRUE
           , title = "Kaplan-Meier Survival Curve"
           , xlab = "Time in days", ylab = "Survival Probability")
  
```
  
## Step 4: Stratified Kaplan-Meier Survival Curve  
```{r, paged.print=FALSE, fig.width=8, fig.height=6}
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# .packagename = "survival"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# library(survminer)
survminer::ggsurvplot(survival::survfit(survival::Surv(time = time, event = status) ~ sex, data = survival::lung), palette = c("#00AFBB", "#FC4E07")
           , break.time.by = 365
           , conf.int = TRUE, risk.table = TRUE, pval = TRUE
           , title = "Survival Curves Stratified by Sex"
           , xlab = "Time in days", ylab = "Survival Probability")
  
```
  
## Step 5: Cox Proportional Hazards Model  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Fit a Cox proportional hazards model
cox_model <- coxph(surv_obj ~ sex + age + ph.ecog, data = survival::lung)
  
# Summary of the Cox model
summary(cox_model)
  
```
  
## Step 6: Check Proportional Hazards Assumption  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Test for proportional hazards
cox.zph(cox_model)
```
  
# https://github.com/mkim0710/tidystat/blob/master/Rdev/50_model_formula_evaluation/57_model_time2event/AnalyticDataset.censor1yr.survfit.ggsurvplot_CIRiskTableP.dev.r  
  
## \$ AnalyticDataset ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
AnalyticDataset = lung |> rename(event = status, Group = sex)
AnalyticDataset.survfit <- survfit(Surv(time = time, event = event) ~ Group, data = AnalyticDataset)
  
# cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
# ?survminer::ggsurvplot  # "event" plots cumulative events (f(y) = 1-y), "cumhaz" plots the cumulative hazard function (f(y) = -log(y)), and "pct" for survival probability in percentage.
  
# AnalyticDataset.survfit |> ggsurvplot(fun = "pct")  # default fun = "pct"?
# AnalyticDataset.survfit |> ggsurvplot(fun = "event")
# AnalyticDataset.survfit |> ggsurvplot(fun = "cumhaz")  # Cumulative Hazard = -log S(t)
  
AnalyticDataset.survfit |> ggsurvplot  # default fun = "pct"?
```
  
  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
AnalyticDataset.survfit |> ggsurvplot(conf.int = T, risk.table = T, pval = T)
```
  
  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
AnalyticDataset.coxph <- coxph(Surv(time = time, event = event) ~ Group, data = AnalyticDataset)
AnalyticDataset.coxph |> summary() #----  
AnalyticDataset.coxph %>% cox.zph # * Caution) significant = bad news, large p = good news~! Having very small p values indicates that there are time dependent coefficients which you need to take care of ----  
AnalyticDataset.coxph %>% cox.zph %>% ggcoxzph #----  
```
  
  
## \$ AnalyticDataset.censor1yr ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
  
value_for_censor_at_1yr = 365 * 1
value_for_break.time.by = 30
AnalyticDataset.censor1yr = AnalyticDataset |> mutate(
    time.censor1yr = pmin(time, value_for_censor_at_1yr)
    , event.censor1yr = ifelse(time < value_for_censor_at_1yr, event, 0)
)
AnalyticDataset.censor1yr.survfit = survfit(Surv(time = time.censor1yr, event = event.censor1yr) ~ Group, data = AnalyticDataset.censor1yr)
  
# AnalyticDataset.censor1yr.survfit |> ggsurvplot(fun = "pct")  # default fun = "pct"?
# AnalyticDataset.censor1yr.survfit |> ggsurvplot(fun = "event")
# AnalyticDataset.censor1yr.survfit |> ggsurvplot(fun = "cumhaz")  # Cumulative Hazard = -log S(t)
  
AnalyticDataset.censor1yr.survfit |> ggsurvplot  # default fun = "pct"?
  
```
  
  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
AnalyticDataset.censor1yr.survfit |> ggsurvplot(conf.int = T, risk.table = T, pval = T, break.time.by = value_for_break.time.by)
  
```
  
  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
AnalyticDataset.censor1yr.survfit |> ggsurvplot(conf.int = T, risk.table = T, pval = T, break.time.by = value_for_break.time.by)
  
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ START) Analysis ----  
  
## \$ analyticDF_time2event =  ----  
#### [Plot] Stratified Kaplan-Meier Survival Curve  
```{r plot-CodeTemplate, eval=FALSE, include=FALSE}
# ```{r plotWidth10Height6, results="markup", collapse=TRUE, paged.print=FALSE, fig.width=10, fig.height=6}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# suppressPackageStartupMessages(library(survival))
for(.packagename in c("survminer")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
# ?survival::lung 
AnalyticDataset = survival::lung |> as_tibble() |> mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] |> as.factor())
# AnalyticDataset |> dplyr::select(sex, Group) %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)}
# AnalyticDataset |> dplyr::select(sex, Group) |> table(useNA="always") |> addmargins()
# # > AnalyticDataset |> dplyr::select(sex, Group) %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)}
# # 'data.frame':	228 obs. of  2 variables:
# #  $ sex  : num  1 1 1 1 1 1 2 2 1 1 ...
# #  $ Group: Factor w/ 2 levels "Female","Male": 2 2 2 2 2 2 1 1 2 2 ...
# # > AnalyticDataset |> dplyr::select(sex, Group) |> table(useNA="always") |> addmargins()
# #    Group
# # sex Female Male
# #   1      0  138
# #   2     90    0
AnalyticDataset |> dplyr::select(time, event, Group) |> summary()
  
# cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
# ?survminer::ggsurvplot  # "event" plots cumulative events (f(y) = 1-y), "cumhaz" plots the cumulative hazard function (f(y) = -log(y)), and "pct" for survival probability in percentage.
# AnalyticDataset.survfit |> ggsurvplot(fun = "pct")  # default fun = "pct"?
# AnalyticDataset.survfit |> ggsurvplot(fun = "event")
# AnalyticDataset.survfit |> ggsurvplot(fun = "cumhaz")  # Cumulative Hazard = -log S(t)
value_for_censor_at_1yr = 365 * 1
value_for_break.time.by = 30
time_scale = "days"
varname4Group = "Group"
AnalyticDataset.censor1yr = AnalyticDataset |> mutate(
    # time.censor1yr = pmin(time, value_for_censor_at_1yr)
    # , event.censor1yr = ifelse(time < value_for_censor_at_1yr, event, 0)
    time = pmin(time, value_for_censor_at_1yr)
    , event = ifelse(time < value_for_censor_at_1yr, event, F)
)

cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
data.formula.survfit = as.formula(survival::Surv(time = time, event = event) ~ Group) |> 
    survival::survfit(data = AnalyticDataset.censor1yr)
data.formula.survfit
# Call: survfit(formula = (survival::Surv(time = time, event = event) ~ 
#     Group), data = dplyr::select(dplyr::filter(analyticDF_time2event.CensorEND, 
#     StudyPopulation), -StudyPopulation))
# 
#                n events median 0.95LCL 0.95UCL
# Group=Female  89     35     NA     348      NA
# Group=Male   130     77    285     229     337
data.formula.survfit |> 
    survminer::ggsurvplot(
        fun = "cumhaz", 
        palette = c("#00AFBB", "#FC4E07"), 
        break.time.by = value_for_break.time.by, 
        conf.int = TRUE, risk.table = TRUE, pval = TRUE, 
        xlim = c(0, value_for_Censor_at_END), ylim = c(0, 1), 
        xlab = paste0("Time in ", time_scale)    )
  
```  
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
```{r createBACKUP, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_filename_ext.createBACKUP(BACKUP_from_path_filename_ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal.attach$f_filename_ext.createBACKUP(BACKUP_from_path_filename_ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$LastSourceEditorContext.path_filename.pdf = env1$path$LastSourceEditorContext.path_filename_ext |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$LastSourceEditorContext.path_filename.html = env1$path$LastSourceEditorContext.path_filename_ext |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
# if (Sys.getenv("PARENT_RENDERING") != "YES") {
#     if (Sys.info()["sysname"] == "Windows") {
#         .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
#         .font_name = "roboto"; if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)
#         .font_name = "cascadia-code"; if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)
#         cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$LastSourceEditorContext.path_filename_ext)),', output_format = "pdf_document")  \n')
#         Sys.setenv(PARENT_RENDERING = "YES"); env1$path$LastSourceEditorContext.path_filename_ext %>% {paste0(env1$path$path1,"/",.)} %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
#         env1$env.internal.attach$f_filename_ext.createBACKUP(BACKUP_from_path_filename_ext = env1$path$LastSourceEditorContext.path_filename.pdf %>% {paste0(env1$path$path1,"/",.)}, .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
#         try(env1$env.internal.attach$f_file_PDF.sumatra(env1$path$LastSourceEditorContext.path_filename.pdf %>% {paste0(env1$path$path1,"/",.)}))
#     }
# }
# env1$path$LastSourceEditorContext.path_filename_ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_filename.pdf %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_filename_ext.createBACKUP(BACKUP_from_path_filename_ext = ',deparse(.path_file),', .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal.attach$f_file_PDF.sumatra(',deparse(.path_file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path_file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$LastSourceEditorContext.path_filename_ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; env1$path$LastSourceEditorContext.path_filename.html %>% {paste0(env1$path$path1,"/",.)} %>% cat('  "',.,'" |> env1$env.internal.attach$f_filename_ext.createBACKUP(.BACKUP_to_path="-BACKUP", timeFormat="%y%m%d", overwrite=TRUE)  \n', sep=""); env1$path$LastSourceEditorContext.path_filename.html %>% {paste0(env1$path$path1,"/",.)} %>% cat('  "',.,'" |> env1$env.internal.attach$f_URL.browse_in_edge_app()  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_filename.nb.html = env1$path$LastSourceEditorContext.path_filename_ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/",mustWork=NA),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$LastSourceEditorContext.path_filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
