---
title: "MHKim's R Notebook"
output: html_notebook
    df_print: tibble
---
  
# _______________
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: \% \$ \# \*   -->

```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "\n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
  eval=TRUE, echo=TRUE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
  comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
  warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
  tidy.opts=list(width.cutoff=120), tidy=FALSE, 
  R.options = list(width=120), paged.print=FALSE
) 
knitr::opts_knit$set(global.par = TRUE)


# ```{r options-width-NoEchoHideResults, echo=FALSE, results="hide"}
if(!exists("env1", envir=.GlobalEnv)) 
    assign("env1", new.env(), envir=.GlobalEnv)
if(!"info" %in% names(.GlobalEnv$env1)) .GlobalEnv$env1$info <- list()
env1$info$options.width = options()$width; cat(options()$width, "\n", sep="")


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
suppressPackageStartupMessages({for(packagename in c("tidyverse","formatR")) {if(!require(packagename,character.only=TRUE))install.packages(packagename) else library(packagename,character.only=TRUE)}});cat(" \n");
if(!exists("env1", envir=.GlobalEnv)) 
    assign("env1", new.env(), envir=.GlobalEnv)
## env1\$path ============  
if(!"path" %in% names(.GlobalEnv$env1)) .GlobalEnv$env1$path <- list()
objectname = "source_base_local"; object = ifelse(.Platform$OS.type == "windows", "D:/OneDrive/[][Rproject]/github_tidystat", "~/github_tidystat"); if(!objectname %in% names(env1$path)) {env1$path[[objectname]] = object};
objectname = "source_base_github"; object = "https://github.com/mkim0710/tidystat/raw/master"; if(!objectname %in% names(env1$path)) {env1$path[[objectname]] = object};
env1$path$source_base = ifelse(dir.exists(env1$path$source_base_local), env1$path$source_base_local, env1$path$source_base_github)  
## env1\$env.internal ============  
sourcename = "env1$env.internal" |> paste0(".source.r"); subpath=r"()"; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename); suppressPackageStartupMessages(source( file.path(env1$path$source_base,subpath.filename.source.r) ))
#### env1\$f_df.t.tribble_construct() ============  
sourcename = "f_df.t.tribble_construct" |> paste0(".source.r"); subpath=r"()"; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename); suppressPackageStartupMessages(source( file.path(env1$path$source_base,subpath.filename.source.r) ))
```
  
  
  
<font size="3">\% env1</font>\  
  
```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
if(!exists("env1", envir=.GlobalEnv)) 
    assign("env1", new.env(), envir=.GlobalEnv)
if(!"info" %in% names(.GlobalEnv$env1)) .GlobalEnv$env1$info <- list()
#### env1\$info\$get_system_info() ============  
sourcename = "get_system_info" |> paste0(".source.r"); subpath=r"()"; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename); suppressPackageStartupMessages(source( file.path(env1$path$source_base,subpath.filename.source.r) ))
env1$info$info_system_info = env1$info$get_system_info()
# str(env1$info$info_system_info)
CodeText = "env1$info$info_system_info$machine_nodename"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
CodeText = "env1$info$info_system_info$Sys.getlocale$LC_COLLATE"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
# CodeText = "env1$info$info_system_info$l10n_info$localization_UTF8"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
env1$info$info_software_versions = env1$info$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "datapasta","openxlsx"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ============  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```  
  


  
  
```{r env1-Path-NoEcho, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE}
###### env1\$path ============  
library(tidyverse);cat(" \n"); 
cat(" \n"); cat(" getwd() == "); dput(getwd()) #------------  
env1$path$getwd = getwd()
# env1$path$path0 = file.path("D:", "OneDrive - SNU", "[][Rproject]")
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
# 
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
# env1$path$path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$path4write = file.path(env1$path$path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  
# 
# path4read  = env1$path$path4read
# # path4write = env1$path$path4read
# # path4write = env1$path$path4write
path4read = getwd()
path4write = getwd()
sourcename = "f_objectname.read.checkEntity" |> paste0(".source.r"); subpath=r"()"; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename); suppressPackageStartupMessages(source( file.path(env1$path$source_base,subpath.filename.source.r) ))
if (getwd() != path4write) warning("getwd() != path4write  == ") else cat(" getwd() == path4write == "); dput(path4write)  #------------  
```
  
  
##\% env1\$f_path.size_files() ============  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# tribble_paste = datapasta::tribble_paste
# https://github.com/mkim0710/tidystat/blob/master/f_df.t.tribble_construct.dev.r
#|________________________________________________________________________________|#  
#@ Old code replaced) load(url("https://github.com/mkim0710/tidystat/raw/master/f_df.t.tribble_construct.RData")) -----------
## env1\$path ============  
if(!"path" %in% names(.GlobalEnv$env1)) .GlobalEnv$env1$path <- list()
objectname = "source_base_local"; object = ifelse(.Platform$OS.type == "windows", "D:/OneDrive/[][Rproject]/github_tidystat", "~/github_tidystat"); if(!objectname %in% names(env1$path)) {env1$path[[objectname]] = object};
objectname = "source_base_github"; object = "https://github.com/mkim0710/tidystat/raw/master"; if(!objectname %in% names(env1$path)) {env1$path[[objectname]] = object};
env1$path$source_base = ifelse(dir.exists(env1$path$source_base_local), env1$path$source_base_local, env1$path$source_base_github)  
## env1\$env.internal ============  
sourcename = "env1$env.internal" |> paste0(".source.r"); subpath=r"()"; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename); suppressPackageStartupMessages(source( file.path(env1$path$source_base,subpath.filename.source.r) ))
#### env1\$f_df.t.tribble_construct() ============  
sourcename = "f_df.t.tribble_construct" |> paste0(".source.r"); subpath=r"()"; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename); suppressPackageStartupMessages(source( file.path(env1$path$source_base,subpath.filename.source.r) ))
#|________________________________________________________________________________|#  
# attach(env1)
  
# regex4filename = "\\.rds(\\.xz)?$"
regex4filename = "\\.rds\\.xz$"
list.files(path4write) %>% grep(regex4filename, ., value = T) %>% {cat(" ----\n", deparse(., width.cutoff=120), "\n\n", sep="")} # dput() cat(deparse(., width.cutoff=120)), width.cutoff=500 is the max ------------  
env1$f_path.size_files(path4read = path4write, regex4filename = regex4filename)
  
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n"); #------------  
regex4filename = "\\.rds$"
list.files(path4write) %>% grep(regex4filename, ., value = T) %>% {cat(" ----\n", deparse(., width.cutoff=120), "\n\n", sep="")} # dput() cat(deparse(., width.cutoff=120)), width.cutoff=500 is the max ------------  
env1$f_path.size_files(path4read = path4write, regex4filename = regex4filename)
```
  
  
  
# @@ START ------------  
  
## \$ objectname = "tblID_gj3_jk" ============  
@ assign(objectname, read_rds(file.path(path4read, paste0(objectname,".rds")))) 
```{r objectname-read.checkEntity, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# sourcename = "f_objectname.read.checkEntity" |> paste0(".source.r"); subpath=r"()"; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename); suppressPackageStartupMessages(source( file.path(env1$path$source_base,subpath.filename.source.r) ))
# objectname = "tblID_gj3_jk"; cat(" ----\n> ", 'objectname = "', objectname, '"\n', sep=""); 
# filename2read = if(file.exists(file.path(path4read, paste0(objectname,".rds")))) paste0(objectname,".rds") else paste0(objectname, ".rds.xz")
# env1$f_path.size_files(path4read = path4read, regex4filename = filename2read)
# system.time(assign(objectname, readRDS(file.path(path4read, filename2read)), envir=.GlobalEnv))
# cat(" dim(",objectname,") = ",deparse(dim(get(objectname))),"\n", sep="")
  
# get(objectname) %>% {.$PERSON_ID} |> n_distinct()
# get(objectname) %>% {.$RN_INDI} |> n_distinct()
# get(objectname) |> names() %>% {cat(" ----\n", deparse(., width.cutoff=120), "\n\n", sep="")} # dput() cat(deparse(., width.cutoff=120)), width.cutoff=500 is the max ------------  
# get(objectname) |> names() |> paste(collapse=", ") %>% {cat(" ----\n", ., "\n\n", sep="")}; # tidyselect: paste(collapse=", ") |> cat() ------------  
# cat(" ----\n> ", "str(get(objectname), max.level = 2, give.attr = F)", "\n", sep=""); str(get(objectname), max.level = 2, give.attr = F); 
# # get(objectname) |> select_if(is.numeric) |> summary() #------------  
# # get(objectname) |> select_if(is.logical) |> summary() #------------  
```
  
  
  
# \$ lung <- as_tibble(survival::lung) ============  
## Step 1: Load the Required Libraries and Data  
## Step 2: Exploratory Data Analysis  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
library(tidyverse)
library(survival)
library(survminer)
  
# # Load the lung dataset
# # data("lung")
# lung <- as_tibble(survival::lung)
# lung
as_tibble(survival::lung)
summary(survival::lung)
```
  
  
  
## Step 3: Kaplan-Meier Survival Curve  
```{r, paged.print=FALSE, fig.width=8, fig.height=6}
library(tidyverse)
# library(survival)
# library(survminer)
survminer::ggsurvplot(survival::survfit(survival::Surv(time = time, event = status) ~ 1, data = survival::lung)
           , break.time.by = 365
           , conf.int = TRUE, risk.table = TRUE, pval = TRUE
           , title = "Kaplan-Meier Survival Curve"
           , xlab = "Time in days", ylab = "Survival Probability")
  
```
  
## Step 4: Stratified Kaplan-Meier Survival Curve  
```{r, paged.print=FALSE, fig.width=8, fig.height=6}
library(tidyverse)
# library(survival)
# library(survminer)
survminer::ggsurvplot(survival::survfit(survival::Surv(time = time, event = status) ~ sex, data = survival::lung), palette = c("#00AFBB", "#FC4E07")
           , break.time.by = 365
           , conf.int = TRUE, risk.table = TRUE, pval = TRUE
           , title = "Survival Curves Stratified by Sex"
           , xlab = "Time in days", ylab = "Survival Probability")
  
```
  
## Step 5: Cox Proportional Hazards Model  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# Fit a Cox proportional hazards model
cox_model <- coxph(surv_obj ~ sex + age + ph.ecog, data = survival::lung)
  
# Summary of the Cox model
summary(cox_model)
  
```
  
## Step 6: Check Proportional Hazards Assumption  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# Test for proportional hazards
cox.zph(cox_model)
```
  
# https://github.com/mkim0710/tidystat/blob/master/Rdev/50_model_formula_evaluation/57_model_time2event/AnalyticDataset.censor1yr.survfit.ggsurvplot_CIRiskTableP.dev.r  
  
## \$ AnalyticDataset ============  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
AnalyticDataset = lung |> rename(event = status, Group = sex)
AnalyticDataset.survfit <- survfit(Surv(time = time, event = event) ~ Group, data = AnalyticDataset)
  
?survminer::ggsurvplot  # "event" plots cumulative events (f(y) = 1-y), "cumhaz" plots the cumulative hazard function (f(y) = -log(y)), and "pct" for survival probability in percentage.
  
# AnalyticDataset.survfit |> ggsurvplot(fun = "pct")  # default fun = "pct"?
# AnalyticDataset.survfit |> ggsurvplot(fun = "event")
# AnalyticDataset.survfit |> ggsurvplot(fun = "cumhaz")  # Cumulative Hazard = -log S(t)
  
AnalyticDataset.survfit |> ggsurvplot  # default fun = "pct"?
```
  
  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
AnalyticDataset.survfit |> ggsurvplot(conf.int = T, risk.table = T, pval = T)
```
  
  
  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
AnalyticDataset.coxph <- coxph(Surv(time = time, event = event) ~ Group, data = AnalyticDataset)
AnalyticDataset.coxph |> summary() #------------  
AnalyticDataset.coxph %>% cox.zph # * Caution) significant = bad news, large p = good news~! Having very small p values indicates that there are time dependent coefficients which you need to take care of ------------  
AnalyticDataset.coxph %>% cox.zph %>% ggcoxzph #------------  
```
  
  
  
## \$ AnalyticDataset.censor1yr ============  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
  
value_for_censor_at_1yr = 365 * 1
value_for_break.time.by = 30
AnalyticDataset.censor1yr = AnalyticDataset |> mutate(
    time.censor1yr = pmin(time, value_for_censor_at_1yr)
    , event.censor1yr = ifelse(time < value_for_censor_at_1yr, event, 0)
)
AnalyticDataset.censor1yr.survfit = survfit(Surv(time = time.censor1yr, event = event.censor1yr) ~ Group, data = AnalyticDataset.censor1yr)
  
# AnalyticDataset.censor1yr.survfit |> ggsurvplot(fun = "pct")  # default fun = "pct"?
# AnalyticDataset.censor1yr.survfit |> ggsurvplot(fun = "event")
# AnalyticDataset.censor1yr.survfit |> ggsurvplot(fun = "cumhaz")  # Cumulative Hazard = -log S(t)
  
AnalyticDataset.censor1yr.survfit |> ggsurvplot  # default fun = "pct"?
  
```
  
  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
AnalyticDataset.censor1yr.survfit |> ggsurvplot(conf.int = T, risk.table = T, pval = T, break.time.by = value_for_break.time.by)
  
```
  
  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
AnalyticDataset.censor1yr.survfit |> ggsurvplot(conf.int = T, risk.table = T, pval = T, break.time.by = value_for_break.time.by)
  
```
  
  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
  
```
  
  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
  
```
  
  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
  
```
  
  
# @@ START) Analysis ------------  
  
## \$ DataSetName = "analyticDF_time2event" ============  
#### [Plot] Stratified Kaplan-Meier Survival Curve  
```{r plot-CodeTemplate, eval=FALSE, include=FALSE}
# {r plotWidth10Height6, results="markup", collapse=TRUE, paged.print=FALSE, fig.width=10, fig.height=6}
options(width=120)
suppressPackageStartupMessages(library(tidyverse))
# suppressPackageStartupMessages(library(survival))
# suppressPackageStartupMessages(library(survminer))
?survival::lung 
AnalyticDataset = survival::lung |> mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] |> as.factor())
# AnalyticDataset |> dplyr::select(sex, Group) %>% {cat(" > ",deparse(substitute(.))," |> str()","\n", sep=""); str(.)}
# AnalyticDataset |> dplyr::select(sex, Group) |> table(useNA="always") |> addmargins()
# # > AnalyticDataset |> dplyr::select(sex, Group) %>% {cat(" > ",deparse(substitute(.))," |> str()","\n", sep=""); str(.)}
# # 'data.frame':	228 obs. of  2 variables:
# #  $ sex  : num  1 1 1 1 1 1 2 2 1 1 ...
# #  $ Group: Factor w/ 2 levels "Female","Male": 2 2 2 2 2 2 1 1 2 2 ...
# # > AnalyticDataset |> dplyr::select(sex, Group) |> table(useNA="always") |> addmargins()
# #    Group
# # sex Female Male
# #   1      0  138
# #   2     90    0
AnalyticDataset |> dplyr::select(time, event, Group) |> summary()
  
?survminer::ggsurvplot  # "event" plots cumulative events (f(y) = 1-y), "cumhaz" plots the cumulative hazard function (f(y) = -log(y)), and "pct" for survival probability in percentage.
# AnalyticDataset.survfit |> ggsurvplot(fun = "pct")  # default fun = "pct"?
# AnalyticDataset.survfit |> ggsurvplot(fun = "event")
# AnalyticDataset.survfit |> ggsurvplot(fun = "cumhaz")  # Cumulative Hazard = -log S(t)
value_for_censor_at_1yr = 365 * 1
value_for_break.time.by = 30
time_scale = "days"
varname4Group = "Group"
AnalyticDataset.censor1yr = AnalyticDataset |> mutate(
    # time.censor1yr = pmin(time, value_for_censor_at_1yr)
    # , event.censor1yr = ifelse(time < value_for_censor_at_1yr, event, 0)
    time = pmin(time, value_for_censor_at_1yr)
    , event = ifelse(time < value_for_censor_at_1yr, event, F)
)
survminer::ggsurvplot(survival::survfit(survival::Surv(time = time, event = event) ~ Group, data = AnalyticDataset.censor1yr), palette = c("#00AFBB", "#FC4E07")
           , break.time.by = value_for_break.time.by
           , conf.int = TRUE, risk.table = TRUE, pval = TRUE
           , title = paste0("Survival Curves Stratified by ", varname4Group)
           , xlab = paste0("Time in ", time_scale), ylab = "Survival Probability")
  
```
  
# @@ END ------------  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# @@ END ------------  
```
  
  
```{r writeRDS-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# # @ write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds"))) ------------  
# objectname = "AnalyticDataset200621"
# system.time(write_rds( get(objectname), paste0(objectname,".rds") ))
# system.time(write_rds( get(paste0(objectname,".NA",".rmAllNA",".fct")), paste0(objectname,".NA",".rmAllNA",".fct",".rds") ))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds"))))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds")), compress = "gz" ))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname, ".rds", "")), compress = "xz", compression = 9 ))
# # system.time(openxlsx::write.xlsx(get(objectname), file=paste0(objectname,".xlsx"), asTable=TRUE, withFilter=TRUE))
# # if (.Platform$OS.type == "windows") openxlsx::openXL(paste0(objectname, ".xlsx"))
```
  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (.Platform$OS.type == "windows") {
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render, eval=TRUE, include=FALSE}
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.pdf = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".pdf")
env1$path$CurrentSource.path.filename.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".html")
# if (Sys.getenv("PARENT_RENDERING") != "YES") {
#     if (.Platform$OS.type == "windows") {
#         tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
#         font_name = "roboto"; if(tlmgr_installed_packages |> str_subset(font_name) |> length() == 0) tinytex::tlmgr_install(font_name)
#         font_name = "cascadia-code"; if(tlmgr_installed_packages |> str_subset(font_name) |> length() == 0) tinytex::tlmgr_install(font_name)
#         cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_format = "pdf_document") \n')
#         Sys.setenv(PARENT_RENDERING = "YES"); env1$path$CurrentSource.path.filename.ext |> rmarkdown::render(output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")
#         env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = env1$path$CurrentSource.path.filename.pdf, backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
#         env1$env.internal$f_file_PDF.sumatra(env1$path$CurrentSource.path.filename.pdf)
#     }
# }
cat(' Sys.setenv(PARENT_RENDERING = "YES"); "',env1$path$CurrentSource.path.filename.ext,'" |> rmarkdown::render(output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")',"\n", 
    ' if (.Platform$OS.type == "windows") { env1$env.internal$f_file_PDF.sumatra("',env1$path$CurrentSource.path.filename.pdf,'") } else { browseURL("',env1$path$CurrentSource.path.filename.pdf,'") }',"\n",
    ' env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = "',env1$path$CurrentSource.path.filename.pdf,'", backup_to_path="-backup", timeFormat="%y%m%d", overwrite=TRUE)',"\n", sep="")
cat("    ________________________________________________________________________    \n")
cat(' Sys.setenv(PARENT_RENDERING = "YES"); "',env1$path$CurrentSource.path.filename.ext,'" |> rmarkdown::render(output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")',"\n", 
    ' if (.Platform$OS.type == "windows") { system("\\"C:/Program Files (x86)/Microsoft/Edge/Application/msedge.exe\\" --app=\\"',env1$path$CurrentSource.path.filename.html |> normalizePath(winslash="/", mustWork = FALSE),'\\"") } else { browseURL("',env1$path$CurrentSource.path.filename.html,'") }',"\n",
    ' env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = "',env1$path$CurrentSource.path.filename.html,'", backup_to_path="-backup", timeFormat="%y%m%d", overwrite=TRUE)',"\n", sep="")
```
  
  
```{r gitCheckout, eval=TRUE, include=FALSE}
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.nb.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (.Platform$OS.type == "windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge.exe" --app="',env1$path$CurrentSource.path.filename.nb.html|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$CurrentSource.path.filename.nb.html) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("\n")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("\n")
cat(" * To revert to the last commited file, run the following terminal command:\n", 
    '"git checkout -- ',env1$path$CurrentSource.path.filename.ext,'" |> system(intern=TRUE)',"\n",
    '"git checkout -- ',env1$path$CurrentSource.path.filename.nb.html,'" |> system(intern=TRUE)',"\n", sep="")
```
  
  
