---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = options()$width; cat(options()$width, "  \n", sep="")
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.echo(Execute = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .sourcename = "f_DataSetName.Search.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  


# @@ START) data example ----  
## \$ text_example =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
suppressPackageStartupMessages(library(tidyverse))
# suppressPackageStartupMessages(library(survival))


```
  
  
# @@ START) dev ----  

## \% text_example |>  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ START) function ----  
https://chatgpt.com/c/b6d36a06-90b6-4835-919b-94ffa260b00f
## \% |> function_name()  
```{r, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
translate_korean_to_english <- function(korean_text) {
  # Load necessary packages
  if (!requireNamespace("googlesheets4", quietly = TRUE)) {
    install.packages("googlesheets4")
  }
  if (!requireNamespace("googledrive", quietly = TRUE)) {
    install.packages("googledrive")
  }
  library(googlesheets4)
  library(googledrive)
  
  # Authorize Google Sheets and Drive access with specified email
  gs4_auth(email = "mhkim710@gmail.com")
  drive_auth(email = "mhkim710@gmail.com")
  
  # Create a new Google Sheet
  sheet <- gs4_create("TranslationSheet")
  
  # Write Korean text to the first cell (A1)
  data <- data.frame(Text = korean_text)
  sheet_write(data, ss = sheet, sheet = "Sheet1")
  
  # Write the GOOGLETRANSLATE function directly into the desired cell
  formula_data <- data.frame(Text = '=GOOGLETRANSLATE(A1, "ko", "en")')
  range_write(ss = sheet, data = formula_data, sheet = "Sheet1", range = "B1")
  
  # Retry logic to ensure the translation is ready before reading
  translated_text <- NULL
  retries <- 3
  for (i in 1:retries) {
    Sys.sleep(5)  # Wait for 5 seconds before each retry
    translated_text <- read_sheet(sheet, range = "B1", col_names = FALSE)
    if (nrow(translated_text) > 0) {
      break
    }
  }
  
  # Check if the translation was successful
  if (is.null(translated_text) || nrow(translated_text) == 0) {
    stop("Translation failed or did not complete in time.")
  }
  
  # Clean up by deleting the Google Sheet using googledrive package
  drive_trash(as_id(sheet))
  
  # Return the translated text
  return(translated_text[[1, 1]])
}

# Example usage of the function
translated_text <- translate_korean_to_english("안녕하세요. 만나서 반갑습니다.")
print(translated_text)

```
  
  
## \% |> function_name()  
```{r, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
translate_korean_to_english <- function(korean_text) {
  # Load necessary packages
  if (!requireNamespace("googlesheets4", quietly = TRUE)) {
    install.packages("googlesheets4")
  }
  if (!requireNamespace("googledrive", quietly = TRUE)) {
    install.packages("googledrive")
  }
  library(googlesheets4)
  library(googledrive)
  
  # Authorize Google Sheets and Drive access with specified email
  gs4_auth(email = "mhkim710@gmail.com")
  drive_auth(email = "mhkim710@gmail.com")
  
  # Create a new Google Sheet
  sheet <- gs4_create("TranslationSheet")
  
  # Write Korean text to the first cell (A1)
  data <- data.frame(Text = korean_text)
  sheet_write(data, ss = sheet, sheet = "Sheet1")
  
  # Write the GOOGLETRANSLATE function directly into the desired cell
  formula_data <- data.frame(Text = '=GOOGLETRANSLATE(A1, "ko", "en")')
  range_write(ss = sheet, data = formula_data, sheet = "Sheet1", range = "B1")
  
  # Print the Google Sheet ID and URL
  sheet_id <- as_id(sheet)
  sheet_url <- paste0("https://docs.google.com/spreadsheets/d/", sheet_id)
  message("Please check the Google Sheet manually at this URL: ", sheet_url)
  
  # Pause the execution to allow manual inspection
  readline(prompt = "Press [Enter] key after you've checked the Google Sheet...")
  
  # Read the translated text from the Google Sheet
  translated_text <- read_sheet(sheet, range = "B1", col_names = FALSE)
  
  # Clean up by deleting the Google Sheet using googledrive package
  drive_trash(sheet_id)
  
  # Return the translated text
  return(translated_text[[1, 1]])
}

# Example usage of the function
translated_text <- translate_korean_to_english("안녕하세요. 만나서 반갑습니다.")
print(translated_text)
# ✔ Creating new Sheet: TranslationSheet.
# ✔ Writing to TranslationSheet.
# ✔ Writing to sheet Sheet1.
# ✔ Editing TranslationSheet.
# ✔ Writing to sheet Sheet1.
# ✔ Changing dims: (2 x 1) --> (2 x 2).
# Please check the Google Sheet manually at this URL: https://docs.google.com/spreadsheets/d/1V32ZTbPFNNFFXx4JfXEhYqSFEfCpfY45h6OlKX0vWtI
# Error in translated_text[[1, 1]] :
# 15.
# stop(fallback)
# 14.
# signal_abort(cnd)
# 13.
# cnd_signal(cnd)
# 12.
# (function (cnd)
# {
# cnd$subscript_arg <- i_arg
# cnd$subscript_elt <- "row" ...
# 11.
# signalCondition(cnd)
# 10.
# signal_abort(cnd)
# 9.
# cnd_signal(x$err)
# 8.
# result_get(vec_as_location2_result(i, n = n, names = names, negative = "error",
# missing = missing, arg = arg, call = call))
# 7.
# vec_as_location2(i, n, call = call)
# 6.
# withCallingHandlers(expr, vctrs_error_subscript = function(cnd) {
# cnd$subscript_arg <- i_arg
# cnd$subscript_elt <- "row"
# if (isTRUE(assign) && !isTRUE(cnd$subscript_action %in% c("negate"))) { ...
# 5.
# subclass_row_index_errors(vec_as_location2(i, n, call = call),
# i_arg = i_arg, assign = assign)
# 4.
# vectbl_as_row_location2(i, fast_nrow(x), i_arg)
# 3.
# `[[.tbl_df`(translated_text, 1, 1)
# 2.
# translated_text[[1, 1]]
# 1.
# translate_korean_to_english("안녕하세요. 만나서 반갑습니다.")

```
  
  
## \% |> function_name()  
```{r, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
translate_korean_to_english <- function(korean_text) {
  # Load necessary packages
  if (!requireNamespace("googlesheets4", quietly = TRUE)) {
    install.packages("googlesheets4")
  }
  if (!requireNamespace("googledrive", quietly = TRUE)) {
    install.packages("googledrive")
  }
  library(googlesheets4)
  library(googledrive)
  
  # Authorize Google Sheets and Drive access with specified email
  gs4_auth(email = "mhkim710@gmail.com")
  drive_auth(email = "mhkim710@gmail.com")
  
  # Create a new Google Sheet
  sheet <- gs4_create("TranslationSheet")
  
  # Write Korean text to the second row, first cell (A2)
  data <- data.frame(Text = korean_text)
  sheet_write(data, ss = sheet, sheet = "Sheet1", range = "A2")
  
  # Write the GOOGLETRANSLATE formula directly into the second row, second cell (B2)
  formula_data <- data.frame(Text = '=GOOGLETRANSLATE(A2, "ko", "en")')
  range_write(ss = sheet, data = formula_data, sheet = "Sheet1", range = "B2", col_names = FALSE)
  
  # Print the Google Sheet ID and URL
  sheet_id <- as_id(sheet)
  sheet_url <- paste0("https://docs.google.com/spreadsheets/d/", sheet_id)
  message("Please check the Google Sheet manually at this URL: ", sheet_url)
  
  # Pause the execution to allow manual inspection
  readline(prompt = "Press [Enter] key after you've checked the Google Sheet...")
  
  # Read the translated text from the Google Sheet
  translated_text <- read_sheet(sheet, range = "B2", col_names = FALSE)
  
  # Clean up by deleting the Google Sheet using googledrive package
  drive_trash(sheet_id)
  
  # Return the translated text
  return(translated_text[[1, 1]])
}

# Example usage of the function
translated_text <- translate_korean_to_english("안녕하세요. 만나서 반갑습니다.")
print(translated_text)
# ✔ Creating new Sheet: TranslationSheet.
# ✔ Writing to TranslationSheet.
# ✔ Writing to sheet Sheet1.
# ✔ Editing TranslationSheet.
# ✔ Writing to sheet Sheet1.
# ✔ Changing dims: (2 x 1) --> (2 x 2).
# Please check the Google Sheet manually at this URL: https://docs.google.com/spreadsheets/d/1G379SpILn5kE7hivyf0KdqWpvk36yD2378DVjYs4TuA
# Error in translated_text[[1, 1]] :
# 15.
# stop(fallback)
# 14.
# signal_abort(cnd)
# 13.
# cnd_signal(cnd)
# 12.
# (function (cnd)
# {
# cnd$subscript_arg <- i_arg
# cnd$subscript_elt <- "row" ...
# 11.
# signalCondition(cnd)
# 10.
# signal_abort(cnd)
# 9.
# cnd_signal(x$err)
# 8.
# result_get(vec_as_location2_result(i, n = n, names = names, negative = "error",
# missing = missing, arg = arg, call = call))
# 7.
# vec_as_location2(i, n, call = call)
# 6.
# withCallingHandlers(expr, vctrs_error_subscript = function(cnd) {
# cnd$subscript_arg <- i_arg
# cnd$subscript_elt <- "row"
# if (isTRUE(assign) && !isTRUE(cnd$subscript_action %in% c("negate"))) { ...
# 5.
# subclass_row_index_errors(vec_as_location2(i, n, call = call),
# i_arg = i_arg, assign = assign)
# 4.
# vectbl_as_row_location2(i, fast_nrow(x), i_arg)
# 3.
# `[[.tbl_df`(translated_text, 1, 1)
# 2.
# translated_text[[1, 1]]
# 1.
# translate_korean_to_english("안녕하세요. 만나서 반갑습니다.")

```
  
  
```{r, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
translate_korean_to_english <- function(korean_text) {
  # Load necessary packages
  if (!requireNamespace("googlesheets4", quietly = TRUE)) {
    install.packages("googlesheets4")
  }
  if (!requireNamespace("googledrive", quietly = TRUE)) {
    install.packages("googledrive")
  }
  library(googlesheets4)
  library(googledrive)

  # Authorize Google Sheets and Drive access with specified email
  gs4_auth(email = "mhkim710@gmail.com")
  drive_auth(email = "mhkim710@gmail.com")

  # Create a new Google Sheet
  sheet <- gs4_create("TranslationSheet")

  # Get the full sheet details
  sheet_details <- gs4_get(sheet)

  # Get the name of the first sheet (in case it's not "Sheet1")
  sheet_name <- sheet_details$sheets$name[1]

  # Write Korean text to the second row, first cell (A2)
  data <- data.frame(Text = korean_text)
  range_write(ss = sheet, data = data, sheet = sheet_name, range = "A2", col_names = FALSE)

  # Write the GOOGLETRANSLATE formula directly into the second row, second cell (B2)
  formula_data <- data.frame(Text = '=GOOGLETRANSLATE(A2, "ko", "en")')
  range_write(ss = sheet, data = formula_data, sheet = sheet_name, range = "B2", col_names = FALSE)

  # Print the Google Sheet ID and URL
  sheet_id <- as_id(sheet)
  sheet_url <- paste0("https://docs.google.com/spreadsheets/d/", sheet_id)
  message("Please check the Google Sheet manually at this URL: ", sheet_url)

  # Pause the execution to allow manual inspection
  readline(prompt = "Press [Enter] key after you've checked the Google Sheet...")

  # Read the translated text from the Google Sheet
  translated_text <- read_sheet(sheet, range = "B2", col_names = FALSE)

  # Clean up by deleting the Google Sheet using googledrive package
  drive_trash(sheet_id)

  # Return the translated text
  return(translated_text[[1, 1]])
}

# Example usage of the function
translated_text <- translate_korean_to_english("안녕하세요. 만나서 반갑습니다.")
print(translated_text)
# ✔ Creating new Sheet: TranslationSheet.
# 
# Quitting from lines  at lines 458-514 [unnamed-chunk-7] (f_chr_ko.translate2en.dev.Rmd)
# ✔ Editing TranslationSheet.
# ✔ Writing to sheet 시트1.
# ✔ Editing TranslationSheet.
# ✔ Writing to sheet 시트1.
# Please check the Google Sheet manually at this URL: https://docs.google.com/spreadsheets/d/1Bp7CZLvUgZAzJTJRQg1Zns1D3ERJWLb_6aXVujv-fUg
# [1] "=GOOGLETRANSLATE(A2, \"ko\", \"en\")"

```
  
  
## \% working version~!  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
translate_korean_to_english <- function(korean_text) {
  # Load necessary packages
  if (!requireNamespace("googlesheets4", quietly = TRUE)) {
    install.packages("googlesheets4")
  }
  if (!requireNamespace("googledrive", quietly = TRUE)) {
    install.packages("googledrive")
  }
  library(googlesheets4)
  library(googledrive)
  
  # Authorize Google Sheets and Drive access with specified email
  gs4_auth(email = "mhkim710@gmail.com")
  drive_auth(email = "mhkim710@gmail.com")
  
  # Create a new Google Sheet
  sheet <- gs4_create("TranslationSheet")
  
  # Get the full sheet details
  sheet_details <- gs4_get(sheet)
  
  # Get the name of the first sheet (in case it's not "Sheet1")
  sheet_name <- sheet_details$sheets$name[1]
  
  # Write Korean text to the second row, first cell (A2)
  data <- data.frame(Text = korean_text)
  range_write(ss = sheet, data = data, sheet = sheet_name, range = "A2", col_names = FALSE)
  
  # Prepare the GOOGLETRANSLATE formula
  formula_data <- data.frame(Text = gs4_formula('=GOOGLETRANSLATE(A2, "ko", "en")'))
  
  # Write the formula into the second row, second cell (B2)
  range_write(ss = sheet, data = formula_data, sheet = sheet_name, range = "B2", col_names = FALSE)
  
  # Print the Google Sheet ID and URL
  sheet_id <- as_id(sheet)
  sheet_url <- paste0("https://docs.google.com/spreadsheets/d/", sheet_id)
  message("Please check the Google Sheet manually at this URL: ", sheet_url)
  
  # Pause the execution to allow manual inspection
  readline(prompt = "Press [Enter] key after you've checked the Google Sheet...")
  
  # Read the translated text from the Google Sheet
  translated_text <- read_sheet(sheet, range = "B2", col_names = FALSE)
  
  # Clean up by deleting the Google Sheet using googledrive package
  drive_trash(sheet_id)
  
  # Return the translated text
  return(translated_text[[1, 1]])
}

# Example usage of the function
translated_text <- translate_korean_to_english("안녕하세요. 만나서 반갑습니다.")
print(translated_text)
# ✔ Creating new Sheet: TranslationSheet.
# ✔ Editing TranslationSheet.
# ✔ Writing to sheet 시트1.
# ✔ Editing TranslationSheet.
# ✔ Writing to sheet 시트1.
# Please check the Google Sheet manually at this URL: https://docs.google.com/spreadsheets/d/1LX9N-mntUHWWSG4Pacvd9gHHmmlAPAW_nsttu0qQBfc
# [1] "hello. nice to meet you"
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
```{r writeRDS-EvalNoEchoNoMsgNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## @ write_rds( get(.objectname), file.path(.path4write, paste0(.objectname,".rds"))) ----  
.path4write = env1$path$.path4write
# MetaData$DataSetNames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
cat("    ========================================================================    \n")
for (.objectname in names(MetaData$DataSetNames)) {
    assign(.objectname, structure(get(.objectname), MetaData = MetaData))
    .path.file = paste0(.path4write,"/",.objectname,".rds",".xz")
    cat(.objectname, ' |> write_rds(',shQuote(.path.file),', compress = "xz", compression = 9) |> system.time()', "  \n", sep="")
    # system.time(write_rds( get(.objectname), .path.file, compress = "xz", compression = 9 ))
    cat('env1$f$f_path.size_files(.path4read = ',shQuote(.path4write),', regex4filename = ',shQuote(.objectname),")  \n", sep="")
    env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, Execute = FALSE)
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
}
# #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
# .path.filename.xlsx = paste0(.path4write,"/",.objectname,".xlsx")
# system.time(openxlsx2::write_xlsx(get(.objectname), file=.path.filename.xlsx, as_table=TRUE))
# if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(.path.filename.xlsx)
```
  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$CurrentSource.path.filename.pdf = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$CurrentSource.path.filename.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (Sys.info()["sysname"] == "Windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$CurrentSource.path.filename.ext)),', output_format = "pdf_document")  \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
        .path.file = env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}
        env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, Execute = FALSE)
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = .path.file, .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal$f_file_PDF.sumatra(.path.file))
    }
}
# env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path.file = env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, Execute = FALSE); cat('  env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = ',deparse(.path.file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal$f_file_PDF.sumatra(',deparse(.path.file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path.file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path.file = env1$path$CurrentSource.path.filename.html %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, Execute = FALSE); cat('  env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = ',deparse(.path.file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); cat('  env1$env.internal$f_URL.open_in_edge_app(',deparse(.path.file),')  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$CurrentSource.path.filename.nb.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
