---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in â‰ˆ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
if(.Platform$OS.type == "windows") Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=TRUE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
env1$info$options.width = options()$width; cat(options()$width, "  \n", sep="")
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
## env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

# @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
cat("> .tmp |> str(max.level = 1, give.attr = FALSE)", "  \n", sep="") 
.tmp |> str(max.level = 1, give.attr = FALSE)
cat("> env1 |> as.list() |> str(max.level = 2, give.attr = FALSE)", "  \n", sep="") 
env1 |> as.list() |> str(max.level = 2, give.attr = FALSE)
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
# .sourcename = "f_DataSetName.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  
```{r dfDIRsRecursive-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# *** Results hidden in 00env1 - see 01df_dirs_recursive.df_files ***
# #### env1\$env.internal\$f_path.df_dirs_recursive.df_files() ----  
# .sourcename = "f_path.df_dirs_recursive.df_files" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# env1$path$df_dirs_recursive.df_files = env1$env.internal$f_path.df_dirs_recursive.df_files(input_path=".", print.message=FALSE)
# env1$path$print_tree_path = env1$path$df_dirs_recursive.df_files |> dplyr::filter(path.level <= 5) |> 
#     dplyr::select(print_tree_path) |> unlist() |> paste(collapse="") 
# # env1$path$print_tree_path |> cat("  \n", sep="")
# env1$path$print_tree_path_files.codes = env1$path$df_dirs_recursive.df_files |> dplyr::filter(path.level <= 5) |> 
#     dplyr::select(print_tree_path_files.codes) |> unlist() |> paste(collapse="") 
# # env1$path$print_tree_path_files.codes |> cat("  \n", sep="")
# env1$path$print_tree_path_files.data = env1$path$df_dirs_recursive.df_files |> dplyr::filter(path.level <= 5) |> 
#     dplyr::select(print_tree_path_files.data) |> unlist() |> paste(collapse="") 
# env1$path$print_tree_path_files.data |> cat("  \n", sep="")
```
  
  
```{r sizeFiles-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# *** Results hidden in 00env1 - see 01df_dirs_recursive.df_files ***
# #### env1\$f_path.size_files() ----  
# .sourcename = "f_path.size_files" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# #### env1\$f_DataSetName.read.checkEntity() ----  
# .sourcename = "f_DataSetName.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# env1$f$f_path.size_files(.path4read = .path4read)
```
  
  
```{r open-envCustom-dfDirs-CodeBook, eval=TRUE, include=FALSE}
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
## env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# .GlobalEnv$.tmp = list() ====  
.listname = ".tmp"; if(!exists(.listname, envir=.GlobalEnv)) { assign(.listname, list(), envir=.GlobalEnv) }
for (SourceFileBaseName in rev(c("00env1", "01df_dirs_recursive.df_files", "10CodeBook"))) {
    .tmp$SourceFileName.ext = paste0(SourceFileBaseName,"-",basename(env1$path$path1),".Rmd")
    if(.tmp$SourceFileName.ext != basename(env1$path$CurrentSource.path.filename.ext)) {
        # .tmp$SourceFileName.ext %>% {paste0(env1$path$path1,"/",.)} |> file.edit(); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext))
        .tmp$SourceFileName.ext %>% {paste0(env1$path$path1,"/",.)} %>% {.[file.exists(.)]} |> file.edit(); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext))
    }
}
```
  
  
# @@ START) data example ----  
https://chatgpt.com/c/4f1ce650-0362-497e-882b-d48792bf6b9a
## \% |> extract_non_ascii_with_codes_df()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
extract_non_ascii_with_codes_df <- function(text) {
  # Use a regular expression to identify non-ASCII characters
  non_ascii <- gregexpr("[^\\x00-\\x7F]", text, perl = TRUE)
  
  # Extract the matched characters
  result <- regmatches(text, non_ascii)
  
  # Combine the extracted characters into a single vector
  extracted_chars <- unlist(result)
  
  # Convert characters to their Unicode code points
  unicode_codes <- sapply(extracted_chars, function(char) {
    sprintf("\\u%04X", utf8ToInt(char))
  })
  
  # Create a data frame
  df <- data.frame(Character = extracted_chars, Unicode_Code = unicode_codes, stringsAsFactors = FALSE)
  
  return(df)
}


```

## \$ text_with_rounded_numbers3 =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
suppressPackageStartupMessages(library(tidyverse))
# suppressPackageStartupMessages(library(survival))
text_with_rounded_numbers2 <- "â“žâ‘ â‘¡â‘¢â‘£â‘¤â‘¥â‘¦â‘§â‘¨"
text_with_rounded_numbers2 %>% dput
text_with_rounded_numbers2 %>% extract_non_ascii_with_codes_df()

text_with_rounded_numbers3 = "â“ª â‘  â‘¡ â‘¢ â‘£ â‘¤ â‘¥ â‘¦ â‘§ â‘¨ â‘© â‘ª â‘« â‘¬ â‘­ â‘® â‘¯ â‘° â‘± â‘² â‘³ ã‰‘ ã‰’ ã‰“ ã‰” ã‰• ã‰– ã‰— ã‰˜ ã‰™ ã‰š ã‰› ã‰œ ã‰ ã‰ž ã‰Ÿ ãŠ± ãŠ² ãŠ³ ãŠ´ ãŠµ ãŠ¶ ãŠ· ãŠ¸ ãŠ¹ ãŠº ãŠ» ãŠ¼ ãŠ½ ãŠ¾ ãŠ¿ ðŸ„‹ âž€ âž âž‚ âžƒ âž„ âž… âž† âž‡ âžˆ âž‰ â“¿ â¶ â· â¸ â¹ âº â» â¼ â½ â¾ â¿ â“« â“¬ â“­ â“® â“¯ â“° â“± â“² â“³ â“´ â“µ â“¶ â“· â“¸ â“¹ â“º â“» â“¼ â“½ â“¾ ã‰ˆ ã‰‰ ã‰Š ã‰‹ ã‰Œ ã‰ ã‰Ž ã‰ "
text_with_rounded_numbers3 %>% dput
text_with_rounded_numbers3 %>% extract_non_ascii_with_codes_df()
```
  
## \$ text_with_numbers_with_a_period =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
text_with_numbers_with_a_period = "ðŸ„€ â’ˆ â’‰ â’Š â’‹ â’Œ â’ â’Ž â’ â’ â’‘ â’’ â’“ â’” â’• â’– â’— â’˜ â’™ â’š â’›"
text_with_numbers_with_a_period %>% dput
text_with_numbers_with_a_period %>% extract_non_ascii_with_codes_df()
```


## \$ text_with_numbers_inside_parenthesis =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
text_with_numbers_inside_parenthesis = "â‘´ â‘µ â‘¶ â‘· â‘¸ â‘¹ â‘º â‘» â‘¼ â‘½ â‘¾ â‘¿ â’€ â’ â’‚ â’ƒ â’„ â’… â’† â’‡" 
text_with_numbers_inside_parenthesis %>% dput
text_with_numbers_inside_parenthesis %>% extract_non_ascii_with_codes_df()

```



  
  
# @@ START) dev ----  

## \% text_with_rounded_numbers |>  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ START) function ----  
https://chatgpt.com/c/ae6269b8-2256-435c-8881-c6c8962debee
https://chatgpt.com/c/e3de44e5-961f-4244-a2fd-94668801c04c
## \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# Function to convert Unicode rounded/circled numbers to regular numbers
convert_unicode_numbers <- function(text) {
  # Define the mapping of Unicode characters to regular numbers
  unicode_to_number <- c(
    # Parenthesized Numbers
    "\u2460" = "1", "\u2461" = "2", "\u2462" = "3", "\u2463" = "4", "\u2464" = "5",
    "\u2465" = "6", "\u2466" = "7", "\u2467" = "8", "\u2468" = "9", "\u2469" = "10",
    "\u246A" = "11", "\u246B" = "12", "\u246C" = "13", "\u246D" = "14", "\u246E" = "15",
    "\u246F" = "16", "\u2470" = "17", "\u2471" = "18", "\u2472" = "19", "\u2473" = "20",
    
    # Circled Numbers
    "\u24EA" = "0", "\u2460" = "1", "\u2461" = "2", "\u2462" = "3", "\u2463" = "4",
    "\u2464" = "5", "\u2465" = "6", "\u2466" = "7", "\u2467" = "8", "\u2468" = "9",
    "\u2469" = "10", "\u246A" = "11", "\u246B" = "12", "\u246C" = "13", "\u246D" = "14",
    "\u246E" = "15", "\u246F" = "16", "\u2470" = "17", "\u2471" = "18", "\u2472" = "19",
    "\u2473" = "20",
    
    # Negative Circled Numbers
    "\u2776" = "1", "\u2777" = "2", "\u2778" = "3", "\u2779" = "4", "\u277A" = "5",
    "\u277B" = "6", "\u277C" = "7", "\u277D" = "8", "\u277E" = "9", "\u277F" = "10",
    
    # Double Circled Numbers
    "\u24F5" = "1", "\u24F6" = "2", "\u24F7" = "3", "\u24F8" = "4", "\u24F9" = "5",
    "\u24FA" = "6", "\u24FB" = "7", "\u24FC" = "8", "\u24FD" = "9", "\u24FE" = "10",
    
    # Dingbat Circled Numbers
    "\u2780" = "1", "\u2781" = "2", "\u2782" = "3", "\u2783" = "4", "\u2784" = "5",
    "\u2785" = "6", "\u2786" = "7", "\u2787" = "8", "\u2788" = "9", "\u2789" = "10",
    
    # Fullwidth Numbers
    "\uFF10" = "0", "\uFF11" = "1", "\uFF12" = "2", "\uFF13" = "3", "\uFF14" = "4",
    "\uFF15" = "5", "\uFF16" = "6", "\uFF17" = "7", "\uFF18" = "8", "\uFF19" = "9"
  )
  
  # Convert each character in the text to its corresponding number if it matches the mapping
  replaced_text <- sapply(strsplit(text, NULL)[[1]], function(char) {
    if (char %in% names(unicode_to_number)) {
      unicode_to_number[[char]]
    } else {
      char
    }
  })
  
  # Combine the replaced characters back into a single string
  return(paste(replaced_text, collapse = ""))
}

# Example usage
text_with_rounded_numbers <- "â“žâ‘ â‘¡â‘¢â‘£"
text_with_rounded_numbers |> convert_unicode_numbers()
text_with_rounded_numbers2 |> convert_unicode_numbers()
text_with_rounded_numbers3 |> convert_unicode_numbers()

```
  
  
## \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
convert_unicode_numbers <- function(input_text) {
  # Define a named vector to map Unicode number variants to standard digits
  unicode_map <- c(
    # Superscript Numbers
    "\u2070" = "0", "\u00B9" = "1", "\u00B2" = "2", "\u00B3" = "3", "\u2074" = "4", 
    "\u2075" = "5", "\u2076" = "6", "\u2077" = "7", "\u2078" = "8", "\u2079" = "9",
    
    # Subscript Numbers
    "\u2080" = "0", "\u2081" = "1", "\u2082" = "2", "\u2083" = "3", "\u2084" = "4", 
    "\u2085" = "5", "\u2086" = "6", "\u2087" = "7", "\u2088" = "8", "\u2089" = "9",
    
    # Parenthesized Numbers
    "\u2460" = "1", "\u2461" = "2", "\u2462" = "3", "\u2463" = "4", "\u2464" = "5",
    "\u2465" = "6", "\u2466" = "7", "\u2467" = "8", "\u2468" = "9", "\u2469" = "10",
    "\u246A" = "11", "\u246B" = "12", "\u246C" = "13", "\u246D" = "14", "\u246E" = "15",
    "\u246F" = "16", "\u2470" = "17", "\u2471" = "18", "\u2472" = "19", "\u2473" = "20",
    
    # Circled Numbers
    "\u24EA" = "0", "\u2460" = "1", "\u2461" = "2", "\u2462" = "3", "\u2463" = "4",
    "\u2464" = "5", "\u2465" = "6", "\u2466" = "7", "\u2467" = "8", "\u2468" = "9",
    "\u2469" = "10", "\u246A" = "11", "\u246B" = "12", "\u246C" = "13", "\u246D" = "14",
    "\u246E" = "15", "\u246F" = "16", "\u2470" = "17", "\u2471" = "18", "\u2472" = "19",
    "\u2473" = "20",
    
    # Negative Circled Numbers
    "\u2776" = "1", "\u2777" = "2", "\u2778" = "3", "\u2779" = "4", "\u277A" = "5",
    "\u277B" = "6", "\u277C" = "7", "\u277D" = "8", "\u277E" = "9", "\u277F" = "10",
    
    # Double Circled Numbers
    "\u24F5" = "1", "\u24F6" = "2", "\u24F7" = "3", "\u24F8" = "4", "\u24F9" = "5",
    "\u24FA" = "6", "\u24FB" = "7", "\u24FC" = "8", "\u24FD" = "9", "\u24FE" = "10",
    
    # Dingbat Circled Numbers
    "\u2780" = "1", "\u2781" = "2", "\u2782" = "3", "\u2783" = "4", "\u2784" = "5",
    "\u2785" = "6", "\u2786" = "7", "\u2787" = "8", "\u2788" = "9", "\u2789" = "10",
    
    # Fullwidth Numbers
    "\uFF10" = "0", "\uFF11" = "1", "\uFF12" = "2", "\uFF13" = "3", "\uFF14" = "4",
    "\uFF15" = "5", "\uFF16" = "6", "\uFF17" = "7", "\uFF18" = "8", "\uFF19" = "9",

    # Additional Parenthesized Numbers
    "\u2474" = "1", "\u2475" = "2", "\u2476" = "3", "\u2477" = "4", "\u2478" = "5",
    "\u2479" = "6", "\u247A" = "7", "\u247B" = "8", "\u247C" = "9", "\u247D" = "10",
    "\u247E" = "11", "\u247F" = "12", "\u2480" = "13", "\u2481" = "14", "\u2482" = "15",
    "\u2483" = "16", "\u2484" = "17", "\u2485" = "18", "\u2486" = "19", "\u2487" = "20",

    # Additional Circled Numbers
    "\u24EB" = "0", "\u24EC" = "1", "\u24ED" = "2", "\u24EE" = "3", "\u24EF" = "4",
    "\u24F0" = "5", "\u24F1" = "6", "\u24F2" = "7", "\u24F3" = "8", "\u24F4" = "9",
    "\u24F5" = "10", "\u24F6" = "11", "\u24F7" = "12", "\u24F8" = "13", "\u24F9" = "14",
    "\u24FA" = "15", "\u24FB" = "16", "\u24FC" = "17", "\u24FD" = "18", "\u24FE" = "19",
    "\u24FF" = "20", "\u2770" = "21", "\u2771" = "22", "\u2772" = "23", "\u2773" = "24",
    "\u2774" = "25", "\u2775" = "26", "\u2776" = "27", "\u2777" = "28", "\u2778" = "29",
    "\u2779" = "30", "\u277A" = "31", "\u277B" = "32", "\u277C" = "33", "\u277D" = "34",
    "\u277E" = "35", "\u277F" = "36",

    # Additional Negative Circled Numbers
    "\u2770" = "1", "\u2771" = "2", "\u2772" = "3", "\u2773" = "4", "\u2774" = "5",
    "\u2775" = "6", "\u2776" = "7", "\u2777" = "8", "\u2778" = "9", "\u2779" = "10",
    
    # Additional Dingbat Circled Numbers
    "\u2780" = "1", "\u2781" = "2", "\u2782" = "3", "\u2783" = "4", "\u2784" = "5",
    "\u2785" = "6", "\u2786" = "7", "\u2787" = "8", "\u2788" = "9", "\u2789" = "10",

    # Other special forms and parenthesized/ circled numbers
    "\u24B6" = "A", "\u24B7" = "B", "\u24B8" = "C", "\u24B9" = "D", "\u24BA" = "E",
    "\u24BB" = "F", "\u24BC" = "G", "\u24BD" = "H", "\u24BE" = "I", "\u24BF" = "J",
    "\u24C0" = "K", "\u24C1" = "L", "\u24C2" = "M", "\u24C3" = "N", "\u24C4" = "O",
    "\u24C5" = "P", "\u24C6" = "Q", "\u24C7" = "R", "\u24C8" = "S", "\u24C9" = "T",
    "\u24CA" = "U", "\u24CB" = "V", "\u24CC" = "W", "\u24CD" = "X", "\u24CE" = "Y",
    "\u24CF" = "Z", "\u24D0" = "a", "\u24D1" = "b", "\u24D2" = "c", "\u24D3" = "d",
    "\u24D4" = "e", "\u24D5" = "f", "\u24D6" = "g", "\u24D7" = "h", "\u24D8" = "i",
    "\u24D9" = "j", "\u24DA" = "k", "\u24DB" = "l", "\u24DC" = "m", "\u24DD" = "n",
    "\u24DE" = "o", "\u24DF" = "p", "\u24E0" = "q", "\u24E1" = "r", "\u24E2" = "s",
    "\u24E3" = "t", "\u24E4" = "u", "\u24E5" = "v", "\u24E6" = "w", "\u24E7" = "x",
    "\u24E8" = "y", "\u24E9" = "z",

    # Enclosed Alphanumerics
    "\u2460" = "1", "\u2461" = "2", "\u2462" = "3", "\u2463" = "4", "\u2464" = "5",
    "\u2465" = "6", "\u2466" = "7", "\u2467" = "8", "\u2468" = "9", "\u2469" = "10",
    "\u246A" = "11", "\u246B" = "12", "\u246C" = "13", "\u246D" = "14", "\u246E" = "15",
    "\u246F" = "16", "\u2470" = "17", "\u2471" = "18", "\u2472" = "19", "\u2473" = "20",
    "\u2474" = "1", "\u2475" = "2", "\u2476" = "3", "\u2477" = "4", "\u2478" = "5",
    "\u2479" = "6", "\u247A" = "7", "\u247B" = "8", "\u247C" = "9", "\u247D" = "10",
    "\u247E" = "11", "\u247F" = "12", "\u2480" = "13", "\u2481" = "14", "\u2482" = "15",
    "\u2483" = "16", "\u2484" = "17", "\u2485" = "18", "\u2486" = "19", "\u2487" = "20",

    # Additional Enclosed Alphanumerics
    "\u24FF" = "0", "\u2776" = "1", "\u2777" = "2", "\u2778" = "3", "\u2779" = "4",
    "\u277A" = "5", "\u277B" = "6", "\u277C" = "7", "\u277D" = "8", "\u277E" = "9",
    "\u277F" = "10", "\u24EB" = "1", "\u24EC" = "2", "\u24ED" = "3", "\u24EE" = "4",
    "\u24EF" = "5", "\u24F0" = "6", "\u24F1" = "7", "\u24F2" = "8", "\u24F3" = "9",
    "\u24F4" = "10", "\u24F5" = "11", "\u24F6" = "12", "\u24F7" = "13", "\u24F8" = "14",
    "\u24F9" = "15", "\u24FA" = "16", "\u24FB" = "17", "\u24FC" = "18", "\u24FD" = "19",
    "\u24FE" = "20", "\u24FF" = "0"
  )
  
  # Convert the input text by replacing each Unicode variant with its corresponding digit
  converted_text <- chartr(paste(names(unicode_map), collapse = ""), paste(unicode_map, collapse = ""), input_text)
  
  return(converted_text)
}

# Example usage:
input_text <- "The unicode numbers are \u24EA\u2461\u2462 and \u2776\u2777\u2778."
convert_unicode_numbers(input_text)

text_with_rounded_numbers <- "â“žâ‘ â‘¡â‘¢â‘£"
text_with_rounded_numbers |> convert_unicode_numbers()
text_with_rounded_numbers2 |> convert_unicode_numbers()
text_with_rounded_numbers3 |> convert_unicode_numbers()
```
  
  
## \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
library(dplyr)

convert_unicode_numbers <- function(input_text) {
  # Define a named vector to map Unicode number variants to standard digits
  unicode_map <- c(
    # Superscript Numbers
    "\u2070" = "0", "\u00B9" = "1", "\u00B2" = "2", "\u00B3" = "3", "\u2074" = "4", 
    "\u2075" = "5", "\u2076" = "6", "\u2077" = "7", "\u2078" = "8", "\u2079" = "9",
    
    # Subscript Numbers
    "\u2080" = "0", "\u2081" = "1", "\u2082" = "2", "\u2083" = "3", "\u2084" = "4", 
    "\u2085" = "5", "\u2086" = "6", "\u2087" = "7", "\u2088" = "8", "\u2089" = "9",
    
    # Parenthesized Numbers
    "\u2460" = "1", "\u2461" = "2", "\u2462" = "3", "\u2463" = "4", "\u2464" = "5",
    "\u2465" = "6", "\u2466" = "7", "\u2467" = "8", "\u2468" = "9", "\u2469" = "10",
    "\u246A" = "11", "\u246B" = "12", "\u246C" = "13", "\u246D" = "14", "\u246E" = "15",
    "\u246F" = "16", "\u2470" = "17", "\u2471" = "18", "\u2472" = "19", "\u2473" = "20",
    
    # Circled Numbers
    "\u24EA" = "0", "\u2460" = "1", "\u2461" = "2", "\u2462" = "3", "\u2463" = "4",
    "\u2464" = "5", "\u2465" = "6", "\u2466" = "7", "\u2467" = "8", "\u2468" = "9",
    "\u2469" = "10", "\u246A" = "11", "\u246B" = "12", "\u246C" = "13", "\u246D" = "14",
    "\u246E" = "15", "\u246F" = "16", "\u2470" = "17", "\u2471" = "18", "\u2472" = "19",
    "\u2473" = "20",
    
    # Negative Circled Numbers
    "\u2776" = "1", "\u2777" = "2", "\u2778" = "3", "\u2779" = "4", "\u277A" = "5",
    "\u277B" = "6", "\u277C" = "7", "\u277D" = "8", "\u277E" = "9", "\u277F" = "10",
    
    # Double Circled Numbers
    "\u24F5" = "1", "\u24F6" = "2", "\u24F7" = "3", "\u24F8" = "4", "\u24F9" = "5",
    "\u24FA" = "6", "\u24FB" = "7", "\u24FC" = "8", "\u24FD" = "9", "\u24FE" = "10",
    
    # Dingbat Circled Numbers
    "\u2780" = "1", "\u2781" = "2", "\u2782" = "3", "\u2783" = "4", "\u2784" = "5",
    "\u2785" = "6", "\u2786" = "7", "\u2787" = "8", "\u2788" = "9", "\u2789" = "10",
    
    # Fullwidth Numbers
    "\uFF10" = "0", "\uFF11" = "1", "\uFF12" = "2", "\uFF13" = "3", "\uFF14" = "4",
    "\uFF15" = "5", "\uFF16" = "6", "\uFF17" = "7", "\uFF18" = "8", "\uFF19" = "9",
    
    # Enclosed Alphanumerics
    "\u24B6" = "A", "\u24B7" = "B", "\u24B8" = "C", "\u24B9" = "D", "\u24BA" = "E",
    "\u24BB" = "F", "\u24BC" = "G", "\u24BD" = "H", "\u24BE" = "I", "\u24BF" = "J",
    "\u24C0" = "K", "\u24C1" = "L", "\u24C2" = "M", "\u24C3" = "N", "\u24C4" = "O",
    "\u24C5" = "P", "\u24C6" = "Q", "\u24C7" = "R", "\u24C8" = "S", "\u24C9" = "T",
    "\u24CA" = "U", "\u24CB" = "V", "\u24CC" = "W", "\u24CD" = "X", "\u24CE" = "Y",
    "\u24CF" = "Z", "\u24D0" = "a", "\u24D1" = "b", "\u24D2" = "c", "\u24D3" = "d",
    "\u24D4" = "e", "\u24D5" = "f", "\u24D6" = "g", "\u24D7" = "h", "\u24D8" = "i",
    "\u24D9" = "j", "\u24DA" = "k", "\u24DB" = "l", "\u24DC" = "m", "\u24DD" = "n",
    "\u24DE" = "o", "\u24DF" = "p", "\u24E0" = "q", "\u24E1" = "r", "\u24E2" = "s",
    "\u24E3" = "t", "\u24E4" = "u", "\u24E5" = "v", "\u24E6" = "w", "\u24E7" = "x",
    "\u24E8" = "y", "\u24E9" = "z"
  )
  
  # Create a data frame from the unicode map
  unicode_df <- data.frame(
    Unicode_Character = names(unicode_map),
    Unicode_Code = sapply(names(unicode_map), function(x) sprintf("\\u%04X", utf8ToInt(x))),
    Converted_Alphanumeric = unicode_map,
    stringsAsFactors = FALSE
  )
  
  return(unicode_df)
}

convert_unicode_numbers() %>% str
convert_unicode_numbers() %>% as_tibble
```
  
  
## \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
library(dplyr)

convert_unicode_numbers <- function(input_text) {
  # Define a named vector to map Unicode number variants to standard digits
  unicode_map <- c(
    # Superscript Numbers
    "\u2070" = "0", "\u00B9" = "1", "\u00B2" = "2", "\u00B3" = "3", "\u2074" = "4", 
    "\u2075" = "5", "\u2076" = "6", "\u2077" = "7", "\u2078" = "8", "\u2079" = "9",
    
    # Subscript Numbers
    "\u2080" = "0", "\u2081" = "1", "\u2082" = "2", "\u2083" = "3", "\u2084" = "4", 
    "\u2085" = "5", "\u2086" = "6", "\u2087" = "7", "\u2088" = "8", "\u2089" = "9",
    
    # Parenthesized Numbers
    "\u2460" = "1", "\u2461" = "2", "\u2462" = "3", "\u2463" = "4", "\u2464" = "5",
    "\u2465" = "6", "\u2466" = "7", "\u2467" = "8", "\u2468" = "9", "\u2469" = "10",
    "\u246A" = "11", "\u246B" = "12", "\u246C" = "13", "\u246D" = "14", "\u246E" = "15",
    "\u246F" = "16", "\u2470" = "17", "\u2471" = "18", "\u2472" = "19", "\u2473" = "20",
    
    # Circled Numbers
    "\u24EA" = "0", "\u2460" = "1", "\u2461" = "2", "\u2462" = "3", "\u2463" = "4",
    "\u2464" = "5", "\u2465" = "6", "\u2466" = "7", "\u2467" = "8", "\u2468" = "9",
    "\u2469" = "10", "\u246A" = "11", "\u246B" = "12", "\u246C" = "13", "\u246D" = "14",
    "\u246E" = "15", "\u246F" = "16", "\u2470" = "17", "\u2471" = "18", "\u2472" = "19",
    "\u2473" = "20",
    
    # Negative Circled Numbers
    "\u2776" = "1", "\u2777" = "2", "\u2778" = "3", "\u2779" = "4", "\u277A" = "5",
    "\u277B" = "6", "\u277C" = "7", "\u277D" = "8", "\u277E" = "9", "\u277F" = "10",
    
    # Double Circled Numbers
    "\u24F5" = "1", "\u24F6" = "2", "\u24F7" = "3", "\u24F8" = "4", "\u24F9" = "5",
    "\u24FA" = "6", "\u24FB" = "7", "\u24FC" = "8", "\u24FD" = "9", "\u24FE" = "10",
    
    # Dingbat Circled Numbers
    "\u2780" = "1", "\u2781" = "2", "\u2782" = "3", "\u2783" = "4", "\u2784" = "5",
    "\u2785" = "6", "\u2786" = "7", "\u2787" = "8", "\u2788" = "9", "\u2789" = "10",
    
    # Fullwidth Numbers
    "\uFF10" = "0", "\uFF11" = "1", "\uFF12" = "2", "\uFF13" = "3", "\uFF14" = "4",
    "\uFF15" = "5", "\uFF16" = "6", "\uFF17" = "7", "\uFF18" = "8", "\uFF19" = "9",
    
    # Enclosed Alphanumerics
    "\u24B6" = "A", "\u24B7" = "B", "\u24B8" = "C", "\u24B9" = "D", "\u24BA" = "E",
    "\u24BB" = "F", "\u24BC" = "G", "\u24BD" = "H", "\u24BE" = "I", "\u24BF" = "J",
    "\u24C0" = "K", "\u24C1" = "L", "\u24C2" = "M", "\u24C3" = "N", "\u24C4" = "O",
    "\u24C5" = "P", "\u24C6" = "Q", "\u24C7" = "R", "\u24C8" = "S", "\u24C9" = "T",
    "\u24CA" = "U", "\u24CB" = "V", "\u24CC" = "W", "\u24CD" = "X", "\u24CE" = "Y",
    "\u24CF" = "Z", "\u24D0" = "a", "\u24D1" = "b", "\u24D2" = "c", "\u24D3" = "d",
    "\u24D4" = "e", "\u24D5" = "f", "\u24D6" = "g", "\u24D7" = "h", "\u24D8" = "i",
    "\u24D9" = "j", "\u24DA" = "k", "\u24DB" = "l", "\u24DC" = "m", "\u24DD" = "n",
    "\u24DE" = "o", "\u24DF" = "p", "\u24E0" = "q", "\u24E1" = "r", "\u24E2" = "s",
    "\u24E3" = "t", "\u24E4" = "u", "\u24E5" = "v", "\u24E6" = "w", "\u24E7" = "x",
    "\u24E8" = "y", "\u24E9" = "z"
  )
  
  # Find all unique Unicode characters in the input text
  unique_chars <- unique(strsplit(input_text, NULL)[[1]])
  
  # Filter to only those characters that have a conversion in the unicode_map
  converted_chars <- unique_chars[unique_chars %in% names(unicode_map)]
  
  # Create a data frame for the conversion
  conversion_df <- data.frame(
    Unicode_Character = converted_chars,
    Unicode_Code = sapply(converted_chars, function(x) sprintf("\\u%04X", utf8ToInt(x))),
    Converted_Alphanumeric = unicode_map[converted_chars],
    stringsAsFactors = FALSE
  )
  
  return(conversion_df)
}

# Example usage
input_text <- "The unicode numbers are â°Â¹Â²Â³â‚„â‚…â‚†â‚‡â‚ˆâ‚‰ and â“ªâ“«â“¬."
convert_unicode_numbers(input_text)
text_with_rounded_numbers2 |> convert_unicode_numbers()
text_with_rounded_numbers3 |> convert_unicode_numbers()
```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# @@ END ----  
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
```{r writeRDS-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# @ write_rds( get(.objectname), file.path(.path4write, paste0(.objectname,".rds"))) ----  
.path4write = env1$path$.path4write
# MetaData$DataSetNames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
for (.objectname in names(MetaData$DataSetNames)) {
    assign(.objectname, structure(get(.objectname), MetaData = MetaData))
    cat(.objectname, ' |> write_rds("',paste0(.path4write,"/",.objectname,".rds"),'", compress = "none") |> system.time()', "  \n", sep="")
    paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
}
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# .objectname = MetaData$DataSetNames %>% {names(.)[length(.)]}; .objectname %>% cat(deparse(substitute(.)), ' == "',.,'"  \n', sep="")
assign(.objectname, structure(get(.objectname), MetaData = MetaData))
cat(.objectname, ' |> write_rds("',paste0(.path4write,"/",.objectname,".rds"),'", compress = "none") |> system.time()', "  \n", sep="")
paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
# paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> system(intern=TRUE)
.objectname = paste0(.objectname,".NA",".rmAllNA",".fct")
cat(.objectname, ' |> write_rds("',paste0(.path4write,"/",.objectname,".rds"),'", compress = "none") |> system.time()', "  \n", sep="")
paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
# paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> system(intern=TRUE)
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# .objectname = MetaData$DataSetNames %>% {names(.)[length(.)]}; .objectname %>% cat(deparse(substitute(.)), ' == "',.,'"  \n', sep="")
assign(.objectname, structure(get(.objectname), MetaData = MetaData))
system.time(write_rds( get(.objectname), paste0(.objectname,".rds") ))
# system.time(write_rds( get(.objectname), file.path(.path4write, paste0(.objectname,".rds"))))
# # system.time(saveRDS( get(.objectname), file.path(.path4write, paste0(.objectname,".rds")), compress = "gzip" ))
# system.time(write_rds( get(.objectname), file.path(.path4write, paste0(.objectname,".rds")), compress = "gz", compression = 9 ))
# system.time(write_rds( get(.objectname), file.path(.path4write, paste0(.objectname, ".rds", ".xz")), compress = "xz", compression = 9 ))
# system.time(openxlsx::write.xlsx(get(.objectname), file=paste0(.objectname,".xlsx"), asTable=TRUE, withFilter=TRUE))
# if (.Platform$OS.type == "windows") openxlsx::openXL(paste0(.objectname, ".xlsx"))
env1$f$f_path.size_files(.path4read = .path4write, regex4filename  = .objectname)
paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
# paste0( "git add -f ",shQuote(paste0(.path4write,"/",.objectname,".rds", ".xz")) ) |> system(intern=TRUE)
```
  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (.Platform$OS.type == "windows") {
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$CurrentSource.path.filename.pdf = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all("[ ()]","-")
env1$path$CurrentSource.path.filename.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all("[ ()]","-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (.Platform$OS.type == "windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_format = "pdf_document") \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} |> rmarkdown::render(output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}, .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal$f_file_PDF.sumatra(env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}))
    }
}
# cat(' Sys.setenv(PARENT_RENDERING = "YES"); "',env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)},'" |> rmarkdown::render(output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")',"\n", 
#     ' if (.Platform$OS.type == "windows") { env1$env.internal$f_file_PDF.sumatra("',env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)},'") } else { browseURL("',env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)},'") }',"\n",
#     ' env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = "',env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)},'", .backup_to_path="-backup", timeFormat="%y%m%d", overwrite=TRUE)',"  \n", sep="")
# cat("    ________________________________________________________________________    \n")
env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% cat('  Sys.setenv(PARENT_RENDERING = "YES"); "',.,'" |> rmarkdown::render(output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep=""); env1$path$CurrentSource.path.filename.html %>% {paste0(env1$path$path1,"/",.)} %>% cat('  "',.,'" |> env1$env.internal$f_filename.ext.createBackup(.backup_to_path="-backup", timeFormat="%y%m%d", overwrite=TRUE)  \n', sep=""); env1$path$CurrentSource.path.filename.html %>% {paste0(env1$path$path1,"/",.)} %>% cat('  "',.,'" |> env1$env.internal$f_URL.open_in_edge_app()  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$CurrentSource.path.filename.nb.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (.Platform$OS.type == "windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
