---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  # - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)
```
  
  
```{r MetaData0-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}

```
  
  
# __________|------  
# @@ SOURCE) ----  
## @ .RelativeSubPath, .FileName.source.r = "f_df.Table1byExposure.xlsx" |> paste0(".source.r") ----  
```{r RUN-ALL-CHUNKS-ABOVE, echo=FALSE, results="hide", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
```


```{r .RelativeSubPath_FileName.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
options(DEVMODE = TRUE);  # isTRUE(getOption("DEVMODE"))
.RelativeSubPath = r"(Rdev/10_import_clean_datatype/16_categorical_factor)" |> str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
# if(.RelativeSubPath!="") .RelativeSubPath |> normalizePath(winslash="/",mustWork=TRUE) |> utils::browseURL() |> try()
.FileName.source.r = "f_df.add_BMI.5bins" |> paste0(".source.r")
### \% source( file.path(env1$path$source_base,.RelativeSubPath_FileName.source.r) )  ----  
env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = list(.RelativeSubPath, .FileName.source.r) %>% {.[nzchar(.)]} %>% c(fsep = "/") %>% {do.call(file.path, .)})
```
  
  
# __________|------  
# @@ DATA) mutate() ----  
```{r DATA-MUTATE-SYNC, eval=FALSE, include=FALSE}
paste0('### ->> Now synced to: "',dir(env1$path$path1, ".*\\.Rmd$", ignore.case = TRUE),'"  \n') |> cat(sep="")
```
## ->> Now synced to: ""  
## ()()()()()()()()()()------  
## ()()()()()()()()()()------  
## ->> PENDING synced to: ""  
## \$ df_NewDMv3.CensorEND.n88.select293.NR.recode.rds  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
  

# \$ assign( DSN, read_rds(paste0(.path4read,"/",DSN,".rds")) ) ====  
# .path4read = file.path(env1$path$path0,"Rproject_KNHIS.CohortGJ0910 NoHx")
# DSN = "CohortGJ0910.BaselineJKGJ2085NoHx.drop_na.MetS_NoMeds"
.path4read = paste0(env1$path$path1,"/data")
DSN = "df_NewDMv3.CensorEND.n88.select293.NR.recode.rds" |> str_replace("\\.rds$", "")
assign( DSN, read_rds(paste0(.path4read,"/",DSN,".rds")) )

# df_NewDMv3.CensorEND.n88.select293.NR.recode |> names() |> paste0(collapse = ", ") |> cat("  \n", sep="") ###### |> cat("  \n", sep="") ----

df_NewDMv3.CensorEND.n88.select293.NR.recode |> names() |> str_subset("^A0[01]") |> paste0(collapse = ",  \n") |> cat("  \n", sep="") ###### |> cat("  \n", sep="") ----

```


## \$ DS.DNR =  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# DS.DNR = DataSet.Date.NA.rmAllNA
DS.DNR = df_NewDMv3.CensorEND.n88.select293.NR.recode %>% 
    select(matches("HEIGHT|WEIGHT")) %>% 
    rownames_to_column() 
DS.DNR |> str(max.level = 2, give.attr = TRUE)
```


# __________|------  
## @ DATA) mutate(byVar = ) ----  
### # DATA) mutate() env1$f$f_df.add_BMI.5bins(varname_BMI)  
### ->> Now synced to: "35CodeBook_DS.recode-df_NewDMv3.CensorEND.select971.NR.lbl.fct.recode-deltaj.cut.51.Rmd"  
#### (STANDARD) \$ A01_BMI.4bins =  
##### \% f_df.add_BMI_calculated()  
##### \% f_df.add_BMI.5bins()  
```{r DATA-MUTATE-add_BMI, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### # DATA) mutate() env1$f$f_df.add_BMI.5bins(varname_BMI)  ----  
.RelativeSubPath = r"(Rdev/10_import_clean_datatype/16_categorical_factor)" |> str_replace_all("\\\\","/")  
.FileName.source.r = "f_df.add_BMI.5bins" |> paste0(".source.r")
env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = list(.RelativeSubPath, .FileName.source.r) %>% {.[nzchar(.)]} %>% c(fsep = "/") %>% {do.call(file.path, .)})

for(i in 1:7) {
    DS.DNR.lbl.fct =
        DS.DNR.lbl.fct %>% 
        env1$f$f_df.add_BMI_calculated(varname_Height = paste0("A0",i,"_","HEIGHT"), varname_Weight = paste0("A0",i,"_","WEIGHT"), varname_BMI = paste0("A0",i,"_","BMI")) %>% 
        env1$f$f_df.add_BMI.5bins(varname_BMI = paste0("A0",i,"_","BMI"))
}

DS.DNR.lbl.fct %>% select(matches("HEIGHT|WEIGHT|BMI")) |> str(max.level = 2, give.attr = TRUE)
```


#### (VOID) \$ A02_BMI_ge300.delta =  
##### \% f_df.add_VarNameT.deltaT0()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# ## :: f_df.add_VarNameT.deltaT0 =  ----  
# ## -> included in "f_df.t.tribble_construct.source.r"
# .RegEx2match = "BMI"
# i = 2
# DS.DNR %>% select(matches(.RegEx2match)) %>% select(matches(paste0("A0",i))) |> str(max.level = 2, give.attr = TRUE)
# DS.DNR %>% select(matches(.RegEx2match)) %>% select(matches(paste0("A0",i))) %>% select_if(function(x) is.numeric(x) | is.logical(x)) %>% names %>% str_replace(paste0("^A0",i,"_"),"") %>% dput
# 
# for (i in 2:7) {
#     # for (.VarName.suffix in c("BMI", "BMI_lt185", "BMI_ge185lt230", "BMI_ge230lt250", "BMI_ge185lt250", "BMI_ge250lt300", "BMI_ge230", "BMI_ge250", "BMI_ge300", "BMI_ge350", "BMI_ge400")) {
#     for (.VarName.suffix in c("BMI_lt185", "BMI_ge185lt230", "BMI_ge230lt250", "BMI_ge185lt250", "BMI_ge250lt300", "BMI_ge230", "BMI_ge250", "BMI_ge300", "BMI_ge350", "BMI_ge400")) {
#         print(paste0("A0",i,"_",.VarName.suffix,".delta"))
#         # DS.DNR = DataSet.Date.NA.rmAllNA
#         DS.DNR = 
#             DS.DNR %>% 
#             env1$f$f_df.add_VarNameT.deltaT0(paste0("A0",i-1,"_",.VarName.suffix), paste0("A0",i,"_",.VarName.suffix), prefix = "", suffix = ".delta")
#     }
# }
# DS.DNR %>% select(matches("BMI")) %>% select(matches("A02")) |> str(max.level = 2, give.attr = TRUE)
```
  

#### (CONTINUOUS) \$ A0{1+j}_BMI.deltaj, A0{1+j}_WEIGHT.deltaj =  
##### \% f_df.add_VarNameT.deltaT0()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
### # DATA) mutate() f_df.add_VarNameT.deltaT0(VarName0, VarNameT)  ----  
.RegEx2match = "BMI|WEIGHT"
i = 7
DS.DNR %>% select(matches(.RegEx2match)) %>% select(matches(paste0("A0",i))) |> str(max.level = 2, give.attr = TRUE)
DS.DNR %>% select(matches(.RegEx2match)) %>% select(matches(paste0("A0",i))) %>% select_if(function(x) is.numeric(x) | is.logical(x)) %>% names %>% str_replace(paste0("^A0",i,"_"),"") %>% dput


for (j in 1:(7-1)) {
    for (i in (1+j):7) {
        for (.VarName.suffix in c("BMI", "WEIGHT")) {
            print(paste0("A0",i,"_",.VarName.suffix,paste0(".delta",j)))
            # DS.DNR = DataSet.Date.NA.rmAllNA
            DS.DNR =
                DS.DNR |>
                env1$f$f_df.add_VarNameT.deltaT0(paste0("A0",i-j,"_",.VarName.suffix), paste0("A0",i,"_",.VarName.suffix), prefix = "", suffix = paste0(".delta",j))
        }
    }
}
DS.DNR %>% select(matches("BMI")) %>% select(matches("A07")) |> str(max.level = 2, give.attr = TRUE)
```


#### (VOID, CONTINUOUS) \$ A0{1+j}_BMI.pdeltaj =  
##### \% f_df.add_VarNameT.pdeltaT0()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
### # DATA) mutate() f_df.add_VarNameT.pdeltaT0(VarName0, VarNameT)  ----  
.RegEx2match = "BMI|WEIGHT"
i = 7
DS.DNR %>% select(matches(.RegEx2match)) %>% select(matches(paste0("A0",i))) |> str(max.level = 2, give.attr = TRUE)
DS.DNR %>% select(matches(.RegEx2match)) %>% select(matches(paste0("A0",i))) %>% select_if(function(x) is.numeric(x) | is.logical(x)) %>% names %>% str_replace(paste0("^A0",i,"_"),"") %>% dput


for (j in 1:(7-1)) {
    for (i in (1+j):7) {
        for (.VarName.suffix in c("BMI", "WEIGHT")) {
            print(paste0("A0",i,"_",.VarName.suffix,paste0(".pdelta",j)))
            # DS.DNR = DataSet.Date.NA.rmAllNA
            DS.DNR = 
                DS.DNR |> 
                env1$f$f_df.add_VarNameT.pdeltaT0(paste0("A0",i-j,"_",.VarName.suffix), paste0("A0",i,"_",.VarName.suffix), prefix = "", suffix = paste0(".pdelta",j))
        }
    }
}
DS.DNR %>% select(matches("BMI")) %>% select(matches("A07")) |> str(max.level = 2, give.attr = TRUE)
```


#### \%  print() A0{1+j}_BMI.deltaj, A0{1+j}_BMI.pdeltaj, A0{1+j}_WEIGHT.pdj 
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
for (j in 1:(7-1)) {
    for (i in (1+j):7) {
        # for (.VarName.suffix in c("BMI", "WEIGHT")) {
        #     print(paste0("A0",i,"_",.VarName.suffix,paste0(".delta",j)))
        #     # DS.DNR = DataSet.Date.NA.rmAllNA
        #     DS.DNR =
        #         DS.DNR %>%
        #         env1$f$f_df.add_VarNameT.deltaT0(paste0("A0",i-j,"_",.VarName.suffix), paste0("A0",i,"_",.VarName.suffix), prefix = "", suffix = paste0(".delta",j))
        # }
        .VarName.suffix = c("BMI", "WEIGHT")
        # DS.DNR[c(
        #     paste0("A0",i-j,"_",.VarName.suffix), 
        #     paste0("A0",i,"_",.VarName.suffix), 
        #     paste0("A0",i,"_",.VarName.suffix,".delta",j), 
        #     paste0("A0",i,"_",.VarName.suffix,".pdelta",j) 
        # )] |> head() |> as.data.frame() |> print()
        DS.DNR[c(
            paste0("A0",i-j,"_"), 
            paste0("A0",i,"_"), 
            paste0("A0",i,"_"), 
            paste0("A0",i,"_") 
        ) %>% outer(.VarName.suffix, paste0) %>% 
            paste0(c("", "", paste0(".delta",j), paste0(".pdelta",j)))
        ] |> head() |> as.data.frame() |> print()
    }
}
```
  
  
#### (VOID) \$ A0{1+j}_BMI.pdeltaj.5bins =  
##### \% f_df.add_RegExVars.kbins()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
## :: f_df.add_RegExVars.kbins =  ----  
## -> included in "f_df.t.tribble_construct.source.r"
# https://chatgpt.com/c/20d6b4e3-c198-49c2-90f5-c8959d55c1ed
# Rdev/10_import_clean_datatype/16_categorical_factor/f_df.add_RegExVars.kbins.dev.Rmd

# .regex_pattern_part = "\\.pdelta[1-6]"
# .breaks4cut = c(-Inf, -0.1, -0.05, 0.05, 0.1, Inf)
# .suffix = paste0(".",length(.breaks4cut)-1,"bins")
# DS.DNR <- DS.DNR |> env1$f$f_df.add_RegExVars.kbins(regex_pattern = paste0(.regex_pattern_part,"$"), breaks = .breaks4cut, suffix = .suffix)
# DS.DNR %>% select(matches(paste0(.regex_pattern_part,.suffix,"$"))) %>% summary

```
  
  
#### (REFERENCE) \$ A0{1+j}_BMI.pdeltaj.quintile =  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
## :: f_df.add_VarNameT.pdeltaT0 =  ----  
## -> included in "f_df.t.tribble_construct.source.r"
# .RegEx2match = "\\.pdelta[1-6]"
# 
# DS.DNR %>% select(matches(paste0(.RegEx2match,"$"))) %>% select(matches("A07")) |> str(max.level = 2, give.attr = TRUE)
# DS.DNR %>% select(matches(paste0(.RegEx2match,"$"))) %>% select(matches("A07")) %>% select_if(function(x) is.numeric(x) | is.logical(x)) %>% names %>% str_replace("^A07_","") %>% dput
# 
# DS.DNR <- DS.DNR %>%
#   # Adding .quintile variables as ordered factors with rounded labels
#   mutate(across(
#     .cols = matches(paste0(.RegEx2match, "$")), 
#     .fns = ~ {
#       # Compute quintile
#       quintile = ntile(., 5)
#       
#       # Define labels for the quintiles with rounded values
#       labels = c(
#         paste0("(", round(quantile(., 0, na.rm = TRUE), 3), ", ", round(quantile(., 0.2, na.rm = TRUE), 3), "]"),
#         paste0("(", round(quantile(., 0.2, na.rm = TRUE), 3), ", ", round(quantile(., 0.4, na.rm = TRUE), 3), "]"),
#         paste0("(", round(quantile(., 0.4, na.rm = TRUE), 3), ", ", round(quantile(., 0.6, na.rm = TRUE), 3), "]"),
#         paste0("(", round(quantile(., 0.6, na.rm = TRUE), 3), ", ", round(quantile(., 0.8, na.rm = TRUE), 3), "]"),
#         paste0("(", round(quantile(., 0.8, na.rm = TRUE), 3), ", ", round(quantile(., 1, na.rm = TRUE), 3), "]")
#       )
#       
#       # Convert to ordered factor
#       factor(quintile, levels = 1:5, labels = labels, ordered = TRUE)
#     },
#     .names = "{.col}.quintile"
#   ))
# DS.DNR %>% select(matches(paste0(.RegEx2match, "\\.quintile$"))) %>% summary
```
  

#### (REFERENCE) \$ A0{1+j}_BMI.pdeltaj.quintile =  
##### \% f_df.add_RegExVars.quintile_factor ====  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
## :: f_df.add_RegExVars.quintile_factor =  ----  
## -> included in "f_df.t.tribble_construct.source.r"
# https://chatgpt.com/c/516e86f6-008f-4d70-87e7-b99f3b5a7af5
# /github_tidystat/Rdev/10_import_clean_datatype/16_categorical_factor/f_df.add_RegExVars.quintile_factor.dev.Rmd
.tmp$objectname = "f_df.add_RegExVars.quintile_factor"
.tmp$object = function(data, regex_pattern) {
  data %>%
    mutate(across(
      .cols = matches(paste0(regex_pattern)), 
      .fns = ~ {
        # Compute quintile
        quintile <- ntile(., 5)
        
        # Define labels for the quintiles with rounded values
        labels <- c(
          paste0("(", round(quantile(., 0, na.rm = TRUE), 3), ", ", round(quantile(., 0.2, na.rm = TRUE), 3), "]"),
          paste0("(", round(quantile(., 0.2, na.rm = TRUE), 3), ", ", round(quantile(., 0.4, na.rm = TRUE), 3), "]"),
          paste0("(", round(quantile(., 0.4, na.rm = TRUE), 3), ", ", round(quantile(., 0.6, na.rm = TRUE), 3), "]"),
          paste0("(", round(quantile(., 0.6, na.rm = TRUE), 3), ", ", round(quantile(., 0.8, na.rm = TRUE), 3), "]"),
          paste0("(", round(quantile(., 0.8, na.rm = TRUE), 3), ", ", round(quantile(., 1, na.rm = TRUE), 3), "]")
        )
        
        # Convert to ordered factor
        factor(quintile, levels = 1:5, labels = labels, ordered = TRUE)
      },
      .names = "{.col}.quintile"
    ))
}
### |> f_function.load2env.internal(.tmp$objectname, env1_subenv_name) ----
.tmp$env1_subenv_name = "f"; env1$env.internal$f_function.load2env.internal(function_object = .tmp$object, function_name = .tmp$objectname, env1_subenv_name = .tmp$env1_subenv_name, show_packageStartupMessage = TRUE, RELOAD_FUNCTION = isTRUE(getOption("RELOAD_FUNCTION"))||isTRUE(getOption("DEVMODE")), runLoadedFunction = FALSE)

.RegEx2match = "\\.pdelta[1-6]"
DS.DNR <- env1$f$f_df.add_RegExVars.quintile_factor(DS.DNR, paste0(.RegEx2match,"$"))
DS.DNR %>% select(matches(paste0(.RegEx2match, "\\.quintile$"))) %>% summary

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
```{r createBACKUP, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%dT%H", overwrite=TRUE)
        # env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%dT%H", overwrite=TRUE)
    # }
}
```
  

```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_FileName.nb.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") {  try(  paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE),'"') |> shell(wait=FALSE)  )  }  # else { browseURL(env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE)) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileNameExt) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileName.nb.html) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
