---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
# https://ctan.org/pkg/cascadia-code  # caution: usepackage cascadia-code does not work in Rocker
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells -F (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels -F (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=TRUE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
if(!exists(".tmp", envir=.GlobalEnv)) { assign(".tmp", list(), envir=.GlobalEnv) }  
suppressPackageStartupMessages({for(.packagename in c("tidyverse","formatR")) {if(!require(.packagename,character.only=TRUE))install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}});cat("  \n", sep="")
if(!exists("env1", envir=.GlobalEnv)) 
    assign("env1", new.env(), envir=.GlobalEnv)
## env1\$path ----  
if(!"path" %in% names(.GlobalEnv$env1)) { .GlobalEnv$env1$path <- list() }  
.tmp$objectname = "source_base_local"; .tmp$object = ifelse(.Platform$OS.type == "windows", "D:/OneDrive/[][Rproject]/github_tidystat", "~/github_tidystat"); if(!.tmp$objectname %in% names(.GlobalEnv$env1$path)) {.GlobalEnv$env1$path[[.tmp$objectname]] = .tmp$object}  
.tmp$objectname = "source_base_github"; .tmp$object = "https://github.com/mkim0710/tidystat/raw/master"; if(!.tmp$objectname %in% names(.GlobalEnv$env1$path)) {.GlobalEnv$env1$path[[.tmp$objectname]] = .tmp$object}  
if(!"source_base" %in% names(.GlobalEnv$env1$path)) { env1$path$source_base = ifelse(dir.exists(env1$path$source_base_local), env1$path$source_base_local, env1$path$source_base_github) }  
## env1\$env.internal ----  
sourcename = "env1$env.internal" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
#### env1\$f_df.t.tribble_construct() ----  
sourcename = "f_df.t.tribble_construct" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "datapasta","openxlsx"))
# str(env1$info$info_software_versions)
```
env1\$info\$info_system_info\$machine_nodename = "15687d125320"  @Rocker  
env1\$info\$info_system_info\$machine_nodename = "application-12164735-deployment-22732286-l5pm"  @Posit.Cloud  
env1\$info\$info_system_info\$Sys.getlocale\$LC_COLLATE = "en_US.utf8"  
  
#@@ START ----  
## @ whoami ----  
Cf) Ctrl+Alt+Enter @ Rstudio  
  
## whoami  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'whoami' |> system(intern = TRUE) |> cat("  \n", sep="")
```
rstudio@Rocker  
r149319@SharedWorkspace@MKim0710@Posit.Cloud  
r2179046@SharedWorkspace@V@Posit.Cloud  
r2179052@SharedWorkspace@MHKim710@Posit.Cloud  
  
## echo \$PATH  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'echo $PATH' |> system(intern = TRUE) |> cat("  \n", sep="")
```
/usr/local/sbin:/usr/local/bin:/usr/sbin:/usr/bin:/sbin:/bin:/usr/local/texlive/bin/linux:/usr/lib/rstudio-server/bin/quarto/bin:/usr/lib/rstudio-server/bin/postback 
  
  
## @ fc-list ----  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
# On Unix-based systems, you can use the fc-list command to list available fonts. This command shows both system fonts and those managed by fontconfig (including some TeX Live-installed fonts).
'fc-list : family' |> system(intern = TRUE) |> sort() |> env1$f$f_vec.dput_line_by_line()
```
  
  
##@ find -type d texlive  ----  
## find / -type d -iname texlive  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find / -type d -iname texlive' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("/usr/local/texlive",  
  "/usr/local/texlive/tlpkg/TeXLive",  
  "/usr/local/texlive/texmf-dist/tex/context/texlive",  
  "/usr/local/texlive/texmf-dist/scripts/texlive",  
  "/opt/texlive")  
  
## find / -type d -iname texmf-dist  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find / -type d -iname texmf-dist' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("/usr/local/texlive/texmf-dist")  
  
##@ find -type d packages  ----  
### find /usr/share/texlive -type d -iname "fontspec"  
### find /usr/local/texlive -type d -iname "fontspec"  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive -type d -iname "fontspec"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'find /usr/local/texlive -type d -iname "fontspec"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("/usr/share/texlive/texmf-dist/tex/latex/fontspec")  
c("/usr/local/texlive/texmf-dist/tex/latex/fontspec")  
  
## find /usr/share/texlive/texmf-dist/tex/latex -maxdepth 1 -type d -printf  
## find /usr/local/texlive/texmf-dist/tex/latex -maxdepth 1 -type d -printf  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive/texmf-dist/tex/latex -maxdepth 1 -type d -printf "%f\n"' |> system(intern = TRUE) |> sort() |> dput()
'find /usr/local/texlive/texmf-dist/tex/latex -maxdepth 1 -type d -printf "%f\n"' |> system(intern = TRUE) |> sort() |> dput()
```
c("ae", "amsfonts", "amsmath", "atveryend", "auxhook", "base", 
"bookmark", "cascadia-code", "cjk", "cjk-ko", "epstopdf-pkg", 
"etoolbox", "euenc", "fancyvrb", "fira", "firstaid", "fonts-tlwg", 
"fontspec", "framed", "geometry", "graphics", "graphics-cfg", 
"graphics-def", "hycolor", "hyperref", "inconsolata", "koma-script", 
"kvoptions", "kvsetkeys", "l3backend", "l3kernel", "l3packages", 
"latex", "latexconfig", "letltxmacro", "listings", "lm", "mdwtools", 
"parskip", "refcount", "rerunfilecheck", "roboto", "stmaryrd", 
"tex-ini-files", "tikzfill", "tipa", "tools", "unicode-math", 
"url", "xcolor", "xkeyval", "xpatch", "zapfding")  
  
### find /usr/share/texlive -type d -iname "roboto"  
### find /usr/local/texlive -type d -iname "roboto"  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive -type d -iname "roboto"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'find /usr/local/texlive -type d -iname "roboto"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
  
  
### find /usr/share/texlive -type d -iname "cascadia*code"  
### find /usr/local/texlive -type d -iname "cascadia*code"  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive -type d -iname "cascadia*code"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'find /usr/local/texlive -type d -iname "cascadia*code"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
  
  
##@ find -type d fonts  ----  
## find /usr/share/texlive -type d -iname "font[s ]"  
## find /usr/local/texlive -type d -iname "font[s ]"  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive -type d -iname "font[s ]"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'find /usr/local/texlive -type d -iname "font[s ]"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("/usr/local/texlive/texmf-dist/tex/context/fonts",  
  "/usr/local/texlive/texmf-dist/metapost/context/fonts",  
  "/usr/local/texlive/texmf-dist/fonts")  
  
## ls -F /usr/share/texlive/texmf-dist/fonts  
## ls -F /usr/local/texlive/texmf-dist/fonts  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'ls -F /usr/share/texlive/texmf-dist/fonts' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'ls -F /usr/local/texlive/texmf-dist/fonts' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("afm/",  
  "cid/",  
  "cmap/",  
  "enc/",  
  "map/",  
  "misc/",  
  "opentype/",  
  "pk/",  
  "source/",
  "tfm/",
  "type1/",
  "vf/")
  
  
### ls -F /usr/share/texlive/texmf-dist/fonts/opentype  
### ls -F /usr/local/texlive/texmf-dist/fonts/opentype  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'ls -F /usr/share/texlive/texmf-dist/fonts/opentype' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'ls -F /usr/local/texlive/texmf-dist/fonts/opentype' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("google/",  
  "public/")  
  
#### ls -F /usr/share/texlive/texmf-dist/fonts/opentype/public  
#### ls -F /usr/local/texlive/texmf-dist/fonts/opentype/public  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'ls -F /usr/share/texlive/texmf-dist/fonts/opentype/public' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'ls -F /usr/local/texlive/texmf-dist/fonts/opentype/public' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("cascadia-code/",  
  "context-companion-fonts/",  
  "fira/",  
  "fonts-tlwg/",  
  "inconsolata/",  
  "lm/",  
  "lm-math/")  
  
#### ls -F /usr/share/texlive/texmf-dist/fonts/opentype/google  
#### ls -F /usr/local/texlive/texmf-dist/fonts/opentype/google  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'ls -F /usr/share/texlive/texmf-dist/fonts/opentype/google' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'ls -F /usr/local/texlive/texmf-dist/fonts/opentype/google' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("roboto/")  
  
##### ls -F /usr/share/texlive/texmf-dist/fonts/opentype/google/roboto  
##### ls -F /usr/local/texlive/texmf-dist/fonts/opentype/google/roboto  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'ls -F /usr/share/texlive/texmf-dist/fonts/opentype/google/roboto' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'ls -F /usr/local/texlive/texmf-dist/fonts/opentype/google/roboto' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("Roboto-BlackItalic.otf",  
  "Roboto-Black.otf",  
  "Roboto-BoldItalic.otf",  
  "Roboto-Bold.otf",  
  "RobotoCondensed-BoldItalic.otf",  
  "RobotoCondensed-Bold.otf",  
  "RobotoCondensed-Italic.otf",  
  "RobotoCondensed-LightItalic.otf",  
  "RobotoCondensed-Light.otf",
  "RobotoCondensed-Regular.otf",
  "Roboto-Italic.otf",
  "Roboto-LightItalic.otf",
  "Roboto-Light.otf",
  "Roboto-MediumItalic.otf",
  "Roboto-Medium.otf",
  "RobotoMono-BoldItalic.otf",
  "RobotoMono-Bold.otf",
  "RobotoMono-Italic.otf",
  "RobotoMono-LightItalic.otf",
  "RobotoMono-Light.otf",
  "RobotoMono-MediumItalic.otf",
  "RobotoMono-Medium.otf",
  "RobotoMono-Regular.otf",
  "RobotoMono-ThinItalic.otf",
  "RobotoMono-Thin.otf",
  "Roboto-Regular.otf",
  "RobotoSerif-BlackItalic.otf",
  "RobotoSerif-Black.otf",
  "RobotoSerif-BoldItalic.otf",
  "RobotoSerif-Bold.otf",
  "RobotoSerif_Condensed-BlackItalic.otf",
  "RobotoSerif_Condensed-Black.otf",
  "RobotoSerif_Condensed-BoldItalic.otf",
  "RobotoSerif_Condensed-Bold.otf",
  "RobotoSerif_Condensed-ExtraBoldItalic.otf",
  "RobotoSerif_Condensed-ExtraBold.otf",
  "RobotoSerif_Condensed-ExtraLightItalic.otf",
  "RobotoSerif_Condensed-ExtraLight.otf",
  "RobotoSerif_Condensed-Italic.otf",
  "RobotoSerif_Condensed-LightItalic.otf",
  "RobotoSerif_Condensed-Light.otf",
  "RobotoSerif_Condensed-MediumItalic.otf",
  "RobotoSerif_Condensed-Medium.otf",
  "RobotoSerif_Condensed-Regular.otf",
  "RobotoSerif_Condensed-SemiBoldItalic.otf",
  "RobotoSerif_Condensed-SemiBold.otf",
  "RobotoSerif_Condensed-ThinItalic.otf",
  "RobotoSerif_Condensed-Thin.otf",
  "RobotoSerif-ExtraBoldItalic.otf",
  "RobotoSerif-ExtraBold.otf",
  "RobotoSerif-ExtraLightItalic.otf",
  "RobotoSerif-ExtraLight.otf",
  "RobotoSerif-Italic.otf",
  "RobotoSerif-LightItalic.otf",
  "RobotoSerif-Light.otf",
  "RobotoSerif-MediumItalic.otf",
  "RobotoSerif-Medium.otf",
  "RobotoSerif-Regular.otf",
  "RobotoSerif-SemiBoldItalic.otf",
  "RobotoSerif-SemiBold.otf",
  "RobotoSerif-ThinItalic.otf",
  "RobotoSerif-Thin.otf",
  "RobotoSlab-Bold.otf",
  "RobotoSlab-Light.otf",
  "RobotoSlab-Regular.otf",
  "RobotoSlab-Thin.otf",
  "Roboto-ThinItalic.otf",
  "Roboto-Thin.otf")
  
  
### ls -F /usr/share/texlive/texmf-dist/fonts/truetype  
### ls -F /usr/local/texlive/texmf-dist/fonts/truetype  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'ls -F /usr/share/texlive/texmf-dist/fonts/truetype' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'ls -F /usr/local/texlive/texmf-dist/fonts/truetype' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("")  
  
#### ls -F /usr/share/texlive/texmf-dist/fonts/truetype/public  
#### ls -F /usr/local/texlive/texmf-dist/fonts/truetype/public  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'ls -F /usr/share/texlive/texmf-dist/fonts/truetype/public' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'ls -F /usr/local/texlive/texmf-dist/fonts/truetype/public' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
  
  
#### ls -F /usr/share/texlive/texmf-dist/fonts/truetype/google  
#### ls -F /usr/local/texlive/texmf-dist/fonts/truetype/google  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'ls -F /usr/share/texlive/texmf-dist/fonts/truetype/google' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'ls -F /usr/local/texlive/texmf-dist/fonts/truetype/google' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
  
  
##### ls -F /usr/share/texlive/texmf-dist/fonts/truetype/google/roboto  
##### ls -F /usr/local/texlive/texmf-dist/fonts/truetype/google/roboto  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'ls -F /usr/share/texlive/texmf-dist/fonts/truetype/google/roboto' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'ls -F /usr/local/texlive/texmf-dist/fonts/truetype/google/roboto' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
  
  
##@ find -type d/f fontname  ----  
### find /usr/share/texlive -type d -iname "*roboto*"  
### find /usr/local/texlive -type d -iname "*roboto*"  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive -type d -iname "*roboto*"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'find /usr/local/texlive -type d -iname "*roboto*"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("/usr/local/texlive/texmf-dist/tex/latex/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/enc/dvips/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/map/dvips/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/type1/google/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/vf/google/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/tfm/google/roboto")  
  
#### find /usr/share/texlive -type f -iname "*roboto*"  
#### find /usr/local/texlive -type f -iname "*roboto*"  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive -type d -iname "*roboto*"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'find /usr/local/texlive -type d -iname "*roboto*"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("/usr/local/texlive/texmf-dist/tex/latex/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/enc/dvips/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/map/dvips/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/type1/google/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/vf/google/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto",  
  "/usr/local/texlive/texmf-dist/fonts/tfm/google/roboto")  
  
##### find /usr/share/texlive -type f -iname "*roboto*mono*.?tf"  
##### find /usr/local/texlive -type f -iname "*roboto*mono*.?tf"  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive -type f -iname "*roboto*mono*.?tf"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'find /usr/local/texlive -type f -iname "*roboto*mono*.?tf"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto/RobotoMono-Light.otf",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto/RobotoMono-Medium.otf",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto/RobotoMono-MediumItalic.otf",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto/RobotoMono-Bold.otf",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto/RobotoMono-ThinItalic.otf",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto/RobotoMono-Regular.otf",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto/RobotoMono-BoldItalic.otf",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto/RobotoMono-Thin.otf",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto/RobotoMono-Italic.otf",
  "/usr/local/texlive/texmf-dist/fonts/opentype/google/roboto/RobotoMono-LightItalic.otf")
  
  
### find /usr/share/texlive -type d -iname "*inconsolata*"  
### find /usr/local/texlive -type d -iname "*inconsolata*"  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive -type d -iname "*inconsolata*"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'find /usr/local/texlive -type d -iname "*inconsolata*"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
  
  
#### find /usr/share/texlive -type f -iname "*inconsolata*.?tf"  
#### find /usr/local/texlive -type f -iname "*inconsolata*.?tf"  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive -type f -iname "*inconsolata*.?tf"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'find /usr/local/texlive -type f -iname "*inconsolata*.?tf"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
c("/usr/local/texlive/texmf-dist/fonts/opentype/public/inconsolata/Inconsolatazi4-Bold.otf",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/public/inconsolata/InconsolataN-Bold.otf",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/public/inconsolata/InconsolataN-Regular.otf",  
  "/usr/local/texlive/texmf-dist/fonts/opentype/public/inconsolata/Inconsolatazi4-Regular.otf")  
  
### find /usr/share/texlive -type d -iname "cascadia*code"  
### find /usr/local/texlive -type d -iname "cascadia*code"  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive -type d -iname "cascadia*code"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'find /usr/local/texlive -type d -iname "cascadia*code"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
  
  
#### find /usr/share/texlive -type f -iname "*cascadia*.?tf"  
#### find /usr/local/texlive -type f -iname "*cascadia*.?tf"  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
'find /usr/share/texlive -type f -iname "*cascadia*.?tf"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
'find /usr/local/texlive -type f -iname "*cascadia*.?tf"' |> system(intern = TRUE) |> env1$f$f_vec.dput_line_by_line()
```
  
  
#@@ END ----  
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#@@ END ----  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# /usr/lib/rstudio-server/bin/quarto/bin/tools/pandoc +RTS -K512m -RTS system.find_filename.texlive@Rocker.knit.md --to latex --from markdown+autolink_bare_uris+tex_math_single_backslash --output system.find_filename.texlive@Rocker.tex --lua-filter /usr/local/lib/R/site-library/rmarkdown/rmarkdown/lua/pagebreak.lua --lua-filter /usr/local/lib/R/site-library/rmarkdown/rmarkdown/lua/latex-div.lua --embed-resources --standalone --table-of-contents --toc-depth 6 --highlight-style tango --pdf-engine xelatex --variable graphics --include-in-header /tmp/RtmpzAV6ir/rmarkdown-str51c28523670.html 
# find: ‘/usr/share/texlive’: No such file or directory
# find: ‘/usr/share/texlive’: No such file or directory
# output file: system.find_filename.texlive@Rocker.knit.md
# 
# tlmgr: package repository https://www.texlive.info/tlnet-archive/2024/04/23/tlnet (not verified: gpg unavailable)
# [1/6, ??:??/??:??] install: euenc [4k]
# [2/6, 00:01/15:15] install: fontspec [27k]
# [3/6, 00:02/03:17] install: l3packages [20k]
# [4/6, 00:04/03:56] install: tipa [2809k]
# [5/6, 00:11/00:11] install: unicode-math [42k]
# [6/6, 00:12/00:12] install: xunicode [26k]
# running mktexlsr ...
# done running mktexlsr.
# running updmap-sys ...
# done running updmap-sys.
# tlmgr: package log updated: /opt/texlive/texmf-var/web2c/tlmgr.log
# tlmgr: command log updated: /opt/texlive/texmf-var/web2c/tlmgr-commands.log
# tlmgr: package repository https://www.texlive.info/tlnet-archive/2024/04/23/tlnet (not verified: gpg unavailable)
# [1/1, ??:??/??:??] install: roboto [24761k]
# running mktexlsr ...
# done running mktexlsr.
# running updmap-sys ...
# done running updmap-sys.
# tlmgr: package log updated: /opt/texlive/texmf-var/web2c/tlmgr.log
# tlmgr: command log updated: /opt/texlive/texmf-var/web2c/tlmgr-commands.log
# 
# Output created: system.find_filename.texlive@Rocker.pdf
```
  
  
