---
##HHHHHHHHHHHHHHHHHH BEGINNING OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##  
# TABLE OF CONTENTS (level 1) ----  
# @@ REFERENCES)                                                            #L247
# @@ DATA) example                                                          #L256
# @@ START) dev                                                             #L276
# @@ SOURCE)                                                                #L311
# @@ START) function                                                        #L353
# @@ MetaData) Read & Check                                                 #L402
# @@ DATA) Read & Check                                                     #L472
# @@ ANALYSIS) (Breif) byVar =                                              #L638
# @@ DATA) mutate()                                                         #L644
# @@ DATA) filter() -> New DS                                               #L675
# @@ DATA) select(matches(VarName.suffix.regex))                            #L708
# @@ ANALYSIS) byVar =                                                      #L722
##HHHHHHHHHHHHHHHHHHHH THE END OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##   
##HHHHHHHHHHHHHHHHHH BEGINNING OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##  
# TABLE OF CONTENTS (level 1) ----  
# @@ REFERENCES)                                                            # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L247
# @@ DATA) example                                                          # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L256
# @@ START) dev                                                             # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L276
# @@ SOURCE)                                                                # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L311
# @@ START) function                                                        # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L353
# @@ MetaData) Read & Check                                                 # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L402
# @@ DATA) Read & Check                                                     # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L472
# @@ ANALYSIS) (Breif) byVar =                                              # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L638
# @@ DATA) mutate()                                                         # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L644
# @@ DATA) filter() -> New DS                                               # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L675
# @@ DATA) select(matches(VarName.suffix.regex))                            # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L708
# @@ ANALYSIS) byVar =                                                      # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L722
##HHHHHHHHHHHHHHHHHHHH THE END OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##   
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/  
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  # - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd())  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_filename_ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$LastSourceEditorContext.path_filename_ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(getwd()|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
# env1$path$LastSourceEditorContext.path_filename_ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_filename_ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) Not using a relative path~!
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .filename.source.r = "f_DSN.Search.read.checkEntity" |> paste0(".source.r"); .relative.subpath=r"()"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.relative.subpath_filename.source.r = paste0(.relative.subpath,ifelse(.relative.subpath=="","","/"),.filename.source.r))
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  
```
  
  
# __________|------  
# @@ REFERENCES) ----  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ DATA) example ----  
### :: vec1 = 1:6
### :: vec2 = 1:3 * 2
### :: vec3 = 1:2 * 3
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
vec1 = 1:6
vec2 = 1:3 * 2
vec3 = 1:2 * 3
f_vec1_vec2.setdiff_list(vec1, vec2)
f_vec1_vec2.setdiff_list(vec1, vec2, output_as_data_frame = TRUE)
# > f_vec1_vec2.setdiff_list(vec1, vec2)
# List of 7
#  $ vec1.character: chr [1:5] "1" "2" "3" "4" ...
#  $ vec2.character: chr [1:3] "2" "4" "6"
#  $ union         : chr [1:6] "1" "2" "3" "4" ...
#  $ intersect     : chr [1:2] "2" "4"
#  $ setdiff_1_2   : chr [1:3] "1" "3" "5"
#  $ setdiff_2_1   : chr "6"
#  $ identical     : chr [1:2] "Lengths (5, 3) differ (string compare on first 3)" "3 string mismatches"
# > f_vec1_vec2.setdiff_list(vec1, vec2, output_as_data_frame = TRUE)
# 'data.frame':	6 obs. of  6 variables:
#  $ union      : chr  "1" "2" "3" "4" ...
#  $ vec1       : logi  TRUE TRUE TRUE TRUE TRUE FALSE
#  $ vec2       : logi  FALSE TRUE FALSE TRUE FALSE TRUE
#  $ intersect  : logi  FALSE TRUE FALSE TRUE FALSE FALSE
#  $ setdiff_1_2: logi  TRUE FALSE TRUE FALSE TRUE FALSE
#  $ setdiff_2_1: logi  FALSE FALSE FALSE FALSE FALSE TRUE
#     union              vec1            vec2         intersect       setdiff_1_2     setdiff_2_1    
#  Length:6           Mode :logical   Mode :logical   Mode :logical   Mode :logical   Mode :logical  
#  Class :character   FALSE:1         FALSE:3         FALSE:4         FALSE:3         FALSE:5        
#  Mode  :character   TRUE :5         TRUE :3         TRUE :2         TRUE :3         TRUE :1        
#   union  vec1  vec2 intersect setdiff_1_2 setdiff_2_1
# 1     1  TRUE FALSE     FALSE        TRUE       FALSE
# 2     2  TRUE  TRUE      TRUE       FALSE       FALSE
# 3     3  TRUE FALSE     FALSE        TRUE       FALSE
# 4     4  TRUE  TRUE      TRUE       FALSE       FALSE
# 5     5  TRUE FALSE     FALSE        TRUE       FALSE
# 6     6 FALSE  TRUE     FALSE       FALSE        TRUE
```
  
  
# __________|------  
# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ SOURCE) ----  
```{r RUN-ALL-CHUNKS-ABOVE, echo=FALSE, results="hide", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
```


```{r .subpath_filename.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
options(DEVMODE = TRUE);  # isTRUE(getOption("DEVMODE"))
# .subpath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") {.subpath = env1$path$LastSourceEditorContext.path_filename_ext |> dirname(); ".subpath" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
# if(.subpath!="") utils::browseURL(normalizePath(.subpath))
# .filename.source.r = "default.template" |> paste0(".source.r")
if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") {.sourcename_root = env1$path$LastSourceEditorContext.path_filename_ext |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),""); ".sourcename_root" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.relative.subpath = .relative.subpath
if(!exists(".sourcename_root") && exists(".filename.source.r")) .sourcename_root = .filename.source.r |> str_replace("\\.source\\.r$", "")
.filename.source.r = .sourcename_root |> paste0(".source.r")
env1$path$.sourcename_root = .sourcename_root
env1$path$.relative.subpath_filename.dev.r = paste0(.relative.subpath,ifelse(.relative.subpath=="","","/"),.sourcename_root,".dev.r")
env1$path$.relative.subpath_filename.dev.Rmd = paste0(.relative.subpath,ifelse(.relative.subpath=="","","/"),.sourcename_root,".dev.Rmd")
env1$path$.relative.subpath_filename.source.r = paste0(.relative.subpath,ifelse(.relative.subpath=="","","/"),.sourcename_root,".source.r")
cat("# ",'.sourcename_root = "',.sourcename_root,'"  \n',
    "#### ",env1$path$.relative.subpath_filename.dev.r, "----  \n",
    "#### ",env1$path$.relative.subpath_filename.dev.Rmd, "----  \n",
    "#### ",env1$path$.relative.subpath_filename.source.r, "----  \n",
    '# # source(paste0(env1$path$source_base,"/","',env1$path$.relative.subpath_filename.source.r,'"))', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.relative.subpath_filename.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.relative.subpath_filename.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.relative.subpath_filename.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.relative.subpath_filename.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.relative.subpath_filename.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.relative.subpath_filename.source.r,'")', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.relative.subpath_filename.dev.r,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.relative.subpath_filename.dev.Rmd,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.relative.subpath_filename.source.r,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext));', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.subpath_filename.source.r) ) ----  
# env1$f$f_sourcePath.execute_if_not_sourced(.relative.subpath_filename.source.r = paste0(.relative.subpath,ifelse(.relative.subpath=="","","/"),.filename.source.r))
```
  
  
# __________|------  
# @@ START) function o1p ----  

## https://chatgpt.com/g/g-p-6774e267f75c8191bd6b9efd78dc6392-o1-pro/c/67780ea5-dfb8-800e-a3c9-0d73059a1dd4
## :: f_vecs.setdiff_df = function() -dev -pending  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_vecs.setdiff_df <- function(..., VERBOSE = getoption("verbose")) {
    # # Capture all vectors in a list
    # if(VERBOSE) {  cat("> str(...)  \n"); str(...)  }
    # if(VERBOSE) cat("length(...) == ", length(...), "  \n", sep="")
    # if(VERBOSE) cat("is.list(...) == ", is.list(...), "  \n", sep="")
    # 
    # # vec_list = ifelse(length(...) == 1, ..., list(...))
    # vec_list = ifelse(is.list(...), ..., list(...))
    # if(VERBOSE) {  cat("> str(vec_list)  \n"); str(vec_list)  }
    
    vec_list = list(...)
    
    # If any input is unnamed, assign default names (e.g., "vec1", "vec2", etc.)
    vec_names <- names(vec_list)
    if (is.null(vec_names) || any(vec_names == "")) {
        vec_names <- paste0("vec", seq_along(vec_list))
        names(vec_list) <- vec_names
    }
    
    # Convert all elements of the list to character
    vec_list_char <- lapply(vec_list, as.character)
    
    # Compute the union of all vector elements
    union_all <- sort(unique(unlist(vec_list_char)))
    
    # Initialize the output data frame
    df_out <- data.frame(rowname = union_all, stringsAsFactors = FALSE)
    
    # For each vector, create a logical indicator column of membership
    for (nm in names(vec_list_char)) {
        df_out[[nm]] <- df_out$rowname %in% vec_list_char[[nm]]
    }
    
    return(df_out)
}


# Example lists of ICD-10 codes
DiabetesCodes    = c("E10", "E11", "E13")
HypertensionCodes = c("I10", "I11")
RespiratoryCodes  = c("J45", "J20", "E11")
icdList_vec <- list(
  DiabetesCodes    = c("E10", "E11", "E13"),
  HypertensionCodes = c("I10", "I11"),
  RespiratoryCodes  = c("J45", "J20", "E11")
)
f_vecs.setdiff_df(DiabetesCodes, HypertensionCodes, RespiratoryCodes, VERBOSE = TRUE)
# icdList_vec %>% f_vecs.setdiff_df(VERBOSE = TRUE)
```
  
  
# __________|------  
# @@ START) function o1p ----  

## https://chatgpt.com/g/g-p-6774e267f75c8191bd6b9efd78dc6392-o1-pro/c/67780ea5-dfb8-800e-a3c9-0d73059a1dd4
## :: f_listVec.setdiff_df = function() -dev -pending  
### \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
f_list_vecs.union_df <- function(input_list_vecs, print_str = TRUE, VERBOSE = isTRUE(getOption("verbose"))) {
    # 1. If verbose, print the function call
    if (VERBOSE) {
        cat("[DEBUG] Entering f_list_vecs.union_df()\n")
    }

    # 2. Check that the input is indeed a list
    if (!is.list(input_list_vecs)) {
        stop("The input must be a list of vectors.")
    }
    
    # 3. Handle unnamed vectors by assigning default names only where needed
    originalNames_vec <- names(input_list_vecs)
    
    # If no names exist at all, create them:
    if (is.null(originalNames_vec)) {
        defaultNames_vec <- paste0("vec", seq_along(input_list_vecs))
        names(input_list_vecs) <- defaultNames_vec
        if (VERBOSE) {
            cat("[DEBUG] All vectors were unnamed. Assigned default names:\n")
            print(defaultNames_vec)
        }
    } else {
        # If some are named and others are empty, only replace the empty ones
        for (i in seq_along(originalNames_vec)) {
            if (is.na(originalNames_vec[i]) || originalNames_vec[i] == "") {
                originalNames_vec[i] <- paste0("Vec", i)
            }
        }
        names(input_list_vecs) <- originalNames_vec
        if (VERBOSE) {
            cat("[DEBUG] Some vectors were unnamed. Assigned default names for those only:\n")
            print(originalNames_vec)
        }
    }
    
    # 4. Convert all vectors to character
    input_list_vecs.as_character <- purrr::map(
        .x = input_list_vecs,
        .f = function(single_vec) {
            as.character(single_vec)
        }
    )

    # 5. Compute the union of all elements (sorted, unique)
    union_vec <- sort(unique(unlist(input_list_vecs.as_character)))
    if (VERBOSE) {
        cat("[DEBUG] union_vec (all unique elements):\n")
        print(union_vec)
    }

    # 6. Initialize output tibble
    output_df <- tibble::tibble(UNION = union_vec)

    # 7. Create logical indicator columns
    for (vec_name in names(input_list_vecs.as_character)) {
        membership_vec <- output_df[["UNION"]] %in% input_list_vecs.as_character[[vec_name]]
        output_df[[vec_name]] <- membership_vec
        if (VERBOSE) {
            cat("[DEBUG] Processed membership for:", vec_name, "\n")
        }
    }

    # 8. Print final output if requested
    if (print_str) {str(output_df); print(summary(output_df))}

    # 9. Return the tibble
    return(output_df)
}


# Example lists of ICD-10 codes
icdList_vec <- list(
  DiabetesCodes    = c("E10", "E11", "E13"),
  HypertensionCodes = c("I10", "I11"),
  RespiratoryCodes  = c("J45", "J20", "E11"), 
  c("A01", "A02", "A03")
)

# Call the function
icdList_vec %>% f_list_vecs.union_df(VERBOSE = TRUE)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ START) function ----  
## :: function_name = function() -dev -pending  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## ->> Now included in f_df.t.tribble_construct.source.r ----

##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## :: f_list_vecs.union_df = function() ====
## Rdev/00_base_program/009_base_computation/f_list_vecs.union_df.dev.Rmd
.tmp$env1_subenv_name = "f"
.tmp$objectname = "f_list_vecs.union_df" 
env1[[.tmp$env1_subenv_name]][[.tmp$objectname]] = function(input_list_vecs, print_str = TRUE, VERBOSE = isTRUE(getOption("verbose"))) {
    # 1. If verbose, print the function call
    if (VERBOSE) {
        cat("[DEBUG] Entering f_list_vecs.union_df()\n")
    }

    # 2. Check that the input is indeed a list
    if (!is.list(input_list_vecs)) {
        stop("The input must be a list of vectors.")
    }
    
    # 3. Handle unnamed vectors by assigning default names only where needed
    originalNames_vec <- names(input_list_vecs)
    
    # If no names exist at all, create them:
    if (is.null(originalNames_vec)) {
        defaultNames_vec <- paste0("vec", seq_along(input_list_vecs))
        names(input_list_vecs) <- defaultNames_vec
        if (VERBOSE) {
            cat("[DEBUG] All vectors were unnamed. Assigned default names:\n")
            print(defaultNames_vec)
        }
    } else {
        # If some are named and others are empty, only replace the empty ones
        for (i in seq_along(originalNames_vec)) {
            if (is.na(originalNames_vec[i]) || originalNames_vec[i] == "") {
                originalNames_vec[i] <- paste0("Vec", i)
            }
        }
        names(input_list_vecs) <- originalNames_vec
        if (VERBOSE) {
            cat("[DEBUG] Some vectors were unnamed. Assigned default names for those only:\n")
            print(originalNames_vec)
        }
    }
    
    # 4. Convert all vectors to character
    input_list_vecs.as_character <- purrr::map(
        .x = input_list_vecs,
        .f = function(single_vec) {
            as.character(single_vec)
        }
    )

    # 5. Compute the union of all elements (sorted, unique)
    union_vec <- sort(unique(unlist(input_list_vecs.as_character)))
    if (VERBOSE) {
        cat("[DEBUG] union_vec (all unique elements):\n")
        print(union_vec)
    }

    # 6. Initialize output tibble
    output_df <- tibble::tibble(UNION = union_vec)

    # 7. Create logical indicator columns
    for (vec_name in names(input_list_vecs.as_character)) {
        membership_vec <- output_df[["UNION"]] %in% input_list_vecs.as_character[[vec_name]]
        output_df[[vec_name]] <- membership_vec
        if (VERBOSE) {
            cat("[DEBUG] Processed membership for:", vec_name, "\n")
        }
    }

    # 8. Print final output if requested
    if (print_str) {str(output_df); print(summary(output_df))}

    # 9. Return the tibble
    return(output_df)
}
```
  
  
### \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  



# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
  
```{r createBACKUP, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_filename_ext.createBACKUP(BACKUP_from_path_filename_ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal.attach$f_filename_ext.createBACKUP(BACKUP_from_path_filename_ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_filename.nb.html = env1$path$LastSourceEditorContext.path_filename_ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") {  try(  paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/",mustWork=TRUE),'"') |> shell(wait=FALSE)  )  }  # else { browseURL(env1$path$LastSourceEditorContext.path_filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_filename_ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
