---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  # - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd())  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_FileNameExt ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# .tmp$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) not a relative path~!  
# env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) Not using a relative path~!
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .FileName.source.r = "f_DSN.Search.read.checkEntity" |> paste0(".source.r"); .RelativeSubPath=r"()"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = file.path(.RelativeSubPath, .FileName.source.r))
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  
```
  
  
# __________|------  
# @@ DATA) example ----  
  
## :: JK02ID.CCW.MIN_Date.ge365.MDD.EndTime.i.recode.bin.4c.EndTimeP.NA_rm.CC69.agg4.4069AgeNum.i2007.1.1 = ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# # Define variable names
# varnames <- c(
#   "EndTime.is.Case.confirm.365", "EndTime", "AgeDecade", "Female", "Income",
#   "DisabilityGrade", "AcquiredHypothyroidism", "AdjustmentDisorder", "Anemia",
#   "Anxiety", "Arthritis", "AtrialFibrillation", "BenignProstatic",
#   "BrainInjury", "Cataract", "ChronicKidney", "Diabetes", "Dysthymia",
#   "Epilepsy", "Fibromyalgia_Pain_Fatigue", "Glaucoma", "HearingImpairment",
#   "HeartFailure", "Hyperlipidemia", "Hypertension", "IschemicHeart",
#   "Migraine_ChronicHeadache", "MobilityImpairments", "Osteoporosis",
#   "PelvicFx", "PersonalityDisorders", "SpinalCordInjury", "StrokeTIA",
#   "AlzheimerDementia", "LiverDisease", "ObstructiveLungDisease",
#   "CancerSurvivors"
# )
# 
# # Function to load and preprocess data
# load_preprocess_data <- function(file_path, varnames, is_test = FALSE) {
#   data <- readRDS(file_path)[varnames] %>%
#     mutate(EndTime = as.numeric(EndTime))
#   
#   if (is_test) {
#     data <- data %>% mutate(testset = TRUE)
#   }
#   
#   return(as_tibble(data))
# }
# 
# # Load training and testing datasets
# train_file <- "JK02ID.CCW.MIN_Date.ge365.MDD.EndTime.i.recode.bin.4c.EndTimeP.NA_rm.CC69.agg4.4069AgeNum.i2007.1.1.rda"
# test_file <- "JK02ID.CCW.MIN_Date.ge365.MDD.EndTime.i.recode.bin.4test.EndTimeP.NA_rm.CC69.agg4.4069AgeNum.i2007.1.1.rda"
# 
# TheTrainSet <- load_preprocess_data(train_file, varnames, is_test = FALSE)
# TheTestSet  <- load_preprocess_data(test_file, varnames, is_test = TRUE)
```
  
  
## :: example_train_data() ----  
### :: example_test_data() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Load necessary libraries
library(tidyverse)
library(survival)

# Create non-random example dataset
example_train_data <- tibble(
  EndTime.is.Case.confirm.365 = c(1, 1, 0, 0, 1, 0),
  EndTime = c(2, 3, 5, 10, 7, 8),
  AgeDecade = factor(c(5, 5, 4, 4, 3, 3)),  # Age in decades (3 = 30s, 4 = 40s, 5 = 50s)
  Female = c(TRUE, FALSE, TRUE, FALSE, TRUE, FALSE),
  Income = factor(c(3, 2, 1, 3, 2, 1)),  # Income levels (1 = low, 2 = medium, 3 = high)
  DisabilityGrade = factor(c("Mild", "Severe", "Mild", "Severe", "Mild", "Severe")),
  Anxiety = c(TRUE, FALSE, TRUE, FALSE, TRUE, FALSE)
)

example_test_data <- tibble(
  EndTime.is.Case.confirm.365 = c(1, 0, 1),
  EndTime = c(4, 12, 9),
  AgeDecade = factor(c(5, 3, 4)),
  Female = c(TRUE, FALSE, TRUE),
  Income = factor(c(3, 1, 2)),
  DisabilityGrade = factor(c("Severe", "Mild", "Severe")),
  Anxiety = c(FALSE, TRUE, FALSE)
)

# Ensure no randomness is used in creating the data
example_train_data
example_test_data

```
  
  
## :: TheTrainSet() ----  
### :: TheTestSet() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

# Define variable names
varnames <- c(
  "EndTime.is.Case.confirm.365", "EndTime", "AgeDecade", "Female", "Income",
  "DisabilityGrade", "AcquiredHypothyroidism", "AdjustmentDisorder", "Anemia",
  "Anxiety", "Arthritis", "AtrialFibrillation", "BenignProstatic",
  "BrainInjury", "Cataract", "ChronicKidney", "Diabetes", "Dysthymia",
  "Epilepsy", "Fibromyalgia_Pain_Fatigue", "Glaucoma", "HearingImpairment",
  "HeartFailure", "Hyperlipidemia", "Hypertension", "IschemicHeart",
  "Migraine_ChronicHeadache", "MobilityImpairments", "Osteoporosis",
  "PelvicFx", "PersonalityDisorders", "SpinalCordInjury", "StrokeTIA",
  "AlzheimerDementia", "LiverDisease", "ObstructiveLungDisease",
  "CancerSurvivors"
)

# Create Training Dataset
TheTrainSet <- tibble(
  EndTime.is.Case.confirm.365 = c(0, 1, 0, 1, 0),
  EndTime = c(100, 200, 150, 300, 250),
  AgeDecade = c(5, 6, 5, 7, 6),
  Female = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  Income = c(3, 5, 2, 4, 3),
  DisabilityGrade = factor(c("None", "Severe", "Mild", "None", "Severe")),
  AcquiredHypothyroidism = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  AdjustmentDisorder = c(FALSE, FALSE, TRUE, FALSE, FALSE),
  Anemia = c(TRUE, FALSE, FALSE, TRUE, FALSE),
  Anxiety = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  Arthritis = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  AtrialFibrillation = c(FALSE, FALSE, TRUE, FALSE, FALSE),
  BenignProstatic = c(FALSE, FALSE, FALSE, FALSE, FALSE),
  BrainInjury = c(FALSE, TRUE, FALSE, FALSE, FALSE),
  Cataract = c(FALSE, FALSE, TRUE, FALSE, TRUE),
  ChronicKidney = c(FALSE, FALSE, FALSE, TRUE, FALSE),
  Diabetes = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  Dysthymia = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  Epilepsy = c(FALSE, FALSE, TRUE, FALSE, FALSE),
  Fibromyalgia_Pain_Fatigue = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  Glaucoma = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  HearingImpairment = c(FALSE, FALSE, FALSE, TRUE, FALSE),
  HeartFailure = c(FALSE, TRUE, FALSE, FALSE, FALSE),
  Hyperlipidemia = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  Hypertension = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  IschemicHeart = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  Migraine_ChronicHeadache = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  MobilityImpairments = c(FALSE, FALSE, TRUE, FALSE, FALSE),
  Osteoporosis = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  PelvicFx = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  PersonalityDisorders = c(FALSE, TRUE, FALSE, FALSE, FALSE),
  SpinalCordInjury = c(FALSE, FALSE, TRUE, FALSE, FALSE),
  StrokeTIA = c(FALSE, TRUE, FALSE, FALSE, FALSE),
  AlzheimerDementia = c(FALSE, FALSE, FALSE, TRUE, FALSE),
  LiverDisease = c(FALSE, TRUE, FALSE, FALSE, TRUE),
  ObstructiveLungDisease = c(FALSE, TRUE, FALSE, FALSE, TRUE),
  CancerSurvivors = c(FALSE, TRUE, FALSE, FALSE, FALSE)
)

# Create Test Dataset
TheTestSet <- tibble(
  EndTime.is.Case.confirm.365 = c(0, 1, 0),
  EndTime = c(120, 220, 180),
  AgeDecade = c(5, 7, 6),
  Female = c(FALSE, TRUE, FALSE),
  Income = c(4, 3, 5),
  DisabilityGrade = factor(c("Mild", "None", "Severe")),
  AcquiredHypothyroidism = c(TRUE, FALSE, TRUE),
  AdjustmentDisorder = c(FALSE, TRUE, FALSE),
  Anemia = c(FALSE, TRUE, FALSE),
  Anxiety = c(TRUE, FALSE, TRUE),
  Arthritis = c(FALSE, TRUE, FALSE),
  AtrialFibrillation = c(TRUE, FALSE, FALSE),
  BenignProstatic = c(FALSE, FALSE, FALSE),
  BrainInjury = c(TRUE, FALSE, FALSE),
  Cataract = c(FALSE, TRUE, FALSE),
  ChronicKidney = c(TRUE, FALSE, TRUE),
  Diabetes = c(FALSE, TRUE, FALSE),
  Dysthymia = c(TRUE, FALSE, TRUE),
  Epilepsy = c(FALSE, TRUE, FALSE),
  Fibromyalgia_Pain_Fatigue = c(FALSE, TRUE, FALSE),
  Glaucoma = c(TRUE, FALSE, TRUE),
  HearingImpairment = c(TRUE, FALSE, TRUE),
  HeartFailure = c(TRUE, FALSE, TRUE),
  Hyperlipidemia = c(FALSE, TRUE, FALSE),
  Hypertension = c(TRUE, FALSE, TRUE),
  IschemicHeart = c(FALSE, TRUE, FALSE),
  Migraine_ChronicHeadache = c(TRUE, FALSE, TRUE),
  MobilityImpairments = c(TRUE, FALSE, TRUE),
  Osteoporosis = c(FALSE, TRUE, FALSE),
  PelvicFx = c(TRUE, FALSE, TRUE),
  PersonalityDisorders = c(TRUE, FALSE, TRUE),
  SpinalCordInjury = c(TRUE, FALSE, TRUE),
  StrokeTIA = c(FALSE, TRUE, FALSE),
  AlzheimerDementia = c(TRUE, FALSE, TRUE),
  LiverDisease = c(TRUE, FALSE, TRUE),
  ObstructiveLungDisease = c(TRUE, FALSE, TRUE),
  CancerSurvivors = c(TRUE, FALSE, TRUE)
) %>%
  mutate(testset = TRUE)

TheTrainSet
TheTestSet
```
  
  
### |> augment_with_bootstrap() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
set.seed(123)
augment_with_bootstrap <- function(data, n = 500) {
  # Random sampling with replacement
  bootstrapped_data <- data[sample(nrow(data), size = n, replace = TRUE), ]
  return(bootstrapped_data)
}

# Example: augment TheTrainSet by increasing to 500 observations
TrainSet.augment_with_bootstrap <- augment_with_bootstrap(TheTrainSet, n = 500)
TrainSet.augment_with_bootstrap %>% as_tibble()
```
  
  
### |> augment_with_noise() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
augment_with_noise <- function(data, noise_level = 0.01, n = 500) {
  augmented_data <- data[sample(nrow(data), size = n, replace = TRUE), ]
  
  # Add noise to continuous variables (e.g., AgeDecade, Income)
  augmented_data$AgeDecade <- augmented_data$AgeDecade + rnorm(n, mean = 0, sd = noise_level)
  augmented_data$Income <- augmented_data$Income + rnorm(n, mean = 0, sd = noise_level)
  
  return(augmented_data)
}

# Example: augment TheTrainSet with noise
TheTrainSet.augment_with_noise <- augment_with_noise(TheTrainSet, noise_level = 0.1, n = 500)
TheTrainSet.augment_with_noise %>% as_tibble()
```
  
  
### |> augment_with_smote() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# SMOTE can be used for balancing event/censored classes
# Please note, SMOTE is typically used for classification and not survival analysis

for(.packagename in c("smotefamily")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  

augment_with_smote <- function(data, target_var = "EndTime.is.Case.confirm.365", dup_size = 2) {
  # Convert non-numeric columns to numeric (factors to dummies, logical to binary)
  data_numeric <- data %>%
    select(-all_of(target_var)) %>%
    mutate(across(where(is.factor), ~ as.numeric(as.factor(.))),  # Convert factor to numeric
           across(where(is.logical), ~ as.numeric(.)))            # Convert logical to 0/1
  
  # Count the number of minority class instances
  minority_class_size <- sum(data[[target_var]] == 1)
  
  # Ensure K is less than the number of minority class samples
  K <- min(5, minority_class_size - 1)  # K must be at least 1 less than the minority class size
  
  # Apply SMOTE to the binary event indicator to balance the classes
  smote_result <- SMOTE(
    X = data_numeric, 
    target = data[[target_var]], 
    K = K, 
    dup_size = dup_size
  )
  
  # Return the augmented dataset
  augmented_data <- cbind(smote_result$data[, -ncol(smote_result$data)], EndTime.is.Case.confirm.365 = smote_result$data[, ncol(smote_result$data)])
  return(augmented_data)
}

# Example: augment TheTrainSet using SMOTE (over-sampling event cases)
TheTrainSet.augment_with_smote <- augment_with_smote(TheTrainSet)
TheTrainSet.augment_with_smote
```
  
  
### |> mice::mice() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
for(.packagename in c("mice")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  

# Perform multiple imputation on the dataset
imputed_data <- mice(TheTrainSet, m = 1, maxit = 50, method = 'pmm', seed = 500)

# Extract the imputed dataset
complete_data <- complete(imputed_data, 1)
complete_data %>% as_tibble()
```
  
  
### |> augment_with_synthetic_data() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
augment_with_synthetic_data <- function(data, n = 500) {
  # Sample continuous variables from the observed distributions
  synthetic_data <- data[sample(nrow(data), size = n, replace = TRUE), ]
  
  # Generate synthetic times based on existing time distribution
  synthetic_data$EndTime <- sample(data$EndTime, n, replace = TRUE)
  
  # Generate synthetic events (same proportion of events)
  synthetic_data$EndTime.is.Case.confirm.365 <- sample(data$EndTime.is.Case.confirm.365, n, replace = TRUE)
  
  return(synthetic_data)
}

# Example: augment TheTrainSet with synthetic data
augmented_synthetic_data <- augment_with_synthetic_data(TheTrainSet, n = 500)
augmented_synthetic_data %>% as_tibble()
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ START) dev ----  
# https://chatgpt.com/c/671605d9-92ac-800e-86da-6a01437532e9?model=gpt-4o
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ SOURCE) ----  
```{r RUN-ALL-CHUNKS-ABOVE, echo=FALSE, results="hide", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
```


```{r .RelativeSubPath_FileName.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
options(DEVMODE = TRUE);  # isTRUE(getOption("DEVMODE"))
# .RelativeSubPath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(env1$f$f_object.is_not_null.nor_na.nor_blank(env1$path$LastSourceEditorContext.path_FileNameExt)) {    .RelativeSubPath = env1$path$LastSourceEditorContext.path_FileNameExt |> dirname() |> env1$f$f_path.relative()  ;    ".RelativeSubPath" |> env1$f$f_ObjectName.get.dput.ECHO()    }
# if(.RelativeSubPath!="") .RelativeSubPath |> normalizePath(winslash="/",mustWork=TRUE) |> utils::browseURL() |> try()
# .FileName.source.r = "default.template" |> paste0(".source.r")
if(env1$f$f_object.is_not_null.nor_na.nor_blank(env1$path$LastSourceEditorContext.path_FileNameExt)) {    .SourceName_root = env1$path$LastSourceEditorContext.path_FileNameExt |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),"")  ;    ".SourceName_root" |> env1$f$f_ObjectName.get.dput.ECHO()    }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.RelativeSubPath = .RelativeSubPath
if(!exists(".SourceName_root") && exists(".FileName.source.r")) .SourceName_root = .FileName.source.r |> str_replace("\\.source\\.r$", "")
.FileName.source.r = .SourceName_root |> paste0(".source.r")
env1$path$.SourceName_root = .SourceName_root
env1$path$.RelativeSubPath_FileName.dev.r = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".dev.r")
env1$path$.RelativeSubPath_FileName.dev.Rmd = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".dev.Rmd")
env1$path$.RelativeSubPath_FileName.source.r = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".source.r")
cat("# ",'.SourceName_root = "',.SourceName_root,'"  \n',
    "#### ",env1$path$.RelativeSubPath_FileName.dev.r, "----  \n",
    "#### ",env1$path$.RelativeSubPath_FileName.dev.Rmd, "----  \n",
    "#### ",env1$path$.RelativeSubPath_FileName.source.r, "----  \n",
    '# # source(paste0(env1$path$source_base,"/","',env1$path$.RelativeSubPath_FileName.source.r,'"))', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'")', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.RelativeSubPath_FileName.source.r) )  ----  
# env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = file.path(.RelativeSubPath, .FileName.source.r))
```
  
  
# __________|------  
# @@ START) function ----  
## \% |> create_summary_table()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Install and load required libraries
if (!require("glmnet")) install.packages("glmnet")
if (!require("flextable")) install.packages("flextable")
library(glmnet)
library(flextable)

# Define the function
create_summary_table <- function(dataset, byVar, alpha = 1, create_flextable = FALSE) {
  # Prepare data
  x <- model.matrix(as.formula(paste("~ . -", byVar)), data = dataset)
  y <- dataset[[byVar]]
  
  # Print intermediate values for debugging
  print("x:")
  print(head(x)) # Print the first few rows of x
  print("y:")
  print(head(y)) # Print the first few values of y
  
  # Perform lasso/elastic net regression
  # Force lambda to be numeric to avoid potential issues
  lambda_seq <- as.numeric(seq(0.01, 1, by = 0.01))
  print("lambda sequence:")
  print(head(lambda_seq)) # Print the first few lambda values
  model <- glmnet(x, y, alpha = alpha, lambda = lambda_seq) 

  # Extract lambda.min from the model object
  lambda.min <- model$lambda.min
  print("lambda.min:")
  print(lambda.min) # Print the value of lambda.min

  # Extract coefficients and other statistics (example)
  coefficients <- coef(model, s = lambda.min)
  # ... extract other statistics as needed ...
  
  # Create a data frame for the table
  table_data <- data.frame(
    Variable = rownames(coefficients),
    Coefficient = coefficients[, 1]
    # ... add other statistics to the data frame ...
  )
  
  if (create_flextable) {
      # Create and format the flextable
      ft <- flextable(table_data)
      ft <- set_header_labels(ft, Variable = "Variable", Coefficient = "Coefficient")
      # ... add other formatting options as desired ...
      return(ft)
  } else {
      return(table_data)
  }
}



```
  
  
###### \% df_5vars_10obs |> create_summary_table() ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

# Use the provided dataset (same as before)
df_5vars_10obs <- data.frame(
  Group = rep(c("Group1", "Group2"), each = 5),
  Var1 = c(2.5, 3.0, 2.8, 2.9, 3.1, 3.6, 3.7, 3.5, 3.8, 3.9),
  Var2 = c(7.1, 7.3, 7.2, 7.4, 7.5, 6.8, 6.9, 7.0, 6.7, 6.6),
  Var3 = c(15, 16, 15, 14, 15, 18, 17, 19, 18, 17),
  Var4 = c(0.5, 0.6, 0.55, 0.58, 0.57, 0.65, 0.66, 0.64, 0.67, 0.68),
  Var5 = c(100, 105, 102, 101, 103, 110, 112, 111, 113, 114)
)

# Apply the create_summary_table function
lasso_table <- create_summary_table(dataset = df_5vars_10obs, byVar = "Var1", alpha = 1)

# Print the table
print(lasso_table)
```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
library(reticulate)
system("python2 --version")
system("python3 --version")
```


```{py, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
import pandas as pd
from sklearn.linear_model import Lasso
from sklearn.preprocessing import StandardScaler
import numpy as np

# Define the function
def create_summary_table(dataset, byVar, alpha=1):
    # Prepare data
    X = dataset.drop(byVar, axis=1)
    if 'Group' in X:
      X = pd.get_dummies(X, columns=['Group'], drop_first=True)
    y = dataset[byVar]

    # Perform lasso/elastic net regression
    scaler = StandardScaler()
    X_scaled = scaler.fit_transform(X)

    # Generate a lambda sequence
    lambdas = np.logspace(-4, 4, 100)

    model = Lasso(alpha=alpha)
    model.fit(X_scaled, y)

    # Extract coefficients and other statistics (example)
    coefficients = model.coef_
    intercept = model.intercept_

    # Create a data frame for the table
    table_data = pd.DataFrame({
        'Variable': X.columns,
        'Coefficient': coefficients
    })

    # Add intercept to table_data
    table_data.loc[len(table_data)] = ['Intercept', intercept]

    return table_data

# Use the provided dataset
df_5vars_10obs = pd.DataFrame({
    'Group': ['Group1'] * 5 + ['Group2'] * 5,
    'Var1': [2.5, 3.0, 2.8, 2.9, 3.1, 3.6, 3.7, 3.5, 3.8, 3.9],
    'Var2': [7.1, 7.3, 7.2, 7.4, 7.5, 6.8, 6.9, 7.0, 6.7, 6.6],
    'Var3': [15, 16, 15, 14, 15, 18, 17, 19, 18, 17],
    'Var4': [0.5, 0.6, 0.55, 0.58, 0.57, 0.65, 0.66, 0.64, 0.67, 0.68],
    'Var5': [100, 105, 102, 101, 103, 110, 112, 111, 113, 114]
})

# Apply the create_summary_table function
lasso_table = create_summary_table(dataset=df_5vars_10obs, byVar='Var1', alpha=1)

# Print the table
print(lasso_table.to_markdown(index=False, numalign="left", stralign="left"))
```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
  
```{r createBACKUP, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$LastSourceEditorContext.path_FileName.pdf = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$LastSourceEditorContext.path_FileName.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (Sys.info()["sysname"] == "Windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$LastSourceEditorContext.path_FileNameExt)),', output_format = "pdf_document")  \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
        .path_file = env1$path$LastSourceEditorContext.path_FileName.pdf
        env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE)
        env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = .path_file, .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal.attach$f_file_PDF.sumatra(.path_file))
    }
}
# env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_FileName.pdf; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = ',deparse(.path_file),', .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal.attach$f_file_PDF.sumatra(',deparse(.path_file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path_file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_FileName.html; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = ',deparse(.path_file),', .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); cat('  env1$env.internal.attach$f_URL.browse_in_edge_app(',deparse(.path_file),')  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_FileName.nb.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") {  try(  paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE),'"') |> shell(wait=FALSE)  )  }  # else { browseURL(env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE)) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileNameExt) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileName.nb.html) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
