---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_filename_ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$LastSourceEditorContext.path_filename_ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(getwd()|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_filename_ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .filename.source.r = "f_DataSetName.Search.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.subpath_filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.filename.source.r))
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  
# __________|------  
# @@ START) data example ----  
## \$ analyticDF_time2event =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# suppressPackageStartupMessages(library(survival))
for(.packagename in c("survminer")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
# ?survival::lung
.objectname = DataSetName = "analyticDF_time2event"
assign(
    DataSetName, 
    survival::lung |> as_tibble() |> mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] |> as.factor(), StudyPopulation = time >= 30) |>
        # dplyr::select(-status, -sex)
        dplyr::select(-status)
)
analyticDF_time2event %>% {cat(" > ",deparse(substitute(.))," |> as_tibble() |> print()","  \n", sep=""); print(as_tibble(.))}
```
  
  
### :: df_5vars_10obs ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Manually create a dataset
df_5vars_10obs <- data.frame(
  Group = rep(c("Group1", "Group2"), each = 5),
  Var1 = c(2.5, 3.0, 2.8, 2.9, 3.1, 3.6, 3.7, 3.5, 3.8, 3.9),
  Var2 = c(7.1, 7.3, 7.2, 7.4, 7.5, 6.8, 6.9, 7.0, 6.7, 6.6),
  Var3 = c(15, 16, 15, 14, 15, 18, 17, 19, 18, 17),
  Var4 = c(0.5, 0.6, 0.55, 0.58, 0.57, 0.65, 0.66, 0.64, 0.67, 0.68),
  Var5 = c(100, 105, 102, 101, 103, 110, 112, 111, 113, 114)
)

# Display the dataset
print(df_5vars_10obs)
```

  
### :: df_numeric5_categorical2 ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
df_numeric5_categorical2 = 
    structure(list(group_variable = c("A", "A", "A", "B", "B", "B", "C", "C", "C"), numeric_var1 = c(10L, 12L, 11L, 20L, 22L, 21L, 30L, 32L, 31L), numeric_var2 = c(100L, 102L, 101L, 200L, 202L, 201L, 300L, 302L, 301L), numeric_var3 = c(5, 6, 5.5, 10, 11, 10.5, 15, 16, 15.5), numeric_var4 = c(25, 26, 25.5, 50, 51, 50.5, 75, 76, 75.5), numeric_var5 = c(2, 2.2, 2.1, 4, 4.2, 4.1, 6, 6.2, 6.1), categorical_var1 = c("X", "Y", "X", "Y", "Z", "Y", "Z", "X", "Z"), categorical_var2 = c("M", "N", "M", "N", "O",  "N", "O", "M", "O")), class = "data.frame", row.names = c(NA, -9L))
df_numeric5_categorical2
```
  
  
## :: titanic_train() ----  
### :: titanic_data() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
for(.packagename in c("titanic")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  

# Load the Titanic dataset
data("titanic_train")

# View the first few rows
titanic_train |> str(max.level = 2, give.attr = TRUE)
titanic_train %>% as_tibble

# Select relevant variables
titanic_data <- titanic_train %>%
  select(Survived, Pclass, Sex, Age, Fare) %>% as_tibble

# Handle missing values by removing rows with NA
titanic_data <- na.omit(titanic_data)

# Convert 'Survived' and 'Sex' to factors
titanic_data$Survived <- factor(titanic_data$Survived)
titanic_data$Sex <- factor(titanic_data$Sex)
titanic_data |> str(max.level = 2, give.attr = TRUE)
titanic_data %>% as_tibble
```
  
  
# __________|------  
# @@ START) dev ----  
# https://gemini.google.com/app/f47a57ed798a76cb
# https://chatgpt.com/c/67153dee-3214-800e-ab61-db0a7ac38510?model=o1-preview
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```
  
  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
for(.packagename in c("boot", "caret", "dplyr")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
```
  
  

  
  
### titanic_data |> glm() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

# Fit logistic regression model
model_full <- glm(Survived ~ Pclass + Sex + Age + Fare, data = titanic_data, family = binomial)

# Summarize the model
summary(model_full)

```
  
  
####  \% |> residuals() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Calculate residuals
residuals_deviance <- residuals(model_full, type = "deviance")

# Plot residuals
plot(predict(model_full, type = "link"), residuals_deviance,
     xlab = "Linear Predictor", ylab = "Deviance Residuals",
     main = "Residual Plot")
abline(h = 0, lty = 2)


```
  
  
### library(ResourceSelection) ----  
#### \% |> hoslem.test() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

for(.packagename in c("ResourceSelection")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  

# Hosmer-Lemeshow Test
library(ResourceSelection)
hoslem.test(as.numeric(titanic_data$Survived)-1, fitted(model_full))

```
  
  
### \% |> caret::createFolds() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Set seed for reproducibility
set.seed(123)

# Define number of folds
k <- 5

# Create folds
folds <- createFolds(titanic_data$Survived, k = k, list = TRUE, returnTrain = FALSE)

# Initialize a data frame to store coefficients
coefficients_cv <- data.frame()

# Perform cross-validation
for(i in 1:k) {
  # Split data into training and validation sets
  validation_indices <- folds[[i]]
  training_data <- titanic_data[-validation_indices, ]
  validation_data <- titanic_data[validation_indices, ]
  
  # Fit model on training data
  model_cv <- glm(Survived ~ Pclass + Sex + Age + Fare, data = training_data, family = binomial)
  
  # Store coefficients
  coeffs <- coef(model_cv)
  coefficients_cv <- rbind(coefficients_cv, coeffs)
}

# Add fold numbers
coefficients_cv$Fold <- 1:k

# View coefficient estimates across folds
print(coefficients_cv)

# Reshape data for plotting
library(tidyr)
coefficients_long <- coefficients_cv %>%
  gather(key = "Coefficient", value = "Estimate", -Fold)

# Plot coefficient estimates across folds
library(ggplot2)
ggplot(coefficients_long, aes(x = as.factor(Fold), y = Estimate, group = Coefficient, color = Coefficient)) +
  geom_line() +
  geom_point() +
  labs(title = "Coefficient Estimates Across Folds",
       x = "Fold",
       y = "Coefficient Estimate") +
  theme_minimal()

```
  
  
### library(pROC) ----  
#### \% |> roc() |> plot() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Initialize vector to store predicted probabilities
predicted_probs <- rep(NA, nrow(titanic_data))

# Perform cross-validation
for(i in 1:k) {
  # Split data into training and validation sets
  validation_indices <- folds[[i]]
  training_data <- titanic_data[-validation_indices, ]
  validation_data <- titanic_data[validation_indices, ]
  
  # Fit model on training data
  model_cv <- glm(Survived ~ Pclass + Sex + Age + Fare, data = training_data, family = binomial)
  
  # Predict on validation data
  predicted_probs[validation_indices] <- predict(model_cv, newdata = validation_data, type = "response")
}

# Add predicted probabilities to the dataset
titanic_data$Predicted_Prob <- predicted_probs

# Evaluate model performance
library(pROC)
roc_curve <- roc(titanic_data$Survived, titanic_data$Predicted_Prob)
auc_value <- auc(roc_curve)

# Plot ROC curve
plot(roc_curve, main = paste("ROC Curve (AUC =", round(auc_value, 2), ")"))

```
  
  
### library(boot) ----  
#### ECHO \% |> boot() |> boot.ci() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Define a function to fit the model and return coefficients
boot_fn <- function(data, indices) {
  d <- data[indices, ]  # Allows boot to select sample
  fit <- glm(Survived ~ Pclass + Sex + Age + Fare, data = d, family = binomial)
  return(coef(fit))
}

# Perform bootstrapping
set.seed(123)
boot_results <- boot(data = titanic_data, statistic = boot_fn, R = 1000)

# View bootstrapped coefficient estimates
print(boot_results)

# Calculate bootstrapped confidence intervals
boot.ci(boot_results, type = "perc", index = 2)  # For Pclass
boot.ci(boot_results, type = "perc", index = 3)  # For Sex
boot.ci(boot_results, type = "perc", index = 4)  # For Age
boot.ci(boot_results, type = "perc", index = 5)  # For Fare

```
  
  
### ECHO \% |> stats::influence.measures() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Calculate influence measures
influence_measures <- influence.measures(model_full)

# Summary of influence measures
summary(influence_measures)

# Identify observations with high Cook's distance
cook_threshold <- 4 / nrow(titanic_data)
high_cook <- which(influence_measures$cook.d > cook_threshold)

# Print influential observations
print(high_cook)

```
  
  
### \% |> caret::createFolds() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Assume titanic_data is already prepared as in previous examples
library(caret)

set.seed(123)
k <- 5
folds <- createFolds(titanic_data$Survived, k = k, list = TRUE)

coefficients_cv <- data.frame()

for(i in 1:k) {
  training_data <- titanic_data[-folds[[i]], ]
  model_cv <- glm(Survived ~ Pclass + Sex + Age + Fare, data = training_data, family = binomial)
  coeffs <- coef(model_cv)
  coefficients_cv <- rbind(coefficients_cv, coeffs)
}

coefficients_cv$Fold <- 1:k
print(coefficients_cv)

```
  
  
### ECHO \% |> confint() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Fit the model on the full dataset
model_full <- glm(Survived ~ Pclass + Sex + Age + Fare, data = titanic_data, family = binomial)

# Extract confidence intervals
conf_intervals <- confint(model_full)
print(conf_intervals)

```
  
  
### \% |> MASS::mvrnorm() ----  
#### \% |> predict_interval() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
library(MASS)

# Revised function to calculate prediction intervals
predict_interval <- function(model, newdata, level = 0.95, nsim = 1000) {
  # Simulate coefficient estimates
  sim_coeffs <- mvrnorm(nsim, coef(model), vcov(model))
  
  # Create design matrix (including intercept)
  newdata_matrix <- model.matrix(~ Pclass + Sex + Age + Fare, data = newdata)
  
  # Predict probabilities using simulated coefficients
  pred_probs <- apply(sim_coeffs, 1, function(beta) {
    eta <- newdata_matrix %*% beta
    1 / (1 + exp(-eta))  # Logistic function for probabilities
  })
  
  # Convert the predicted probabilities to a matrix (if it's a vector)
  pred_probs <- matrix(pred_probs, nrow = nsim)
  
  # Calculate prediction intervals
  lower <- quantile(pred_probs, probs = (1 - level) / 2)
  upper <- quantile(pred_probs, probs = 1 - (1 - level) / 2)
  
  data.frame(Lower = lower, Upper = upper)
}

# Example for a new observation
new_obs <- data.frame(Pclass = 3, Sex = "male", Age = 25, Fare = 7.25)
new_obs$Sex <- factor(new_obs$Sex, levels = levels(titanic_data$Sex))

# Calculate prediction interval
pi_result <- predict_interval(model_full, new_obs)
print(pi_result)


```
  
  
### library(boot) ----  
#### ECHO \% |> boot() |> boot.ci() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
library(boot)

# Define a function to calculate the coefficients for bootstrapping
boot_fn <- function(data, indices) {
  d <- data[indices, ]  # Resample the data
  fit <- glm(Survived ~ Pclass + Sex + Age + Fare, data = d, family = binomial)
  return(coef(fit))  # Return the model coefficients
}

# Perform bootstrapping with 1000 resamples
set.seed(123)
boot_results <- boot(data = titanic_data, statistic = boot_fn, R = 1000)

# View bootstrapped estimates
print(boot_results)

# Calculate bootstrap confidence intervals for each coefficient
boot_ci_pclass <- boot.ci(boot_results, type = "perc", index = 2)  # Pclass
boot_ci_sex <- boot.ci(boot_results, type = "perc", index = 3)  # Sex
boot_ci_age <- boot.ci(boot_results, type = "perc", index = 4)  # Age
boot_ci_fare <- boot.ci(boot_results, type = "perc", index = 5)  # Fare

# Print bootstrap confidence intervals
print(boot_ci_pclass)
print(boot_ci_sex)
print(boot_ci_age)
print(boot_ci_fare)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
library(boot)
library(MASS)

# Function to calculate predicted probabilities for bootstrap samples
boot_pred_fn <- function(data, indices, newdata) {
  d <- data[indices, ]  # Resample the data
  fit <- glm(Survived ~ Pclass + Sex + Age + Fare, data = d, family = binomial)  # Fit the model
  
  # Create design matrix for the new observation
  newdata_matrix <- model.matrix(~ Pclass + Sex + Age + Fare, data = newdata)
  
  # Predicted probabilities
  eta <- newdata_matrix %*% coef(fit)  # Linear predictor
  pred_prob <- 1 / (1 + exp(-eta))  # Logistic function for probabilities
  return(pred_prob)  # Return predicted probabilities
}

# Example new observation for prediction
new_obs <- data.frame(Pclass = 3, Sex = "male", Age = 25, Fare = 7.25)
new_obs$Sex <- factor(new_obs$Sex, levels = levels(titanic_data$Sex))

# Perform bootstrapping to generate predicted probabilities
set.seed(123)
boot_pred_results <- boot(data = titanic_data, statistic = boot_pred_fn, R = 1000, newdata = new_obs)

# Extract predicted probabilities from the bootstrap results
pred_probs <- boot_pred_results$t  # Each row represents one bootstrap sample's prediction

# Calculate prediction intervals (e.g., 95% interval)
lower <- quantile(pred_probs, probs = 0.025)  # 2.5th percentile
upper <- quantile(pred_probs, probs = 0.975)  # 97.5th percentile

# Display the prediction interval
pred_interval <- data.frame(Lower = lower, Upper = upper)
print(pred_interval)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ START) source ----  
```{r RUN-ALL-CHUNKS-ABOVE, echo=FALSE, results="hide", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
```


```{r .subpath_filename.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
options(DEVMODE = TRUE);  # isTRUE(getOption("DEVMODE"))
# .subpath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") {.subpath = env1$path$LastSourceEditorContext.path_filename_ext |> dirname(); ".subpath" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
# if(.subpath!="") utils::browseURL(normalizePath(.subpath))
# .filename.source.r = "default.template" |> paste0(".source.r")
if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") {.sourcename_root = env1$path$LastSourceEditorContext.path_filename_ext |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),""); ".sourcename_root" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.subpath = .subpath
if(!exists(".sourcename_root") && exists(".filename.source.r")) .sourcename_root = .filename.source.r |> str_replace("\\.source\\.r$", "")
.filename.source.r = .sourcename_root |> paste0(".source.r")
env1$path$.sourcename_root = .sourcename_root
env1$path$.subpath_filename.dev.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.r")
env1$path$.subpath_filename.dev.Rmd = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.Rmd")
env1$path$.subpath_filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".source.r")
cat("# ",'.sourcename_root = "',.sourcename_root,'"  \n',
    "#### ",env1$path$.subpath_filename.dev.r, "----  \n",
    "#### ",env1$path$.subpath_filename.dev.Rmd, "----  \n",
    "#### ",env1$path$.subpath_filename.source.r, "----  \n",
    '# # source(paste0(env1$path$source_base,"/","',env1$path$.subpath_filename.source.r,'"))', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath_filename.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath_filename.source.r,'")', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.r,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath_filename.dev.Rmd,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath_filename.source.r,'"); if(!is.null(env1$path$LastSourceEditorContext.path_filename_ext)) if(env1$path$LastSourceEditorContext.path_filename_ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext));', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.subpath_filename.source.r) ) ----  
# env1$f$f_sourcePath.execute_if_not_sourced(.subpath_filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.filename.source.r))
```
  
  
# __________|------  
# @@ START) function ----  
## \% |> create_summary_table()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Install and load required libraries
if (!require("glmnet")) install.packages("glmnet")
if (!require("flextable")) install.packages("flextable")
library(glmnet)
library(flextable)

# Define the function
create_summary_table <- function(dataset, byVar, alpha = 1, create_flextable = FALSE) {
  # Prepare data
  x <- model.matrix(as.formula(paste("~ . -", byVar)), data = dataset)
  y <- dataset[[byVar]]
  
  # Print intermediate values for debugging
  print("x:")
  print(head(x)) # Print the first few rows of x
  print("y:")
  print(head(y)) # Print the first few values of y
  
  # Perform lasso/elastic net regression
  # Force lambda to be numeric to avoid potential issues
  lambda_seq <- as.numeric(seq(0.01, 1, by = 0.01))
  print("lambda sequence:")
  print(head(lambda_seq)) # Print the first few lambda values
  model <- glmnet(x, y, alpha = alpha, lambda = lambda_seq) 

  # Extract lambda.min from the model object
  lambda.min <- model$lambda.min
  print("lambda.min:")
  print(lambda.min) # Print the value of lambda.min

  # Extract coefficients and other statistics (example)
  coefficients <- coef(model, s = lambda.min)
  # ... extract other statistics as needed ...
  
  # Create a data frame for the table
  table_data <- data.frame(
    Variable = rownames(coefficients),
    Coefficient = coefficients[, 1]
    # ... add other statistics to the data frame ...
  )
  
  if (create_flextable) {
      # Create and format the flextable
      ft <- flextable(table_data)
      ft <- set_header_labels(ft, Variable = "Variable", Coefficient = "Coefficient")
      # ... add other formatting options as desired ...
      return(ft)
  } else {
      return(table_data)
  }
}



```
  
  
###### \% df_5vars_10obs |> create_summary_table() ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

# Use the provided dataset (same as before)
df_5vars_10obs <- data.frame(
  Group = rep(c("Group1", "Group2"), each = 5),
  Var1 = c(2.5, 3.0, 2.8, 2.9, 3.1, 3.6, 3.7, 3.5, 3.8, 3.9),
  Var2 = c(7.1, 7.3, 7.2, 7.4, 7.5, 6.8, 6.9, 7.0, 6.7, 6.6),
  Var3 = c(15, 16, 15, 14, 15, 18, 17, 19, 18, 17),
  Var4 = c(0.5, 0.6, 0.55, 0.58, 0.57, 0.65, 0.66, 0.64, 0.67, 0.68),
  Var5 = c(100, 105, 102, 101, 103, 110, 112, 111, 113, 114)
)

# Apply the create_summary_table function
lasso_table <- create_summary_table(dataset = df_5vars_10obs, byVar = "Var1", alpha = 1)

# Print the table
print(lasso_table)
```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
library(reticulate)
system("python2 --version")
system("python3 --version")
```


```{py, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
import pandas as pd
from sklearn.linear_model import Lasso
from sklearn.preprocessing import StandardScaler
import numpy as np

# Define the function
def create_summary_table(dataset, byVar, alpha=1):
    # Prepare data
    X = dataset.drop(byVar, axis=1)
    if 'Group' in X:
      X = pd.get_dummies(X, columns=['Group'], drop_first=True)
    y = dataset[byVar]

    # Perform lasso/elastic net regression
    scaler = StandardScaler()
    X_scaled = scaler.fit_transform(X)

    # Generate a lambda sequence
    lambdas = np.logspace(-4, 4, 100)

    model = Lasso(alpha=alpha)
    model.fit(X_scaled, y)

    # Extract coefficients and other statistics (example)
    coefficients = model.coef_
    intercept = model.intercept_

    # Create a data frame for the table
    table_data = pd.DataFrame({
        'Variable': X.columns,
        'Coefficient': coefficients
    })

    # Add intercept to table_data
    table_data.loc[len(table_data)] = ['Intercept', intercept]

    return table_data

# Use the provided dataset
df_5vars_10obs = pd.DataFrame({
    'Group': ['Group1'] * 5 + ['Group2'] * 5,
    'Var1': [2.5, 3.0, 2.8, 2.9, 3.1, 3.6, 3.7, 3.5, 3.8, 3.9],
    'Var2': [7.1, 7.3, 7.2, 7.4, 7.5, 6.8, 6.9, 7.0, 6.7, 6.6],
    'Var3': [15, 16, 15, 14, 15, 18, 17, 19, 18, 17],
    'Var4': [0.5, 0.6, 0.55, 0.58, 0.57, 0.65, 0.66, 0.64, 0.67, 0.68],
    'Var5': [100, 105, 102, 101, 103, 110, 112, 111, 113, 114]
})

# Apply the create_summary_table function
lasso_table = create_summary_table(dataset=df_5vars_10obs, byVar='Var1', alpha=1)

# Print the table
print(lasso_table.to_markdown(index=False, numalign="left", stralign="left"))
```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_filename_ext.createBackup(backup_from_path_filename_ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal.attach$f_filename_ext.createBackup(backup_from_path_filename_ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$LastSourceEditorContext.path_filename.pdf = env1$path$LastSourceEditorContext.path_filename_ext |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$LastSourceEditorContext.path_filename.html = env1$path$LastSourceEditorContext.path_filename_ext |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (Sys.info()["sysname"] == "Windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$LastSourceEditorContext.path_filename_ext)),', output_format = "pdf_document")  \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$LastSourceEditorContext.path_filename_ext %>% {paste0(env1$path$path1,"/",.)} %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
        .path_file = env1$path$LastSourceEditorContext.path_filename.pdf %>% {paste0(env1$path$path1,"/",.)}
        env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE)
        env1$env.internal.attach$f_filename_ext.createBackup(backup_from_path_filename_ext = .path_file, .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal.attach$f_file_PDF.sumatra(.path_file))
    }
}
# env1$path$LastSourceEditorContext.path_filename_ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_filename.pdf %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_filename_ext.createBackup(backup_from_path_filename_ext = ',deparse(.path_file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal.attach$f_file_PDF.sumatra(',deparse(.path_file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path_file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$LastSourceEditorContext.path_filename_ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_filename.html %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_filename_ext.createBackup(backup_from_path_filename_ext = ',deparse(.path_file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); cat('  env1$env.internal.attach$f_URL.open_in_edge_app(',deparse(.path_file),')  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_filename.nb.html = env1$path$LastSourceEditorContext.path_filename_ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/",mustWork=NA),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$LastSourceEditorContext.path_filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_filename_ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_filename_ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename_ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$LastSourceEditorContext.path_filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
