---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  # - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd())  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_FileNameExt ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# .tmp$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) not a relative path~!  
# env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) Not using a relative path~!
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$path4read = here::here(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$path4write = here::here(env1$path$path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$path4write = getwd()
.path4read  = env1$path$path4read
.path4write = env1$path$path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .FileName.source.r = "f_DSname.Search.read.checkEntity" |> paste0("-source.R"); .RelativeSubPath=r"(R)"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = list(.RelativeSubPath, .FileName.source.r) %>% {.[nzchar(.)]} %>% c(fsep = "/") %>% {do.call(here::here, .)})
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  
```
  
  
Rdev/50_model_formula_evaluation/53_model_selection/trainset.cv.glmnet_alphas_cox.dev-GPT.Rmd
Rdev/60_communicate_report_export/f_df.glmnet.GT1.flextable.dev-Gemini-pending.Rmd
Rdev/60_communicate_report_export/f_df.glmnet.GT1.flextable.dev-GPT-pending.Rmd


# __________|------  
# @@ DATA) example ----  
## \$ ADS_time2event =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# suppressPackageStartupMessages(library(survival))
for(.packagename in c("survminer")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
# ?survival::lung
.objectname = DSN = "ADS_time2event"
assign(
    DSN, 
    survival::lung |> as_tibble() |> mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] |> as.factor(), StudyPopulation = time >= 30) |>
        # dplyr::select(-status, -sex)
        dplyr::select(-status)
)
ADS_time2event %>% {cat(" > ",deparse(substitute(.))," |> as_tibble() |> print()","  \n", sep=""); print(as_tibble(.))}
```
  
  
### :: df_5vars_10obs ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Manually create a dataset
df_5vars_10obs <- data.frame(
    Group = rep(c("Group1", "Group2"), each = 5),
    Var1 = c(2.5, 3.0, 2.8, 2.9, 3.1, 3.6, 3.7, 3.5, 3.8, 3.9),
    Var2 = c(7.1, 7.3, 7.2, 7.4, 7.5, 6.8, 6.9, 7.0, 6.7, 6.6),
    Var3 = c(15, 16, 15, 14, 15, 18, 17, 19, 18, 17),
    Var4 = c(0.5, 0.6, 0.55, 0.58, 0.57, 0.65, 0.66, 0.64, 0.67, 0.68),
    Var5 = c(100, 105, 102, 101, 103, 110, 112, 111, 113, 114)
)

# Display the dataset
print(df_5vars_10obs)
```
  
  
### :: df_numeric5_categorical2 ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
df_numeric5_categorical2 = 
    structure(list(group_variable = c("A", "A", "A", "B", "B", "B", "C", "C", "C"), numeric_var1 = c(10L, 12L, 11L, 20L, 22L, 21L, 30L, 32L, 31L), numeric_var2 = c(100L, 102L, 101L, 200L, 202L, 201L, 300L, 302L, 301L), numeric_var3 = c(5, 6, 5.5, 10, 11, 10.5, 15, 16, 15.5), numeric_var4 = c(25, 26, 25.5, 50, 51, 50.5, 75, 76, 75.5), numeric_var5 = c(2, 2.2, 2.1, 4, 4.2, 4.1, 6, 6.2, 6.1), categorical_var1 = c("X", "Y", "X", "Y", "Z", "Y", "Z", "X", "Z"), categorical_var2 = c("M", "N", "M", "N", "O",  "N", "O", "M", "O")), class = "data.frame", row.names = c(NA, -9L))
df_numeric5_categorical2
```
  
  
## :: titanic_train() ----  
### :: titanic_data() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
for(.packagename in c("titanic")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  

# Load the Titanic dataset
data("titanic_train")

# View the first few rows
titanic_train |> str(max.level = 2, give.attr = TRUE)
titanic_train %>% as_tibble

# Select relevant variables
titanic_data <- titanic_train %>%
    select(Survived, Pclass, Sex, Age, Fare) %>% as_tibble

# Handle missing values by removing rows with NA
titanic_data <- na.omit(titanic_data)

# Convert 'Survived' and 'Sex' to factors
titanic_data$Survived <- factor(titanic_data$Survived)
titanic_data$Sex <- factor(titanic_data$Sex)
titanic_data |> str(max.level = 2, give.attr = TRUE)
titanic_data %>% as_tibble
```
  
  
## :: JK02ID.CCW.MIN_Date.ge365.MDD.EndTime.i.recode.bin.4c.EndTimeP.NA_rm.CC69.agg4.4069AgeNum.i2007.1.1 = ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# # Define variable names
# varnames <- c(
#   "EndTime.is.Case.confirm.365", "EndTime", "AgeDecade", "Female", "Income",
#   "DisabilityGrade", "AcquiredHypothyroidism", "AdjustmentDisorder", "Anemia",
#   "Anxiety", "Arthritis", "AtrialFibrillation", "BenignProstatic",
#   "BrainInjury", "Cataract", "ChronicKidney", "Diabetes", "Dysthymia",
#   "Epilepsy", "Fibromyalgia_Pain_Fatigue", "Glaucoma", "HearingImpairment",
#   "HeartFailure", "Hyperlipidemia", "Hypertension", "IschemicHeart",
#   "Migraine_ChronicHeadache", "MobilityImpairments", "Osteoporosis",
#   "PelvicFx", "PersonalityDisorders", "SpinalCordInjury", "StrokeTIA",
#   "AlzheimerDementia", "LiverDisease", "ObstructiveLungDisease",
#   "CancerSurvivors"
# )
# 
# # Function to load and preprocess data
# load_preprocess_data <- function(file_path, varnames, is_test = FALSE) {
#   data <- readRDS(file_path)[varnames] %>%
#     mutate(EndTime = as.numeric(EndTime))
#   
#   if (is_test) {
#     data <- data %>% mutate(testset = TRUE)
#   }
#   
#   return(as_tibble(data))
# }
# 
# # Load training and testing datasets
# train_file <- "JK02ID.CCW.MIN_Date.ge365.MDD.EndTime.i.recode.bin.4c.EndTimeP.NA_rm.CC69.agg4.4069AgeNum.i2007.1.1.rda"
# test_file <- "JK02ID.CCW.MIN_Date.ge365.MDD.EndTime.i.recode.bin.4test.EndTimeP.NA_rm.CC69.agg4.4069AgeNum.i2007.1.1.rda"
# 
# TheTrainSet <- load_preprocess_data(train_file, varnames, is_test = FALSE)
# TheTestSet  <- load_preprocess_data(test_file, varnames, is_test = TRUE)
```
  
  
## :: example_train_data() ----  
### :: example_test_data() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Load necessary libraries
library(tidyverse)
library(survival)

# Create non-random example dataset
example_train_data <- tibble(
  EndTime.is.Case.confirm.365 = c(1, 1, 0, 0, 1, 0),
  EndTime = c(2, 3, 5, 10, 7, 8),
  AgeDecade = factor(c(5, 5, 4, 4, 3, 3)),  # Age in decades (3 = 30s, 4 = 40s, 5 = 50s)
  Female = c(TRUE, FALSE, TRUE, FALSE, TRUE, FALSE),
  Income = factor(c(3, 2, 1, 3, 2, 1)),  # Income levels (1 = low, 2 = medium, 3 = high)
  DisabilityGrade = factor(c("Mild", "Severe", "Mild", "Severe", "Mild", "Severe")),
  Anxiety = c(TRUE, FALSE, TRUE, FALSE, TRUE, FALSE)
)

example_test_data <- tibble(
  EndTime.is.Case.confirm.365 = c(1, 0, 1),
  EndTime = c(4, 12, 9),
  AgeDecade = factor(c(5, 3, 4)),
  Female = c(TRUE, FALSE, TRUE),
  Income = factor(c(3, 1, 2)),
  DisabilityGrade = factor(c("Severe", "Mild", "Severe")),
  Anxiety = c(FALSE, TRUE, FALSE)
)

# Ensure no randomness is used in creating the data
example_train_data
example_test_data

```
  
  
## :: TheTrainSet() ----  
### :: TheTestSet() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

# Define variable names
varnames <- c(
  "EndTime.is.Case.confirm.365", "EndTime", "AgeDecade", "Female", "Income",
  "DisabilityGrade", "AcquiredHypothyroidism", "AdjustmentDisorder", "Anemia",
  "Anxiety", "Arthritis", "AtrialFibrillation", "BenignProstatic",
  "BrainInjury", "Cataract", "ChronicKidney", "Diabetes", "Dysthymia",
  "Epilepsy", "Fibromyalgia_Pain_Fatigue", "Glaucoma", "HearingImpairment",
  "HeartFailure", "Hyperlipidemia", "Hypertension", "IschemicHeart",
  "Migraine_ChronicHeadache", "MobilityImpairments", "Osteoporosis",
  "PelvicFx", "PersonalityDisorders", "SpinalCordInjury", "StrokeTIA",
  "AlzheimerDementia", "LiverDisease", "ObstructiveLungDisease",
  "CancerSurvivors"
)

# Create Training Dataset
TheTrainSet <- tibble(
  EndTime.is.Case.confirm.365 = c(0, 1, 0, 1, 0),
  EndTime = c(100, 200, 150, 300, 250),
  AgeDecade = c(5, 6, 5, 7, 6),
  Female = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  Income = c(3, 5, 2, 4, 3),
  DisabilityGrade = factor(c("None", "Severe", "Mild", "None", "Severe")),
  AcquiredHypothyroidism = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  AdjustmentDisorder = c(FALSE, FALSE, TRUE, FALSE, FALSE),
  Anemia = c(TRUE, FALSE, FALSE, TRUE, FALSE),
  Anxiety = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  Arthritis = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  AtrialFibrillation = c(FALSE, FALSE, TRUE, FALSE, FALSE),
  BenignProstatic = c(FALSE, FALSE, FALSE, FALSE, FALSE),
  BrainInjury = c(FALSE, TRUE, FALSE, FALSE, FALSE),
  Cataract = c(FALSE, FALSE, TRUE, FALSE, TRUE),
  ChronicKidney = c(FALSE, FALSE, FALSE, TRUE, FALSE),
  Diabetes = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  Dysthymia = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  Epilepsy = c(FALSE, FALSE, TRUE, FALSE, FALSE),
  Fibromyalgia_Pain_Fatigue = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  Glaucoma = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  HearingImpairment = c(FALSE, FALSE, FALSE, TRUE, FALSE),
  HeartFailure = c(FALSE, TRUE, FALSE, FALSE, FALSE),
  Hyperlipidemia = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  Hypertension = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  IschemicHeart = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  Migraine_ChronicHeadache = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  MobilityImpairments = c(FALSE, FALSE, TRUE, FALSE, FALSE),
  Osteoporosis = c(TRUE, FALSE, TRUE, FALSE, TRUE),
  PelvicFx = c(FALSE, TRUE, FALSE, TRUE, FALSE),
  PersonalityDisorders = c(FALSE, TRUE, FALSE, FALSE, FALSE),
  SpinalCordInjury = c(FALSE, FALSE, TRUE, FALSE, FALSE),
  StrokeTIA = c(FALSE, TRUE, FALSE, FALSE, FALSE),
  AlzheimerDementia = c(FALSE, FALSE, FALSE, TRUE, FALSE),
  LiverDisease = c(FALSE, TRUE, FALSE, FALSE, TRUE),
  ObstructiveLungDisease = c(FALSE, TRUE, FALSE, FALSE, TRUE),
  CancerSurvivors = c(FALSE, TRUE, FALSE, FALSE, FALSE)
)

# Create Test Dataset
TheTestSet <- tibble(
  EndTime.is.Case.confirm.365 = c(0, 1, 0),
  EndTime = c(120, 220, 180),
  AgeDecade = c(5, 7, 6),
  Female = c(FALSE, TRUE, FALSE),
  Income = c(4, 3, 5),
  DisabilityGrade = factor(c("Mild", "None", "Severe")),
  AcquiredHypothyroidism = c(TRUE, FALSE, TRUE),
  AdjustmentDisorder = c(FALSE, TRUE, FALSE),
  Anemia = c(FALSE, TRUE, FALSE),
  Anxiety = c(TRUE, FALSE, TRUE),
  Arthritis = c(FALSE, TRUE, FALSE),
  AtrialFibrillation = c(TRUE, FALSE, FALSE),
  BenignProstatic = c(FALSE, FALSE, FALSE),
  BrainInjury = c(TRUE, FALSE, FALSE),
  Cataract = c(FALSE, TRUE, FALSE),
  ChronicKidney = c(TRUE, FALSE, TRUE),
  Diabetes = c(FALSE, TRUE, FALSE),
  Dysthymia = c(TRUE, FALSE, TRUE),
  Epilepsy = c(FALSE, TRUE, FALSE),
  Fibromyalgia_Pain_Fatigue = c(FALSE, TRUE, FALSE),
  Glaucoma = c(TRUE, FALSE, TRUE),
  HearingImpairment = c(TRUE, FALSE, TRUE),
  HeartFailure = c(TRUE, FALSE, TRUE),
  Hyperlipidemia = c(FALSE, TRUE, FALSE),
  Hypertension = c(TRUE, FALSE, TRUE),
  IschemicHeart = c(FALSE, TRUE, FALSE),
  Migraine_ChronicHeadache = c(TRUE, FALSE, TRUE),
  MobilityImpairments = c(TRUE, FALSE, TRUE),
  Osteoporosis = c(FALSE, TRUE, FALSE),
  PelvicFx = c(TRUE, FALSE, TRUE),
  PersonalityDisorders = c(TRUE, FALSE, TRUE),
  SpinalCordInjury = c(TRUE, FALSE, TRUE),
  StrokeTIA = c(FALSE, TRUE, FALSE),
  AlzheimerDementia = c(TRUE, FALSE, TRUE),
  LiverDisease = c(TRUE, FALSE, TRUE),
  ObstructiveLungDisease = c(TRUE, FALSE, TRUE),
  CancerSurvivors = c(TRUE, FALSE, TRUE)
) %>%
  mutate(testset = TRUE)

TheTrainSet
TheTestSet
```
  
  
## glmnet::CoxExample ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# system.file("data", "CoxExample.rda", package = "glmnet")
# # > system.file("data", "CoxExample.rda", package = "glmnet")
# # [1] "/usr/local/lib/R/site-library/glmnet/data/CoxExample.rda"
# 
# library(glmnet)
# # load(system.file("data", "CoxExample.rda", package = "glmnet"))
# data(CoxExample)
# CoxExample |> str(max.level = 2, give.attr = TRUE)
# # CoxExample %>% map(function(mat) mat %>% round(3)) %>% deparse(width.cutoff = 500) %>% cat("\n")

load(url("https://github.com/mkim0710/tidystat/raw/master/data/library_glmnet_glmnet_coxExample_tibble.rda"))
glmnet_coxExample_tibble
glmnet_coxExample_tibble.round3 = glmnet_coxExample_tibble %>% mutate(across(matches("V"), function(vec) round(vec, 3)))
glmnet_coxExample_tibble.round3
# glmnet_coxExample_tibble %>% write_csv(paste0(env1$path$path1,"/data/", "glmnet_coxExample_tibble", ".csv"))
# glmnet_coxExample_tibble.round3 %>% write_csv(paste0(env1$path$path1,"/data/", "glmnet_coxExample_tibble.round3", ".csv"))
```
  
  
    > glmnet_coxExample_tibble |> str(max.level = 2, give.attr = TRUE)
    tibble [1,000 × 32] (S3: tbl_df/tbl/data.frame)
     $ time  : num [1:1000] 1.7688 0.5453 0.0449 0.8503 0.6149 ...
     $ status: num [1:1000] 1 1 0 0 1 0 0 1 1 0 ...
     $ V1    : num [1:1000] -0.877 -0.746 1.376 0.238 0.109 ...
     $ V2    : num [1:1000] -0.614 -1.752 -0.264 0.786 0.467 ...
     $ V3    : num [1:1000] -0.568 0.285 0.887 -0.897 -0.576 ...
     $ V4    : num [1:1000] 0.662 1.139 0.384 -0.834 1.704 ...
     $ V5    : num [1:1000] 1.8222 0.8018 0.0575 -0.5824 0.3275 ...
     $ V6    : num [1:1000] -1.091 1.85 -1.092 0.187 -0.121 ...
     $ V7    : num [1:1000] -0.332 0.307 0.821 -0.586 0.885 ...
     $ V8    : num [1:1000] 3.675 -1.373 2.296 0.476 0.451 ...
     $ V9    : num [1:1000] 0.2458 -0.0325 -0.4477 -0.6058 0.5888 ...
     $ V10   : num [1:1000] 1.138 0.748 -0.305 -1.27 0.55 ...
     $ V11   : num [1:1000] -0.46 -0.899 -3.682 0.868 0.552 ...
     $ V12   : num [1:1000] -0.618 0.282 1.313 -0.483 -1.105 ...
     $ V13   : num [1:1000] 0.365 1.542 -1.864 -0.101 1.598 ...
     $ V14   : num [1:1000] -1.365 0.222 -0.204 0.942 -0.339 ...
     $ V15   : num [1:1000] 1.79 -0.447 0.889 -0.235 -0.501 ...
     $ V16   : num [1:1000] -0.6 1.808 -0.396 0.262 -1.205 ...
     $ V17   : num [1:1000] 0.0712 1.541 0.5496 0.4586 -1.9601 ...
     $ V18   : num [1:1000] -1.107 1.762 0.163 0.389 -0.769 ...
     $ V19   : num [1:1000] 1.047 -0.911 -2.45 -1.539 0.714 ...
     $ V20   : num [1:1000] 0.0847 0.1854 -1.3069 -0.5914 1.2637 ...
     $ V21   : num [1:1000] 0.87 -0.443 0.393 -0.814 0.16 ...
     $ V22   : num [1:1000] -0.486 -0.136 1.112 -1.198 -1.063 ...
     $ V23   : num [1:1000] 0.23314 0.17755 0.00555 0.74975 1.7165 ...
     $ V24   : num [1:1000] -0.89 -0.121 -1.462 -0.983 -0.222 ...
     $ V25   : num [1:1000] 1.537 1.011 -1.3 2.005 0.785 ...
     $ V26   : num [1:1000] 0.362 0.978 -2.768 -0.571 -0.613 ...
     $ V27   : num [1:1000] -0.0518 0.9053 -0.1672 -0.2355 1.2637 ...
     $ V28   : num [1:1000] -0.178 -1.424 -0.7 0.939 -1.801 ...
     $ V29   : num [1:1000] 0.945 -0.733 0.929 0.363 -1.588 ...
     $ V30   : num [1:1000] 1.775 -0.0569 -1.5611 0.5486 1.0087 ...
 
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ SOURCE) Rdev/50_model_formula_evaluation/53_model_selection/f_df.cv.glmnet.source.r
# @@ RENDER) Rdev/50_model_formula_evaluation/53_model_selection/f_df.cv.glmnet.dev.Rmd
# @@ RENDER) Rdev/50_model_formula_evaluation/53_model_selection/f_cv_glmnet_object.plot.dev.Rmd
# @@ RENDER) Rdev/50_model_formula_evaluation/53_model_selection/f_df.cv.glmnet_alphas.dev.Rmd
# @@ RENDER) Rdev/50_model_formula_evaluation/53_model_selection/trainset.cv.glmnet_alphas_cox.dev.Rmd
# @@ RENDER) Rdev/60_communicate_report_export/f_df.glmnet.GT1.flextable.dev-GPT-pending.Rmd
# @@ RENDER) Rdev/60_communicate_report_export/f_df.glmnet.GT1.flextable.dev-Gemini-pending.Rmd

# __________|------  
# @@ START) dev ----  
# https://chatgpt.com/c/671605d9-92ac-800e-86da-6a01437532e9?model=gpt-4o
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```
  
  
## bind_rows(train_data, test_data) |> create_and_export_table1() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Load and install required packages using pacman
# if (!require("pacman")) install.packages("pacman")
# library(pacman)

for(.packagename in c("tidyverse", "glmnet", "useful", "survival", "tableone", "openxlsx", "broom")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  

TheTrainSet = TheTrainSet
TheTestSet = TheTestSet

# Function to create and export Table One
create_and_export_table1 <- function(train_data, test_data, strata, write_xlsx = FALSE, output_path_file) {
  combined_data <- bind_rows(train_data, test_data)
  
  table1 <- CreateTableOne(
    strata = strata,
    data = as.data.frame(combined_data),
    test = FALSE,
    includeNA = TRUE
  )
  
  # Print table with standardized mean differences (SMD)
  print_table <- print(table1, smd = TRUE, nonnormal = c("AgeDecade", "Income"))
  
  # Export table to Excel
  table_df <- as.data.frame(print_table) %>%
    rownames_to_column(var = "Variable")
  
  if (write_xlsx) {
      write.xlsx(table_df, output_path_file, asTable = TRUE)
      
      # Open the Excel file (optional)
      openXL(output_path_file)
  }
  
  return(table1)
}

# Create and export Table One
TheTable1byCase <- create_and_export_table1(
  train_data = TheTrainSet,
  test_data = TheTestSet,
  strata = "EndTime.is.Case.confirm.365",
  write_xlsx = FALSE
)
```

                                             Stratified by EndTime.is.Case.confirm.365
                                              0                   1                   SMD   
      n                                            5                   3                    
      EndTime.is.Case.confirm.365 (mean (SD))   0.00 (0.00)         1.00 (0.00)          Inf
      EndTime (mean (SD))                     160.00 (58.74)      240.00 (52.92)       1.431
      AgeDecade (median [IQR])                  5.00 [5.00, 6.00]   7.00 [6.50, 7.00]  2.251
      Female = TRUE (%)                            3 ( 60.0)           1 ( 33.3)       0.555
      Income (median [IQR])                     3.00 [3.00, 4.00]   4.00 [3.50, 4.50]  0.560
      DisabilityGrade (%)                                                              1.399
         Mild                                      2 ( 40.0)           0 (  0.0)            
         None                                      1 ( 20.0)           2 ( 66.7)            
         Severe                                    2 ( 40.0)           1 ( 33.3)            
      AcquiredHypothyroidism = TRUE (%)            2 ( 40.0)           2 ( 66.7)       0.555
      AdjustmentDisorder = TRUE (%)                1 ( 20.0)           1 ( 33.3)       0.305
      Anemia = TRUE (%)                            1 ( 20.0)           2 ( 66.7)       1.067
      Anxiety = TRUE (%)                           2 ( 40.0)           2 ( 66.7)       0.555
      Arthritis = TRUE (%)                         3 ( 60.0)           1 ( 33.3)       0.555
      AtrialFibrillation = TRUE (%)                2 ( 40.0)           0 (  0.0)       1.155
      BenignProstatic = FALSE (%)                  5 (100.0)           3 (100.0)      <0.001
      BrainInjury = TRUE (%)                       1 ( 20.0)           1 ( 33.3)       0.305
      Cataract = TRUE (%)                          2 ( 40.0)           1 ( 33.3)       0.139
      ChronicKidney = TRUE (%)                     2 ( 40.0)           1 ( 33.3)       0.139
      Diabetes = TRUE (%)                          3 ( 60.0)           1 ( 33.3)       0.555
      Dysthymia = TRUE (%)                         2 ( 40.0)           2 ( 66.7)       0.555
      Epilepsy = TRUE (%)                          1 ( 20.0)           1 ( 33.3)       0.305
      Fibromyalgia_Pain_Fatigue = TRUE (%)         3 ( 60.0)           1 ( 33.3)       0.555
      Glaucoma = TRUE (%)                          2 ( 40.0)           2 ( 66.7)       0.555
      HearingImpairment = TRUE (%)                 2 ( 40.0)           1 ( 33.3)       0.139
      HeartFailure = TRUE (%)                      2 ( 40.0)           1 ( 33.3)       0.139
      Hyperlipidemia = TRUE (%)                    3 ( 60.0)           1 ( 33.3)       0.555
      Hypertension = TRUE (%)                      2 ( 40.0)           2 ( 66.7)       0.555
      IschemicHeart = TRUE (%)                     3 ( 60.0)           1 ( 33.3)       0.555
      Migraine_ChronicHeadache = TRUE (%)          2 ( 40.0)           2 ( 66.7)       0.555
      MobilityImpairments = TRUE (%)               3 ( 60.0)           0 (  0.0)       1.732
      Osteoporosis = TRUE (%)                      3 ( 60.0)           1 ( 33.3)       0.555
      PelvicFx = TRUE (%)                          2 ( 40.0)           2 ( 66.7)       0.555
      PersonalityDisorders = TRUE (%)              2 ( 40.0)           1 ( 33.3)       0.139
      SpinalCordInjury = TRUE (%)                  3 ( 60.0)           0 (  0.0)       1.732
      StrokeTIA = TRUE (%)                         0 (  0.0)           2 ( 66.7)       2.000
      AlzheimerDementia = TRUE (%)                 2 ( 40.0)           1 ( 33.3)       0.139
      LiverDisease = TRUE (%)                      3 ( 60.0)           1 ( 33.3)       0.555
      ObstructiveLungDisease = TRUE (%)            3 ( 60.0)           1 ( 33.3)       0.555
      CancerSurvivors = TRUE (%)                   2 ( 40.0)           1 ( 33.3)       0.139
      testset = NA (%)                             3 ( 60.0)           2 ( 66.7)       0.139



## *** :: f_df.cv.glmnet_cox = function()
### *** :: f_cv_glmnet_object.mat_coef = function()
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
# Function to train cross-validated glmnet Cox models
f_df.cv.glmnet_cox <- function(
        train_data,
        formula,
        i.alpha = 1,
        family = "cox",
        type_measure = "deviance",
        nfolds = 5,
        seed = 1,
        save_models = FALSE,
        save_plots = FALSE,
        plot_size = 1280,
        output_dir = "glmnet_outputs"
) {
    # Ensure output directory exists
    if (!dir.exists(output_dir)) {
        dir.create(output_dir, recursive = TRUE)
    }
    
    set.seed(seed)
    
    # Prepare model matrix
    x <- model.matrix(formula, data = train_data)[, -1]  # Remove intercept
    
    # Extract response variable
    y <- model.response(model.frame(formula, data = train_data))
    
    
    message(paste("Training glmnet model with alpha =", i.alpha))
    
    # Train cross-validated glmnet model
    cv_glmnet_object <- cv.glmnet(
        x = x,
        y = y,
        alpha = i.alpha,
        family = family,
        type.measure = type_measure,
        nfolds = nfolds
    )
    
    # Save model if required
    if (save_models) {
        model_FileName <- here::here(output_dir, paste0("cv_glmnet_a", sprintf("%02d", i.alpha * 10), ".rds"))
        saveRDS(cv_glmnet_object, model_FileName)
        message(paste("Saved model to", model_FileName))
    }
    
    # Plot cross-validation results if required
    if (save_plots) {
        plot_FileName <- here::here(output_dir, paste0("cv_glmnet_a", sprintf("%02d", i.alpha * 10), "_plot.png"))
        png(plot_FileName, width = plot_size, height = plot_size, units = "px", bg = "transparent")
        plot(cv_glmnet_object, main = paste("Alpha =", i.alpha))
        dev.off()
        message(paste("Saved plot to", plot_FileName))
    }
    
    attributes(cv_glmnet_object)$mat_coef = cv_glmnet_object %>% f_cv_glmnet_object.mat_coef
    
    return(cv_glmnet_object)
}

f_cv_glmnet_object.mat_coef = function(cv_glmnet_object) {
    cv_glmnet_object.list_coef = list()
    cv_glmnet_object.list_coef[["min"]] = cv_glmnet_object %>% coef(s = "lambda.min")
    cv_glmnet_object.list_coef[["1se"]] = cv_glmnet_object %>% coef(s = "lambda.1se")

    cv_glmnet_object.mat_coef = cv_glmnet_object.list_coef %>% (function(ls) {
        out = ls %>% reduce(cbind); 
        colnames(out) = names(ls); 
        out
    })()
    cv_glmnet_object.mat_coef
}
```



### glmnet_coxExample_tibble |> **f_df.cv.glmnet_cox**() ----
#### :: TheTrainSet.cv.glmnet_cox.a00
##### :: TheTrainSet.cv.glmnet_cox.a00.coef = TheTrainSet.cv.glmnet_cox.a00 |> 
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
TheTrainSet = glmnet_coxExample_tibble
cox_formula <- as.formula(Surv(time, status) ~ .)
alpha = 1
# Train glmnet Cox models
TheTrainSet.cv.glmnet_cox.a00 <- f_df.cv.glmnet_cox(
  train_data = TheTrainSet,
  formula = cox_formula,
  i.alpha = 1,
  family = "cox",
  type_measure = "deviance",
  nfolds = 5,
  seed = 123,  # Changed seed for reproducibility
  save_models = FALSE,
  save_plots = FALSE,
  plot_size = 1280,
  output_dir = "glmnet_outputs"
)

# # Save all glmnet models for future use
# saveRDS(TheTrainSet.cv.glmnet_cox.alphas, file = "TheTrainSet.cv.glmnet_cox.alphas.rds")

cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
TheTrainSet.cv.glmnet_cox.a00 |> str(max.level = 1, give.attr = TRUE)
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
TheTrainSet.cv.glmnet_cox.a00$glmnet.fit |> str(max.level = 1, give.attr = TRUE)
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")

TheTrainSet.cv.glmnet_cox.a00.list_coef = list()
TheTrainSet.cv.glmnet_cox.a00.list_coef[["min"]] = TheTrainSet.cv.glmnet_cox.a00 %>% coef(s = "lambda.min")
TheTrainSet.cv.glmnet_cox.a00.list_coef[["1se"]] = TheTrainSet.cv.glmnet_cox.a00 %>% coef(s = "lambda.1se")
TheTrainSet.cv.glmnet_cox.a00.list_coef |> str(max.level = 2, give.attr = TRUE)

cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
TheTrainSet.cv.glmnet_cox.a00.mat_coef = TheTrainSet.cv.glmnet_cox.a00.list_coef %>% (function(ls) {
    out = ls %>% reduce(cbind); 
    colnames(out) = names(ls); 
    out
})()

TheTrainSet.cv.glmnet_cox.a00.mat_coef |> str(max.level = 2, give.attr = TRUE)
TheTrainSet.cv.glmnet_cox.a00.mat_coef %>% print()

cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")

cv_glmnet_object <- TheTrainSet.cv.glmnet_cox.a00
f_cv_glmnet_object.mat_coef(cv_glmnet_object)

```


    Training glmnet model with alpha = 1
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    
    List of 12
     $ lambda    : num [1:49] 0.237 0.216 0.197 0.179 0.163 ...
     $ cvm       : num [1:49] 13.6 13.6 13.5 13.5 13.4 ...
     $ cvsd      : num [1:49] 0.0606 0.0615 0.0581 0.0554 0.0535 ...
     $ cvup      : num [1:49] 13.6 13.6 13.6 13.5 13.5 ...
     $ cvlo      : num [1:49] 13.5 13.5 13.5 13.4 13.4 ...
     $ nzero     : Named int [1:49] 0 1 3 3 4 4 4 4 5 6 ...
      ..- attr(*, "names")= chr [1:49] "s0" "s1" "s2" "s3" ...
     $ call      : language cv.glmnet(x = x, y = y, type.measure = type_measure, nfolds = nfolds, alpha = i.alpha, family = family)
     $ name      : Named chr "Partial Likelihood Deviance"
      ..- attr(*, "names")= chr "deviance"
     $ glmnet.fit:List of 12
      ..- attr(*, "class")= chr [1:2] "coxnet" "glmnet"
     $ lambda.min: num 0.0175
     $ lambda.1se: num 0.0487
     $ index     : int [1:2, 1] 29 18
      ..- attr(*, "dimnames")=List of 2
     - attr(*, "class")= chr "cv.glmnet"
     - attr(*, "mat_coef")=Formal class 'dgCMatrix' [package "Matrix"] with 6 slots
        ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    
    List of 12
     $ a0       : NULL
     $ beta     :Formal class 'dgCMatrix' [package "Matrix"] with 6 slots
     $ df       : int [1:49] 0 1 3 3 4 4 4 4 5 6 ...
     $ dim      : int [1:2] 30 49
     $ lambda   : num [1:49] 0.237 0.216 0.197 0.179 0.163 ...
     $ dev.ratio: num [1:49] 0 0.0018 0.00596 0.01049 0.01438 ...
     $ nulldev  : num 8177
     $ npasses  : int 453
     $ jerr     : int 0
     $ offset   : logi FALSE
     $ call     : language glmnet(x = x, y = y, alpha = i.alpha, family = family)
     $ nobs     : int 1000
     - attr(*, "class")= chr [1:2] "coxnet" "glmnet"
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    
    List of 2
     $ min:Formal class 'dgCMatrix' [package "Matrix"] with 6 slots
      .. ..@ i       : int [1:15] 0 1 2 3 4 5 6 7 8 9 ...
      .. ..@ p       : int [1:2] 0 15
      .. ..@ Dim     : int [1:2] 30 1
      .. ..@ Dimnames:List of 2
      .. .. ..$ : chr [1:30] "V1" "V2" "V3" "V4" ...
      .. .. ..$ : chr "1"
      .. ..@ x       : num [1:15] 0.486 -0.171 -0.215 0.172 -0.183 ...
      .. ..@ factors : list()
     $ 1se:Formal class 'dgCMatrix' [package "Matrix"] with 6 slots
      .. ..@ i       : int [1:10] 0 1 2 3 4 5 6 7 8 9
      .. ..@ p       : int [1:2] 0 10
      .. ..@ Dim     : int [1:2] 30 1
      .. ..@ Dimnames:List of 2
      .. .. ..$ : chr [1:30] "V1" "V2" "V3" "V4" ...
      .. .. ..$ : chr "1"
      .. ..@ x       : num [1:10] 0.3811 -0.0984 -0.139 0.1011 -0.117 ...
      .. ..@ factors : list()
        ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    
    Formal class 'dgCMatrix' [package "Matrix"] with 6 slots
      ..@ i       : int [1:25] 0 1 2 3 4 5 6 7 8 9 ...
      ..@ p       : int [1:3] 0 15 25
      ..@ Dim     : int [1:2] 30 2
      ..@ Dimnames:List of 2
      .. ..$ : chr [1:30] "V1" "V2" "V3" "V4" ...
      .. ..$ : chr [1:2] "min" "1se"
      ..@ x       : num [1:25] 0.486 -0.171 -0.215 0.172 -0.183 ...
      ..@ factors : list()
    30 x 2 sparse Matrix of class "dgCMatrix"
                 min         1se
    V1   0.485893233  0.38108115
    V2  -0.170984544 -0.09838545
    V3  -0.214678273 -0.13898708
    V4   0.171590155  0.10107014
    V5  -0.183226956 -0.11703684
    V6  -0.485720457 -0.39278773
    V7   0.330857020  0.24631270
    V8   0.089241603  0.03861551
    V9   0.445547954  0.35114295
    V10  0.112475686  0.04167588
    V11  .            .         
    V12  .            .         
    V13  0.015366488  .         
    V14  .            .         
    V15  .            .         
    V16  .            .         
    V17 -0.016244341  .         
    V18  .            .         
    V19  .            .         
    V20  .            .         
    V21 -0.000624133  .         
    V22  .            .         
    V23  .            .         
    V24  .            .         
    V25 -0.020923039  .         
    V26  .            .         
    V27  .            .         
    V28  .            .         
    V29  .            .         
    V30 -0.005784334  .         
        ________________________________________________________________________    
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    
        ************************************************************************    
        ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    
        ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~




## *** :: f_df.cv.glmnet_cox.alphas = function()
### *** :: f_list_cv_glmnet_object.mat_coef = function()
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
# Function to train cross-validated glmnet Cox models
f_df.cv.glmnet_cox.alphas <- function(
  train_data,
  formula,
  alphas = c(1, 0.5),
  family = "cox",
  type_measure = "deviance",
  nfolds = 5,
  seed = 1,
  save_models = TRUE,
  save_plots = TRUE,
  plot_size = 1280,
  output_dir = "glmnet_outputs"
) {
    list_cv_glmnet_object = 
        alphas %>% map(function(i.alpha) {
            f_df.cv.glmnet_cox(
                train_data = train_data,
                formula = formula,
                i.alpha = i.alpha,
                family = family,
                type_measure = type_measure,
                nfolds = nfolds,
                seed = seed,
                save_models = save_models,
                save_plots = save_plots,
                plot_size = plot_size,
                output_dir = output_dir
            )
        }) %>% set_names(paste0("a", sprintf("%02d", alphas * 10)))
    
    attributes(list_cv_glmnet_object)$mat_coef = list_cv_glmnet_object %>% f_list_cv_glmnet_object.mat_coef
    
    return(list_cv_glmnet_object)
}

f_list_cv_glmnet_object.mat_coef = function(list_cv_glmnet_object) {
    list_cv_glmnet_object.mat_coef = list_cv_glmnet_object %>% 
        map(f_cv_glmnet_object.mat_coef) %>% 
        reduce(cbind)
    colnames(list_cv_glmnet_object.mat_coef) = names(list_cv_glmnet_object) %>% rep(each = 2) %>% 
        paste0(".") %>% 
        paste0(colnames(list_cv_glmnet_object.mat_coef))
    list_cv_glmnet_object.mat_coef
}


```





### glmnet_coxExample_tibble |> **f_df.cv.glmnet_cox.alphas**() ----
#### :: TheTrainSet.cv.glmnet_cox.alphas
##### :: TheTrainSet.cv.glmnet_cox.alphas.coef = TheTrainSet.cv.glmnet_cox.alphas |> 
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
TheTrainSet = glmnet_coxExample_tibble
cox_formula <- as.formula(Surv(time, status) ~ .)

# Train glmnet Cox models
TheTrainSet.cv.glmnet_cox.alphas <- f_df.cv.glmnet_cox.alphas(
  train_data = TheTrainSet,
  formula = cox_formula,
  alphas = c(1, 0.5),
  family = "cox",
  type_measure = "deviance",
  nfolds = 5,
  seed = 123,  # Changed seed for reproducibility
  save_models = FALSE,
  save_plots = FALSE,
  plot_size = 1280,
  output_dir = "glmnet_outputs"
)

# # Save all glmnet models for future use
# saveRDS(TheTrainSet.cv.glmnet_cox.alphas, file = "TheTrainSet.cv.glmnet_cox.alphas.rds")

cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
TheTrainSet.cv.glmnet_cox.alphas |> str(max.level = 1, give.attr = TRUE)
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
TheTrainSet.cv.glmnet_cox.alphas[[1]] |> str(max.level = 1, give.attr = TRUE)
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
TheTrainSet.cv.glmnet_cox.alphas[[1]]$glmnet.fit |> str(max.level = 1, give.attr = TRUE)
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")

# TheTrainSet.cv.glmnet_cox.alphas.coef_list_list = list()
# TheTrainSet.cv.glmnet_cox.alphas.coef_list_list[["min"]] = TheTrainSet.cv.glmnet_cox.alphas %>% map(coef, s = "lambda.min")
# TheTrainSet.cv.glmnet_cox.alphas.coef_list_list[["1se"]] = TheTrainSet.cv.glmnet_cox.alphas %>% map(coef, s = "lambda.1se")
# TheTrainSet.cv.glmnet_cox.alphas.coef_list_list |> str(max.level = 2, give.attr = TRUE)
# 
# cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
# TheTrainSet.cv.glmnet_cox.alphas.coef = TheTrainSet.cv.glmnet_cox.alphas.coef_list_list %>% (function(ls_ls) { 
#     ls = ls_ls %>% map(function(ls) {
#         out = ls %>% reduce(cbind); 
#         colnames(out) = names(ls); 
#         out
#     }) ; 
#     out2 = ls %>% reduce(cbind);
#     colnames(out2) = ls %>% map(colnames) %>% reduce(c) %>% paste0(".") %>% paste0(rep(names(ls), each = 2)) ;
#     out2
# })()
# 
# TheTrainSet.cv.glmnet_cox.alphas.coef |> str(max.level = 2, give.attr = TRUE)
# TheTrainSet.cv.glmnet_cox.alphas.coef %>% print()
# 
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")

list_cv_glmnet_object = TheTrainSet.cv.glmnet_cox.alphas
list_cv_glmnet_object %>% f_list_cv_glmnet_object.mat_coef

```


    Training glmnet model with alpha = 1
    Training glmnet model with alpha = 0.5
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    
    List of 2
     $ a10:List of 12
      ..- attr(*, "class")= chr "cv.glmnet"
      ..- attr(*, "mat_coef")=Formal class 'dgCMatrix' [package "Matrix"] with 6 slots
     $ a05:List of 12
      ..- attr(*, "class")= chr "cv.glmnet"
      ..- attr(*, "mat_coef")=Formal class 'dgCMatrix' [package "Matrix"] with 6 slots
     - attr(*, "mat_coef")=Formal class 'dgCMatrix' [package "Matrix"] with 6 slots
        ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    
    List of 12
     $ lambda    : num [1:49] 0.237 0.216 0.197 0.179 0.163 ...
     $ cvm       : num [1:49] 13.6 13.6 13.5 13.5 13.4 ...
     $ cvsd      : num [1:49] 0.0606 0.0615 0.0581 0.0554 0.0535 ...
     $ cvup      : num [1:49] 13.6 13.6 13.6 13.5 13.5 ...
     $ cvlo      : num [1:49] 13.5 13.5 13.5 13.4 13.4 ...
     $ nzero     : Named int [1:49] 0 1 3 3 4 4 4 4 5 6 ...
      ..- attr(*, "names")= chr [1:49] "s0" "s1" "s2" "s3" ...
     $ call      : language cv.glmnet(x = x, y = y, type.measure = type_measure, nfolds = nfolds, alpha = i.alpha, family = family)
     $ name      : Named chr "Partial Likelihood Deviance"
      ..- attr(*, "names")= chr "deviance"
     $ glmnet.fit:List of 12
      ..- attr(*, "class")= chr [1:2] "coxnet" "glmnet"
     $ lambda.min: num 0.0175
     $ lambda.1se: num 0.0487
     $ index     : int [1:2, 1] 29 18
      ..- attr(*, "dimnames")=List of 2
     - attr(*, "class")= chr "cv.glmnet"
     - attr(*, "mat_coef")=Formal class 'dgCMatrix' [package "Matrix"] with 6 slots
        ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    
    List of 12
     $ a0       : NULL
     $ beta     :Formal class 'dgCMatrix' [package "Matrix"] with 6 slots
     $ df       : int [1:49] 0 1 3 3 4 4 4 4 5 6 ...
     $ dim      : int [1:2] 30 49
     $ lambda   : num [1:49] 0.237 0.216 0.197 0.179 0.163 ...
     $ dev.ratio: num [1:49] 0 0.0018 0.00596 0.01049 0.01438 ...
     $ nulldev  : num 8177
     $ npasses  : int 453
     $ jerr     : int 0
     $ offset   : logi FALSE
     $ call     : language glmnet(x = x, y = y, alpha = i.alpha, family = family)
     $ nobs     : int 1000
     - attr(*, "class")= chr [1:2] "coxnet" "glmnet"
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    
        ________________________________________________________________________    
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    
        ************************************************************************    
        ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    
        ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    
    30 x 4 sparse Matrix of class "dgCMatrix"
             a10.min     a10.1se      a05.min     a05.1se
    V1   0.485893233  0.38108115  0.477164043  0.36843231
    V2  -0.170984544 -0.09838545 -0.170150003 -0.10261307
    V3  -0.214678273 -0.13898708 -0.213308605 -0.14116848
    V4   0.171590155  0.10107014  0.170690050  0.10609169
    V5  -0.183226956 -0.11703684 -0.182938873 -0.12166498
    V6  -0.485720457 -0.39278773 -0.476812068 -0.38030840
    V7   0.330857020  0.24631270  0.326603008  0.24257717
    V8   0.089241603  0.03861551  0.090303550  0.04599669
    V9   0.445547954  0.35114295  0.437766240  0.34078534
    V10  0.112475686  0.04167588  0.113026043  0.05070948
    V11  .            .           .            .         
    V12  .            .           .            .         
    V13  0.015366488  .           0.019780962  .         
    V14  .            .           .            .         
    V15  .            .           .            .         
    V16  .            .           .            .         
    V17 -0.016244341  .          -0.019298765  .         
    V18  .            .           .            .         
    V19  .            .           .            .         
    V20  .            .           .            .         
    V21 -0.000624133  .          -0.004383282  .         
    V22  .            .          -0.002035236  .         
    V23  .            .           .            .         
    V24  .            .           .            .         
    V25 -0.020923039  .          -0.024429532  .         
    V26  .            .           .            .         
    V27  .            .           0.003319417  .         
    V28  .            .           .            .         
    V29  .            .           .            .         
    V30 -0.005784334  .          -0.010267049  .         


## :: extract_selected_variables = function()
### |> extract_selected_variables()
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
extract_selected_variables <- function(cv_glmnet_model, lambda = "lambda.min") {
  # Extract coefficients at specified lambda
  coef_matrix <- coef(cv_glmnet_model, s = lambda)
  
  # Identify non-zero coefficients
  selected_vars <- rownames(coef_matrix)[which(coef_matrix != 0)]
  
  # Check if any variables were selected
  if (length(selected_vars) == 0) {
    message("No variables were selected at the specified lambda.")
    return(NULL)
  }
  
  # Remove the intercept if present
  selected_vars <- selected_vars[selected_vars != "(Intercept)"]
  
  return(selected_vars)
}

# Extract variables for alpha = 1
selected_vars_a1 <- extract_selected_variables(TheTrainSet.cv.glmnet_cox.alphas$a1)
selected_vars_a1 %>% dput

# Extract variables for alpha = 0.5
selected_vars_a0_5 <- extract_selected_variables(TheTrainSet.cv.glmnet_cox.alphas$a0.5)
selected_vars_a0_5 %>% dput


```


### run_coxph_on_test() ----
### summarize_coxph_model() ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
# Function to create and run Cox PH model on test set
run_coxph_on_test <- function(cv_glmnet_model, train_formula, test_data, lambda = "lambda.min") {
  selected_vars <- extract_selected_variables(cv_glmnet_model, lambda = lambda)
  
  # Construct new formula
  response_vars <- all.vars(train_formula)[1:2]  # Extract response variables
  new_formula <- as.formula(
    paste(response_vars, "~", paste(selected_vars, collapse = " + "))
  )
  
  # Fit Cox PH model on test set
  cox_model <- coxph(new_formula, data = test_data)
  
  return(cox_model)
}

# Function to summarize Cox PH model with exponentiated coefficients
summarize_coxph_model <- function(cox_model, adjust_p = c("fdr", "bonferroni")) {
  if (!inherits(cox_model, "coxph")) {
    stop("Model is not a coxph object.")
  }
  
  # Extract summary
  summary_cox <- summary(cox_model)
  
  # Create a tidy dataframe using broom
  summary_df <- tidy(summary_cox, exponentiate = TRUE, conf.int = TRUE) %>%
    rename(
      Variable = term,
      Hazard_Ratio = estimate,
      CI_lower = conf.low,
      CI_upper = conf.high,
      p_value = p.value
    )
  
  # Adjust p-values
  for (method in adjust_p) {
    adj_col <- paste0("p.adjust.", method)
    summary_df[[adj_col]] <- p.adjust(summary_df$p_value, method = method)
  }
  
  # Add significance stars based on raw p-values
  summary_df <- summary_df %>%
    mutate(
      star = case_when(
        p_value <= 0.001 ~ "***",
        p_value <= 0.01 ~ "** ",
        p_value <= 0.05 ~ "*  ",
        TRUE ~ "   "
      )
    )
  
  # Format the confidence intervals
  summary_df <- summary_df %>%
    mutate(
      CI = paste0("(", round(CI_lower, 2), " ~ ", round(CI_upper, 2), ")"),
      Hazard_Ratio = round(Hazard_Ratio, 2),
      p_value = ifelse(p_value <= 0.001, "<0.001", sprintf("%.3f", p_value))
    )
  
  # Select and arrange columns
  summary_df <- summary_df %>%
    select(Variable, Hazard_Ratio, CI, p_value, star, starts_with("p.adjust."), everything())
  
  return(summary_df)
}

# Function to generate Cox PH summaries for all model combinations
generate_coxph_summaries <- function(glmnet_models, train_formula, test_data, lambdas = c("lambda.min", "lambda.1se")) {
  model_combinations <- expand.grid(
    alpha = c(1, 0.5),
    lambda = lambdas,
    stringsAsFactors = FALSE
  )
  
  coxph_summaries <- list()
  
  for (i in 1:nrow(model_combinations)) {
    i.alpha <- model_combinations$alpha[i]
    lambda_val <- model_combinations$lambda[i]
    
    model_name <- paste0("alpha", i.alpha, "_", lambda_val)
    
    # Retrieve the glmnet model
    glmnet_model <- glmnet_models[[paste0("a", i.alpha)]]
    
    # Run Cox PH model on test set
    cox_model <- run_coxph_on_test(
      cv_glmnet_model = glmnet_model,
      train_formula = train_formula,
      test_data = test_data,
      lambda = lambda_val
    )
    
    # Summarize the model
    summary_df <- summarize_coxph_model(cox_model, adjust_p = c("fdr", "bonferroni"))
    
    # Store the summary with a descriptive name
    coxph_summaries[[model_name]] <- summary_df
  }
  
  return(coxph_summaries)
}

# Generate Cox PH summaries
coxph_summaries <- generate_coxph_summaries(
  glmnet_models = TheTrainSet.cv.glmnet_cox.alphas,
  train_formula = Surv(time = EndTime, event = EndTime.is.Case.confirm.365) ~ .,
  test_data = TheTestSet,
  lambdas = c("lambda.min", "lambda.1se")
)

# # Save Cox PH summaries to Excel
# write.xlsx(coxph_summaries, "CoxPH_Summaries.xlsx", asTable = TRUE)
# 
# # Open the Excel file (optional)
# openXL("CoxPH_Summaries.xlsx")

```
  
  

  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
## pacman::p_load() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# #' Load and install required packages using pacman
# #'
# #' This function checks if the 'pacman' package is installed, installs it if 
# #' necessary, and then uses \code{pacman::p_load()} to efficiently load or 
# #' install a list of required packages.
# #'
# #' @param required_packages A character vector of package names to be loaded or
# #'   installed.
# #'
# #' @examples
# #' required_packages <- c("tidyverse", "glmnet", "useful", "survival")
# #' load_packages(required_packages)
# load_packages <- function(required_packages) {
#   if (!require("pacman")) install.packages("pacman")
#   library(pacman)
#   p_load(char = required_packages, install = TRUE)
# }
# 
# # Load necessary packages
# required_packages <- c(
#   "tidyverse", "glmnet", "useful", "survival", "tableone", 
#   "openxlsx", "broom"
# )
# load_packages(required_packages)



for(.packagename in c("tidyverse", "glmnet", "useful", "survival", "tableone", "openxlsx", "broom")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  

#' Load and Preprocess Data
#'
#' This function loads data from an RDS file, selects specific variables,
#' converts the 'EndTime' variable to numeric, and optionally adds a 'testset'
#' indicator if the data is from a test set.
#'
#' @param file_path The path to the RDS file.
#' @param varnames A character vector of variable names to select.
#' @param is_test Logical indicating whether the data is a test set (default:
#'   FALSE).
#'
#' @return A tibble containing the loaded and preprocessed data.
#'
#' @examples
#' train_data <- load_preprocess_data("train_data.rds", varnames)
#' test_data <- load_preprocess_data("test_data.rds", varnames, is_test = TRUE)
load_preprocess_data <- function(file_path, varnames, is_test = FALSE) {
  data <- readRDS(file_path)[varnames] %>%
    mutate(EndTime = as.numeric(EndTime))
  
  if (is_test) {
    data <- data %>% mutate(testset = TRUE)
  }
  
  return(as_tibble(data))
}

# Define variable names
varnames <- c(
  "EndTime.is.Case.confirm.365", "EndTime", "AgeDecade", "Female", "Income",
  "DisabilityGrade", "AcquiredHypothyroidism", "AdjustmentDisorder", "Anemia",
  "Anxiety", "Arthritis", "AtrialFibrillation", "BenignProstatic",
  "BrainInjury", "Cataract", "ChronicKidney", "Diabetes", "Dysthymia",
  "Epilepsy", "Fibromyalgia_Pain_Fatigue", "Glaucoma", "HearingImpairment",
  "HeartFailure", "Hyperlipidemia", "Hypertension", "IschemicHeart",
  "Migraine_ChronicHeadache", "MobilityImpairments", "Osteoporosis",
  "PelvicFx", "PersonalityDisorders", "SpinalCordInjury", "StrokeTIA",
  "AlzheimerDementia", "LiverDisease", "ObstructiveLungDisease",
  "CancerSurvivors"
)

# Load training and testing datasets
train_file <- "JK02ID.CCW.MIN_Date.ge365.MDD.EndTime.i.recode.bin.4c.EndTimeP.NA_rm.CC69.agg4.4069AgeNum.i2007.1.1.rda"
test_file <- "JK02ID.CCW.MIN_Date.ge365.MDD.EndTime.i.recode.bin.4test.EndTimeP.NA_rm.CC69.agg4.4069AgeNum.i2007.1.1.rda"

TheTrainSet <- load_preprocess_data(train_file, varnames)
TheTestSet  <- load_preprocess_data(test_file, varnames, is_test = TRUE)

#' Create and Export Table One
#'
#' This function creates a Table One summarizing patient characteristics 
#' stratified by a specified variable. It uses the \code{tableone} package to 
#' generate the table and the \code{openxlsx} package to export it to an Excel 
#' file.
#'
#' @param train_data A tibble or data frame containing the training data.
#' @param test_data A tibble or data frame containing the test data.
#' @param strata The variable to stratify by.
#' @param output_file The name of the output Excel file.
#' @param open_file Logical. Should the Excel file be opened after creation? 
#'   Defaults to FALSE.
#'
#' @return A tableone object.
#'
#' @examples
#' create_and_export_table1(
#'   train_data, 
#'   test_data, 
#'   "Treatment", 
#'   "table_one.xlsx", 
#'   open_file = FALSE
#' )
create_and_export_table1 <- function(train_data, test_data, 
                                     strata, output_file, open_file = FALSE) {
  combined_data <- bind_rows(train_data, test_data)
  
  table1 <- CreateTableOne(
    strata = strata,
    data = as.data.frame(combined_data),
    test = FALSE,
    includeNA = TRUE
  )
  
  # Print table with standardized mean differences (SMD)
  print(table1, smd = TRUE, nonnormal = c("AgeDecade", "Income"))
  
  # Export table to Excel
  table_df <- as.data.frame(print(table1, printToggle = FALSE)) %>%
    rownames_to_column(var = "Variable")
  
  write.xlsx(table_df, output_file, asTable = TRUE)
  
  # Open the Excel file (optional)
  if (open_file) {
    openXL(output_file) 
  }
  
  return(invisible(table1))  # Return invisibly
}

# Create and export Table One
create_and_export_table1(
  train_data = TheTrainSet,
  test_data = TheTestSet,
  strata = "EndTime.is.Case.confirm.365",
  output_file = "TheTable1byCase.xlsx"
)

#' Train Cross-Validated glmnet Cox Models
#'
#' This function trains a series of cross-validated Cox proportional hazards 
#' models using \code{glmnet} for a specified range of alpha (elastic net 
#' mixing parameter) values. It provides options for saving the trained models,
#' generating cross-validation plots, and customizing the output directory.
#'
#' @param train_data A tibble or data frame containing the training data.
#' @param formula A formula object specifying the model.
#' @param alphas A numeric vector of alpha values (mixing parameter for elastic
#'   net). Default is \code{c(1, 0.5)}.
#' @param family A character string specifying the glmnet family. 
#'   Default is \code{"cox"}.
#' @param type_measure A character string specifying the type of measure for
#'   cross-validation. Default is \code{"deviance"}.
#' @param nfolds The number of folds for cross-validation. Default is 5.
#' @param seed An integer seed for reproducibility. Default is 1.
#' @param save_models Logical indicating whether to save the trained models as
#'   RDS files (default: TRUE).
#' @param save_plots Logical indicating whether to save cross-validation plots
#'   (default: TRUE).
#' @param plot_size The size of the plots in pixels (default: 1280).
#' @param output_dir The directory to save the models and plots (default:
#'   "glmnet_outputs").
#'
#' @return A named list of trained \code{cv.glmnet} models, where each element's 
#'   name corresponds to the alpha value used for training.
#'
#' @examples
#' glmnet_models <- f_df.cv.glmnet_cox(
#'   train_data = train_data,
#'   formula = Surv(time, status) ~ .,
#'   alphas = c(1, 0.5),
#'   nfolds = 10,
#'   seed = 123
#' )
f_df.cv.glmnet_cox <- function(
  train_data,
  formula,
  alphas = c(1, 0.5),
  family = "cox",
  type_measure = "deviance",
  nfolds = 5,
  seed = 1,
  save_models = TRUE,
  save_plots = TRUE,
  plot_size = 1280,
  output_dir = "glmnet_outputs"
) {
  # Ensure output directory exists
  if (!dir.exists(output_dir)) {
    dir.create(output_dir, recursive = TRUE)
  }
  
  set.seed(seed)
  
  # Prepare model matrix
  x <- model.matrix(formula, data = train_data)[, -1]  # Remove intercept
  
  # Extract response variable
  y <- model.response(model.frame(formula, data = train_data))
  
  # Initialize list to store models
  glmnet_models <- list()
  
  # Iterate over each alpha
  for (i.alpha in alphas) {
    message(paste("Training glmnet model with alpha =", i.alpha))
    
    # Train cross-validated glmnet model
    cv_glmnet_object <- cv.glmnet(
      x = x,
      y = y,
      alpha = i.alpha,
      family = family,
      type.measure = type_measure,
      nfolds = nfolds
    )
    
    # Save model if required
    if (save_models) {
      model_FileName <- here::here(output_dir, paste0("cv_glmnet_a", i.alpha, ".rds"))
      saveRDS(cv_glmnet_object, model_FileName)
      message(paste("Saved model to", model_FileName))
    }
    
    # Plot cross-validation results if required
    if (save_plots) {
      plot_FileName <- here::here(output_dir, paste0("cv_glmnet_a", i.alpha, "_plot.png"))
      png(plot_FileName, width = plot_size, height = plot_size, units = "px", bg = "transparent")
      plot(cv_glmnet_object, main = paste("Alpha =", i.alpha))
      dev.off()
      message(paste("Saved plot to", plot_FileName))
    }
    
    # Store the model in the list
    glmnet_models[[paste0("a", i.alpha)]] <- cv_glmnet_object
  }
  
  return(glmnet_models)
}

# Train glmnet Cox models
TheTrainSet.cv.glmnet_cox.alphas <- f_df.cv.glmnet_cox(
  train_data = TheTrainSet,
  formula = Surv(time = EndTime, event = EndTime.is.Case.confirm.365) ~ .,
  alphas = c(1, 0.5),
  seed = 123  # Changed seed for reproducibility
)

# Save all glmnet models for future use
saveRDS(TheTrainSet.cv.glmnet_cox.alphas, file = "TheTrainSet.cv.glmnet_cox.alphas.rds")

#' Extract Selected Variables
#'
#' This function extracts the names of variables with non-zero coefficients from
#' a \code{cv.glmnet} model at a specified lambda value.
#'
#' @param cv_glmnet_model A \code{cv.glmnet} model object.
#' @param lambda A character string specifying the lambda value to use 
#'   (e.g., "lambda.min", "lambda.1se"). Default is "lambda.min".
#'
#' @return A character vector of selected variable names.
#'
#' @examples
#' selected_vars <- extract_selected_variables(cv_glmnet_object, lambda = "lambda.1se")
extract_selected_variables <- function(cv_glmnet_model, lambda = "lambda.min") {
  # Extract coefficients at specified lambda
  coef_matrix <- coef(cv_glmnet_model, s = lambda)
  
  # Identify non-zero coefficients
  selected_vars <- rownames(coef_matrix)[which(coef_matrix != 0)]
  
  # Remove the intercept if present
  selected_vars <- selected_vars[selected_vars != "(Intercept)"]
  
  return(selected_vars)
}

#' Run Cox PH Model on Test Set
#'
#' This function takes a trained \code{cv.glmnet} model, extracts the selected
#' variables (those with non-zero coefficients), constructs a new formula with
#' these variables, and fits a Cox proportional hazards model (\code{coxph}) on
#' a test dataset.
#'
#' @param cv_glmnet_model A \code{cv.glmnet} model object.
#' @param train_formula The formula used to train the \code{cv.glmnet} model.
#' @param test_data A tibble or data frame containing the test data.
#' @param lambda A character string specifying the lambda value to use for
#'   variable selection (e.g., "lambda.min", "lambda.1se"). Default is
#'   "lambda.min".
#'
#' @return A \code{coxph} model object fit on the test data using the selected
#'   variables.
#'
#' @examples
#' cox_model <- run_coxph_on_test(cv_glmnet_object, Surv(time, status) ~ ., test_data)
run_coxph_on_test <- function(cv_glmnet_model, train_formula, test_data, lambda = "lambda.min") {
  selected_vars <- extract_selected_variables(cv_glmnet_model, lambda = lambda)
  
  # Construct new formula
  response_vars <- all.vars(train_formula)[1:2]  # Extract response variables
  new_formula <- as.formula(
    paste(response_vars, "~", paste(selected_vars, collapse = " + "))
  )
  
  # Fit Cox PH model on test set
  cox_model <- coxph(new_formula, data = test_data)
  
  return(cox_model)
}

#' Summarize Cox PH Model
#'
#' This function summarizes a fitted Cox proportional hazards model 
#' (\code{coxph}) and formats the output into a tidy data frame. It includes 
#' options for adjusting p-values and adding significance stars.
#'
#' @param cox_model A \code{coxph} model object.
#' @param adjust_p A character vector of methods for adjusting p-values 
#'   (e.g., "fdr", "bonferroni"). Default is \code{c("fdr", "bonferroni")}.
#'
#' @return A tibble containing the summarized model results with exponentiated
#'   coefficients (hazard ratios), confidence intervals, p-values, adjusted
#'   p-values, and significance stars.
#'
#' @examples
#' summary_df <- summarize_coxph_model(cox_model)
summarize_coxph_model <- function(cox_model, adjust_p = c("fdr", "bonferroni")) {
  if (!inherits(cox_model, "coxph")) {
    stop("Model is not a coxph object.")
  }
  
  # Extract summary
  summary_cox <- summary(cox_model)
  
  # Create a tidy dataframe using broom
  summary_df <- tidy(summary_cox, exponentiate = TRUE, conf.int = TRUE) %>%
    rename(
      Variable = term,
      Hazard_Ratio = estimate,
      CI_lower = conf.low,
      CI_upper = conf.high,
      p_value = p.value
    )
  
  # Adjust p-values
  for (method in adjust_p) {
    adj_col <- paste0("p.adjust.", method)
    summary_df[[adj_col]] <- p.adjust(summary_df$p_value, method = method)
  }
  
  # Add significance stars based on raw p-values
  summary_df <- summary_df %>%
    mutate(
      star = case_when(
        p_value <= 0.001 ~ "***",
        p_value <= 0.01 ~ "** ",
        p_value <= 0.05 ~ "*  ",
        TRUE ~ "   "
      )
    )
  
  # Format the confidence intervals
  summary_df <- summary_df %>%
    mutate(
      CI = paste0("(", round(CI_lower, 2), " ~ ", round(CI_upper, 2), ")"),
      Hazard_Ratio = round(Hazard_Ratio, 2),
      p_value = ifelse(p_value <= 0.001, "<0.001", sprintf("%.3f", p_value))
    )
  
  # Select and arrange columns
  summary_df <- summary_df %>%
    select(Variable, Hazard_Ratio, CI, p_value, star, starts_with("p.adjust."), everything())
  
  return(summary_df)
}

#' Generate Cox PH Summaries
#'
#' This function generates summaries for Cox proportional hazards models fit on
#' a test dataset using variables selected from trained \code{cv.glmnet} models.
#' It iterates through combinations of alpha and lambda values, extracts
#' selected variables, fits \code{coxph} models, and summarizes the results.
#'
#' @param glmnet_models A named list of \code{cv.glmnet} model objects, where
#'   names correspond to alpha values.
#' @param train_formula The formula used to train the \code{cv.glmnet} models.
#' @param test_data A tibble or data frame containing the test data.
#' @param lambdas A character vector of lambda values to use for variable
#'   selection (e.g., "lambda.min", "lambda.1se"). Default is
#'   \code{c("lambda.min", "lambda.1se")}.
#'
#' @return A named list of tibbles, where each tibble contains a summarized
#'   \code{coxph} model for a specific combination of alpha and lambda.
#'
#' @examples
#' coxph_summaries <- generate_coxph_summaries(
#'   glmnet_models, 
#'   Surv(time, status) ~ ., 
#'   test_data
#' )
generate_coxph_summaries <- function(
  glmnet_models, 
  train_formula, 
  test_data, 
  lambdas = c("lambda.min", "lambda.1se")
) {
  model_combinations <- expand.grid(
    alpha = names(glmnet_models),
    lambda = lambdas,
    stringsAsFactors = FALSE
  )
  
  coxph_summaries <- list()
  
  for (i in 1:nrow(model_combinations)) {
    i.alpha <- model_combinations$alpha[i]
    lambda_val <- model_combinations$lambda[i]
    
    model_name <- paste0(i.alpha, "_", lambda_val)
    
    # Retrieve the glmnet model
    glmnet_model <- glmnet_models[[i.alpha]]
    
    # Run Cox PH model on test set
    cox_model <- run_coxph_on_test(
      cv_glmnet_model = glmnet_model,
      train_formula = train_formula,
      test_data = test_data,
      lambda = lambda_val
    )
    
    # Summarize the model
    summary_df <- summarize_coxph_model(cox_model)
    
    # Store the summary with a descriptive name
    coxph_summaries[[model_name]] <- summary_df
  }
  
  return(coxph_summaries)
}

# Generate Cox PH summaries
coxph_summaries <- generate_coxph_summaries(
  glmnet_models = TheTrainSet.cv.glmnet_cox.alphas,
  train_formula = Surv(time = EndTime, event = EndTime.is.Case.confirm.365) ~ .,
  test_data = TheTestSet
)

# # Save Cox PH summaries to Excel
# write.xlsx(coxph_summaries, "CoxPH_Summaries.xlsx", asTable = TRUE)

# Open the Excel file (optional)
# openXL("CoxPH_Summaries.xlsx")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ SOURCE) ----  
```{r RUN-ALL-CHUNKS-ABOVE, echo=FALSE, results="hide", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
```


```{r .RelativeSubPath_FileName.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
options(DEVMODE = TRUE);  # isTRUE(getOption("DEVMODE"))
# .RelativeSubPath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(env1$f$f_object.is_not_null.nor_na.nor_blank(env1$path$LastSourceEditorContext.path_FileNameExt)) {    .RelativeSubPath = env1$path$LastSourceEditorContext.path_FileNameExt |> dirname() |> env1$f$f_path.relative()  ;    ".RelativeSubPath" |> env1$f$f_ObjectName.get.dput.ECHO()    }
# if(.RelativeSubPath!="") .RelativeSubPath |> normalizePath(winslash="/",mustWork=TRUE) |> utils::browseURL() |> try()
# .FileName.source.r = "default.template" |> paste0(".source.r")
if(env1$f$f_object.is_not_null.nor_na.nor_blank(env1$path$LastSourceEditorContext.path_FileNameExt)) {    .SourceName_root = env1$path$LastSourceEditorContext.path_FileNameExt |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),"")  ;    ".SourceName_root" |> env1$f$f_ObjectName.get.dput.ECHO()    }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.RelativeSubPath = .RelativeSubPath
if(!exists(".SourceName_root") && exists(".FileName.source.r")) .SourceName_root = .FileName.source.r |> str_replace("\\.source\\.r$", "")
.FileName.source.r = .SourceName_root |> paste0(".source.r")
env1$path$.SourceName_root = .SourceName_root
env1$path$.RelativeSubPath_FileName.dev.r = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".dev.r")
env1$path$.RelativeSubPath_FileName.dev.Rmd = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".dev.Rmd")
env1$path$.RelativeSubPath_FileName.source.r = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".source.r")
cat("# ",'.SourceName_root = "',.SourceName_root,'"  \n',
    "#### ",env1$path$.RelativeSubPath_FileName.dev.r, "----  \n",
    "#### ",env1$path$.RelativeSubPath_FileName.dev.Rmd, "----  \n",
    "#### ",env1$path$.RelativeSubPath_FileName.source.r, "----  \n",
    '# # source(paste0(env1$path$source_base,"/","',env1$path$.RelativeSubPath_FileName.source.r,'"))', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'")', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( here::here(env1$path$source_base,.RelativeSubPath_FileName.source.r) )  ----  
# env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = list(.RelativeSubPath, .FileName.source.r) %>% {.[nzchar(.)]} %>% c(fsep = "/") %>% {do.call(here::here, .)})
```
  
  
# __________|------  
# @@ START) function ----  
## \% |> create_summary_table()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Install and load required libraries
if (!require("glmnet")) install.packages("glmnet")
if (!require("flextable")) install.packages("flextable")
library(glmnet)
library(flextable)

# Define the function
create_summary_table <- function(dataset, byVar, alpha = 1, create_flextable = FALSE) {
  # Prepare data
  x <- model.matrix(as.formula(paste("~ . -", byVar)), data = dataset)
  y <- dataset[[byVar]]
  
  # Print intermediate values for debugging
  print("x:")
  print(head(x)) # Print the first few rows of x
  print("y:")
  print(head(y)) # Print the first few values of y
  
  # Perform lasso/elastic net regression
  # Force lambda to be numeric to avoid potential issues
  lambda_seq <- as.numeric(seq(0.01, 1, by = 0.01))
  print("lambda sequence:")
  print(head(lambda_seq)) # Print the first few lambda values
  model <- glmnet(x, y, alpha = alpha, lambda = lambda_seq) 

  # Extract lambda.min from the model object
  lambda.min <- model$lambda.min
  print("lambda.min:")
  print(lambda.min) # Print the value of lambda.min

  # Extract coefficients and other statistics (example)
  coefficients <- coef(model, s = lambda.min)
  # ... extract other statistics as needed ...
  
  # Create a data frame for the table
  table_data <- data.frame(
    Variable = rownames(coefficients),
    Coefficient = coefficients[, 1]
    # ... add other statistics to the data frame ...
  )
  
  if (create_flextable) {
      # Create and format the flextable
      ft <- flextable(table_data)
      ft <- set_header_labels(ft, Variable = "Variable", Coefficient = "Coefficient")
      # ... add other formatting options as desired ...
      return(ft)
  } else {
      return(table_data)
  }
}



```
  
  
###### \% df_5vars_10obs |> create_summary_table() ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

# Use the provided dataset (same as before)
df_5vars_10obs <- data.frame(
  Group = rep(c("Group1", "Group2"), each = 5),
  Var1 = c(2.5, 3.0, 2.8, 2.9, 3.1, 3.6, 3.7, 3.5, 3.8, 3.9),
  Var2 = c(7.1, 7.3, 7.2, 7.4, 7.5, 6.8, 6.9, 7.0, 6.7, 6.6),
  Var3 = c(15, 16, 15, 14, 15, 18, 17, 19, 18, 17),
  Var4 = c(0.5, 0.6, 0.55, 0.58, 0.57, 0.65, 0.66, 0.64, 0.67, 0.68),
  Var5 = c(100, 105, 102, 101, 103, 110, 112, 111, 113, 114)
)

# Apply the create_summary_table function
lasso_table <- create_summary_table(dataset = df_5vars_10obs, byVar = "Var1", alpha = 1)

# Print the table
print(lasso_table)
```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
library(reticulate)
system("python2 --version")
system("python3 --version")
```


```{py, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
import pandas as pd
from sklearn.linear_model import Lasso
from sklearn.preprocessing import StandardScaler
import numpy as np

# Define the function
def create_summary_table(dataset, byVar, alpha=1):
    # Prepare data
    X = dataset.drop(byVar, axis=1)
    if 'Group' in X:
      X = pd.get_dummies(X, columns=['Group'], drop_first=True)
    y = dataset[byVar]

    # Perform lasso/elastic net regression
    scaler = StandardScaler()
    X_scaled = scaler.fit_transform(X)

    # Generate a lambda sequence
    lambdas = np.logspace(-4, 4, 100)

    model = Lasso(alpha=alpha)
    model.fit(X_scaled, y)

    # Extract coefficients and other statistics (example)
    coefficients = model.coef_
    intercept = model.intercept_

    # Create a data frame for the table
    table_data = pd.DataFrame({
        'Variable': X.columns,
        'Coefficient': coefficients
    })

    # Add intercept to table_data
    table_data.loc[len(table_data)] = ['Intercept', intercept]

    return table_data

# Use the provided dataset
df_5vars_10obs = pd.DataFrame({
    'Group': ['Group1'] * 5 + ['Group2'] * 5,
    'Var1': [2.5, 3.0, 2.8, 2.9, 3.1, 3.6, 3.7, 3.5, 3.8, 3.9],
    'Var2': [7.1, 7.3, 7.2, 7.4, 7.5, 6.8, 6.9, 7.0, 6.7, 6.6],
    'Var3': [15, 16, 15, 14, 15, 18, 17, 19, 18, 17],
    'Var4': [0.5, 0.6, 0.55, 0.58, 0.57, 0.65, 0.66, 0.64, 0.67, 0.68],
    'Var5': [100, 105, 102, 101, 103, 110, 112, 111, 113, 114]
})

# Apply the create_summary_table function
lasso_table = create_summary_table(dataset=df_5vars_10obs, byVar='Var1', alpha=1)

# Print the table
print(lasso_table.to_markdown(index=False, numalign="left", stralign="left"))
```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
  
```{r createBACKUP, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%dT%H", overwrite=TRUE)
        # env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%dT%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$LastSourceEditorContext.path_FileName.pdf = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$LastSourceEditorContext.path_FileName.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (Sys.info()["sysname"] == "Windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$LastSourceEditorContext.path_FileNameExt)),', output_format = "pdf_document")  \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
        .path_file = env1$path$LastSourceEditorContext.path_FileName.pdf
        env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE)
        env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = .path_file, .BACKUP_to_path="-BACKUP", timeFormat="%y%m%dT%H", overwrite=TRUE)
        try(env1$env.internal.attach$f_file_PDF.sumatra(.path_file))
    }
}
# env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_FileName.pdf; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = ',deparse(.path_file),', .BACKUP_to_path="-BACKUP", timeFormat="%y%m%dT%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal.attach$f_file_PDF.sumatra(',deparse(.path_file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path_file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_FileName.html; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = ',deparse(.path_file),', .BACKUP_to_path="-BACKUP", timeFormat="%y%m%dT%H", overwrite=TRUE)  \n', sep=""); cat('  env1$env.internal.attach$f_URL.browse_in_edge_app(',deparse(.path_file),')  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_FileName.nb.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") {  try(  paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE),'"') |> shell(wait=FALSE)  )  }  # else { browseURL(env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE)) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileNameExt) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileName.nb.html) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
