---
##HHHHHHHHHHHHHHHHHH BEGINNING OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##  
# TABLE OF CONTENTS (level 1) ----  
# @@ REFERENCES)                                                            #L247
# @@ DATA) example                                                          #L256
# @@ START) dev                                                             #L276
# @@ SOURCE)                                                                #L311
# @@ START) function                                                        #L353
# @@ MetaData) Read & Check                                                 #L402
# @@ DATA) Read & Check                                                     #L472
# @@ ANALYSIS) (Breif) byVar =                                              #L638
# @@ DATA) mutate()                                                         #L644
# @@ DATA) filter() -> New DS                                               #L675
# @@ DATA) select(matches(VarName.suffix.regex))                            #L708
# @@ ANALYSIS) byVar =                                                      #L722
##HHHHHHHHHHHHHHHHHHHH THE END OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##   
##HHHHHHHHHHHHHHHHHH BEGINNING OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##  
# TABLE OF CONTENTS (level 1) ----  
# @@ REFERENCES)                                                            # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L247
# @@ DATA) example                                                          # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L256
# @@ START) dev                                                             # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L276
# @@ SOURCE)                                                                # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L311
# @@ START) function                                                        # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L353
# @@ MetaData) Read & Check                                                 # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L402
# @@ DATA) Read & Check                                                     # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L472
# @@ ANALYSIS) (Breif) byVar =                                              # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L638
# @@ DATA) mutate()                                                         # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L644
# @@ DATA) filter() -> New DS                                               # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L675
# @@ DATA) select(matches(VarName.suffix.regex))                            # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L708
# @@ ANALYSIS) byVar =                                                      # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L722
##HHHHHHHHHHHHHHHHHHHH THE END OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##   
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  # - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd())  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_FileNameExt ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# .tmp$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) not a relative path~!  
# env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) Not using a relative path~!
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .FileName.source.r = "f_DSN.Search.read.checkEntity" |> paste0(".source.r"); .RelativeSubPath=r"()"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = list(.RelativeSubPath, .FileName.source.r) %>% {.[nzchar(.)]} %>% c(fsep = "/") %>% {do.call(file.path, .)})
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  
```
  
  
# __________|------  
# @@ REFERENCES) ----  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ DATA) example ----  
## \$ ADS_time2event =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# suppressPackageStartupMessages(library(survival))
for(.packagename in c("survminer")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
# ?survival::lung
.objectname = DSN = "ADS_time2event"
assign(
    DSN, 
    survival::lung |> as_tibble() |> mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] |> as.factor(), StudyPopulation = time >= 30) |>
        # dplyr::select(-status, -sex)
        dplyr::select(-status)
)
ADS_time2event %>% {cat(" > ",deparse(substitute(.))," |> as_tibble() |> print()","  \n", sep=""); print(as_tibble(.))}
```
  
  
# __________|------  
# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```
  
  
## \% ADS_time2event |>  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ SOURCE) ----  
```{r RUN-ALL-CHUNKS-ABOVE, echo=FALSE, results="hide", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
```


```{r .RelativeSubPath_FileName.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
options(DEVMODE = TRUE);  # isTRUE(getOption("DEVMODE"))
# .RelativeSubPath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(env1$f$f_object.is_not_null.nor_na.nor_blank(env1$path$LastSourceEditorContext.path_FileNameExt)) {    .RelativeSubPath = env1$path$LastSourceEditorContext.path_FileNameExt |> dirname() |> env1$f$f_path.relative()  ;    ".RelativeSubPath" |> env1$f$f_ObjectName.get.dput.ECHO()    }
# if(.RelativeSubPath!="") .RelativeSubPath |> normalizePath(winslash="/",mustWork=TRUE) |> utils::browseURL() |> try()
# .FileName.source.r = "default.template" |> paste0(".source.r")
if(env1$f$f_object.is_not_null.nor_na.nor_blank(env1$path$LastSourceEditorContext.path_FileNameExt)) {    .SourceName_root = env1$path$LastSourceEditorContext.path_FileNameExt |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),"")  ;    ".SourceName_root" |> env1$f$f_ObjectName.get.dput.ECHO()    }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.RelativeSubPath = .RelativeSubPath
if(!exists(".SourceName_root") && exists(".FileName.source.r")) .SourceName_root = .FileName.source.r |> str_replace("\\.source\\.r$", "")
.FileName.source.r = .SourceName_root |> paste0(".source.r")
env1$path$.SourceName_root = .SourceName_root
env1$path$.RelativeSubPath_FileName.dev.r = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".dev.r")
env1$path$.RelativeSubPath_FileName.dev.Rmd = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".dev.Rmd")
env1$path$.RelativeSubPath_FileName.source.r = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".source.r")
cat("# ",'.SourceName_root = "',.SourceName_root,'"  \n',
    "#### ",env1$path$.RelativeSubPath_FileName.dev.r, "----  \n",
    "#### ",env1$path$.RelativeSubPath_FileName.dev.Rmd, "----  \n",
    "#### ",env1$path$.RelativeSubPath_FileName.source.r, "----  \n",
    '# # source(paste0(env1$path$source_base,"/","',env1$path$.RelativeSubPath_FileName.source.r,'"))', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'")', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.RelativeSubPath_FileName.source.r) )  ----  
# env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = list(.RelativeSubPath, .FileName.source.r) %>% {.[nzchar(.)]} %>% c(fsep = "/") %>% {do.call(file.path, .)})
```
  
  
# __________|------  
# @@ START) function ----  
## :: function_name = function() -dev -pending  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## ->> Not Yet included in env1$env.internal.source.r ----
## ->> Not Yet included in f_df.t.tribble_construct.source.r ----

##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## :: function_name = function() ====
## Rdev/00_base_program/001_base_file/function_name.dev.Rmd
.tmp$env1_subenv_name = "env.internal"
.tmp$objectname = "function_name" 
env1[[.tmp$env1_subenv_name]][[.tmp$objectname]] = function(input_object) {
    output_object = input_object
    invisible()
}
```
  
  
### \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ MetaData) Read & Check ----  
```{r MetaData0-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
## .GlobalEnv$MetaData = list() ====  
env1$path$LastSourceEditorContext.path_FileName.MetaData.rds = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".MetaData.rds")
if(file.exists(env1$path$LastSourceEditorContext.path_FileName.MetaData.rds)) { 
    .MetaData0 = env1$path$LastSourceEditorContext.path_FileName.MetaData.rds |> read_rds() 
}
if(!exists("MetaData", envir=.GlobalEnv)) { assign("MetaData", list(), envir=.GlobalEnv) }  
.parentname = "MetaData"
# for (.sublistname in c("tblVarName", "DSNs", "VarNames", "VarNames.select", "VarNames.filter", "VarNames.recode", "ModelList")) {
for (.sublistname in c("tblVarName", "DSNs", "VarNames", "VarNames.select", "ModelList")) {
    if(!.sublistname %in% names(.GlobalEnv[[.parentname]])) { .GlobalEnv[[.parentname]][[.sublistname]] = list() }
}

### # MetaData\$ModelList  ====   
.parentname = "MetaData"; 
.sublistname = "ModelList"; 
for (.sub2listname in c("time2DM", "time2HTN", "time2DL", "time2MetS")) {
    if(!.sub2listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]])) { .GlobalEnv[[.parentname]][[.sublistname]] = list() }
}

### # MetaData\$VarNames  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
for (.sub2listname in c("Event", "Mediator", "Exposure", "PMHx", "Tx", "FHx", "Exam", "Social", "Behavioral", "Unclassified", "Calculated")) {
    if(!.sub2listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]])) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]] = list() }
}

#### \$ MetaData\$VarNames\$Event  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Event"; 
for (.sub3listname in c("DM", "HTN", "DL", "MetS")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

#### \$ MetaData\$VarNames\$Mediator  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Mediator"; 
for (.sub3listname in c("BMI", "Waist")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

#### \$ MetaData\$VarNames\$Exposure  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Exposure"; 
for (.sub3listname in c("Exercise", "Diet", "Alcohol", "Smoking")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

#### \$ MetaData\$VarNames\$Demographic  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Social"; 
for (.sub3listname in c("Age", "Sex", "Income", "Education", "Residence", "Marriage")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

if(exists(".MetaData0", envir=.GlobalEnv)) { 
    ".MetaData0 |> str(max.level = 2, give.attr = TRUE)" %>% {cat("> ", ., "  \n", sep = "")}
    .MetaData0 |> str(max.level = 2, give.attr = TRUE)
} else { .MetaData0 = MetaData }
"MetaData |> str(max.level = 2, give.attr = TRUE)" %>% {cat("> ", ., "  \n", sep = "")}
MetaData |> str(max.level = 2, give.attr = TRUE)
```
  
  
# __________|------  
# @@ DATA) Read & Check-----
```{r RUN-ALL-CHUNKS-ABOVE, echo=FALSE, results="hide", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
# .packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# #@@ START) data -----
# ## \$  DSN |> paste0(".rds") %>% paste0(.path4read.RelativeSubPath,ifelse(.path4read.RelativeSubPath=="","","/"),.) |> read_rds() %>% assign(DSN, value = ., envir = .GlobalEnv) ====
# .path4read.RelativeSubPath = r"(data)"|>str_replace_all("\\\\","/")
# DSN = "CohortGJ0910.BaselineJKGJ2085NoHx...01"
# # # .path4read.RelativeSubPath_FileNameExt = DSN |> paste0(".rds") %>% paste0(.path4read.RelativeSubPath,ifelse(.path4read.RelativeSubPath=="","","/"),.)
# # # .path_FileNameExt = ifelse( file.exists(.path4read.RelativeSubPath_FileNameExt), .path4read.RelativeSubPath_FileNameExt, paste0(env1$path$source_base_github,"/data/",DSN,".rds") )
# # # cat(".path_FileNameExt = ", .path_FileNameExt, "  \n", sep = "")
# #  DSN |> paste0(".rds") %>% paste0(.path4read.RelativeSubPath,ifelse(.path4read.RelativeSubPath=="","","/"),.) |> read_rds() %>% assign(DSN, value = ., envir = .GlobalEnv)
# if(!exists("DSN0")) {DSN0 = DSN; cat('  Setting DSN0 = "',DSN0,'"  \n', sep="")}
# MetaData$DSNs[[DSN]] = env1$f$f_DSN.Search.read.checkEntity(DSN=DSN,ext="rds", .path4read=.path4read|>paste0(ifelse(.path4read.RelativeSubPath=="","","/"),.path4read.RelativeSubPath), return.output = TRUE)
```
  
  
## \$ ADS_time2event =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}
# suppressPackageStartupMessages(library(survival))
for(.packagename in c("survminer")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
# ?survival::lung
.objectname = DSN = "ADS_time2event"
assign(
    DSN, 
    survival::lung |> as_tibble() |> mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] |> as.factor(), StudyPopulation = time >= 30) |>
        # dplyr::select(-status, -sex)
        dplyr::select(-status)
)
ADS_time2event %>% {cat(" > ",deparse(substitute(.))," |> as_tibble() |> print(n=9)","  \n", sep=""); print(as_tibble(.),n=9)}
ADS_time2event %>% {cat(" > ",deparse(substitute(.))," |> rownames_to_column() |> tail() |> as_tibble()","  \n", sep=""); print(as_tibble(tail(rownames_to_column(.))))}
# survival::lung |> dplyr::select(sex) %>% mutate(Group = c("Male", "Female")[.$sex] |> as.factor()) %>% {cat("> ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)}
# survival::lung |> dplyr::select(sex) %>% mutate(Group = c("Male", "Female")[.$sex] |> as.factor()) |> table(useNA="always") |> addmargins()
# # > survival::lung |> dplyr::select(sex) %>% mutate(Group = c("Male", "Female")[.$sex] |> as.factor()) %>% {cat("> ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)}
# # 'data.frame':	228 obs. of  2 variables:
# #  $ sex  : num  1 1 1 1 1 1 2 2 1 1 ...
# #  $ Group: Factor w/ 2 levels "Female","Male": 2 2 2 2 2 2 1 1 2 2 ...
# # > survival::lung |> dplyr::select(sex) %>% mutate(Group = c("Male", "Female")[.$sex] |> as.factor()) |> table(useNA="always") |> addmargins()
# #    Group
# # sex Female Male
# #   1      0  138
# #   2     90    0
# 
# cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
# ADS_time2event |> dplyr::select(time, event, Group, StudyPopulation) %>% by(.$StudyPopulation, summary)
# # > ADS_time2event |> dplyr::select(time, event, Group, StudyPopulation) %>% by(.$StudyPopulation, summary)
# # .$StudyPopulation: FALSE
# #       time     event            Group   StudyPopulation
# #  Min.   : 5   Mode:logical   Female:1   Mode :logical  
# #  1st Qu.:11   TRUE:9         Male  :8   FALSE:9        
# #  Median :12                                            
# #  Mean   :13                                            
# #  3rd Qu.:13                                            
# #  Max.   :26                                            
# # ----  
# # .$StudyPopulation: TRUE
# #       time          event            Group     StudyPopulation
# #  Min.   :  30.0   Mode :logical   Female: 89   Mode:logical   
# #  1st Qu.: 176.5   FALSE:63        Male  :130   TRUE:219       
# #  Median : 269.0   TRUE :156                                   
# #  Mean   : 317.2                                               
# #  3rd Qu.: 419.5                                               
# #  Max.   :1022.0   
  
```
  
  
### ---- < Key Variables Check > ----  
#### \$ varname4ID  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# source("https://raw.githubusercontent.com/mkim0710/tidystat/master/Rdev/10_import_clean_datatype/13_missing_value/f_df.NotNA_p_df.source.r")
# --> Now included in "f_df.t.tribble_construct.source.r"
  
varname4ID = c("ID", "CompositeKey", "PERSON_ID", "RN_INDI", "NIHID")
get(DSN)[intersect(varname4ID, colnames(get(DSN)))] |> str(max.level = 2, give.attr = TRUE)
get(DSN) |> dim()
get(DSN)[intersect(varname4ID, colnames(get(DSN)))] |> n_distinct()
get(DSN)[intersect(varname4ID, colnames(get(DSN)))] |> env1$f$f_df.NotNA_p_df()
  
varname4CompositKey = c("age", "sex")
vecCompositeKey = get(DSN)[intersect(varname4CompositKey, colnames(get(DSN)))] |> apply(MARGIN = 1, paste0, collapse = "-")
vecCompositeKey |> n_distinct()
```
  
  
#### \$ .varname4outcome ----  
#### \$ varname4time ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.varname4outcome = "event"
varname4time = c("time", "age")
get(DSN)[c(.varname4outcome, varname4time)] |> 
    mutate_if(is.factor, as.character) |>  
    mutate_if(is.character, na_if, "") |> mutate_if(is.character, na_if, "N/A") |> mutate_if(is.character, na_if, "NA") |> 
    mutate_if(is.character, as.factor) |> 
    summary()
  
```
  
  
##### \$ varname4measures ----  
##### \$ varname4labs ----  
##### \$ varname4lifestyle ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
### ---- < Data Availability Check > ----  
#### \$ DS.Date.NA  ----  
##### \% f_df.NotNA_p_df() ----  
#### \$ DS.DNR  ----  
```{r DS.Date.NA-f_df.NotNA_p_df-NoEcho, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# source("https://raw.githubusercontent.com/mkim0710/tidystat/master/Rdev/10_import_clean_datatype/13_missing_value/f_df.NotNA_p_df.source.r")
# --> Now included in "f_df.t.tribble_construct.source.r"
  
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
if(!exists("DSN.Date")) DSN.Date = ifelse(exists(paste0(DSN,".Date")), paste0(DSN,".Date"), DSN)
.vec_nlevel_lt20.value_number.unique = 'get(DSN.Date) %>% map(function (vec) {vec.unique = unique(vec); if(length(vec.unique) < 20) return(vec.unique) else return(NULL) }) %>% unlist %>% unique %>% str_subset("^[0-9]+$") %>% sort' |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = TRUE, LinePrefix4CodeText = "> ", LinePrefix4Output = "", CodeEqualsOutput = FALSE)
.vec_nlevel_lt20.value_number.unique |> str(max.level = 2, give.attr = TRUE)
intersect(outer(5:9, 3:5, function(x, y) strrep(x, y)), .vec_nlevel_lt20.value_number.unique) %>% dput
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
DSN.Date.NA = DSN.Date |> paste0(".NA"); assign( DSN.Date.NA, get(DSN.Date) |> mutate_if(is.factor, as.character) ); MetaData$DSNs[[DSN.Date.NA]] = list(DSN = DSN.Date.NA)
.vec_value4NA = c( "", "N/A", "NA"); cat("    ",".vec_value4NA == ",deparse(.vec_value4NA),"  \n", sep="")
for (.value4NA in .vec_value4NA) {
    DSN.Date.NA = DSN.Date |> paste0(".NA"); assign( DSN.Date.NA, get(DSN.Date.NA) |> mutate_if(is.character, na_if, .value4NA) )
}
DSN.DNR = paste0(DSN,".DNR"); assign( DSN.DNR, get(DSN.Date.NA) |> select_if(function(vec) !all(is.na(vec))) ); MetaData$DSNs[[DSN.DNR]] = list(DSN = DSN.DNR)
cat(" dim(",DSN.Date,") == ",deparse(dim(get(DSN.Date))),"  \n", sep="") 
cat(" dim(",DSN.DNR,") == ",deparse(dim(get(DSN.DNR))),"  \n", sep="") 
DS.DNR = get(DSN.DNR)
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
"get(DSN.Date.NA) |> env1$f$f_df.NotNA_p_df()" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
```
  
  
### ---- < DS Summary > ----  
#### \$ DS.DNR.lbl_pending.fct  ----
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
vec_candidate4ID = c("rowname", "rownum", "Num", "ID", "CompositeKey", "PERSON_ID", "RN_INDI", "NIHID")
for (varname in vec_candidate4ID) {if(varname %in% names(get(DSN.DNR))) cat(" n_distinct(",DSN.DNR,"$",varname,") == ",n_distinct(get(DSN.DNR)[[varname]]),"  \n", sep="")}
  
  
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n"); 
"ADS_time2event.DNR |> select_if(is.numeric) |> summary()" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "") |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n"); 
"ADS_time2event.DNR |> select_if(is.logical) |> summary()" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "") |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n"); 
DSN.Date.NA = DSN.Date |> paste0(".NA"); 
DSN.DNR = paste0(DSN.DNR); 
DSN.DNR.lbl_pending.fct = paste0(DSN.DNR,".fct"); 
"assign( DSN.DNR.lbl_pending.fct, get(DSN.DNR) |> mutate_if(is.character, as.factor) , envir = .GlobalEnv)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "") |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
cat("   #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n"); 
"get(DSN.DNR.lbl_pending.fct) |> select_if(is.factor) |> summary()" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "") |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
# https://github.com/mkim0710/tidystat/blob/master/Rdev/10_import_clean_datatype/18_dichotomous_logical/function.dichotomous2logical.dev.r
```
  
  
# __________|------  
# @@ ANALYSIS) (Breif) byVar =  ----  
 
### # ModelList\$time2DM ====   
 

# __________|------  
# @@ DATA) mutate() ----  
```{r DATA-MUTATE-SYNC, eval=FALSE, include=FALSE}
paste0('### ->> Now synced to: "',dir(env1$path$path1, ".*\\.Rmd$", ignore.case = TRUE),'"  \n') |> cat(sep="")
```
## ->> Now synced to: ""  
## ()()()()()()()()()()------  
## ()()()()()()()()()()------  
## ->> PENDING synced to: ""  
  
  
#### \$ .InclusionCriteria = ----  
#### \$ .ExclusionCriteria = ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
.InclusionCriteria = "time_ge30"
.ExclusionCriteria = "age_lt40_gt70"
assign(DSN.DNR.lbl_pending.fct, 
       get(DSN.DNR.lbl_pending.fct) %>% mutate(
           !!rlang::sym(.InclusionCriteria) := (time >= 30),
           !!rlang::sym(.ExclusionCriteria) := (age < 40) | (age > 70) | (is.na(age))
       )
)
```
  
  
# __________|------  
## @ DATA) mutate(byVar = ) ----  
#### \$  =  
  
  
# __________|------  
# @@ DATA) filter() -> New DS ----  
## :: DS1.recode = DS.DNR.lbl_pending.fct.recode
## :: DSN1.recode.n = paste0(DSN,".DNR",".lbl_pending",".fct",".recode",".n",nrow(DS1.recode))

### \% DS1.recode |> 
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
DS1.recode = get(DSN.DNR.lbl_pending.fct)
DSN1.recode.n = paste0(DSN,".DNR",".lbl_pending",".fct",".recode",".n",nrow(DS1.recode))
DSN1.recode.n
DS1.recode
```
  
  
## :: DS2.recode.filter = DS1.recode |> filter(!!rlang::sym(.InclusionCriteria) == TRUE & !!rlang::sym(.ExclusionCriteria) == FALSE)
## :: DSN2.recode.filter.n = paste0(DSN,".DNR",".lbl_pending",".fct",".recode",".n",nrow(DS2.recode.filter))  
```{r DS.Date-recode-filter-n-writeRDS-NoEvalNoEchoNoMsgNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
.objectname = "DSN1.recode.n"; cat("> ", .objectname, " = ", deparse(get(.objectname)), "  \n", sep="")
cat("*** Old DSN = ", deparse(DSN), "  \n", sep="")
##________________________________________________________________________________  
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
DS2.recode.filter = DS1.recode |> filter(!!rlang::sym(.InclusionCriteria) == TRUE & !!rlang::sym(.ExclusionCriteria) == FALSE)
DSN2.recode.filter.n = paste0(DSN,".DNR",".lbl_pending",".fct",".recode",".n",nrow(DS2.recode.filter))  
assign(DSN2.recode.filter.n, DS2.recode.filter)
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
.objectname = "DSN2.recode.filter.n"; cat("> ", .objectname, " = ", deparse(get(.objectname)), "  \n", sep="")
assign(.objectname, structure(get(.objectname, envir = .GlobalEnv), MetaData = as.environment(MetaData)), envir = .GlobalEnv)
.path4write = .path4write %>% str_replace(fixed(env1$path$path1), "") %>% str_replace("^/", "")  # [][Rproject] makes an error in git bash
env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = .objectname, .path4write = .path4write, createBACKUP = FALSE, EXECUTE = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE)
```
  
  
# __________|------  
# @@ DATA) select(matches(VarName.suffix.regex)) ----  
## @ VarName.suffix.regex = 
## :: get(DSN2.recode.filter.n) |> select(matches(VarName.suffix.regex))
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
get(DSN2.recode.filter.n) |> names() |> env1$env.internal.attach$deparse.cat0()
VarName.suffix.regex = get(DSN2.recode.filter.n) |> names() |> paste0(collapse="|")
VarName.suffix.regex |> dput()
DSN2.recode.filter.n.select = paste0(DSN2.recode.filter.n,"select",ncol(get(DSN2.recode.filter.n) |> names() |> str_subset(VarName.suffix.regex)))
assign(  DSN2.recode.filter.n.select, get(DSN2.recode.filter.n) |> select(matches(VarName.suffix.regex))  )
get(DSN2.recode.filter.n.select) |> str(max.level = 2, give.attr = TRUE)
```
  
  
# __________|------  
# @@ ANALYSIS) byVar =  ----  
## @ ANALYSIS) byVar, Table1 ----  
#### \$ 
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
  
```{r MetaData99-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
if(is.null(env1$path$LastSourceEditorContext.path_FileName.MetaData.rds)) env1$path$LastSourceEditorContext.path_FileName.MetaData.rds = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".MetaData.rds")
if (Sys.getenv("PARENT_RENDERING") != "YES") {    
    if(exists("MetaData") && !is.null(unlist(MetaData))) {
        "MetaData |> str(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        # "MetaData$tblVarName |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        # "MetaData$DSNs |> str(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        "MetaData$VarNames |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        "MetaData$VarNames.select |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        "MetaData$ModelList |> str(max.level = 3, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        
        if(!exists(".MetaData0")) .MetaData0 = MetaData
        MetaData$DSNs = MetaData$DSNs %>% map(function(ls) {  if("str" %in% names(attributes(ls))) {  if(!is.environment(attributes(ls)$str)) {  attributes(ls)$str = as.environment(list(DSN.get.str.capture.output = attributes(ls)$str))  }  }; ls  })
        MetaData %>% list_modify(tblVarName = NULL) %>% str(vec.len = 100, list.len = 1000) %>% capture.output(file = env1$path$LastSourceEditorContext.path_FileName.MetaData.rds %>% str_replace("\\.rds$", "-str.txt"))
        "all.equal(.MetaData0, MetaData)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
        if(!identical(.MetaData0, MetaData)) {
            cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
            .path_file = ifelse(is.null(env1$path$LastSourceEditorContext.path_FileName.MetaData.rds), NULL, env1$path$LastSourceEditorContext.path_FileName.MetaData.rds)
            # MetaData |> env1$f$f_object.get_objectname.size.write_rds.git_lfs_track_add_f(.path_file = .path_file, createBACKUP = TRUE, EXECUTE = TRUE)
            env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = "MetaData", .path_file = .path_file, createBACKUP = TRUE, EXECUTE = TRUE)
        }
    } else {warning('> !exists("MetaData") || is.null(unlist(MetaData))  \n')}
}
```
  
  
```{r writeRDS-EvalNoEchoNoMsgNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# __________|------  
## @ write_rds( get(.objectname), paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".rds",".xz"), compress = "xz", compression = 9L) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n") ----
if (Sys.getenv("PARENT_RENDERING") != "YES") {    
    .path4write = .path4write %>% str_replace(fixed(env1$path$path1), "") %>% str_replace("^/", "")  # [][Rproject] makes an error in git bash
    if(exists("MetaData") && !is.null(unlist(MetaData))) {
        # MetaData$DSNs |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
        cat("    ________________________________________________________________________    \n")
        for (DSN in names(MetaData$DSNs)) {    
            if(exists(DSN)) {
                assign(DSN, structure(get(DSN, envir = .GlobalEnv), MetaData = as.environment(MetaData)), envir = .GlobalEnv)
                if(is.null(attributes(.GlobalEnv[[DSN]])$DSN)) attributes(.GlobalEnv[[DSN]])$DSN = DSN
                if(attributes(.GlobalEnv[[DSN]])$DSN != DSN) attributes(.GlobalEnv[[DSN]])$DSN = DSN
                if (!is.null(attributes(attributes(.GlobalEnv[[DSN]])$DSN)$.path_file)) {
                    message( "attributes(attributes(",DSN,")$DSN)$.path_file == ",deparse(attributes(attributes(get(DSN))$DSN)$.path_file) )
                    env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = DSN, .path_file = attributes(attributes(.GlobalEnv[[DSN]])$DSN)$.path_file, createBACKUP = FALSE, EXECUTE = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE)
                } else {
                    env1$f$f_objectname.size.write_rds.git_lfs_track_add_f(.objectname = DSN, .path4write = .path4write, createBACKUP = FALSE, EXECUTE = FALSE, path.size_files = TRUE, git_lfs_track = TRUE, git_add_f = TRUE)
                }
            } else {  message("!exists(",deparse(DSN),")")  }
            cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        }
    }
    # #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
    # .path_FileName.xlsx = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".xlsx")  ;  openxlsx2::write_xlsx(get(.objectname), file = .path_FileName.xlsx, as_table=TRUE, table_style="none", row_names=TRUE, col_widths="auto", first_active_row=2, first_active_col=2) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")  ;  if (Sys.info()["sysname"] == "Linux") browseURL(.path_FileName.xlsx) else openxlsx2::xl_open(.path_FileName.xlsx)
    # #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
    # .path_FileName.UTF8BOM.csv = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".UTF8BOM.csv")
    # if (Sys.info()["sysname"] == "Windows") {
    #     readr::write_excel_csv(get(.objectname), file = .path_FileName.UTF8BOM.csv) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
    #     openxlsx2::xl_open(.path_FileName.xlsx)
    # } else {
    #     readr::write_excel_csv(get(.objectname), file = .path_FileName.UTF8BOM.csv|>paste0(".xz")) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
    # }
    # #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
    # .path_FileName.UTF8.csv.xz = paste0(.path4write,ifelse(.path4write=="","","/"),.objectname,".UTF8.csv.xz")
    # readr::write_csv(get(.objectname), file = .path_FileName.UTF8.csv.xz) |> system.time() |> round(3) |> unclass() |> deparse() |> cat("\n")
}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    
}
```
  
  
```{r createBACKUP, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$LastSourceEditorContext.path_FileName.pdf = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$LastSourceEditorContext.path_FileName.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (Sys.info()["sysname"] == "Windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$LastSourceEditorContext.path_FileNameExt)),', output_format = "pdf_document")  \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
        .path_file = env1$path$LastSourceEditorContext.path_FileName.pdf
        env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE)
        env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = .path_file, .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal.attach$f_file_PDF.sumatra(.path_file))
    }
}
# env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_FileName.pdf; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = ',deparse(.path_file),', .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal.attach$f_file_PDF.sumatra(',deparse(.path_file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path_file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_FileName.html; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = ',deparse(.path_file),', .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); cat('  env1$env.internal.attach$f_URL.browse_in_edge_app(',deparse(.path_file),')  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_FileName.nb.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") {  try(  paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE),'"') |> shell(wait=FALSE)  )  }  # else { browseURL(env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE)) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileNameExt) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileName.nb.html) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
