---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
mainfont: Arial
monofont: Consolas
header-includes: 
  - \usepackage{kotex}
  - \usepackage{fontspec}
  - \setmainhangulfont{HCR Batang}
  - \setsanshangulfont{HCR Dotum}
  - \setmonohangulfont{HCR Dotum}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Arial', 'Helvetica', sans-serif; }
h1.title { font-size: 28px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 12px; font-family: 'Cascadia Code SemiBold', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 12px; font-family: 'Cascadia Code SemiBold', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>

<!-- font-size: 0.9em; /* 90% of inherited font size */ -->

<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
```{r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE}
# ##### Rstudio RMarkDown Shortcuts
# https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE  
# https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html  
# Insert R chunk	Ctrl+Alt+I	Command+Option+I\
# Preview HTML	Ctrl+Shift+K	Command+Shift+K\
# Run all chunks above	Ctrl+Alt+P	Command+Option+P\
# Run current chunk	Ctrl+Alt+C	Command+Option+C\
# Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter\
# Run next chunk	Ctrl+Alt+N	Command+Option+N\
# Run all chunks	Ctrl+Alt+R	Command+Option+R\
# Go to next chunk/title	Ctrl+PgDown	Command+PgDown\
# Go to previous chunk/title	Ctrl+PgUp	Command+PgUp\
# Show/hide document outline	Ctrl+Shift+O	Command+Shift+O\
# F7 spell-check your document.\
# Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).\
# \
# *** Caution: \% \$ \# \* \
```


```{r setup, eval=TRUE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "\n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=TRUE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=TRUE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)
```


```{r options-width-NoEchoHideResults, echo=FALSE, results="hide"}
if(!exists("env.custom", envir=.GlobalEnv)) 
    assign("env.custom", new.env(), envir=.GlobalEnv)
if(!"info" %in% names(env.custom)) env.custom$info = list()
env.custom$info$options.width = options()$width; cat(options()$width, "\n", sep="")
```


```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
suppressPackageStartupMessages({for(packagename in c("tidyverse","formatR")) {if(!require(packagename,character.only=TRUE))install.packages(packagename) else library(packagename,character.only=TRUE)}});cat("\n");
if(!exists("env.custom", envir=.GlobalEnv)) 
    assign("env.custom", new.env(), envir=.GlobalEnv)
## env.custom\$path ====
if(!"path" %in% names(env.custom)) env.custom$path = list()
objectname = "source_base_local"; object = "D:/OneDrive/[][Rproject]/github_tidystat"; if(!objectname %in% names(env.custom$path)) {env.custom$path[[objectname]] = object};
objectname = "source_base_github"; object = "https://github.com/mkim0710/tidystat/raw/master"; if(!objectname %in% names(env.custom$path)) {env.custom$path[[objectname]] = object};
env.custom$path$source_base = ifelse(dir.exists(env.custom$path$source_base_local), env.custom$path$source_base_local, env.custom$path$source_base_github)  
## env.custom\$env.internal ====
sourcename = "env.custom$env.internal"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
#### env.custom\$f_df.t.tribble_construct() ====
sourcename = "f_df.t.tribble_construct"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
```

<font size="3">\% env.custom</font>\

```{r envCustom-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
if(!exists("env.custom", envir=.GlobalEnv)) 
    assign("env.custom", new.env(), envir=.GlobalEnv)
if(!"info" %in% names(env.custom)) env.custom$info = list()
#### env.custom\$info\$get_system_info() ====
sourcename = "get_system_info"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
env.custom$info$info_system_info = env.custom$info$get_system_info()
# str(env.custom$info$info_system_info)
CodeText = "env.custom$info$info_system_info$machine_nodename"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
CodeText = "env.custom$info$info_system_info$Sys.getlocale$LC_COLLATE"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
# CodeText = "env.custom$info$info_system_info$l10n_info$localization_UTF8"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
env.custom$info$info_software_versions = env.custom$info$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "datapasta","openxlsx"))
# str(env.custom$info$info_software_versions)
```


###### env.custom\$info\$DocumentTitle1 ====
```{r envCustom-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env.custom$info$DocumentTitle0 = paste0("00env.custom.minimum","-",basename(getwd()))
env.custom$info$DocumentTitle1 = paste0(env.custom$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env.custom$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env.custom$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env.custom$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env.custom$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```


###### env.custom\$path ====
```{r envCustom-Path-NoEcho, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE}
# cat("getwd() == "); dput(getwd()) #----
# env.custom$path$project_base = "Rproject_HEALS0215"
# env.custom$path$data_suffix = "_01"
# # env.custom$path$data_suffix = ""
# env.custom$path$project_suffix = "GJ3"
# 
# env.custom$path$path4read = file.path(env.custom$path$path0, paste0(env.custom$path$project_base, env.custom$path$data_suffix))
# env.custom$path$path4write = file.path(env.custom$path$path4read, paste0(env.custom$path$project_base, env.custom$path$data_suffix, env.custom$path$project_suffix))
env.custom$path$path4read = ifelse(is.na(env.custom$path$path1), getwd(), env.custom$path$path1)
env.custom$path$path4write = getwd()
cat("> str(env.custom$path)\n"); str(env.custom$path, max.level = 1, give.attr = F)  
path4read  = env.custom$path$path4read
path4write = env.custom$path$path4write
# sourcename = "f_objectname.read.checkEntity"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
# if (getwd() != path4write) warning("getwd() != path4write  == ") else cat("getwd() == path4write == "); dput(path4write)  #----
```


#### env.custom\$f_path.df_dirs_recursive.df_files() ----
```{r dfDIRsRecursive-NoEcho, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE}
#### env.custom\$f_path.df_dirs_recursive.df_files() ----
sourcename = "f_path.df_dirs_recursive.df_files"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
env.custom$path$df_dirs_recursive.df_files = env.custom$f_path.df_dirs_recursive.df_files(input_path=".", print.message=FALSE)
env.custom$path$print_tree_path = env.custom$path$df_dirs_recursive.df_files |> filter(path.level <= 2) |> 
    dplyr::select(print_tree_path) |> unlist() |> paste(collapse="") 
# env.custom$path$print_tree_path |> cat()
env.custom$path$print_tree_path_files.codes = env.custom$path$df_dirs_recursive.df_files |> filter(path.level <= 2) |> 
    dplyr::select(print_tree_path_files.codes) |> unlist() |> paste(collapse="") 
# env.custom$path$print_tree_path_files.codes |> cat()
env.custom$path$print_tree_path_files.data = env.custom$path$df_dirs_recursive.df_files |> filter(path.level <= 2) |> 
    dplyr::select(print_tree_path_files.data) |> unlist() |> paste(collapse="") 
env.custom$path$print_tree_path_files.data |> cat()
```


#### env.custom\$f_path.size_files() ----
```{r sizeFiles-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=FALSE, results="hide"}
#### env.custom\$f_path.size_files() ----
sourcename = "f_path.size_files"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
#### env.custom\$f_objectname.read.checkEntity() ----
sourcename = "f_objectname.read.checkEntity"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
env.custom$f_path.size_files(path4read = path4read)
```


#### @ Open R Notebooks ------------
```{r open-envCustom-dfDirs-CodeBook, eval=TRUE, include=FALSE}
if(!exists("env.custom", envir=.GlobalEnv)) 
    assign("env.custom", new.env(), envir=.GlobalEnv)
env.custom$path$CurrentSource.path.filename.ext=rstudioapi::getSourceEditorContext()$path 
# if(!"tmp" %in% names(env.custom)) env.custom$tmp = list()
# for (SourceFileBaseName in rev(c("00env.custom", "01df_dirs_recursive.df_files", "10CodeBook"))) {
#     env.custom$tmp$SourceFileName.ext = paste0(SourceFileBaseName,"-",basename(getwd()),".Rmd");
#     if(env.custom$tmp$SourceFileName.ext != basename(env.custom$path$CurrentSource.path.filename.ext)) {
#         if(!file.exists(env.custom$tmp$SourceFileName.ext)) file.create(env.custom$tmp$SourceFileName.ext)
#         file.edit(env.custom$tmp$SourceFileName.ext);
#         file.edit(env.custom$path$CurrentSource.path.filename.ext);
#     }
# }
```


# @@ CODEBOOK ------------


#@@ START) source -----
### \$ subpath, sourcename ======
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# subpath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
# # if(subpath!="") utils::browseURL(normalizePath(subpath))
# sourcename = "default.template"
# subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r")
# # % (source( file.path(env.custom$path$source_base,subpath.filename.source.r) )) ----
# (source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
```


# @@ START) Data ------------

## \$ DataSetName = "analyticDF_time2event" ====
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
suppressPackageStartupMessages(library(tidyverse))
# suppressPackageStartupMessages(library(survival))
# suppressPackageStartupMessages(library(survminer))
?survival::lung
DataSetName = "analyticDF_time2event"
assign(
    DataSetName, 
    survival::lung |> mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] |> as.factor(), StudyPopulation = time >= 30) |>
        # dplyr::select(-status, -sex)
        dplyr::select(-status)
)
analyticDF_time2event %>% {cat("> ",deparse(substitute(.))," |> as_tibble() |> print(n=9)","\n", sep=""); print(as_tibble(.),n=9)}
analyticDF_time2event %>% {cat("> ",deparse(substitute(.))," |> rownames_to_column() |> tail() |> as_tibble()","\n", sep=""); print(as_tibble(tail(rownames_to_column(.))))}
# analyticDF_time2event |> dplyr::select(sex, Group) %>% {cat("> ",deparse(substitute(.))," |> str()","\n", sep=""); str(.)}
# analyticDF_time2event |> dplyr::select(sex, Group) |> table(useNA="always") |> addmargins
# # > analyticDF_time2event |> dplyr::select(sex, Group) %>% {cat("> ",deparse(substitute(.))," |> str()","\n", sep=""); str(.)}
# # 'data.frame':	228 obs. of  2 variables:
# #  $ sex  : num  1 1 1 1 1 1 2 2 1 1 ...
# #  $ Group: Factor w/ 2 levels "Female","Male": 2 2 2 2 2 2 1 1 2 2 ...
# # > analyticDF_time2event |> dplyr::select(sex, Group) |> table(useNA="always") |> addmargins
# #    Group
# # sex Female Male
# #   1      0  138
# #   2     90    0
# analyticDF_time2event |> dplyr::select(time, event, Group, StudyPopulation) %>% by(.$StudyPopulation, summary)
# # > analyticDF_time2event |> dplyr::select(time, event, Group, StudyPopulation) %>% by(.$StudyPopulation, summary)
# # .$StudyPopulation: FALSE
# #       time     event            Group   StudyPopulation
# #  Min.   : 5   Mode:logical   Female:1   Mode :logical  
# #  1st Qu.:11   TRUE:9         Male  :8   FALSE:9        
# #  Median :12                                            
# #  Mean   :13                                            
# #  3rd Qu.:13                                            
# #  Max.   :26                                            
# # ------------------------------------------------------------------------------------------ 
# # .$StudyPopulation: TRUE
# #       time          event            Group     StudyPopulation
# #  Min.   :  30.0   Mode :logical   Female: 89   Mode:logical   
# #  1st Qu.: 176.5   FALSE:63        Male  :130   TRUE:219       
# #  Median : 269.0   TRUE :156                                   
# #  Mean   : 317.2                                               
# #  3rd Qu.: 419.5                                               
# #  Max.   :1022.0   

```

## ------ < Key Variables Check > ------
### \$ varname4ID  -----
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# source("https://github.com/mkim0710/tidystat/raw/master/Rdev/10_import_clean_datatype/13_missing_value/data.NotNA_p_df.source.r")
subpath=r"(Rdev\10_import_clean_datatype\13_missing_value)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
sourcename = "data.NotNA_p_df"
subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))

varname4ID = c("ID", "CompositeKey", "PERSON_ID", "RN_INDI", "NIHID")
get(DataSetName)[intersect(varname4ID, colnames(get(DataSetName)))] |> str()
get(DataSetName) |> dim()
get(DataSetName)[intersect(varname4ID, colnames(get(DataSetName)))] |> n_distinct()
get(DataSetName)[intersect(varname4ID, colnames(get(DataSetName)))] |> env.custom$data.NotNA_p_df()

varname4CompositKey = c("age", "sex")
vecCompositeKey = get(DataSetName)[intersect(varname4CompositKey, colnames(get(DataSetName)))] |> apply(MARGIN = 1, paste0, collapse = "-")
vecCompositeKey |> n_distinct()
```



#### \$ varname4outcome -----
#### \$ varname4time -----
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
varname4outcome = "event"
varname4time = c("time", "age")
get(DataSetName)[c(varname4outcome, varname4time)] |> 
    mutate_if(is.factor, as.character) |>  
    mutate_if(is.character, na_if, "") |> mutate_if(is.character, na_if, "N/A") |> mutate_if(is.character, na_if, "NA") |> 
    mutate_if(is.character, as.factor) |> 
    summary()

```


##### \$ varname4measures -----
##### \$ varname4labs -----
##### \$ varname4lifestyle -----
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


## ------ < Data Availability Check > ------
### \$ paste0(DataSetName,".Date",".NA",".rmAllNA")  ====
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
# source("https://github.com/mkim0710/tidystat/raw/master/Rdev/10_import_clean_datatype/13_missing_value/data.NotNA_p_df.source.r")
subpath=r"(Rdev\10_import_clean_datatype\13_missing_value)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
sourcename = "data.NotNA_p_df"
subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))

assign( paste0(DataSetName,".Date",".NA"), get(DataSetName) |> mutate_if(is.factor, as.character) |> mutate_if(is.character, na_if, "") |> mutate_if(is.character, na_if, "N/A") |> mutate_if(is.character, na_if, "NA") |> as_tibble() )
assign( paste0(DataSetName,".Date",".NA",".rmAllNA"), get(paste0(DataSetName,".Date",".NA")) |> select_if(function(vec) !all(is.na(vec))) )
cat("dim(",DataSetName,") = ",deparse(dim(get(DataSetName))),"\n", sep="") 
cat("dim(",DataSetName,".Date",".NA",".rmAllNA",") = ",deparse(dim(get(paste0(DataSetName,".Date",".NA",".rmAllNA")))),"\n", sep="") 
cat(strrep("%",80),"\n",sep=""); 
cat("> ",DataSetName,".Date",".NA"," |> env.custom$data.NotNA_p_df()","\n", sep=""); env.custom$data.NotNA_p_df(get(paste0(DataSetName,".Date",".NA")))
```


## ------ < DataSet Summary > ------
### \$ paste0(DataSetName,".Date",".NA",".rmAllNA",".fct") ====
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
vec_varname4ID = c("ID", "CompositeKey", "PERSON_ID", "RN_INDI", "NIHID")
for (varname in vec_varname4ID) {if(varname %in% names(get(paste0(DataSetName,".Date",".NA",".rmAllNA")))) cat("n_distinct(",paste0(DataSetName,".Date",".NA",".rmAllNA"),"$",varname,") = ",n_distinct(get(paste0(DataSetName,".Date",".NA",".rmAllNA"))[[varname]]),"\n", sep="")}


t0=Sys.time()
cat(strrep("~",80),"\n",sep=""); cat("> ",paste0(DataSetName,".Date",".NA",".rmAllNA")," |> select_if(is.numeric))"," |> summary()","\n", sep=""); get(paste0(DataSetName,".Date",".NA",".rmAllNA")) |> select_if(is.numeric) |> summary() #-----
Sys.time()-t0
t0=Sys.time()
cat(strrep("~",80),"\n",sep=""); cat("> ",paste0(DataSetName,".Date",".NA",".rmAllNA")," |> select_if(is.logical))"," |> summary()","\n", sep=""); get(paste0(DataSetName,".Date",".NA",".rmAllNA")) |> select_if(is.logical) |> summary() #-----
Sys.time()-t0

t0=Sys.time()
cat(strrep("%",80),"\n",sep=""); cat("> ",paste0(DataSetName,".Date",".NA",".rmAllNA",".fct")," = ",paste0(DataSetName,".Date",".NA",".rmAllNA")," |> mutate_if(is.character, as.factor)","\n", sep=""); assign( paste0(DataSetName,".Date",".NA",".rmAllNA",".fct"), get(paste0(DataSetName,".Date",".NA",".rmAllNA")) |> mutate_if(is.character, as.factor) )
Sys.time()-t0

t0=Sys.time()
cat(strrep("+",80),"\n",sep=""); cat("> ",paste0(DataSetName,".Date",".NA",".rmAllNA",".fct")," |> select_if(is.factor))"," |> summary()","\n", sep=""); get(paste0(DataSetName,".Date",".NA",".rmAllNA",".fct")) |> select_if(is.factor) |> summary() #-----
Sys.time()-t0
# cat(strrep("~",80),"\n",sep=""); cat("> ",paste0(DataSetName,".Date",".NA",".rmAllNA")," |> select_if(is.factor))"," |> summary()","\n", sep=""); get(paste0(DataSetName,".Date",".NA",".rmAllNA")) |> select_if(is.character) |> map_df(as.factor) |> summary() #-----
# Sys.time()-t0
# https://github.com/mkim0710/tidystat/blob/master/Rdev/10_import_clean_datatype/18_dichotomous_logical/function.dichotomous2logical.dev.r
```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


# @@ END ------------
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=FALSE, results="hide", collapse=TRUE, paged.print=FALSE}
# @@ END ------------
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
```


```{r updateDefaultNotebook-NoEchoNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="hide", collapse=TRUE, paged.print=FALSE}
# @@ update default notebook.Rmd -----
template.filename.ext = "templates-00env.custom.minimum.Rmd"
CurrentSource.path.filename.ext=rstudioapi::getSourceEditorContext()$path; if(basename(CurrentSource.path.filename.ext) == template.filename.ext) {
    if (.Platform$OS.type == "windows") {path4APPDATA_RStudio = file.path(Sys.getenv("APPDATA"), "RStudio") |> str_replace_all("\\\\","/")} # else if (.Platform$OS.type == "unix") {path4APPDATA_RStudio = "~/.config/rstudio"} ;
    if(!dir.exists(file.path(path4APPDATA_RStudio, "templates"))) dir.create(file.path(path4APPDATA_RStudio, "templates")) ;
    
    destination.path.filename.ext = file.path(path4APPDATA_RStudio, "templates", "notebook.Rmd"); if(file.copy(from=CurrentSource.path.filename.ext, to=destination.path.filename.ext, overwrite=TRUE)) message(paste0("Update successful: ", destination.path.filename.ext)) else warning(paste0("Update failed: ", destination.path.filename.ext)); if (.Platform$OS.type == "windows") {shell(paste0("notepad.exe ",destination.path.filename.ext),wait=FALSE)} else if (.Platform$OS.type == "unix") {system(paste0("open -a TextEdit ",destination.path.filename.ext),wait=FALSE)};
    for ( destination.path.filename.ext in c(
        file.path(env.custom$path$source_base_local, "rstudio-prefs", "templates", template.filename.ext)
        , file.path(env.custom$path$path0, "Rproject_Rmd", template.filename.ext)
    )) {if(CurrentSource.path.filename.ext != destination.path.filename.ext) {
        destination.filename = basename(destination.path.filename.ext) |> str_remove("\\.([[:alnum:]]+)$")
        destination.ext = basename(destination.path.filename.ext) |> str_extract("\\.([[:alnum:]]+)$")
        backup.path.filename = file.path(env.custom$path$path0, "Rproject_Rmd", "-backup", paste0(destination.filename,"-",format(Sys.time(),"%y%m%d_%H%M"),destination.ext))
        file.copy(from=destination.path.filename.ext, to=backup.path.filename, overwrite=TRUE); message(paste0("Backup file created: ",backup.path.filename))
        if(file.copy(from=CurrentSource.path.filename.ext, to=destination.path.filename.ext, overwrite=TRUE)) message(paste0("Update successful: ", destination.path.filename.ext)) else warning(paste0("Update failed: ", destination.path.filename.ext));
        if (.Platform$OS.type == "windows") {shell(paste0("notepad.exe ",destination.path.filename.ext),wait=FALSE)} else if (.Platform$OS.type == "unix") {system(paste0("open -a TextEdit ",destination.path.filename.ext),wait=FALSE)};
    }}
    file.edit(CurrentSource.path.filename.ext);
}
# template.filename.ext = "notebook.Rmd"; if(!file.exists(file.path(path4APPDATA_RStudio, "templates", template.filename.ext))) file.create(file.path(path4APPDATA_RStudio, "templates", template.filename.ext)); file.edit(file.path(path4APPDATA_RStudio, "templates", template.filename.ext))
```


```{r RenderMessages, eval=FALSE, include=FALSE}
# dput(names(knitr::knit_engines$get()))
```


```{r writeRDS-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# # @ write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds"))) -----
# objectname = "AnalyticDataset200621"
# system.time(write_rds( get(objectname), paste0(objectname,".rds") ))
# system.time(write_rds( get(paste0(objectname,".NA",".rmAllNA",".fct")), paste0(objectname,".NA",".rmAllNA",".fct",".rds") ))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds"))))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds")), compress = "gz" ))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname, ".rds", "")), compress = "xz", compression = 9 ))
# # system.time(openxlsx::write.xlsx(get(objectname), file=paste0(objectname,".xlsx"), asTable=TRUE, withFilter=TRUE))
# # openxlsx::openXL(paste0(objectname, ".xlsx"))
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
```


```{r gitCheckout-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
cat("* To revert to the last commited file, run the following terminal command:\n", 
    '"git checkout -- ',rstudioapi::getSourceEditorContext()$path,'" |> system(intern=TRUE)',"\n",
    '"git checkout -- ',rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"),'" |> system(intern=TRUE)',"\n", sep="")
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
```

