---
##HHHHHHHHHHHHHHHHHH BEGINNING OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##  
# TABLE OF CONTENTS (level 1) ----  
# @@ REFERENCES)                                                            #L247
# @@ DATA) example                                                          #L256
# @@ START) dev                                                             #L276
# @@ SOURCE)                                                                #L311
# @@ START) function                                                        #L353
# @@ MetaData) Read & Check                                                 #L402
# @@ DATA) Read & Check                                                     #L472
# @@ ANALYSIS) (Breif) byVar =                                              #L638
# @@ DATA) mutate()                                                         #L644
# @@ DATA) filter() -> New DS                                               #L675
# @@ DATA) select(matches(VarName.suffix.regex))                            #L708
# @@ ANALYSIS) byVar =                                                      #L722
##HHHHHHHHHHHHHHHHHHHH THE END OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##   
##HHHHHHHHHHHHHHHHHH BEGINNING OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##  
# TABLE OF CONTENTS (level 1) ----  
# @@ REFERENCES)                                                            # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L247
# @@ DATA) example                                                          # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L256
# @@ START) dev                                                             # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L276
# @@ SOURCE)                                                                # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L311
# @@ START) function                                                        # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L353
# @@ MetaData) Read & Check                                                 # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L402
# @@ DATA) Read & Check                                                     # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L472
# @@ ANALYSIS) (Breif) byVar =                                              # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L638
# @@ DATA) mutate()                                                         # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L644
# @@ DATA) filter() -> New DS                                               # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L675
# @@ DATA) select(matches(VarName.suffix.regex))                            # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L708
# @@ ANALYSIS) byVar =                                                      # https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd#L722
##HHHHHHHHHHHHHHHHHHHH THE END OF TABLE OF CONTENTS HHHHHHHHHHHHHHHHHHHHHH##   
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    md_extensions: -smart
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  # - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd())  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_FileNameExt ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# .tmp$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) not a relative path~!  
# env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) Not using a relative path~!
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$path4write = file.path(env1$path$path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$path4write = getwd()
.path4read  = env1$path$path4read
.path4write = env1$path$path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .FileName.source.r = "f_DSN.Search.read.checkEntity" |> paste0(".source.r"); .RelativeSubPath=r"()"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = list(.RelativeSubPath, .FileName.source.r) %>% {.[nzchar(.)]} %>% c(fsep = "/") %>% {do.call(file.path, .)})
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  
```
  
  
# __________|------  
# @@ REFERENCES) ----  
## https://cran.r-project.org/doc/FAQ/R-FAQ.pdf#page=42&view=FitV&navpanes=1
## https://stat.ethz.ch/R-manual/R-devel/library/base/html/regex.html
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
## https://chatgpt.com/c/66f605cf-6be4-800e-88a3-e8e23a7cb379?model=o1-pro
## https://chatgpt.com/c/67776103-6c28-800e-9b02-b455688f189e

### 1. Escaping Special Characters When Developing a Regex

#### 1.1. Which Characters Are Special in Regex?

In most regex engines (including PCRE, POSIX ERE, and those used in languages like R, Python, and Java), the following characters typically have special meaning and **must be escaped** if you want to treat them literally:

        `.  +  *  ?  ^  $  (  )  [  ]  {  }  |  \` 

Some regex engines also treat **`-`** (hyphen) as special inside character classes (e.g., `[a-z]`). Therefore, a practical approach is to escape the hyphen **when it appears inside** a character class.

#### 1.2. A Robust Regex Pattern for Escaping

Below is a common pattern to catch **all** of these characters (including the hyphen and the dot). In a PCRE or most standard engines, you can use:

        `([.\\+*?^$(){}|[\]\-])`

-   **Explanation**:
    -   `(` and `)` — Capturing group.
    -   Inside `[ ]`, we place all characters that need escaping:
        -   `.` (dot), `\` (backslash), `+`, `*`, `?`, `^`, `$`, `(`, `)`, `{`, `}`, `|`, `[`, `]`, `\-`.
    -   We have to backslash-escape the backslash itself (`\\`) and also the bracket-related characters where needed.

Depending on the programming language, you may need additional escapes. For example, in an R string literal, you might write this as:


        `"([\\.\\\\+*?^\\$(){}|\\[\\]\\-])"`

  
  
# __________|------  
# @@ DATA) example ----  

## @ ASCII code (0:127) ----
### \% intToUtf8(0:31) |> cat0()  
### \% intToUtf8(32:47) |> cat0()    #  !"#$%&'()*+,-./
### \% intToUtf8(48:57) |> cat0()    # 0123456789
### \% intToUtf8(58:64) |> cat0()    # :;<=>?@
### \% intToUtf8(65:90) |> cat0()    # ABCDEFGHIJKLMNOPQRSTUVWXYZ
### \% intToUtf8(91:96) |> cat0()    # [\]^_`
### \% intToUtf8(97:122) |> cat0()    # abcdefghijklmnopqrstuvwxyz
### \% intToUtf8(123:126) |> cat0()    # {|}~
### \% intToUtf8(127) |> cat0()    # DEL
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
intToUtf8(0:31) |> cat0()  
intToUtf8(32:47) |> cat0()    #  !"#$%&'()*+,-./
intToUtf8(48:57) |> cat0()    # 0123456789
intToUtf8(58:64) |> cat0()    # :;<=>?@
intToUtf8(65:90) |> cat0()    # ABCDEFGHIJKLMNOPQRSTUVWXYZ
intToUtf8(91:96) |> cat0()    # [\]^_`
intToUtf8(97:122) |> cat0()    # abcdefghijklmnopqrstuvwxyz
intToUtf8(123:126) |> cat0()    # {|}~
intToUtf8(127) |> cat0()    # DEL
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
c(32:47,58:64,91:96,123:126) |> intToUtf8() |> cat0()   #  !"#$%&'()*+,-./:;<=>?@[\]^_`{|}~  
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
vec_chr.ASCII_nonalphanumeric = c(32:47,58:64,91:96,123:126) %>% {function(vec_chr) {  vec_chr |> intToUtf8() |> str_split("") |> unlist() |> set_names(vec_chr)  }}()
vec_chr.ASCII_nonalphanumeric %>% str()
```


### inclusion_glob = 
### exclusion_glob = 
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
inclusion_glob  <- "{**/*.[Rr],**/*.[Rr].txt,**/*.[Rr][Mm][Dd],default.R,.Rprofile}"
exclusion_glob  <- "{.history,-[Bb][Aa][Cc][Kk][Uu][Pp],VScode Replace*.*,.git,.Rproj.user,*symlink*,r4ds-master}"
```


###### ECHO \% |> str_replace_all("([\\.\\\\+*?^\\$(){}|\\[\\]\\-])", "\\\\$1") ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
inclusion_glob |> str_replace_all("([\\.\\\\+*?^\\$(){}|\\[\\]\\-])", "\\\\\\1")
exclusion_glob |> str_replace_all("([\\.\\\\+*?^\\$(){}|\\[\\]\\-])", "\\\\\\1")
```
  
  
### path_windows_D_OneDrive_Project_github_tidystat = 
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
path_windows_D_OneDrive_Project_github_tidystat = r"(D:\OneDrive\[][Rproject]\github_tidystat)"
path_windows_D_OneDrive_Project_github_tidystat %>% dput()
path_windows_D_OneDrive_Project_github_tidystat %>% cat0()
```


## @ RegEx Special Characters ----
### RegExChrClass34strings_cheatsheet = "[]$*+.?[^{|(\\#%&~_/<=>'!,:;`\")}@-]"
### RegExChrClass_gpt_o1 = "[.\\\\+*?^$(){}|\\[\\]\\-]"
### RegExChrClass_gpt_o1p = "[.*+?^=!:|\\\\/()\\[\\]{}]"
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
RegExChrClass34strings_cheatsheet = "[]$*+.?[^{|(\\#%&~_/<=>'!,:;`\")}@-]"
RegExChrClass34strings_cheatsheet %>% dput
RegExChrClass34strings_cheatsheet %>% {cat(" ",.,"\n", sep="")}
# "[]$*+.?[^{|(\\#%&~_/<=>'!,:;`\")}@-]"
#  []$*+.?[^{|(\#%&~_/<=>'!,:;`")}@-]
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
RegExChrClass34strings_cheatsheet_MHsort = "[]$*+.?[^{|(\\#%&~_/<=>'!,:;`\")}@-]"
RegExChrClass34strings_cheatsheet_MHsort %>% dput
RegExChrClass34strings_cheatsheet_MHsort %>% {cat(" ",.,"\n", sep="")}
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
RegExChrClass_gpt_o1 = "[.\\\\+*?^$(){}|\\[\\]\\-]"
RegExChrClass_gpt_o1 %>% dput
RegExChrClass_gpt_o1 %>% {cat(" ",.,"\n", sep="")}
# "[.\\\\+*?^$(){}|\\[\\]\\-]"
#  [.\+*?^$(){}|\[\]\-]
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
RegExChrClass_gpt_o1p = "[.*+?^=!:|\\\\/()\\[\\]{}]"
RegExChrClass_gpt_o1p %>% dput
RegExChrClass_gpt_o1p %>% {cat(" ",.,"\n", sep="")}
# "[.*+?^=!:|\\\\/()\\[\\]{}]"
#  [.*+?^=!:|\\/()\[\]{}]
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
RegExChrClass4RegExEscape_gpt_o1 = "[$()*+.?[^{|(\\#%&~_/<=>'!,:;`)}@-]"


```
  
  
# __________|------  
# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```
  
  
## \% ADS_time2event |>  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ SOURCE) ----  
```{r RUN-ALL-CHUNKS-ABOVE, echo=FALSE, results="hide", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
```


```{r .RelativeSubPath_FileName.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
options(DEVMODE = TRUE);  # isTRUE(getOption("DEVMODE"))
# .RelativeSubPath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(env1$f$f_object.is_not_null.nor_na.nor_blank(env1$path$LastSourceEditorContext.path_FileNameExt)) {    .RelativeSubPath = env1$path$LastSourceEditorContext.path_FileNameExt |> dirname() |> env1$f$f_path.relative()  ;    ".RelativeSubPath" |> env1$f$f_ObjectName.get.dput.ECHO()    }
# if(.RelativeSubPath!="") .RelativeSubPath |> normalizePath(winslash="/",mustWork=TRUE) |> utils::browseURL() |> try()
# .FileName.source.r = "default.template" |> paste0(".source.r")
if(env1$f$f_object.is_not_null.nor_na.nor_blank(env1$path$LastSourceEditorContext.path_FileNameExt)) {    .SourceName_root = env1$path$LastSourceEditorContext.path_FileNameExt |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),"")  ;    ".SourceName_root" |> env1$f$f_ObjectName.get.dput.ECHO()    }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.RelativeSubPath = .RelativeSubPath
if(!exists(".SourceName_root") && exists(".FileName.source.r")) .SourceName_root = .FileName.source.r |> str_replace("\\.source\\.r$", "")
.FileName.source.r = .SourceName_root |> paste0(".source.r")
env1$path$.SourceName_root = .SourceName_root
env1$path$.RelativeSubPath_FileName.dev.r = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".dev.r")
env1$path$.RelativeSubPath_FileName.dev.Rmd = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".dev.Rmd")
env1$path$.RelativeSubPath_FileName.source.r = paste0(.RelativeSubPath,ifelse(.RelativeSubPath=="","","/"),.SourceName_root,".source.r")
cat("# ",'.SourceName_root = "',.SourceName_root,'"  \n',
    "#### ",env1$path$.RelativeSubPath_FileName.dev.r, "----  \n",
    "#### ",env1$path$.RelativeSubPath_FileName.dev.Rmd, "----  \n",
    "#### ",env1$path$.RelativeSubPath_FileName.source.r, "----  \n",
    '# # source(paste0(env1$path$source_base,"/","',env1$path$.RelativeSubPath_FileName.source.r,'"))', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'")', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.r,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.dev.Rmd,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    '# "',env1$path$source_base_local,"/",env1$path$.RelativeSubPath_FileName.source.r,'" |> env1$env.internal.attach$f_file.edit_if_exists.return2LastSourceEditorContext()', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.RelativeSubPath_FileName.source.r) )  ----  
# env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = list(.RelativeSubPath, .FileName.source.r) %>% {.[nzchar(.)]} %>% c(fsep = "/") %>% {do.call(file.path, .)})
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ START) function@o1 ----  
## https://chatgpt.com/c/66f605cf-6be4-800e-88a3-e8e23a7cb379
## :: f_vec.escapeRegex_vec 
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
###############################################################################
# Load Libraries
###############################################################################
library(tidyverse)
library(purrr)

###############################################################################
# Function: f_vec.escapeRegex_vec
# Description:
#   Escapes special regex characters in a string vector, including the backslash.
# Requested conventions:
#   - Name prefix: "f_vec."
#   - Suffix: "_vec" means we return a vector.
#   - Additional parameter: VERBOSE for debug printing.
###############################################################################

f_vec.escapeRegex_vec <- function(
  input_str_vec,
  VERBOSE = isTRUE(getOption("verbose"))
) {
  # The pattern includes the backslash with four backslashes in the R literal:
  #  - "." and other chars are single backslash in front.
  #  - the single backslash is represented as "\\\\" in the R code.
  pattern_str <- "([.\\\\+*?^$(){}|\\[\\]\\-])"
  
  if (VERBOSE) {
    message("[DEBUG] f_vec.escapeRegex_vec: pattern_str = ", pattern_str)
    message("[DEBUG] f_vec.escapeRegex_vec: length of input_str_vec = ", length(input_str_vec))
  }
  
  # Perform the substitution with perl = TRUE for the PCRE engine
  # "\\\\1" in R string literal means: Insert one backslash before the matched char
  escaped_str_vec <- gsub(pattern_str, "\\\\\\1", input_str_vec, perl = TRUE)
  
  if (VERBOSE) {
    message("[DEBUG] f_vec.escapeRegex_vec: escaped_str_vec = ", paste(escaped_str_vec, collapse = ", "))
  }
  
  return(escaped_str_vec)
}

###############################################################################
# Testing the Function for Backslashes and Other Special Chars
###############################################################################

# We create a character vector that includes various backslashes and other chars.
health_data_examples_vec <- c(
  "patient_name$",
  "some\\backslash",
  "more\\\\backslashes",
  "blood^test+result",
  "D:\\Hospital\\Care",
  "[metadata]{info}"
)

# 1) Default call (VERBOSE = FALSE)
escaped_vec <- f_vec.escapeRegex_vec(health_data_examples_vec)

cat("===== Without VERBOSE =====\n")
cat("[Input]  health_data_examples_vec:\n")
cat(paste(health_data_examples_vec, collapse = ", "), "\n\n")
cat("[Output] escaped_vec:\n")
cat(paste(escaped_vec, collapse = ", "), "\n\n")

# 2) Debug call (VERBOSE = TRUE)
cat("===== With VERBOSE = TRUE =====\n")
escaped_verbose_vec <- f_vec.escapeRegex_vec(
  input_str_vec = health_data_examples_vec,
  VERBOSE = TRUE
)


```
  
  
### inclusion_glob = 
### exclusion_glob = 
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
inclusion_glob  <- "{**/*.[Rr],**/*.[Rr].txt,**/*.[Rr][Mm][Dd],default.R,.Rprofile}"
exclusion_glob  <- "{.history,-[Bb][Aa][Cc][Kk][Uu][Pp],VScode Replace*.*,.git,.Rproj.user,*symlink*,r4ds-master}"
inclusion_glob %>% f_vec.escapeRegex_vec
```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ START) function@o1p ----  
## https://chatgpt.com/c/67776103-6c28-800e-9b02-b455688f189e
## :: f_vecChr.EscapeSpecialCharacters_vecChr 
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
#' Escapes special regex characters in a character vector.
#'
#' @param input_vecChr A character vector to be processed.
#' @param VERBOSE Logical indicating whether to print intermediate outputs
#'   for debugging. Defaults to isTRUE(getOption("verbose")) (usually FALSE).
#'
#' @return A character vector where each special regex character is escaped.
#'
#' @references
#' - R Documentation for 'gsub': https://stat.ethz.ch/R-manual/R-devel/library/base/html/gsub.html
#'
f_vecChr.EscapeSpecialCharacters_vecChr <- function(
  input_vecChr,
  VERBOSE = isTRUE(getOption("verbose"))
) {
  if (VERBOSE) {
    cat("Received input_vecChr:\n")
    print(input_vecChr)
  }
  
  # Define the regex pattern for special characters commonly used in regular expressions
  pattern_chr <- "([.*+?^=!:|\\\\/()\\[\\]{}])"
  
  # This replacement ensures each special character is prefixed by one backslash
  replacement_chr <- "\\\\\\1"
  
  if (VERBOSE) {
    cat("Regex pattern used for escaping special characters:\n")
    print(pattern_chr)
    cat("Replacement string:\n")
    print(replacement_chr)
  }
  
  # gsub is vectorized, so we can apply it directly across the entire vector
  escaped_vecChr <- gsub(
    pattern = pattern_chr,
    replacement = replacement_chr,
    x = input_vecChr,
    perl = TRUE
  )
  
  if (VERBOSE) {
    cat("Escaped output:\n")
    print(escaped_vecChr)
  }
  
  return(escaped_vecChr)
}

# Example usage with well-known health data references:
example_vecChr <- c(
  "Systolic (BP)* is around 120 + 10?", 
  "Patients' heart_rate^ might exceed 90!", 
  "BloodSugar=100: PleaseCheck!"
)

# If you set VERBOSE = TRUE, you will see intermediate outputs:
escaped_vecChr <- f_vecChr.EscapeSpecialCharacters_vecChr(
  input_vecChr = example_vecChr,
  VERBOSE = FALSE  # Change to TRUE to see debugging messages
)

# Expected outputs
escaped_vecChr

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


# __________|------  
# @@ START) function ----  
## :: function_name = function() -dev -pending  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## ->> Not Yet included in env1$env.internal.source.r ----
## ->> Not Yet included in f_df.t.tribble_construct.source.r ----

##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## :: function_name = function() ====
## Rdev/00_base_program/001_base_file/function_name.dev.Rmd
.tmp$env1_subenv_name = "env.internal"
.tmp$objectname = "function_name" 
env1[[.tmp$env1_subenv_name]][[.tmp$objectname]] = function(input_object) {
    output_object = input_object
    invisible()
}
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
```{r createBACKUP, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%dT%H", overwrite=TRUE)
        # env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%dT%H", overwrite=TRUE)
    # }
}
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_FileName.nb.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") {  try(  paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE),'"') |> shell(wait=FALSE)  )  }  # else { browseURL(env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE)) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileNameExt) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileName.nb.html) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
