---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
# ```{r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


# ```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  cat('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  \n')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = options()$width; cat(options()$width, "  \n", sep="")
# ```
#   
# <font size="3">\% env1</font>  
#   
# ```{r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd()) #----   
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## env1\$path\$CurrentSource.path.filename.ext ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(getwd()|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
env1$path$CurrentSource.path.filename.ext = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/") |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/")), "") |> str_replace("^/", "")
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
cat('> ls(all.names = TRUE) |> set_names() |> map(get) |> str(max.level = 1)', "  \n", sep="") 
ls(all.names = TRUE) |> set_names() |> map(get) |> str(max.level = 1)
cat("> .tmp |> str(max.level = 1, give.attr = FALSE)", "  \n", sep="") 
.tmp |> str(max.level = 1, give.attr = FALSE)
cat("> env1 |> as.list() |> str(max.level = 2, give.attr = FALSE)", "  \n", sep="") 
env1 |> as.list() |> str(max.level = 2, give.attr = FALSE)
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .sourcename = "f_DataSetName.Search.read.checkEntity" |> paste0(".source.r"); .subpath=r"()"|>str_replace_all("\\\\","/"); .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.); if(!.sourcename %in% names(.GlobalEnv$env1$source)) {  cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); suppressPackageStartupMessages(source(.GlobalEnv$env1$source[[.sourcename]]))  }
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  #----  
```
  
  
# @@ START) data example ----  
## \$ analyticDF_time2event =  ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
suppressPackageStartupMessages(library(tidyverse))
# suppressPackageStartupMessages(library(survival))
for(.packagename in c("survminer")) {if(!require(.packagename,character.only=TRUE)) install.packages(.packagename)  ;  library(.packagename,character.only=TRUE)}  
# ?survival::lung
.objectname = DataSetName = "analyticDF_time2event"
assign(
    DataSetName, 
    survival::lung |> mutate(event = as.logical(status-1), Group = c("Male", "Female")[sex] |> as.factor(), StudyPopulation = time >= 30) |>
        # dplyr::select(-status, -sex)
        dplyr::select(-status)
)
analyticDF_time2event %>% {cat(" > ",deparse(substitute(.))," |> as_tibble() |> print()","  \n", sep=""); print(as_tibble(.))}
```
  
  
# @@ MetaData ----  
```{r MetaData0-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
# .GlobalEnv$MetaData = list() ====  
env1$path$CurrentSource.path.filename.MetaData.rds = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".MetaData.rds")
if(file.exists(env1$path$CurrentSource.path.filename.MetaData.rds)) { 
    MetaData = env1$path$CurrentSource.path.filename.MetaData.rds |> read_rds() 
} else {
    if(!exists("MetaData", envir=.GlobalEnv)) { assign("MetaData", list(), envir=.GlobalEnv) }  
}
.parentname = "MetaData"
# for (.sublistname in c("tblVarName", "DataSetNames", "VarNames", "VarNames.select", "VarNames.filter", "VarNames.recode", "ModelList")) {
for (.sublistname in c("tblVarName", "DataSetNames", "VarNames", "VarNames.select", "ModelList")) {
    if(!.sublistname %in% names(.GlobalEnv[[.parentname]])) { .GlobalEnv[[.parentname]][[.sublistname]] = list() }
}

### @ MetaData\$ModelList  ====   
.parentname = "MetaData"; 
.sublistname = "ModelList"; 
for (.sub2listname in c("time2DM", "time2HTN", "time2DL", "time2MetS")) {
    if(!.sub2listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]])) { .GlobalEnv[[.parentname]][[.sublistname]] = list() }
}

### @ MetaData\$VarNames  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
for (.sub2listname in c("Event", "Mediator", "Exposure", "PMHx", "Tx", "FHx", "Exam", "Social", "Behavioral", "Unclassified", "Calculated")) {
    if(!.sub2listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]])) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]] = list() }
}

#### @ MetaData\$VarNames\$Event  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Event"; 
for (.sub3listname in c("DM", "HTN", "DL", "MetS")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

#### @ MetaData\$VarNames\$Mediator  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Mediator"; 
for (.sub3listname in c("BMI", "Waist")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

#### @ MetaData\$VarNames\$Exposure  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Exposure"; 
for (.sub3listname in c("Exercise", "Diet", "Alcohol", "Smoking")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

#### @ MetaData\$VarNames\$Demographic  ====   
.parentname = "MetaData"; 
.sublistname = "VarNames"; 
.sub2listname = "Social"; 
for (.sub3listname in c("Age", "Sex", "Income", "Education", "Residence", "Marriage")) {
    if(!.sub3listname %in% names(.GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]]) ) { .GlobalEnv[[.parentname]][[.sublistname]][[.sub2listname]][[.sub3listname]] = list() }
}

MetaData %>% str
## @ .MetaData0 ====
.MetaData0 = MetaData
```
  

## \$ MetaData\$tblVarName\$tblVarName.suffix = KoGES201806vars.CLEAN_TRIM ----   
```{r KoGES201806vars.CLEAN_TRIM-read.checkEntity-NoEcho, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
.DataSetName = "KoGES201806vars.CLEAN_TRIM"
assign(.DataSetName, read_rds(paste0(env1$path$path0,"/Rproject_KoGES_AA10030/",.DataSetName,".rds")))
MetaData$tblVarName$tblVarName.suffix = get(.DataSetName)
attributes(MetaData$tblVarName$tblVarName.suffix)$DataSetName = .DataSetName
```
  
  
## \$ MetaData\$tblVarName\$tblWAVE_VARNAME = KoGES201806vars_waves.rev.CLEAN ----   
```{r KoGES201806vars_waves.rev.CLEAN-read.checkEntity-NoEcho, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
.DataSetName = "KoGES201806vars_waves.rev.CLEAN"
assign(.DataSetName, read_rds(paste0(env1$path$path0,"/Rproject_KoGES_AA10030/",.DataSetName,".rds")))
MetaData$tblVarName$tblWAVE_VARNAME = get(.DataSetName)
attributes(MetaData$tblVarName$tblWAVE_VARNAME)$DataSetName = .DataSetName
```
  
  
```{r MetaData.VarNames-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
### \% KoGES201806vars.CLEAN_TRIM \%>\% {cat(" > ",deparse(substitute(.))," |> str()","\\n", sep=""); str(.)} #----  
MetaData$tblVarName$tblVarName.suffix %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)} #----  
MetaData$VarNames$VarName.suffix503 = KoGES201806vars.CLEAN_TRIM$VarName.suffix |> as.character() |> unique()
MetaData$VarNames$VarName.suffix503 |> str()
### \% KoGES201806vars_waves.rev.CLEAN \%>\% {cat(" > ",deparse(substitute(.))," |> str()","\\n", sep=""); str(.)} #----  
MetaData$tblVarName$tblWAVE_VARNAME %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)} #----  
MetaData$VarNames$WAVE_VARNAME3293 = KoGES201806vars_waves.rev.CLEAN$WAVE_VARNAME |> as.character() |> unique()
```
  
  
## @ MetaData) TableNames ----  

## @ MetaData) VarNames.filter ----  
Caution) filter the variables based on RegEx for VarNames, or VarDescription, or VarClassification.  
  
## @ MetaData) VarNames.select ----  
Caution) filter the selected variables (VarNames.select) from the codebook, select the selected variables (VarNames.select) from the dataset.  
  
```{r MetaData.VarNames.select, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
## @ KoGES201806vars.CLEAN_TRIM |> dplyr::filter(Select == "Select") \%>\% {.\$VarName.suffix} |> as.character()  
## @ KoGES201806vars.CLEAN_TRIM |> dplyr::filter(Select == "Select") \%>\% {.\$WAVE1_VarName.suffix} |> as.character()  
## @ MetaData\$tblVarName$tblWAVE_VARNAME |> dplyr::filter(Select == "Select") \%>\% {.\$WAVE_VARNAME}  
MetaData$VarNames.select$VarName.suffix.select122 = KoGES201806vars.CLEAN_TRIM |> dplyr::filter(Select == "Select") %>% {.$VarName.suffix} |> as.character()
MetaData$VarNames.select$VarName.suffix.select122 %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)}
MetaData$VarNames.select$VarName.suffix.select122 |> deparse(width.cutoff=120-15) |> paste0(collapse="  \n  ") %>% {cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n", ., "  \n", sep="")}  # dput(); |> deparse(width.cutoff=120-15) |> paste0(collapse="  \n") |> cat("  \n", sep=""); # width.cutoff=500 is the max ---    
cat("    ========================================================================    \n")
MetaData$VarNames.select$WAVE_VARNAME.select836 = MetaData$tblVarName$tblWAVE_VARNAME |> dplyr::filter(Select == "Select") %>% {.$WAVE_VARNAME} |> as.character()
MetaData$VarNames.select$WAVE_VARNAME.select836 %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)}
MetaData$tblVarName$tblWAVE_VARNAME |> dplyr::filter(Select == "Select") |> dplyr::select(VarName.suffix, VarDescription, Wave, WAVE_VARNAME, VarType, ValueChange) %>% spread(WAVE_VARNAME, key = "Wave") |> print(n=200)
# MetaData$tblVarName$tblWAVE_VARNAME |> dplyr::filter(Select == "Select") |> group_by(VarName.suffix, VarDescription, VarType, ValueChange) |> summarise(n=n(), nd.Wave = n_distinct(Wave), nd.WAVE_VARNAME = n_distinct(WAVE_VARNAME)) |> print(n=200)
MetaData$tblVarName$tblWAVE_VARNAME |> dplyr::filter(Select == "Select") %>% group_by(VarName.suffix, VarDescription, VarType, ValueChange) %>% summarise(n=n(), nd.Wave = n_distinct(Wave), nd.WAVE_VARNAME = n_distinct(WAVE_VARNAME)) |> filter(n < 7)
```  
  
  
## @ MetaData) Varnames.suffix ----  
  
```{r A00.suffix-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
MetaData$VarNames$A00.suffix = c("DATA_CLASS", "CKSTEAM", "CKROAST", "CKFRI", "CKSSN", "CKSOUP", "CKOIL", "CKOILETC", "SPCOIL", "SPCOILETC",   
  "RMEALFQA", "BMEALFQA", "SKPMEAL", "EATOUTFQ", "ALNMEALFQ", "SOUPEAT", "FRFSWT", "FRFSLT", "FRFSPCY",   
  "FRFSOUR", "FRFOILY", "MNSAG", "PREG", "FPREGAG", "CHILD", "FLABAG", "BRSTF", "BRSTC", "SABHX", "SABNO",   
  "AABHX", "AABNO", "GDM", "VISITALL", "SEX", "EDU", "SMAG")
MetaData$VarNames$A00.suffix %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)}
```
  
  
```{r A01_7.suffix465-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
MetaData$VarNames$A01_7.suffix465 = c("PHYSTB", "PHYSIT", "PHYACTL", "PHYACTM", "PHYACTH", "AEROBFQ", "AEROBAM", "JOGFQ", "JOGAM", "SWIMFQ", "SWIMAM", 
"TENIFQ", "TENIAM", "GOLFFQ", "GOLFAM", "BOWLFQ", "BOWLAM", "HEALTHFQ", "HEALTHAM", "WALKFQ", "WALKAM", "CLIMBFQ", 
"CLIMBAM", "MET", "EXERCUR", "EXER", "EXERFQ", "EXERDU", "SBP_L", "DBP_L", "SBP_R", "DBP_R", "PULSE", "WAIST", 
"HIP", "HEIGHT", "WEIGHT", "DS", "DT", "DZ", "DP", "MS", "MT", "MZ", "MP", "HBA1C", "GLU0_ORI", "GLU0_TR", 
"GLU60_ORI", "GLU60_TR", "GLU120_ORI", "GLU120_TR", "TOTPRT", "ALBUMIN_ORI", "ALBUMIN_TR", "BUN_ORI", "BUN_TR", 
"CREATININ_ORI", "CREATININ_TR", "CA", "TOTBIL", "AST_ORI", "AST_TR", "ALT_ORI", "ALT_TR", "R_GTP_ORI", "R_GTP_TR", 
"CRP", "HSCRP", "TCHL_ORI", "TCHL_TR", "HDL_ORI", "HDL_TR", "TRIGLY_ORI", "TRIGLY_TR", "NA", "K", "CL", "WBC_B_ORI", 
"WBC_B_TR", "RBC_B_ORI", "RBC_B_TR", "HB_ORI", "HB_TR", "HCT_ORI", "HCT_TR", "PLAT_ORI", "PLAT_TR", "INS0", 
"INS60", "INS120", "RENIN", "PRT_U", "CREATINE_U", "URICACID_U", "CA_U", "NA_U", "K_U", "MICALBU_U", "ALBU_U", 
"PH_U", "NITRIT_U", "SG_U", "PRT16_U", "GLU16_U", "KETONE_U", "BILI16_U", "BLOOD16_U", "UROBILI_U", "COLOR_U", 
"RBC_U", "WBC_U", "EPCELL_U", "CASTS_U", "BACTERIA_U", "CRYSTAL1_U", "CRYSTAL2_U", "CRYSTAL3_U", "CRYSTAL4_U", 
"CRYSTAL5_U", "CRYSTAL6_U", "OTHER_U", "VITB12", "FOLATE", "FREET4", "TSH", "CD", "PB", "AL", "INCELL", "IB1_2", 
"IB1_3", "IB1_4", "EXCELL", "BODYPRT", "BODYMIN", "BODYFAT", "OBDIG1", "OBDIG2", "OBDEG", "CH0", "CH2", "CH3", 
"CH4", "CH5", "CH6", "CH7", "CH8", "CH9", "CH10", "CH11", "CH12", "CH13", "CH14", "CH15", "CH16", "CH17", 
"CH18", "CH19", "CH20", "CH21", "CH23", "CH24", "CH25", "CH26", "CH27", "CH28", "CH29", "CH30", "CH31", "CH32", 
"CH33", "BRF", "MEALRG", "OVEREAT", "MEALSPD", "AFTDNN", "MEATFAT", "HTN", "HTNAG", "HTNCU", "DM", "DMAG", 
"DMCU", "ULCER", "ULCERAG", "ULCERCU", "ALLER", "ALLERAG", "ALLERCU", "MI", "MIAG", "MICU", "THY", "THYAG", 
"THYCU", "CHF", "CHFAG", "CHFCU", "CAD", "CADAG", "CADCU", "LIP", "LIPAG", "LIPCU", "ASTH", "ASTHAG", "ASTHCU", 
"CLD", "CLDAG", "CLDCU", "PVD", "PVDAG", "PVDCU", "KID", "KIDAG", "KIDCU", "HEPA", "HEPAAG", "HEPACU", "TB", 
"TBAG", "TBCU", "CEVA", "CEVAAG", "CEVACU", "HEIN", "HEINAG", "HEINCU", "UTI", "UTIAG", "UTICU", "ARTH", "ARTHAG", 
"ARTHCU", "GOUT", "GOUTAG", "GOUTCU", "LCA", "LCAAG", "LCACU", "GCA", "GCAAG", "GCACU", "HCCCA", "HCCCAAG", 
"HCCCACU", "COLCA", "COLCAAG", "COLCACU", "PACA", "PACAAG", "PACACU", "UTCA", "UTCAAG", "UTCACU", "BRCA", 
"BRCAAG", "BRCACU", "THYCA", "THYCAAG", "THYCACU", "PROCA", "PROCAAG", "PROCACU", "GALLCA", "GALLCAAG", "GALLCACU", 
"HTN_C", "HTNAG_C", "DM_C", "DMAG_C", "DRINK", "DRDU", "DRQDU", "TAKFQ", "TAKAM", "RICEFQ", "RICEAM", "WINEFQ", 
"WINEAM", "SOJUFQ", "SOJUAM", "BEERFQ", "BEERAM", "HLIQFQ", "HLIQAM", "ETCNA", "ETCFQ", "ETCT", "ETCAM", "TOTALC", 
"DRUGST", "DRUGSTYR1", "DRUGSTCU", "DRUGSTYR2", "DRUGSP", "DRUGSPYR1", "DRUGSPCU", "DRUGSPYR2", "DRUGSL", 
"DRUGSLYR1", "DRUGSLCU", "DRUGSLYR2", "DRUGCP", "DRUGCPYR1", "DRUGCPCU", "DRUGCPYR2", "DRUGTB", "DRUGTBYR1", 
"DRUGTBCU", "DRUGTBYR2", "DRUGINS", "DRUGINSYR1", "DRUGINSCU", "DRUGINSYR2", "DRUGHT", "DRUGHTYR1", "DRUGHTCU", 
"DRUGHTYR2", "DRUGAR", "DRUGARYR1", "DRUGARCU", "DRUGARYR2", "DRUGUL", "DRUGULYR1", "DRUGULCU", "DRUGULYR2", 
"DRUGTH", "DRUGTHYR1", "DRUGTHCU", "DRUGTHYR2", "DRUGOR", "DRUGORYR1", "DRUGORCU", "DRUGORYR2", "DRUGFH", 
"DRUGFHYR1", "DRUGFHCU", "DRUGFHYR2", "DRUGOS", "DRUGOSYR1", "DRUGOSCU", "DRUGOSYR2", "DRUGDM", "DRUGDMYR1", 
"DRUGDMCU", "DRUGDMYR2", "DRUGICD", "DRUGICDYR1", "DRUGICDCU", "DRUGICDYR2", "DRUGDI", "DRUGDIYR1", "DRUGDICU", 
"DRUGDIYR2", "DRUGAS", "DRUGASYR1", "DRUGASCU", "DRUGASYR2", "DRUGLP", "DRUGLPYR1", "DRUGLPCU", "DRUGLPYR2", 
"EKG", "FMHTN", "FMFHT", "FMFHTAG", "FMMHT", "FMMHTAG", "FMBHT", "FMBHTAG", "FMCHT", "FMCHTAG", "FMDM", "FMFDM", 
"FMFDMAG", "FMMDM", "FMMDMAG", "FMBDM", "FMBDMAG", "FMCDM", "FMCDMAG", "FMHEA", "FMFHEA", "FMFHEAAG", "FMMHEA", 
"FMMHEAAG", "FMBHEA", "FMBHEAAG", "FMCHEA", "FMCHEAAG", "PMYN_C", "PMAG_C", "B01", "B02", "B03", "B04", "B05", 
"B06", "B07", "B08", "B09", "B10", "B11", "B12", "B13", "B14", "B15", "B16", "B17", "B18", "B19", "B20", "B21", 
"B23", "B24", "VISIT", "EDATE", "AGE", "MARRY", "INCOME", "SMOKE", "SMQYR", "SMQMO", "SMDU", "SMAM", "SMIN", 
"PACKYR", "PSM", "PSMHFQ", "PSMHMIN", "PSMOFQ", "PSMOMIN", "PSMDU", "TREATD1", "TREATD2", "TREATD3", "TREATD4", 
"TREATD5", "TREATD6", "TREATD7", "TREATD8", "TREATD9", "TREATD11", "TREATD13", "TREATD14", "TREATD15", "TREATD16", 
"TREATD20", "TREATD21", "TREATD22", "TREATD23", "TREATD24", "TREATD27", "TREATD18A", "TREATD18B", "TREATD18C", 
"TREATD18D", "TREATD18E", "TREATD18F", "TREATD18G", "TREATD18H", "TREATD18I", "TREATD18J")   
MetaData$VarNames$A01_7.suffix465 %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)}
```
  
  
## @ MetaData) Varnames.matrix ----  
  
```{r A00.names-NoEcho, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
## \$ A00.names ----  
MetaData$VarNames$A00.names = paste0("A00_", MetaData$VarNames$A00.suffix)
MetaData$VarNames$A00.names %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)}
```
  
  
```{r A01_7.names.matrix-NoEcho, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
### \$ A01_7.names.matrix ----  
MetaData$VarNames$A01_7.names.matrix = outer(1:7, MetaData$VarNames$A01_7.suffix465, function(x,y) paste0("A0", x, "_", y)) %>% structure(., dimnames=list(paste0("A0", 1:7), MetaData$VarNames$A01_7.suffix465))
MetaData$VarNames$A01_7.names.matrix %>% {cat(" > ",deparse(substitute(.))," |> str()","  \n", sep=""); str(.)}
 # chr [1:7, 1:465] "A01_PHYSTB" "A02_PHYSTB" "A03_PHYSTB" "A04_PHYSTB" "A05_PHYSTB" "A06_PHYSTB" "A07_PHYSTB" "A01_PHYSIT" ...
 # - attr(*, "dimnames")=List of 2
 #  ..$ : chr [1:7] "A01" "A02" "A03" "A04" ...
 #  ..$ : chr [1:465] "PHYSTB" "PHYSIT" "PHYACTL" "PHYACTM" ...
```

# @@ START) Data ----  

## \$ df_NewDMv3.CensorEND.n88.select293.NA.rmAllNA.recode  
### @ VarName.suffix.regex = "A0[0-2]"
### :: DataSet.Date.NA.rmAllNA = get(DataSetName) |> select(matches(VarName.suffix.regex))
#### \% |> select(matches("A0[0-3]")) ----  
#### \% |> env1\$f\$f_df.Table1byExposure.xlsx(VarNames4Exposure =  c("A01_BMI.cut5"))  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
.path4read = paste0(env1$path$path0,"/Rproject_KoGES_AA10030/df_NewDMv3.CensorEND.n88.select971.NA.rmAllNA.recode")
DataSetName = "df_NewDMv3.CensorEND.n88.select293.NA.rmAllNA.recode"
paste0(.path4read,"/",DataSetName,".rds") |> env1$f$f_DataSet_path_filename_ext.read.checkEntity()

#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
VarName.suffix.regex =
    c(
        paste0("A0[1-5]_",
               c("WEIGHT", "HEIGHT",
                 "BMI.cut5")),
        # outer(c("delta", "pd"), 1:4, paste0),
        paste0("A02_", ".*",
               c("delta", "pd"),
               "1"),
        paste0("A02_", ".*",
               c("delta", "pd"),
               "1"),
        paste0("A03_", ".*",
               c("delta", "pd"),
               "2"),
        paste0("A05_", ".*",
               c("delta", "pd"),
               "4"),
        paste0("A00_",
               c("SEX")),
        "Female",
        paste0("A01_",
               c("EDATE", "AGE", "INCOME",
                 "WAIST", "HIP",
                 "BODYFAT", "OBDIG1", "OBDIG2", "OBDEG",
                 # "BP", "PULSE", "HTN_C", "HTNCU", "TREATD1", "DRUGHTCU", "FMHTN",
                 "PULSE", "HTN_C", "HTNCU", "DRUGHTCU", "FMHTN",
                 "HBA1C", "GLU0_TR", "DM_C", "DMCU", "TREATD2", "DRUGDMCU", "DRUGINSCU", "FMDM",
                 "PHYSTB", "PHYSIT", "MET", "EXERCUR", "EXER", "EXERFQ", "EXERDU",
                 "BRF", "MEALRG", "AFTDNN",
                 "DRINK", "DRDU",
                 "SMOKE", "SMAG", "SMDU", "SMAM", "PSM", "PSMDU",
                 "LIPCU",
                 "MICU", "CHFCU", "CADCU", "PVDCU", "TREATD8", "FMHEA",
                 "CEVACU",
                 "KIDCU", "TREATD14"))
    ) %>% paste0(collapse="|")
VarName.suffix.regex %>% dput
DataSet.Date.NA.rmAllNA = get(DataSetName) %>% select(matches(VarName.suffix.regex), matches("A0[0-2]")) %>%
    # select(matches("A00|A01|A04|A07"))
    # select(matches("A00|A01|A07"))
    select(matches("A0[0-3]"))
DataSet.Date.NA.rmAllNA = DataSet.Date.NA.rmAllNA[sort(names(DataSet.Date.NA.rmAllNA))]
DataSet.Date.NA.rmAllNA = DataSet.Date.NA.rmAllNA %>% mutate_if(function(vec) {is.numeric(vec) && n_distinct(vec) <= 10}, as.factor)
DataSet.Date.NA.rmAllNA %>% str(max.level = 2)
```


#### \% |> select(matches("DM")) ----  
#### \% |> select(matches("PHY")) ----  
#### \% |> select(matches("EDU")) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
DataSet.Date.NA.rmAllNA %>% select(matches("DM")) %>% str(max.level = 2)
DataSet.Date.NA.rmAllNA %>% select(matches("PHY")) %>% str(max.level = 2)
DataSet.Date.NA.rmAllNA %>% select(matches("EDU")) %>% str(max.level = 2)
```



# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```
  
# https://cloud.r-project.org/web/packages/labelled/vignettes/intro_labelled.html

# Introduction to labelled  

## library(labelled)
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
if(!requireNamespace("labelled", quietly = TRUE)) install.packages("labelled")
library(labelled)
```

## ## Variable labels  

A variable label could be specified for any vector using `var_label()`.

### ECHO :: var_label(df$Var1) = "VarDescription1" ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
iris = datasets::iris
iris %>% str
var_label(iris$Sepal.Length) <- "Length of sepal"
iris %>% str
```

### ECHO :: var_label(df) <- list(Var1 = "VarDescription1", Var2 = "VarDescription2") ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
iris = datasets::iris
iris %>% str
    var_label(iris) <- list(
      Petal.Length = "Length of petal",
      Petal.Width = "Width of Petal"
    )
iris %>% str
```


You can display and search through variable names and labels with `look_for()`:
#### ECHO \% df |> look_for() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
    look_for(iris)
```

    ##  pos variable     label           col_type missing values    
    ##  1   Sepal.Length —               dbl      0                 
    ##  2   Sepal.Width  —               dbl      0                 
    ##  3   Petal.Length Length of petal dbl      0                 
    ##  4   Petal.Width  Width of Petal  dbl      0                 
    ##  5   Species      —               fct      0       setosa    
    ##                                                    versicolor
    ##                                                    virginica

#### ECHO \% df |> look_for("varname_part") ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
    look_for(iris, "pet")
```

    ##  pos variable     label           col_type missing values
    ##  3   Petal.Length Length of petal dbl      0             
    ##  4   Petal.Width  Width of Petal  dbl      0

#### ECHO \% df |> look_for(details = FALSE) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
    look_for(iris, details = FALSE)
```

    ##  pos variable     label          
    ##  1   Sepal.Length —              
    ##  2   Sepal.Width  —              
    ##  3   Petal.Length Length of petal
    ##  4   Petal.Width  Width of Petal 
    ##  5   Species      —


## ## Value labels  

### :: v = 
### ECHO :: labelled() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
    v <- labelled(
      c(1, 2, 2, 2, 3, 9, 1, 3, 2, NA),
      c(yes = 1, no = 3, "don't know" = 8, refused = 9)
    )
    v
```

    ## <labelled<double>[10]>
    ##  [1]  1  2  2  2  3  9  1  3  2 NA
    ## 
    ## Labels:
    ##  value      label
    ##      1        yes
    ##      3         no
    ##      8 don't know
    ##      9    refused

#### ECHO :: val_labels(df$Var1) = c(ValueLabelA = "ValueA", ValueLabelB = "ValueB") ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
    val_labels(v) <- c(yes = 1, nno = 3, bug = 5)
    v
```

    ## <labelled<double>[10]>
    ##  [1]  1  2  2  2  3  9  1  3  2 NA
    ## 
    ## Labels:
    ##  value label
    ##      1   yes
    ##      3   nno
    ##      5   bug

### :: df =
#### ECHO :: val_labels(df) = list(Var1 = c(ValueLabelA = "ValueA", ValueLabelB = "ValueB"), Var2 = c(ValueLabel1 = 1, ValueLabel2 = 2)) ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
    df <- data.frame(v1 = 1:3, v2 = c(2, 3, 1), v3 = 3:1)
    val_labels(df) <- list(v1 = c(yes = 1, no = 3), v2 = c(a = 1, b = 2, c = 3))
    val_labels(df)
```

    ## $v1
    ## yes  no 
    ##   1   3 
    ## 
    ## $v2
    ## a b c 
    ## 1 2 3 
    ## 
    ## $v3
    ## NULL

## \% analyticDF_time2event |>  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ START) function ----  
## \% |> function_name()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
# @@ START) source ----  
```{r .subpath.filename.source.r-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
# .subpath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") {.subpath = env1$path$CurrentSource.path.filename.ext |> dirname(); ".subpath" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
# if(.subpath!="") utils::browseURL(normalizePath(.subpath))
# .sourcename = "default.template" |> paste0(".source.r")
if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") {.sourcename_root = env1$path$CurrentSource.path.filename.ext |> basename() |> str_replace("\\.(dev|source)\\.(r|Rmd)$"|>regex(ignore_case=TRUE), "") |> str_replace("\\.(r|Rmd)$"|>regex(ignore_case=TRUE),""); ".sourcename_root" %>% {cat(.,' = "',get(.),'"  \n', sep="")} }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
env1$path$.subpath = .subpath
if(!exists(".sourcename_root") && exists(".sourcename")) .sourcename_root = .sourcename |> str_replace("\\.source\\.r$", "")
.sourcename = .sourcename_root |> paste0(".source.r")
env1$path$.sourcename_root = .sourcename_root
env1$path$.subpath.filename.dev.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.r")
env1$path$.subpath.filename.dev.Rmd = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".dev.Rmd")
env1$path$.subpath.filename.source.r = paste0(.subpath,ifelse(.subpath=="","","/"),.sourcename_root,".source.r")
cat("# ",'.sourcename_root = "',.sourcename_root,'"  \n',
    "#### ",env1$path$.subpath.filename.dev.r, "----  \n",
    "#### ",env1$path$.subpath.filename.dev.Rmd, "----  \n",
    "#### ",env1$path$.subpath.filename.source.r, "----  \n",
    '# # source(paste0(env1$path$source_base,"/","',env1$path$.subpath.filename.source.r,'"))', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'")', "  \n",
    '# # if(!file.exists("',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'")) download.file(url = "https://raw.githubusercontent.com/mkim0710/tidystat/master/rstudio-prefs/templates/default.R", destfile = "',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'")', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.r,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.dev.Rmd,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    '# file.edit("',env1$path$source_base_local,"/",env1$path$.subpath.filename.source.r,'"); if(!is.null(env1$path$CurrentSource.path.filename.ext)) if(env1$path$CurrentSource.path.filename.ext != "") file.edit(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext));', "  \n",
    sep="")
# #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# # \% source( file.path(env1$path$source_base,.subpath.filename.source.r) ) ----  
# .subpath.filename.source.r = .sourcename %>% paste0(.subpath,ifelse(.subpath=="","","/"),.)
# if(!.sourcename %in% names(.GlobalEnv$env1$source)) {cat('> source("',file.path(env1$path$source_base,.subpath.filename.source.r),'")', "  \n", sep=""); .GlobalEnv$env1$source[[.sourcename]] = file.path(env1$path$source_base,.subpath.filename.source.r); source(.GlobalEnv$env1$source[[.sourcename]])}
```
  
  

  

###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```

  
  
```{r MetaData99-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
if(exists("MetaData")) {
    "> MetaData |> str(max.level = 2, give.attr = FALSE)" |> cat("  \n", sep="")
    MetaData |> str(max.level = 2, give.attr = FALSE)
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    # "> MetaData$tblVarName |> str(max.level = 3, give.attr = FALSE)" |> cat("  \n", sep="")
    # MetaData$tblVarName |> str(max.level = 3, give.attr = FALSE)
    # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    # "> MetaData$DataSetNames |> str(max.level = 2, give.attr = FALSE)" |> cat("  \n", sep="")
    # MetaData$DataSetNames |> str(max.level = 2, give.attr = FALSE)
    # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "> MetaData$VarNames |> str(max.level = 3, give.attr = FALSE)" |> cat("  \n", sep="")
    MetaData$VarNames |> str(max.level = 3, give.attr = FALSE)
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "> MetaData$VarNames.select |> str(max.level = 3, give.attr = FALSE)" |> cat("  \n", sep="")
    MetaData$VarNames.select |> str(max.level = 3, give.attr = FALSE)
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    "> MetaData$ModelList |> str(max.level = 3, give.attr = FALSE)" |> cat("  \n", sep="")
    MetaData$ModelList |> str(max.level = 3, give.attr = FALSE)
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
    # "> MetaData |> str()" |> cat("  \n", sep="")
    # MetaData |> str()
    "> all.equal(.MetaData0, MetaData)" |> cat("  \n", sep="")
    all.equal(.MetaData0, MetaData)
    if(!identical(.MetaData0, MetaData)) {
        # cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
        .path.file = env1$path$CurrentSource.path.filename.MetaData.rds %>% {paste0(env1$path$path1,"/",.)}
        # cat('env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = "', .path.file, '", .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)', "  ;  ", sep="")
        # cat('MetaData |> write_rds("', .path.file, '", compress = "xz") |> system.time()', "  \n", sep="")
        # cat("'git lfs track ",shQuote(.path.file),"' |> system(intern=TRUE)  \n", sep=""); cat("'git add -f ",shQuote(.path.file),"' |> system(intern=TRUE)  \n", sep="")
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = .path.file, .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  
        MetaData |> write_rds(.path.file, compress = "xz") |> system.time()
        # paste0( "git add -f ",shQuote(.path.file) ) |> system(intern=TRUE)
    }
} else {warning("MetaData does not exist!  \n")}
```


```{r writeRDS-EvalNoEchoNoMsgNoResults, eval=TRUE, echo=FALSE, warning=TRUE, message=NA, results="hide"}
#|________________________________________________________________________________|#  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## @ write_rds( get(.objectname), file.path(.path4write, paste0(.objectname,".rds"))) ----  
.path4write = env1$path$.path4write
# MetaData$DataSetNames |> names() |> paste0(collapse = "\n") |> cat("\n", sep="")
cat("    ========================================================================    \n")
for (.objectname in names(MetaData$DataSetNames)) {
    assign(.objectname, structure(get(.objectname), MetaData = MetaData))
    .path.file = paste0(.path4write,"/",.objectname,".rds",".xz")
    cat(.objectname, ' |> write_rds(',shQuote(.path.file),', compress = "xz", compression = 9) |> system.time()', "  \n", sep="")
    # system.time(write_rds( get(.objectname), .path.file, compress = "xz", compression = 9 ))
    cat('env1$f$f_path.size_files(.path4read = ',shQuote(.path4write),', regex4filename = ',shQuote(.objectname),")  \n", sep="")
    env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, execute_code = FALSE)
    cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
}
# #++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
# .path.filename.xlsx = paste0(.path4write,"/",.objectname,".xlsx")
# system.time(openxlsx2::write_xlsx(get(.objectname), file=.path.filename.xlsx, as_table=TRUE))
# if (Sys.info()["sysname"] == "Windows") openxlsx2::xl_open(.path.filename.xlsx)
```
  
  
```{r createBackup, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$CurrentSource.path.filename.pdf = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$CurrentSource.path.filename.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (Sys.info()["sysname"] == "Windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$CurrentSource.path.filename.ext)),', output_format = "pdf_document")  \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
        .path.file = env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}
        env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, execute_code = FALSE)
        env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = .path.file, .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal$f_file_PDF.sumatra(.path.file))
    }
}
# env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path.file = env1$path$CurrentSource.path.filename.pdf %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, execute_code = FALSE); cat('  env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = ',deparse(.path.file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal$f_file_PDF.sumatra(',deparse(.path.file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path.file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$CurrentSource.path.filename.ext %>% {paste0(env1$path$path1,"/",.)} %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path.file = env1$path$CurrentSource.path.filename.html %>% {paste0(env1$path$path1,"/",.)}; env1$f$f_file.git_lfs_track_add_f(.path.file = .path.file, execute_code = FALSE); cat('  env1$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = ',deparse(.path.file),', .backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); cat('  env1$env.internal$f_URL.open_in_edge_app(',deparse(.path.file),')  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$CurrentSource.path.filename.nb.html = env1$path$CurrentSource.path.filename.ext |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") { paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}|>normalizePath(winslash="/"),'"') |> shell(wait=FALSE) } # else { browseURL(env1$path$CurrentSource.path.filename.nb.html %>% {paste0(env1$path$path1,"/",.)}) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$CurrentSource.path.filename.ext)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.ext)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(paste0(env1$path$path1,"/",env1$path$CurrentSource.path.filename.nb.html)) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
