---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
mainfont: Arial
monofont: Consolas
header-includes: 
  - \usepackage{kotex}
  - \usepackage{fontspec}
  - \setmainhangulfont{HCR Batang}
  - \setsanshangulfont{HCR Dotum}
  - \setmonohangulfont{HCR Dotum}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Arial', 'Helvetica', sans-serif; }
h1.title { font-size: 28px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Arial', 'Helvetica', sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>

<!-- font-size: 0.9em; /* 90% of inherited font size */ -->

<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# _______________
```{r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE}
# ##### Rstudio RMarkDown Shortcuts
# https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE  
# https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html  
# Insert R chunk	Ctrl+Alt+I	Command+Option+I\
# Preview HTML	Ctrl+Shift+K	Command+Shift+K\
# Run all chunks above	Ctrl+Alt+P	Command+Option+P\
# Run current chunk	Ctrl+Alt+C	Command+Option+C\
# Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter\
# Run next chunk	Ctrl+Alt+N	Command+Option+N\
# Run all chunks	Ctrl+Alt+R	Command+Option+R\
# Go to next chunk/title	Ctrl+PgDown	Command+PgDown\
# Go to previous chunk/title	Ctrl+PgUp	Command+PgUp\
# Show/hide document outline	Ctrl+Shift+O	Command+Shift+O\
# F7 spell-check your document.\
# Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).\
# \
# *** Caution: \% \$ \# \* \
```


```{r setup, eval=TRUE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.utf8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "\n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=TRUE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=TRUE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)
```


```{r options-width-NoEchoHideResults, echo=FALSE, results="hide"}
if(!exists("env.custom", envir=.GlobalEnv)) 
    assign("env.custom", new.env(), envir=.GlobalEnv)
if(!"info" %in% names(.GlobalEnv$env.custom)) .GlobalEnv$env.custom$info <- list()
env.custom$info$options.width = options()$width; cat(options()$width, "\n", sep="")
```


```{r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
suppressPackageStartupMessages({for(packagename in c("tidyverse","formatR")) {if(!require(packagename,character.only=TRUE))install.packages(packagename) else library(packagename,character.only=TRUE)}});cat(" \n");
if(!exists("env.custom", envir=.GlobalEnv)) 
    assign("env.custom", new.env(), envir=.GlobalEnv)
## env.custom\$path ====
if(!"path" %in% names(.GlobalEnv$env.custom)) .GlobalEnv$env.custom$path <- list()
objectname = "source_base_local"; object = ifelse(.Platform$OS.type == "windows", "D:/OneDrive/[][Rproject]/github_tidystat", "~/github_tidystat"); if(!objectname %in% names(env.custom$path)) {env.custom$path[[objectname]] = object};
objectname = "source_base_github"; object = "https://github.com/mkim0710/tidystat/raw/master"; if(!objectname %in% names(env.custom$path)) {env.custom$path[[objectname]] = object};
env.custom$path$source_base = ifelse(dir.exists(env.custom$path$source_base_local), env.custom$path$source_base_local, env.custom$path$source_base_github)  
## env.custom\$env.internal ====
sourcename = "env.custom$env.internal"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
#### env.custom\$f_df.t.tribble_construct() ====
sourcename = "f_df.t.tribble_construct"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
```

<font size="3">\% env.custom</font>\

```{r envCustom-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
if(!exists("env.custom", envir=.GlobalEnv)) 
    assign("env.custom", new.env(), envir=.GlobalEnv)
if(!"info" %in% names(.GlobalEnv$env.custom)) .GlobalEnv$env.custom$info <- list()
#### env.custom\$info\$get_system_info() ====
sourcename = "get_system_info"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
env.custom$info$info_system_info = env.custom$info$get_system_info()
# str(env.custom$info$info_system_info)
CodeText = "env.custom$info$info_system_info$machine_nodename"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
CodeText = "env.custom$info$info_system_info$Sys.getlocale$LC_COLLATE"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
# CodeText = "env.custom$info$info_system_info$l10n_info$localization_UTF8"; cat(CodeText, ' = "', eval(parse(text=CodeText)), '"', "\n", sep="")
env.custom$info$info_software_versions = env.custom$info$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "datapasta","openxlsx"))
# str(env.custom$info$info_software_versions)
```


###### env.custom\$info\$DocumentTitle1 ====
```{r envCustom-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env.custom$info$DocumentTitle0 = paste0("00env.custom.minimum","-",basename(getwd()))
env.custom$info$DocumentTitle1 = paste0(env.custom$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env.custom$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env.custom$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env.custom$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env.custom$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```


###### env.custom\$path ====
```{r envCustom-Path-NoEcho, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE}
# cat(" getwd() == "); dput(getwd()) #----
objectname = "getwd"; object = getwd(); if(!objectname %in% names(env.custom$path)) {env.custom$path[[objectname]] = object};
objectname = "path0"; object = c(file.path("D:", "OneDrive", "[][Rproject]"), "/home/rstudio", "/cloud") |> keep(dir.exists) |> first(default = dirname(getwd())); if(!objectname %in% names(env.custom$path)) {env.custom$path[[objectname]] = object};
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
env.custom$path$CurrentSource.path.filename.ext=rstudioapi::getSourceEditorContext()$path 
paste0(env.custom$path$path1,"/",paste0("[Working Files List] ",basename(getwd()),".r")) %>% {.[file.exists(.)]} |> file.edit(); file.edit(env.custom$path$CurrentSource.path.filename.ext)
# env.custom$path$project_base = "Rproject_HEALS0215"
# env.custom$path$data_suffix = "_01"
# # env.custom$path$data_suffix = ""
# env.custom$path$project_suffix = "GJ3"
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
# env.custom$path$path4read = file.path(env.custom$path$path0, paste0(env.custom$path$project_base, env.custom$path$data_suffix))
# env.custom$path$path4write = file.path(env.custom$path$path4read, paste0(env.custom$path$project_base, env.custom$path$data_suffix, env.custom$path$project_suffix))
env.custom$path$path4read = ifelse(is.na(env.custom$path$path1), getwd(), env.custom$path$path1)
env.custom$path$path4write = getwd()
cat(" > str(env.custom$path)\n"); str(env.custom$path, max.level = 1, give.attr = F)  
path4read  = env.custom$path$path4read
path4write = env.custom$path$path4write
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
# sourcename = "f_objectname.read.checkEntity"; subpath=""; subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r"); suppressPackageStartupMessages(source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
# if (getwd() != path4write) warning("getwd() != path4write  == ") else cat(" getwd() == path4write == "); dput(path4write)  #----
```



#@@ START) source -----
### \$ subpath, sourcename = "default.template" ======
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
#| RUN ALL CHUNKS ABOVE: CTRL+ALT+SHIFT+P |#
# subpath=r"(rstudio-prefs\templates)"|>str_replace_all("\\\\","/")  # Using Raw Strings in R 4.0.0 and Later: The raw string literal, denoted by r"(...)", will not process \ as an escape character.
# # if(subpath!="") utils::browseURL(normalizePath(subpath))
# sourcename = "default.template"
# subpath.filename.source.r = paste0(subpath,ifelse(subpath=="","","/"),sourcename,".source.r")
# # % (source( file.path(env.custom$path$source_base,subpath.filename.source.r) )) ----
# (source( file.path(env.custom$path$source_base,subpath.filename.source.r) ))
```


# @@ START) log_file_availability ------------
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

library(tidyverse)

# Function to log file availability
log_file_availability <- function(path) {
  if (file.exists(path)) {
    cat(format.POSIXct(Sys.time(), usetz = TRUE), " - File exists\n")
  } else {
    cat(format.POSIXct(Sys.time(), usetz = TRUE), " - File does not exist\n")
  }
}

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
path4read = "data"
objectname = "fhs.index100"
paste0(path4read,"/",objectname,".rds")
log_file_availability(paste0(path4read,"/",objectname,".rds"))
try(assign( "DataSet", read_rds(paste0(path4read,"/",objectname,".rds")) ))
# error?
path.filename.ext = paste0(path4read,"/",objectname,".rds")
path.filename.ext
log_file_availability(path.filename.ext)
try(assign( "DataSet", read_rds(path.filename.ext) ))
```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

library(tidyverse)
path4read = "data"
objectname = "CohortGJ0910.BaselineJKGJ2085NoHx...01"
paste0(path4read,"/",objectname,".rds")
log_file_availability(paste0(path4read,"/",objectname,".rds"))
try(assign( "DataSet", read_rds(paste0(path4read,"/",objectname,".rds")) ))
# error?
path.filename.ext = paste0(path4read,"/",objectname,".rds")
path.filename.ext
log_file_availability(path.filename.ext)
try(assign( "DataSet", read_rds(path.filename.ext) ))

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

library(tidyverse)
path4read = "data"
objectname = "CohortGJ0910.BaselineJKGJ2085NoHx...01"
paste0(path4read,"/",objectname,".rds")
log_file_availability(paste0(path4read,"/",objectname,".rds"))
try(assign( objectname, read_rds(paste0(path4read,"/",objectname,".rds")) ))
# error?
path.filename.ext = paste0(path4read,"/",objectname,".rds")
path.filename.ext
log_file_availability(path.filename.ext)
try(assign( objectname, read_rds(path.filename.ext) ))

```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

# # path4read = file.path(env.custom$path$path0,"Rproject_KNHIS.CohortGJ0910 NoHx")
# # objectname = "CohortGJ0910.BaselineJKGJ2085NoHx.drop_na.MetS_NoMeds"
# rm("path4read")
# rm("objectname")
# library(tidyverse)
# path4read = "./data"
# objectname = "CohortGJ0910.BaselineJKGJ2085NoHx...01"
# paste0(path4read,"/",objectname,".rds")
# file.exists(paste0(path4read,"/",objectname,".rds"))
# assign( objectname, read_rds(normalizePath(paste0(path4read,"/",objectname,".rds"))) )
# # > paste0(path4read,"/",objectname,".rds")
# # [1] "./data/CohortGJ0910.BaselineJKGJ2085NoHx...01.rds"
# # > file.exists(paste0(path4read,"/",objectname,".rds"))
# # [1] FALSE
# # > assign( objectname, read_rds(normalizePath(paste0(path4read,"/",objectname,".rds"))) )
# # Warning: path[1]="./data/CohortGJ0910.BaselineJKGJ2085NoHx...01.rds": No such file or directoryWarning: cannot open file './data/CohortGJ0910.BaselineJKGJ2085NoHx...01.rds': No such file or directoryError in readRDS(con, refhook = refhook) : cannot open the connection
# 

```


# @@ START) read_rds_safely_with_logging ------------
```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

# Function to safely read an RDS file with logging
read_rds_safely_with_logging <- function(path, max_attempts = 9) {
  attempt <- 1
  while (!file.exists(path) && attempt <= max_attempts) {
    log_file_availability(path)  # Log file existence
    Sys.sleep(1)  # Wait for 1 second before retrying
    attempt <- attempt + 1
  }
  if (file.exists(path)) {
    log_file_availability(path)  # Final log if file exists
    read_rds(path)
  } else {
    stop("File not available after ", max_attempts, " attempts.")
  }
}
```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

path4read = "data"
objectname = "CohortGJ0910.BaselineJKGJ2085NoHx...01"
paste0(path4read,"/",objectname,".rds")
file.exists(paste0(path4read,"/",objectname,".rds"))
assign( objectname, read_rds_safely_with_logging(paste0(path4read,"/",objectname,".rds")) )


```


```{r, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```


# @@ END ------------
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++|#  
#|~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~|#  
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# @@ END ------------
```


```{r writeRDS-NoEcho, eval=TRUE, echo=FALSE, warning=TRUE, message=TRUE, results="markdown", collapse=TRUE, paged.print=FALSE}
#|________________________________________________________________________________|#  
#|%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%|#  
# # @ write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds"))) -----
# objectname = "AnalyticDataset200621"
# system.time(write_rds( get(objectname), paste0(objectname,".rds") ))
# system.time(write_rds( get(paste0(objectname,".NA",".rmAllNA",".fct")), paste0(objectname,".NA",".rmAllNA",".fct",".rds") ))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds"))))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname,".rds")), compress = "gz" ))
# # system.time(write_rds( get(objectname), file.path(path4write, paste0(objectname, ".rds", "")), compress = "xz", compression = 9 ))
# # system.time(openxlsx::write.xlsx(get(objectname), file=paste0(objectname,".xlsx"), asTable=TRUE, withFilter=TRUE))
# # openxlsx::openXL(paste0(objectname, ".xlsx"))
```


```{r createBackup, eval=TRUE, include=FALSE}
env.custom$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
# env.custom$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
```


```{r Render, eval=TRUE, include=FALSE}
# if (Sys.getenv("PARENT_RENDERING") != "YES") {
#     cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_format = "pdf_document") \n')
#     Sys.setenv(PARENT_RENDERING = "YES"); rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")
#     env.custom$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".pdf"), backup_to_path="-backup", timeFormat="%y%m%d_%H", overwrite=TRUE)
#     env.custom$env.internal$f_file_PDF.sumatra(rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".pdf"))
# }
cat(' Sys.setenv(PARENT_RENDERING = "YES"); "',rstudioapi::getSourceEditorContext()$path,'" |> rmarkdown::render(output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")',"\n", 
    ' env.custom$env.internal$f_filename.ext.createBackup(backup_from_path.filename.ext = "',rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".pdf"),'", backup_to_path="-backup", timeFormat="%y%m%d", overwrite=TRUE)',"\n", 
    ' env.custom$env.internal$f_file_PDF.sumatra("',rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".pdf"),'")',"\n", sep="")
```


```{r gitCheckout, eval=TRUE, include=FALSE}
cat(" * To revert to the last commited file, run the following terminal command:\n", 
    '"git checkout -- ',rstudioapi::getSourceEditorContext()$path,'" |> system(intern=TRUE)',"\n",
    '"git checkout -- ',rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"),'" |> system(intern=TRUE)',"\n", sep="")
```



