---
# https://forum.posit.co/t/when-to-use-yaml-vs-when-to-use-setup-code-chunk/56169/
title: "`r params$doc_title`"
author: "MHKim"
date: "`r Sys.setlocale('LC_ALL', 'en_US.utf8'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:  
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    code_folding: none
    df_print: tibble
    highlight: textmate
    fig_width: 10
    fig_height: 6
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: tibble
    code_folding: none
    highlight: textmate
    fig_width: 10
    fig_height: 6
  pdf_document: 
    toc: yes
    toc_depth: 6
    fig_width: 10
    fig_height: 6
    latex_engine: xelatex  # mainfont, sansfont, monofont, mathfont works only with xelatex and lualatex, but not pdflatex
    keep_tex: true
  word_document:
    toc: yes
    toc_depth: 6
    fig_width: 9
    fig_height: 6
# documentclass: scrartcl  # https://pandoc.org/MANUAL.html#variables-for-latex
# classoption: fontsize=9pt 
geometry: portrait, a3paper, margin=20mm # https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-options
# fontsize: 12pt
header-includes: 
  - \usepackage{fontspec}
  - \newcommand{\setfallbackfont}[4]{
      \IfFontExistsTF{#2}
        {#1{#2}}
        {\IfFontExistsTF{#3}
          {#1{#3}}
          {#1{#4}}}}
  # - \setfallbackfont{\setmainfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  # - \setfallbackfont{\setsansfont}{Roboto Condensed}{Noto Sans Condensed}{Arial Narrow}
  - \setfallbackfont{\setmainfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setsansfont}{Roboto}{Noto Sans}{Arial}
  - \setfallbackfont{\setmonofont}{Cascadia Code SemiBold}{Cascadia Code}{Fira Code}
  - \usepackage[hangul]{kotex}
  # - \setfallbackfont{\setmainhangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setsanshangulfont}{NanumGothic}{HCR Dotum LVT}{Malgun Gothic}
  # - \setfallbackfont{\setmonohangulfont}{D2Coding}{NanumGothicCoding}{NanumGothic}
params:
  doc_title: !r basename(rstudioapi::getSourceEditorContext()$path)
# https://stackoverflow.com/questions/55751815/r-markdown-difference-between-parameters-and-variables
# ?rmarkdown::html_document
---
<!-- https://stackoverflow.com/questions/28480625/r-knitr-markown-setting-html-page-width -->
<style type="text/css">
.main-content, .toc {max-width: 785px; margin: 0 auto; font-size: 1rem;} /* A4: 21cm x 29.7cm = 8.27in x 11.69in; 8.27in x 96px/in ≈ 793px */
html { font-size: 12px; }
body { font-size: 12px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; }
h1.title { font-size: 28px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 14px; margin-bottom: 0; color: Navy; }
h1 { font-size: 24px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 12px; margin-bottom: 0; color: Navy; }
h2 { font-size: 21px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 11px; margin-bottom: 0; color: Navy; }
h3 { font-size: 18px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 9px; margin-bottom: 0; color: Navy; }
h4 { font-size: 16px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 8px; margin-bottom: 0; color: Navy; }
h5 { font-size: 14px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 7px; margin-bottom: 0; color: Navy; }
h6 { font-size: 12px; font-family: 'Roboto Serif', 'Noto Serif', 'Source Serif 4', serif; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: Navy; }
table, td, th, figure, figcaption { font-size: 10px; font-family: 'Roboto Condensed', 'Noto Sans Condensed', 'Open Sans Condensed', 'Source Sans 3', 'Arial Narrow', Helvetica, sans-serif; line-height: 1.1; margin-top: 5px; margin-bottom: 0; }
code { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
pre { font-size: 11px; font-family: 'Cascadia Code SemiBold', 'Cascadia Code', 'Fira Code', Consolas, 'Source Code Pro', monospace; line-height: 1.1; margin-top: 6px; margin-bottom: 0; color: DimGray; background-color: Snow; }
</style>
  
<!-- font-size: 0.9em; /* 90% of inherited font size */ -->
  
<!-- Body text (body): The default font size is typically 16 pixels. -->
<!-- Paragraphs (p): Inherit the body's font size, so also typically 16 pixels. -->
<!-- List items (li): Inherit the body's font size, generally 16 pixels. -->
<!-- Headings (h1 to h6): The default sizes decrease with each level. For example: -->
<!-- h1: Typically around 32 pixels. -->
<!-- h2: Often around 24 pixels. -->
<!-- h3: Commonly around 18.72 pixels. -->
<!-- h4: Usually about 16 pixels. -->
<!-- h5: Generally around 13.28 pixels. -->
<!-- h6: Often about 10.72 pixels. -->
<!-- Blockquotes (blockquote): Usually inherit the body's font size, around 16 pixels. -->
<!-- Tables (table), table cells (td, th): Typically inherit the body's font size, so around 16 pixels. -->
<!-- Figures (figure) and figure captions (figcaption): Generally inherit the body's font size, so about 16 pixels. -->
<!-- 1: Approximately 8 pixels. -->
<!-- 2: Approximately 10 pixels. -->
<!-- 3: Approximately 12 pixels (this was often considered the default size). -->
<!-- 4: Approximately 14 pixels. -->
<!-- 5: Approximately 18 pixels. -->
<!-- 6: Approximately 24 pixels. -->
# __________|------  
<!-- {r Rstudio-RMarkDown-Shortcuts, eval=FALSE, include=FALSE} -->
<!-- ##### Rstudio RMarkDown Shortcuts -->
<!-- https://support.posit.co/hc/en-us/articles/200711853-Keyboard-Shortcuts-in-the-RStudio-IDE   -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-shortcuts.html   -->
<!-- Insert R chunk	Ctrl+Alt+I	Command+Option+I   -->
<!-- Preview HTML	Ctrl+Shift+K	Command+Shift+K   -->
<!-- Run all chunks above	Ctrl+Alt+P	Command+Option+P   -->
<!-- Run current chunk	Ctrl+Alt+C	Command+Option+C   -->
<!-- Run current chunk	Ctrl+Shift+Enter	Command+Shift+Enter   -->
<!-- Run next chunk	Ctrl+Alt+N	Command+Option+N   -->
<!-- Run all chunks	Ctrl+Alt+R	Command+Option+R   -->
<!-- Go to next chunk/title	Ctrl+PgDown	Command+PgDown   -->
<!-- Go to previous chunk/title	Ctrl+PgUp	Command+PgUp   -->
<!-- Show/hide document outline	Ctrl+Shift+O	Command+Shift+O   -->
<!-- F7 spell-check your document.   -->
<!-- Restart the R session   Ctrl + Alt + F10 (or Command + Option + F10 on macOS).   -->
<!--    -->
<!-- *** Caution: @ # \$ \% * \\ ***  -->

  
```{r setup, echo=FALSE, results="hide"}
## Cf) {r setup, eval=TRUE, include=FALSE}
if(Sys.info()["sysname"] == "Windows") Sys.setlocale("LC_ALL", "en_US.UTF-8")  # Note that setting category "LC_ALL" sets only categories "LC_COLLATE", "LC_CTYPE", "LC_MONETARY" and "LC_TIME".
# Sys.setlocale("LC_MESSAGES", "en_US.utf8")  # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.  # LC_MESSAGES does not exist in Windows
Sys.setenv(LANGUAGE="en_US");  # Sys.getenv("LANGUAGE");    # Note that the LANGUAGE environment variable has precedence over "LC_MESSAGES" in selecting the language for message translation on most R platforms.
# str(knitr::opts_chunk$get())
# cat(deparse(knitr::opts_chunk$get(), width.cutoff=120), "  \n", sep="")
# list(eval=TRUE, echo=TRUE, results = "markup", tidy = FALSE, tidy.opts = NULL, collapse = FALSE, prompt = FALSE, comment = "##",     highlight = TRUE, size = "normalsize", background = "#F7F7F7", strip.white = structure(TRUE, class = "AsIs"), cache = FALSE,     cache.path = "cache/", cache.vars = NULL, cache.lazy = TRUE, dependson = NULL, autodep = FALSE, cache.rebuild = FALSE,     fig.keep = "high", fig.show = "asis", fig.align = "default", fig.path = "figure/", dev = NULL, dev.args = NULL, dpi = 72,     fig.ext = NULL, fig.width=7, fig.height=7, fig.env = "figure", fig.cap = NULL, fig.scap = NULL, fig.lp = "fig:",     fig.subcap = NULL, fig.pos = "", out.width=NULL, out.height=NULL, out.extra = NULL, fig.retina = 1, external = TRUE,     sanitize = FALSE, interval = 1, aniopts = "controls,loop", warning = TRUE, error = TRUE, message = TRUE, render = NULL,     ref.label = NULL, child = NULL, engine = "R", split = FALSE, include = TRUE, purl = TRUE)
knitr::opts_chunk$set(
    eval=TRUE, echo=FALSE, results="markup", collapse=TRUE, # In Rstudio Notebook Source Pane & nb.HTML, results="hold" does not work
    comment="#", fig.width=10, fig.height=6, # In Rstudio Notebook Source Pane & nb.HTML, comment="##" does not work?
    warning=TRUE, message=TRUE, include=TRUE, 
    error=FALSE,  # error=TRUE: show the errors without stopping R; error=FALSE: stop on error
    tidy.opts=list(width.cutoff=120), tidy=FALSE, 
    R.options = list(width=120), paged.print=FALSE
) 
# knitr::opts_chunk$set(message=TRUE) & {r, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# knitr::opts_chunk$set(message=FALSE) & {r, message=TRUE, results="hide"} -> message shown in Rstudio Notebook Source Pane & knitted HTML, but not in Preview nb.HTML?!
# *** results="hide": results shown only on Rstudio Notebook Source Pane, but not in nb.HTML nor knitted HTML
knitr::opts_knit$set(global.par = TRUE)


## Cf) {r loadPackages-NoEchoHideResults, echo=FALSE, results="hide"}
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/default.R
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/rstudio-prefs/templates/templates-00env1.minimum.Rmd
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# cmd /C C:/PROGRA~2/MICROS~1/Edge/APPLIC~1/msedge_proxy.exe --app=https://github.com/mkim0710/tidystat/blob/master/.Rprofile    
#| ------------------------- < To be covered at .Rprofile > --------------------- |#  
if(!exists("env1", envir=.GlobalEnv)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
if(!".Rprofile" %in% names(.GlobalEnv$env1$source)) {  message('> source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")')  ;  source("https://raw.githubusercontent.com/mkim0710/tidystat/master/.Rprofile")  ;  .First()  }  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
env1$info$options.width = getOption("width"); cat('\tgetOption("width") == ', env1$info$options.width, "  \n", sep="")
#   
## Cf) {r env1-Info-NoEchoHideResults, echo=FALSE, results="hide"}
# https://yihui.org/knitr/options/#package-options
env1$info$info_software_versions = env1$env.internal.attach$get_software_versions(library_names = c("tidyverse", "dplyr", "ggplot2", "purrr", "stringr", "stats","survival"))
# str(env1$info$info_software_versions)


###### env1\$info\$DocumentTitle1 ----  
# ```{r env1-DocumentTitle1-NoEchoHideResults, echo=FALSE, results="hide"}
env1$info$DocumentTitle0 = paste0("00env1.minimum","-",basename(getwd()))
env1$info$DocumentTitle1 = paste0(env1$info$DocumentTitle0,"@", ifelse(grepl("MacBook-Pro", Sys.info()["nodename"]), "MBP", Sys.info()["nodename"]))
cat(env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"), "\n", 
    env1$info$DocumentTitle0,"-",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-dev",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    env1$info$DocumentTitle0,"-clean",format(Sys.time(),"%y%m%d"),".Rmd", "\n", 
    sep="")
```
  
  
```{r env1-Path-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
###### env1\$path ----  
# cat(" getwd() == "); dput(getwd())  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
### env1\$path\$LastSourceEditorContext.path_FileNameExt ====  
# *** Caution) In Rstudio Notebook, the path of the running Rmd file is set as the working directory~!!!
# .tmp$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) not a relative path~!  
# env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA) |> str_replace(fixed(env1$path$path1|>normalizePath(winslash="/",mustWork=NA)), "") |> str_replace("^/", "")
env1$path$LastSourceEditorContext.path_FileNameExt = rstudioapi::getSourceEditorContext()$path |> normalizePath(winslash="/",mustWork=NA)    # Caution) Not using a relative path~!
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# env1$path$project_base = "Rproject_HEALS0215"
# env1$path$data_suffix = "_01"
# # env1$path$data_suffix = ""
# env1$path$project_suffix = "GJ3"
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# env1$path$.path4read = file.path(env1$path$path0, paste0(env1$path$project_base, env1$path$data_suffix))
# env1$path$.path4write = file.path(env1$path$.path4read, paste0(env1$path$project_base, env1$path$data_suffix, env1$path$project_suffix))
env1$path$.path4read = ifelse(is.na(env1$path$path1), getwd(), env1$path$path1)
env1$path$.path4write = getwd()
.path4read  = env1$path$.path4read
.path4write = env1$path$.path4write
# cat(" > str(env1$path)\n"); str(env1$path, max.level = 1, give.attr = F)  

## @ env1 |> as.list() |> str(max.level = 2, give.attr = FALSE) ----  
"ls(all.names = TRUE, envir = .GlobalEnv) |> set_names() |> map(get) |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
".tmp |> str(max.level = 1, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
"env1 |> as.list() |> env1$f$f_list.str_by_element(max.level = 2, give.attr = FALSE)" |> env1$f$f_CodeText.ECHO(EXECUTE = TRUE, deparse_cat = FALSE, LinePrefix4CodeText = "> ", LinePrefix4Output = "")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
# .FileName.source.r = "f_DSN.Search.read.checkEntity" |> paste0(".source.r"); .RelativeSubPath=r"()"|>str_replace_all("\\\\","/"); env1$f$f_sourcePath.execute_if_not_sourced(.RelativeSubPath_FileName.source.r = file.path(.RelativeSubPath, .FileName.source.r))
# if (getwd() != .path4write) warning("getwd() != .path4write  == ") else cat(" getwd() == .path4write == "); dput(.path4write)  
```
  
  
# __________|------  
# @@ Rdev/00_base_program/f_vecNamed.swap.dev.Rmd  
# @@ Rdev/10_import_clean_datatype/11_metadata/f_chrNameValuePairs2vector.dev.Rmd  
# @@ Rdev/10_import_clean_datatype/16_categorical_labelled/f_CodeBook_DS.lbl.dev.Rmd  
  
# __________|------  
# @@ START) dev ----  
```{r env0-NoEchoNoResults, echo=FALSE, results="hide"}
env0 = env1
```

## \% eval(parse(text = .CodeText)) ----  

### \% "ValueA=LabelA, ValueB=LabelB" |> ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
# i.ValueOptions = "ValueA=LabelA, ValueB=LabelB"
# .CodeText = i.ValueOptions %>% {paste0("c(",.,")")}
# eval(parse(text = .CodeText)) %>% dput
```


### \% "1=남자, 2=여자" |> ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
# MetaData$tblVarName$tblVarName.suffix %>% filter(VarName.suffix == "SEX") %>% pull(ValueOptions) %>% as.character %>% dput
# i.ValueOptions = "1=남자, 2=여자"
# .CodeText = i.ValueOptions %>% {paste0("c(",.,")")}
# eval(parse(text = .CodeText)) %>% dput
```



### \% "ValueA=LabelA, ValueB=LabelB" |> ----  
#### https://chatgpt.com/c/670fd3f1-de80-800e-bfdc-f379288fc625

##### \% |> swap_named_vector() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Function to swap names and values in the named vector
swap_named_vector <- function(named_vector) {
  swapped_vector <- setNames(names(named_vector), named_vector)
  return(swapped_vector)
}

# Example usage
named_vector = c(LabelA = "ValueA", LabelB = "ValueB")
named_vector
dput(named_vector)
swapped_vector <- swap_named_vector(named_vector)
print(swapped_vector)
dput(swapped_vector)
```

##### \% |> string_to_named_vector() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}

# Function to convert ValueOptions string to a named vector with customizable separators
string_to_named_vector <- function(value_options, pair_sep = ",", value_label_sep = "=") {
  
  # Step 1: Split the string into individual pairs using pair_sep (handling whitespaces)
  value_label_pairs <- str_split(value_options, paste0("\\s*", pair_sep, "\\s*")) |> unlist()
  
  # Step 2: Separate each pair into values and labels using value_label_sep (handling whitespaces)
  value_label_list <- map(value_label_pairs, ~ str_split(.x, paste0("\\s*", value_label_sep, "\\s*")) |> unlist())
  
  # Step 3: Create the named vector where Value is the name and Label is the value
  named_vector <- setNames(map_chr(value_label_list, 2), map_chr(value_label_list, 1))
  
  return(named_vector)
}

# Example usage with default separators
value_options <- "ValueA = LabelA, ValueB = LabelB"
named_vector <- string_to_named_vector(value_options)
print(named_vector)

# Example usage with custom separators
value_options_custom <- "ValueA:LabelA | ValueB:LabelB"
named_vector_custom <- string_to_named_vector(value_options_custom, pair_sep = "\\|", value_label_sep = ":")
print(named_vector_custom)

```






### \% "ValueA=LabelA, ValueB=LabelB" |> ----  
#### https://gemini.google.com/app/639552d667363004
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}

# Example ValueOptions string
value_options <- "ValueA=LabelA, ValueB=LabelB"

str_split(value_options, ", ") %>% 
  unlist() |> str(max.level = 2, give.attr = TRUE)

str_split(value_options, ", ") %>% 
  unlist() %>% 
  str_split("=") |> str(max.level = 2, give.attr = TRUE)

str_split(value_options, ", ") %>% 
  unlist() %>% 
  str_split("=") %>% 
  map(~ set_names(.x[1], .x[2])) |> str(max.level = 2, give.attr = TRUE)

# Create the named vector using tidyverse functions
named_vector <- str_split(value_options, ", ") %>% 
  unlist() %>% 
  str_split("=") %>% 
  map(~ set_names(.x[1], .x[2])) %>% 
  unlist()

# Print the named vector
print(named_vector)

# Expected output:
# LabelA LabelB 
#    "ValueA"    "ValueB"
```


##### \% |> swap_names_values() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}

# Function to swap names and values in a named vector
swap_names_values <- function(named_vector) {
  set_names(names(named_vector), named_vector)
}
# Example usage
named_vector = c(LabelA = "ValueA", LabelB = "ValueB")
named_vector
dput(named_vector)
swapped_vector <- swap_names_values(named_vector)
print(swapped_vector)
dput(swapped_vector)
```




##### \% |> string_to_named_vector() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}

# Function to convert ValueOptions string to a named vector with swapped names and values
string_to_named_vector <- function(value_options) {
  str_split(value_options, ", ") %>% 
    unlist() %>% 
    str_split("=") %>% 
    map(~ set_names(c(.x[2]), .x[1])) %>%  # Swap here directly
    unlist()
}

# Example usage
value_options <- "ValueA=LabelA, ValueB=LabelB"
value_options

# Convert string to named vector
named_vector <- string_to_named_vector(value_options)
print(named_vector)
dput(named_vector)
# Expected output:
# ValueA ValueB 
# "LabelA" "LabelB" 

```


##### \% |> string_to_named_vector() ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
.packagename = "tidyverse"; if (!paste0("package:",.packagename) %in% search()) {library(.packagename, character.only = TRUE)}

# Function to convert ValueOptions string to a named vector with swapped names and values
string_to_named_vector <- function(value_options, 
                                    pair_separator = ",", 
                                    value_label_separator = "=") {
  
  # Split by pair separator, allowing for variable whitespace
  pairs <- str_split(value_options, paste0("\\s*", pair_separator, "\\s*")) %>% 
    unlist()
  
  # Split by value-label separator, allowing for variable whitespace
  split_pairs <- str_split(pairs, paste0("\\s*", value_label_separator, "\\s*"))
  
  # Create named vector, swapping values and labels
  map(split_pairs, ~ set_names(c(.x[2]), .x[1])) %>% 
    unlist()
}

# Example usage with different separators and whitespace
value_options1 <- "ValueA = LabelA, ValueB=LabelB"
value_options2 <- "ValueA - LabelA;  ValueB-LabelB"

# Convert strings to named vectors
named_vector1 <- string_to_named_vector(value_options1)
named_vector2 <- string_to_named_vector(value_options2, pair_separator = ";", value_label_separator = "-")

# Print the named vectors
print(named_vector1)
dput(named_vector1)
# Expected output:
# ValueA ValueB 
# "LabelA" "LabelB" 

print(named_vector2)
dput(named_vector2)
# Expected output:
# ValueA ValueB 
# "LabelA" "LabelB"
```






  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```
  
  
# __________|------  
# @@ START) my dev ----  

## \% chrNameValuePairs |> str_split(NameValuePair_separator) ----  
## \% vec.NameValuePair |> str_split(Name_Value_separator) ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
NameValuePair_separator = ","
Name_Value_separator = "="
chrNameValuePairs <- "ValueA = LabelA, ValueB = LabelB"

chrNameValuePairs %>% str_split(paste0("\\s*", NameValuePair_separator, "\\s*")) |> str(max.level = 2, give.attr = TRUE)
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
chrNameValuePairs %>% str_split(paste0("\\s*", NameValuePair_separator, "\\s*")) |> unlist() %>% str  # ***

# Step 1: Split the string into individual pairs using NameValuePair_separator (handling whitespaces)
vec.NameValuePair <- chrNameValuePairs %>% str_split(paste0("\\s*", NameValuePair_separator, "\\s*")) |> unlist()

cat("    ________________________________________________________________________    \n")
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
vec.NameValuePair %>% map(~ .x %>% str_split(paste0("\\s*", Name_Value_separator, "\\s*"))) |> str(max.level = 2, give.attr = TRUE)
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
vec.NameValuePair %>% map(~ .x %>% str_split(paste0("\\s*", Name_Value_separator, "\\s*")) |> unlist()) |> str(max.level = 2, give.attr = TRUE)
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
vec.NameValuePair %>% str_split(paste0("\\s*", Name_Value_separator, "\\s*")) %>% str  # ***

# Step 2: Separate each pair into values and labels using Name_Value_separator (handling whitespaces)
list.vec.Name_Value <- vec.NameValuePair %>% str_split(paste0("\\s*", Name_Value_separator, "\\s*"))

cat("    ________________________________________________________________________    \n")
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
list.vec.Name_Value %>% map_chr(1) %>% dput
list.vec.Name_Value %>% map_chr(2) %>% dput
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
list.vec.Name_Value %>% {setNames(map_chr(., 2), map_chr(., 1))} %>% dput
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
list.vec.Name_Value %>% map(~ set_names(c(.x[2]), .x[1])) %>% dput
list.vec.Name_Value %>% map(~ set_names(c(.x[2]), .x[1])) %>% unlist %>% dput  # ***
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
list.vec.Name_Value %>% map_chr(~ set_names(c(.x[2]), .x[1])) %>% dput

cat("    ________________________________________________________________________    \n")
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
# Step 3: Create the named vector where Value is the name and Label is the value
# named_vector <- list.vec.Name_Value %>% {setNames(map_chr(., 2), map_chr(., 1))}
named_vector <- list.vec.Name_Value %>% map(~ set_names(c(.x[2]), .x[1])) %>% unlist
named_vector %>% dput
```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```  
  
  
# __________|------  
# @@ START) function ----  
## \% |> f_vecNamed.swap()  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)
# Function to swap names and values in the named vector
f_vecNamed.swap <- function(vecNamed) {
    names(vecNamed) |> setNames(vecNamed)
}

# Example usage
named_vector = c(LabelA = "ValueA", LabelB = "ValueB")
named_vector
dput(named_vector)
swapped_vector <- f_vecNamed.swap(named_vector)
print(swapped_vector)
dput(swapped_vector)
```


## \% |> f_chrNameValuePairs2vector() ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
## :: f_chrNameValuePairs2vector =  ----  
# https://github.com/mkim0710/tidystat/blob/master/Rdev/10_import_clean_datatype/11_metadata/f_chrNameValuePairs2vector.dev.Rmd
.tmp$objectname = "f_chrNameValuePairs2vector"
.tmp$object = function(chrNameValuePairs, NameValuePair_separator = ",", Name_Value_separator = "=", vecNamed.swap = FALSE) {
    vec.NameValuePair = chrNameValuePairs %>% str_split(paste0("\\s*", NameValuePair_separator, "\\s*")) |> unlist() 
    list.vec.Name_Value = vec.NameValuePair %>% str_split(paste0("\\s*", Name_Value_separator, "\\s*"))
    vecNamed = list.vec.Name_Value %>% map(~ set_names(c(.x[2]), .x[1])) |> unlist()
    if (vecNamed.swap) vecNamed = names(vecNamed) |> setNames(vecNamed)
    return(vecNamed)    
}
#### \% |> f_function.load2env.internal(.tmp$objectname, env1_subenv_name) ---
.tmp$env1_subenv_name = "f"; env1$env.internal$f_function.load2env.internal(function_object = .tmp$object, function_name = .tmp$objectname, env1_subenv_name = .tmp$env1_subenv_name, show_packageStartupMessage = TRUE, RELOAD_FUNCTION = isTRUE(getOption("RELOAD_FUNCTION"))||isTRUE(getOption("DEVMODE")), runLoadedFunction = FALSE)

##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
f_chrNameValuePairs2vector = function(chrNameValuePairs, NameValuePair_separator = ",", Name_Value_separator = "=", vecNamed.swap = FALSE) {
    vec.NameValuePair = chrNameValuePairs %>% str_split(paste0("\\s*", NameValuePair_separator, "\\s*")) |> unlist() 
    list.vec.Name_Value = vec.NameValuePair %>% str_split(paste0("\\s*", Name_Value_separator, "\\s*"))
    vecNamed = list.vec.Name_Value %>% map(~ set_names(c(.x[2]), .x[1])) |> unlist()
    if (vecNamed.swap) vecNamed = names(vecNamed) |> setNames(vecNamed)
    return(vecNamed)    
}

```
  
  
### \% "ValueA=LabelA, ValueB=LabelB" |> ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
"ValueA=LabelA, ValueB=LabelB" |> env1$f$f_chrNameValuePairs2vector() %>% dput
"ValueA=LabelA, ValueB=LabelB" |> env1$f$f_chrNameValuePairs2vector(vecNamed.swap = TRUE) %>% dput

```

  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)

```
  
  
###### \% |> () ----  
```{r, echo=FALSE, results="markup", collapse=TRUE, paged.print=FALSE, comment="", R.options=list(width=120)}
options(width=120)
cat("    ________________________________________________________________________    \n")
```
  
  
  
# __________|------  
# @@ END ----  
```{r END-NoEvalNoEchoNoMsgNoResults, eval=FALSE, echo=FALSE, warning=TRUE, message=NA, results="hide", collapse=TRUE, paged.print=FALSE}
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++  
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~  
##________________________________________________________________________________  
##%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
# @@ END ----  
cat("    ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::    \n")
cat("    [][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][][]    \n")
cat("    {}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}{}    \n")
cat("    ()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()()    \n")
cat("    <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>    \n")
cat("    HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH    \n")
cat("    OOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO    \n")
cat("    XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX    \n")
cat("    VVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVVV    \n")
cat("    WWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW    \n")
cat("    -|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|    \n")
cat("    ________________________________________________________________________    \n")
cat("    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    \n")
cat("    ************************************************************************    \n")
cat("    ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++    \n")
cat("    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~    \n")
```
  
  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
###### ECHO \% |> () ----  
```{r, echo=TRUE, results="markup", collapse=TRUE, paged.print=FALSE, comment="#", R.options=list(width=120)}
options(width=120)

```

  
  
```{r createBACKUP, eval=TRUE, include=FALSE}
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    # if (Sys.info()["sysname"] == "Windows") {
        env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".Rmd"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
        # env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = rstudioapi::getSourceEditorContext()$path|>str_replace("\\.([[:alnum:]]+)$",".nb.html"), .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
    # }
}
```
  
  
```{r Render-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$path$LastSourceEditorContext.path_FileName.pdf = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".pdf") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
env1$path$LastSourceEditorContext.path_FileName.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".html") |> str_replace_all('[ <>()|\\:&;#?*\']', "-")
if (Sys.getenv("PARENT_RENDERING") != "YES") {
    if (Sys.info()["sysname"] == "Windows") {
        .tlmgr_installed_packages <- system2("tlmgr", args = c("info", "--list", "--only-installed"), stdout = TRUE)
        for (.font_name in c("roboto", "cascadia-code")) if(.tlmgr_installed_packages |> str_subset(.font_name) |> length() == 0) tinytex::tlmgr_install(.font_name)

        cat('Starting: rstudioapi::getSourceEditorContext()$path |> rmarkdown::render(output_dir = ',deparse(dirname(env1$path$LastSourceEditorContext.path_FileNameExt)),', output_format = "pdf_document")  \n')
        Sys.setenv(PARENT_RENDERING = "YES"); env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {rmarkdown::render(input = .,output_dir = dirname(.), output_format = "pdf_document")}; Sys.setenv(PARENT_RENDERING = "NO")
        .path_file = env1$path$LastSourceEditorContext.path_FileName.pdf
        env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE)
        env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = .path_file, .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)
        try(env1$env.internal.attach$f_file_PDF.sumatra(.path_file))
    }
}
# env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "pdf_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_FileName.pdf; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = ',deparse(.path_file),', .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); if (Sys.info()["sysname"] == "Windows") { cat('  env1$env.internal.attach$f_file_PDF.sumatra(',deparse(.path_file),')  \n', sep="") } else { cat('  browseURL(',deparse(.path_file),')  \n', sep="") }
# cat("    ________________________________________________________________________    \n")
env1$path$LastSourceEditorContext.path_FileNameExt |> normalizePath(winslash="/",mustWork=NA) %>% {cat('  Sys.setenv(PARENT_RENDERING = "YES"); rmarkdown::render(input = ',deparse(.),', output_dir = ',deparse(dirname(.)),', output_format = "html_document"); Sys.setenv(PARENT_RENDERING = "NO")  \n', sep="")}; .path_file = env1$path$LastSourceEditorContext.path_FileName.html; env1$f$f_file.git_lfs_track_add_f(.path_file = .path_file, EXECUTE = FALSE); cat('  env1$env.internal.attach$f_FileNameExt.createBACKUP(BACKUP_from_path_FileNameExt = ',deparse(.path_file),', .BACKUP_to_path="-BACKUP", timeFormat="%y%m%d_%H", overwrite=TRUE)  \n', sep=""); cat('  env1$env.internal.attach$f_URL.browse_in_edge_app(',deparse(.path_file),')  \n', sep="")
```
  
  
```{r gitCheckout-NoEchoNoMsgNoResults, echo=FALSE, warning=TRUE, message=NA, results="hide"}
env1$source[[basename(rstudioapi::getSourceEditorContext()$path)]] = rstudioapi::getSourceEditorContext()$path
env1$path$LastSourceEditorContext.path_FileName.nb.html = env1$path$LastSourceEditorContext.path_FileNameExt |> str_replace("\\.([[:alnum:]]+)$",".nb.html")
if (Sys.info()["sysname"] == "Windows" && Sys.getenv("PARENT_RENDERING") != "YES") {  try(  paste0('ping -n 5 127.0.0.1 > nul & "C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE),'"') |> shell(wait=FALSE)  )  }  # else { browseURL(env1$path$LastSourceEditorContext.path_FileName.nb.html|>normalizePath(winslash="/",mustWork=TRUE)) }
# paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/blob/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
# paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt) %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') |> system(intern=TRUE)
paste0("https://github.com/mkim0710/",basename(getwd()),"/commits/main/",env1$path$LastSourceEditorContext.path_FileNameExt)  %>% paste0('"C:/Program Files (x86)/Microsoft/Edge/Application/msedge_proxy.exe" --app="',.,'"') %>% paste0("'",.,"' |> system(intern=TRUE)") |> cat("  \n", sep="")
cat("* To revert to the last commited file, run the following terminal command:  \n")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileNameExt) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
paste0( "git checkout -- ",shQuote(env1$path$LastSourceEditorContext.path_FileName.nb.html) ) |> deparse() |> cat(" |> system(intern=TRUE)  \n", sep="")
```
  
  
